### 2018-07-23 paper/ms.tex
init paper

% mnras_template.tex
%
% LaTeX template for creating an MNRAS paper
%
% v3.0 released 14 May 2015
% (version numbers match those of mnras.cls)
%
% Copyright (C) Royal Astronomical Society 2015
% Authors:
% Keith T. Smith (Royal Astronomical Society)

% Change log
%
% v3.0 May 2015
%    Renamed to match the new package name
%    Version number matches mnras.cls
%    A few minor tweaks to wording
% v1.0 September 2013
%    Beta testing only - never publicly released
%    First version: a simple (ish) template for creating an MNRAS paper

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Basic setup. Most papers should leave these options alone.
\documentclass[a4paper,fleqn,usenatbib]{mnras}

% MNRAS is set in Times font. If you don't have this installed (most LaTeX
% installations will be fine) or prefer the old Computer Modern fonts, comment
% out the following line
\usepackage{newtxtext,newtxmath}
% Depending on your LaTeX fonts installation, you might get better results with one of these:
%\usepackage{mathptmx}
%\usepackage{txfonts}

% Use vector fonts, so it zooms properly in on-screen viewing software
% Don't change these lines unless you know what you are doing
\usepackage[T1]{fontenc}
\usepackage{ae,aecompl}

%%%%% AUTHORS - PLACE YOUR OWN PACKAGES HERE %%%%%

% Only include extra packages if you really need them. Common packages are:
\usepackage{graphicx}	% Including figure files
\usepackage{amsmath}	% Advanced maths commands
\usepackage{amssymb}	% Extra maths symbols
\usepackage{xspace}
\usepackage{hyperref}

% added by DH
\newcommand{\numax}{\mbox{$\nu_{\rm max}$}\xspace}
\newcommand{\Dnu}{\mbox{$\Delta \nu$}\xspace}
\newcommand{\dnu}{\mbox{$\delta \nu$}\xspace}
\newcommand{\muHz}{\mbox{$\mu$Hz}\xspace}
\newcommand{\teff}{\mbox{$T_{\rm eff}$}\xspace}
\newcommand{\logg}{\mbox{$\log g$}\xspace}
\newcommand{\feh}{\mbox{$\rm{[Fe/H]}$}\xspace}
\newcommand{\msun}{\mbox{$\mathrm{M}_{\sun}$}\xspace}
\newcommand{\rsun}{\mbox{$\mathrm{R}_{\sun}$}\xspace}
\newcommand{\kepler}{\emph{Kepler}\xspace}
\newcommand{\hipparcos}{\emph{Hipparcos}\xspace}
\newcommand{\gaia}{\emph{Gaia}\xspace}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%%%%% AUTHORS - PLACE YOUR OWN COMMANDS HERE %%%%%

% Please keep new commands to a minimum, and use \newcommand not \def to avoid
% overwriting existing commands. Example:
%\newcommand{\pcm}{\,cm$^{-2}$}	% per cm-squared

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%%%%%%%%%%%%%%%%%%% TITLE PAGE %%%%%%%%%%%%%%%%%%%

% Title of the paper, and the short title which is used in the headers.
% Keep the title short and informative.
\title[The Kepler Smear Campaign]{The \kepler Smear Campaign I: An Asteroseismic Catalogue of Bright Red Giants}

% The list of authors, and the short list which is used in the headers.
% If you need two or more lines of authors, add an extra line using \newauthor
\author[B. J. S. Pope et al.]{Benjamin J. S. Pope,$^{1,2,3}$\thanks{E-mail: benjamin.pope@physics.ox.ac.uk}
Guy R. Davies $^{4,5}$,
Timothy R. White$^{5}$, et al
\\
% List of institutions
$^{1}$Center for Cosmology and Particle Physics, Department of Physics, New York University, 726 Broadway, New York, NY 10003, USA\\
$^{2}$NASA Sagan Fellow\\
$^{3}$Oxford Astrophysics, Denys Wilkinson Building, University of Oxford, OX1 3RH, Oxford, UK\\
$^{4}$School of Physics and Astronomy, University of Birmingham, Birmingham B15 2TT, UK\\
$^{5}$Stellar Astrophysics Centre, Department of Physics and Astronomy, Aarhus University, Ny Munkegade 120, DK-8000 Aarhus C, Denmark\\
}

% These dates will be filled out by the publisher
\date{Accepted XXX. Received YYY; in original form ZZZ}

% Enter the current year, for the copyright statements etc.
\pubyear{2017}

% Don't change these lines
\begin{document}
\label{firstpage}
\pagerange{\pageref{firstpage}--\pageref{lastpage}}
\maketitle

% Abstract of the paper
\begin{abstract}
Here we present the first data release of the \kepler Smear Campaign, using collateral `smear' data obtained by \kepler to reconstruct light curves of 101~stars too bright to have been otherwise observed. We describe the pipeline developed to extract and calibrate these light curves, and show that we attain photometric precision comparable to stars ordinarily more observed in the nominal \kepler mission. In this Paper, we focus in particular on a subset of these consisting of 60~red giants for which we detect solar-like oscillations. Using high-resolution spectroscopy from the Tillinghast Reflector Echelle Spectrograph (TRES) together with asteroseismic modelling, we constrain the masses and evolutionary states of these benchmark red giants. All source code, light curves, TRES spectra, and asteroseismic and stellar parameters are publicly available as a \kepler legacy sample.
\end{abstract}

% Select between one and six entries from the list of approved keywords.
% Don't make up new ones.
\begin{keywords}
asteroseismology -- techniques: photometric -- stars: variable: general
\end{keywords}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%%%%%%%%%%%%%%%%% BODY OF PAPER %%%%%%%%%%%%%%%%%%

\section{Introduction}
\label{intro}

The \kepler Space Telescope, operated by NASA, was launched in 2009 to obtain photometry of hundreds of thousands of stars in a field in Cygnus-Lyra, in order to detect a statistically-useful sample of transiting exoplanets \citep{2010Sci...327..977B}. It achieved this primary goal, showing that exoplanets are common around Sun-like stars \citep{2013ApJ...766...81F,2013PNAS..11019273P,2014ApJ...795...64F}, though with the failure of two reaction wheels, the mission was cut short and there remain substantial uncertainties on these estimates. \kepler was revived as a two-wheeled mission, K2, with its third axis balanced against solar radiation pressure. K2 is therefore constrained to point in the ecliptic plane, which it surveys in a succession of $\sim 80$~day Campaigns. In this paper, we will deal exclusively with data from the nominal \kepler mission before this change.

Beyond searching for planets, \kepler has revolutionized the field of asteroseismology \citep{2010PASP..122..131G}. It has yielded the first detection of gravity-mode period spacings in a red giant \citep{rggmodes}, enabling probes of interior rotation of red giants \citep{rggmoderotation} and distinguishing between hydrogen- and helium-burning cores \citep{rggmodehelium}. It has also permitted the determination of ages and fundamental parameters of main-sequence stars \citep{silvaages}, including planet-hosting stars \citep{huberplanetages,silvaplanetages}, revealing the most ancient known planetary system, dating back to the earliest stages of the galaxy \citep{ancientplanets}. By comparing asteroseismic stellar ages to stellar rotation periods, \citet{angusgyro} have shown that gyrochronology models cannot fit the data with a single relation, leading \citet{vansadersgyro} to suggest a qualitative change in dynamo mechanism as stars age through the main sequence.

A major outcome of the \kepler asteroseismology programme is a legacy sample of extremely well characterized stars which can serve as benchmarks for future work \citep{keplerlegacy1,keplerlegacy2}. As well as asteroseismology, by also using optical interferometry, it has been possible to determine fundamental parameters of main-sequence and giant stars with unprecedented precision \citet{huber12,thetacygwhite,white15}. Likewise by combining with spectroscopy, \citet{hawkinsapogee} have been able to produce a large sample of stars with precise elemental abundances by fitting spectroscopic data with \logg and \teff fixed to asteroseismically-determined values. It is necessary to calibrate such a study against benchmark stars with very precisely-determined parameters, which in practice means requires nearby bright stars that are amenable to very high signal-to-noise spectroscopy plus asteroseismology \citep{creeveybenchmark},  parallaxes \citep{hawkinsbenchmarks}, and/or interferometry \citep{casagrandebenchmark,creeveybenchmark2}.

Brighter \kepler stars are therefore ideal benchmark targets, as photometry can be most easily complemented by \hipparcos parallaxes, interferometric diameters, and high resolution spectroscopy.  
Unfortunately, the \kepler field was deliberately placed to minimize overall the number of saturated stars, so that only a dozen stars brighter than~6th~magnitude landed on silicon \citep{2010ApJ...713L..79K}. This was because stars brighter than $Kp \sim 11$ saturate the CCD detector, spilling electrons up and down their column on the CCD and rendering these pixels otherwise unusable. Furthermore, due to the limited availablility of bandwidth to download data from the satellite, only a fraction \textcolor{red}{What fraction?} of pixels on the \kepler detector are actually downloaded, these being allocated via a competitive proposal process. The result of these two target selection constraints is that photometry was obtained for only \textcolor{red}{a small number} of saturated stars in the \kepler field, while many bright targets were ignored.

\citet{orig_smear} noted that there is a way to obtain photometry of every target on-silicon in \kepler using a data channel normally used for calibration, even if active pixels were not allocated and downloaded. \kepler employs an inter-line transfer CCD as its detector, which successively shuffles each row of pixels down to the edges of the chip where they are ultimately read out. Because the \kepler camera lacks a shutter, the detector is exposed to light during the readout process, with the result that fluxes in each pixel are biased up by light collected from objects in the same column. This is a particularly serious issue for faint objects in the same detector column as brighter stars, and it is important to calibrate this at each readout stage. Six rows of blank `masked' pixels are allocated in each column to measure the smear bias; furthermore, six `virtual' rows are recorded at the end of the readout, with the result that twelve rows of pixels sample the smear bias in each column. \citet{orig_smear} realized that these encode the light curves of bright targets in a 1D projection of the star field. The masked and virtual smear registers each receive $\sim 1/1034$ of the incident flux in each column; if this is dominated by the light from a single star, the flux combining both smear registers is equivalent to that of a star $\sim 6.8$~times fainter.

In \citet{smear}, we demonstrated a method for extracting precise light curves of bright stars in \kepler and K2, and presented light curves of a small number of variable stars as examples to illustrate this method. In this Paper we present light curves of all unobserved or significantly under-observed stars brighter than $V=8$ in the \kepler field. This sample is biased towards red giants and hot stars, containing only a few FG dwarfs. We find no transiting planets, but detect $M$~new eclipsing binaries, and solar-like oscillations in $N$~red giants. We do not model hot stars or FG dwarfs in great detail, but provide some discussion and initial classification of interesting variability. For eclipsing binaries, we present the results of light-curve modelling to precisely determine their parameters. Finally, for the oscillating red giants, which constitute the bulk of the sample, we determine the asteroseismic parameters \numax and \Dnu, and therefore stellar masses and \logg measurements; and we and obtain high-resolution spectroscopy with the Tillinghast Reflector Echelle Spectrograph (TRES), from whose spectra we derive stellar parameters and elemental abundances constrained by asteroseismic parameters. We discuss the potential for these as benchmark stars for other stellar surveys, in particular \gaia.

%We have made all new data products and software discussed in this paper publicly available, and encourage interested readers to use these in their own research.

\section{Method}
\label{method}

\subsection{Photometry}
\label{photometry}

We selected as our sample all stars on-silicon in \kepler with $Kp<8$ which were unobserved for more than $10$ quarters \textcolor{red}{Tim: what was your cutoff in quarters for `underobserved' stars?}, including those stars which were entirely unobserved. A number of these lay just at the edge of a detector, with the result that in some cadences the centroid of the star did not lie on the chip; light curves from these targets were found to be of extremely low quality and all of these objects were discarded. After applying these criteria we obtained a list of \textcolor{red}{101} targets. Aside from the restriction on stars falling on the edge of a chip, the addition of these objects to conventionally-observed stars makes the \kepler survey magnitude-complete down to $Kp=8$.

In preparing light curves of the \kepler smear stars, we follow the methods described in \citet{smear}, with some improvements. We select using RA and Dec values from the \kepler Input Catalog (KIC) \citep{kic}, and query MAST to find the corresponding mean pixel position for a given \kepler quarter. We measure the centroid of smear columns in the vicinity, and use these values to do raw aperture photometry. We find that the cosine-bell aperture used for raw photometry in \citet{smear} can in some light curves introduce position-dependent systematics and jumps. We instead in this work apply a super-Gaussian aperture, $A \propto \exp{\dfrac{-(x-x_0)}{w} ^ 4}$, where $x_0$ is the centroid and $w$ a width in pixels. The very flat top of this function helps avoid significant variation with position, while still smoothly rolling off at the edges to avoid discontinuous artefacts. We calculate this on a grid of $10\times$ subsampled points in time so that the sharply varying edge changes column weights smoothly as a function of centroid. We extract photometry using apertures with a range of widths $w \in\{1.5,~2,~3,~4,~5\}$ pixels.

From this raw photometry we subtract a background light curve, which corrects for time-varying global systematics. Whereas in \citet{smear} we then subtract a background estimate chosen manually, for this larger set of light curves, we now choose the lowest $25\%$ of pixels by median flux as being unlikely to be contaminated by stars, and take our background level to be the median of this at each time sample. To denoise this, we fit a Gaussian Process with a 30-day timescale squared exponential kernel using \textsc{george} \citep{hodlr}, and our final background light curve is taken to be the posterior mean of this GP.

The dominant source of residual systematic errors in nominal \kepler time series is a common-mode variation primarily due to thermal changes on board the spacecraft, an issue which is traditionally dealt with by identifying and fitting a linear combination of systematic modes \citep{pdc0,pdc1,pdc2,petigura}. We adopt the same approach here, using the \kepler Pre-search Data Conditioning (PDC) Cotrending Basis Vectors (CBVs) available from MAST, finding least-squares fits of  either the first~4 or~8 CBVs to each light curve. We note that this can subtract astrophysical signals on long timescales, such that we use and recommend 4~CBV light curves for stars with variability on timescales longer than $\sim 5$ days, but otherwise use the 8~CBV light curves. There is some room for improvement here by simultaneously modelling astrophysical and instrumental variations, but this is beyond the scope of this paper. In the following, we will use the light curves with the lowest 6.5~hr Combined Differential Photometric Precision (CDPP) \citep{cdpp} out of all apertures, as calculated with the \textsc{k2sc} implementation \citep{k2sc}. \textcolor{red}{This is primitive - how do we justify this? We only did it because we didn't have anything cleverer, but now we do. Should I redo this?}. 
\subsection{Asteroseismology}
\label{asteroseismology}

For all \textcolor{red}{N} red giants identified in this sample, we have attempted to extract the asteroseismic parameters \numax and $\langle \Dnu \rangle$. These constrain fundamental stellar parameters independently from spectroscopic or interferometric measurements:

\begin{equation}
\numax \propto \dfrac{g}{g_{\sun}} \cdot \dfrac{\teff}{\teff_{\sun}}^{\dfrac{1}{2}}
\end{equation}

and

\begin{equation}
\langle \Dnu \rangle \propto \sqrt{\langle \rho \rangle} = \sqrt{\dfrac{M}{\msun} (\dfrac{R}{\rsun})^{-3}}
\end{equation}

We follow the method of \citet{2016AN....337..774D}, obtaining a Lomb-Scargle periodogram of the smoothed time series according to the method of \citet{2011MNRAS.414L...6G}. We then conduct a Markov Chain Monte Carlo fit to this, applying the combined granulation and oscillation model of \citet{2014A&A...570A..41K}, consisting of two Harvey profiles for the granulation \citep{1985ESASP.235..199H}, a Gaussian envelope for the stellar oscillations, and a white noise background for instrumental noise. We find that the marginal posterior distribution for the Gaussian envelope is well-approximated by a single Gaussian, and take its median and standard deviation to be our estimates for \numax and its uncertainty.

To estimate \Dnu, we divide the power spectrum through by the granulation and noise models to obtain a signal-to-noise spectrum, and fit a sum of Lorentzians separated by mean large (\Dnu) and small (\dnu) separations to the part of this spectrum in the vicinity of \numax. In practice, for this dataset, \dnu is poorly constrained, but mean $\langle \Dnu \rangle$ is typically well-constrained and its posterior marginal distribution is well-represented by a single Gaussian as with \numax.

We obtain good estimates of these asteroseismic parameters for \textcolor{red}{35} targets. In the remainder of cases, we find that the very-low-frequency ($\lesssim 2\muHz$) oscillations are affected by filter artefacts from detrending, and we are not able to obtain good estimates for these stars. \textcolor{red}{Should we try with these?}

\subsection{Spectroscopy}
\label{spectroscopy}

For the whole red giant sample, we have obtained high-resolution spectroscopy with the Tillinghast Reflector Echelle Spectrograph (TRES) in order to constrain stellar parameters and elemental abundances. Operating with spectral resolving power $R=44 000$, we obtain signal-to-noise ratios of \textcolor{red}{something} per resolution element.

\section{Results}
\label{targets}

\subsection{Red Giants}
\label{rgs}

\subsection{Other Stars}
\label{other}

\section{Open Science}
\label{open}

We believe in open science, and have therefore made all substantive products of this research available to the interested reader. All code used to produce smear light curves is available under a GPL~v3 license at \url{https://github.com/benjaminpope/keplersmear}. All smear light curves, both including the red giant sample studied in detail in Section~\ref{rgs}, and other stars as discussed in Section~\ref{other}, can be downloaded from the Mikulski Archive for Space Telescopes (MAST) as a High-Level Science Product. TRES spectra are available from \textcolor{red}{somewhere}, and all asteroseismic parameters and derived stellar parameters for the red giants in Section~\ref{rgs} are provided in an online-only table as Supplementary Material to this paper.

\section{Conclusions}
\label{conclusions}

\section*{Acknowledgements}

This research made use of NASA's Astrophysics Data System; the SIMBAD database, operated at CDS, Strasbourg, France; the IPython package \citep{PER-GRA:2007}; SciPy \citep{jones_scipy_2001}; and Astropy, a community-developed core Python package for Astronomy \citep{2013A&A...558A..33A}. Some of the data presented in this paper were obtained from the Mikulski Archive for Space Telescopes (MAST). STScI is operated by the Association of Universities for Research in Astronomy, Inc., under NASA contract NAS5-26555. Support for MAST for non-HST data is provided by the NASA Office of Space Science via grant NNX13AC07G and by other grants and contracts. We acknowledge the support of the Group of Eight universities and the German Academic Exchange Service through the Go8 Australia-Germany Joint Research Co-operation Scheme.

B.P. acknowledges support from Balliol College and the Clarendon Fund. D.H. acknowledges support by the Australian Research Council's Discovery Projects funding scheme (project number DE140101364) and support by the NASA Grant NNX14AB92G issued through the \emph{Kepler} Participating Scientist Program.

BP acknowledges being on the traditional territory of the Lenape Nations and, today, recognize that Manhattan continues to be the home to many Algonkian peoples. We thank the Lenape peoples for allowing us to carry out this work on the Lenape original homelands at New York University. BP and TW would like to acknowledge the Gadigal people of the Eora Nation and the Norongerragal and Gweagal peoples of the Tharawal Nation as the traditional owners of the land at the University of Sydney and the Sutherland Shire on which some of this work was carried out, and pay their respects to their knowledge, and their elders past, present and future.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%%%%%%%%%%%%%%%%%%%% REFERENCES %%%%%%%%%%%%%%%%%%

% The best way to enter references is to use BibTeX:

\bibliographystyle{mnras}
\bibliography{ms} % if your bibtex file is called example.bib

% Alternatively you could enter them by hand, like this:
% This method is tedious and prone to error if you have lots of references

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%%%%%%%%%%%%%%%%% APPENDICES %%%%%%%%%%%%%%%%%%%%%

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

% Don't change these lines
\bsp	% typesetting comment
\label{lastpage}
\end{document}

% End of mnras_template.tex

### 2018-07-23 paper/ms.tex
updates
keith hawkins

@@
 % If you need two or more lines of authors, add an extra line using \newauthor
-\author[B. J. S. Pope et al.]{Benjamin J. S. Pope,$^{1,2,3}$\thanks{E-mail: benjamin.pope@physics.ox.ac.uk}
+\author[B. J. S. Pope et al.]{Benjamin J. S. Pope,$^{1,2,3}$\thanks{E-mail: benjamin.pope@nyu.edu}
 Guy R. Davies $^{4,5}$,
+Keith Hawkins $^{6,7}$
 Timothy R. White$^{5}$, et al
@@
 $^{5}$Stellar Astrophysics Centre, Department of Physics and Astronomy, Aarhus University, Ny Munkegade 120, DK-8000 Aarhus C, Denmark\\
+$^{6}$Department of Astronomy, The University of Texas at Austin, 2515 Speedway Boulevard, Austin, TX 78712, USA\\
+$^{7}$Department of Astronomy, Columbia University, 550 W 120th St, New York, NY 10027, USA
 }

### 2018-07-23 paper/ms.tex
affiliations, dan

--- 2018-07-23 paper/ms.tex
@@
 % If you need two or more lines of authors, add an extra line using \newauthor
-\author[B. J. S. Pope et al.]{Benjamin J. S. Pope,$^{1,2,3}$\thanks{E-mail: benjamin.pope@physics.ox.ac.uk}
-Guy R. Davies $^{4,5}$,
-Timothy R. White$^{5}$, et al
+\author[B. J. S. Pope et al.]{Benjamin J. S. Pope,$^{1,2,3}$\thanks{E-mail: benjamin.pope@nyu.edu}
+Guy R. Davies,$^{4,5}$
+Keith Hawkins,$^{6,7}$
+Timothy R. White,$^{5,8}$\\ 
+Daniel Huber,$^{9,10,11}$ et al
 \\
@@
 $^{5}$Stellar Astrophysics Centre, Department of Physics and Astronomy, Aarhus University, Ny Munkegade 120, DK-8000 Aarhus C, Denmark\\
+$^{6}$Department of Astronomy, The University of Texas at Austin, 2515 Speedway Boulevard, Austin, TX 78712, USA\\
+$^{7}$Department of Astronomy, Columbia University, 550 W 120th St, New York, NY 10027, USA\\
+$^{8}$Research School of Astronomy and Astrophysics, Mount Stromlo Observatory, The Australian National University, Canberra, ACT 2611, Australia\\
+$^{9}$Institute for Astronomy, University of Hawai‘i, 2680 Woodlawn Drive, Honolulu, HI 96822, USA\\
+$^{10}$Sydney Institute for Astronomy (SIfA), School of Physics, University of Sydney, NSW 2006, Australia\\
+$^{11}$SETI Institute, 189 Bernardo Avenue, Mountain View, CA 94043, USA
 }

### 2018-07-23 paper/ms.tex
typo

@@
 Keith Hawkins,$^{6,7}$
-Timothy R. White,$^{5,8}$\\ 
+Timothy R. White,$^{5,8}$\newauthor
 Daniel Huber,$^{9,10,11}$ et al
@@
 By comparing asteroseismic stellar ages to stellar rotation periods, \citet{angusgyro} have shown that gyrochronology models cannot fit the data with a single relation, leading \citet{vansadersgyro} to suggest a qualitative change in dynamo mechanism as stars age through the main sequence.
+\newpage
 
 A major outcome of the \kepler asteroseismology programme is a legacy sample of extremely well characterized stars which can serve as benchmarks for future work \citep{keplerlegacy1,keplerlegacy2}.
-As well as asteroseismology, by also using optical interferometry, it has been possible to determine fundamental parameters of main-sequence and giant stars with unprecedented precision \citet{huber12,thetacygwhite,white15}.
+As well as asteroseismology, by also using optical interferometry, it has been possible to determine fundamental parameters of main-sequence and giant stars with unprecedented precision \citep{huber12,thetacygwhite,white15}.
 Likewise by combining with spectroscopy, \citet{hawkinsapogee} have been able to produce a large sample of stars with precise elemental abundances by fitting spectroscopic data with \logg and \teff fixed to asteroseismically-determined values.

### 2018-07-24 paper/ms.tex
Add chontos
readme
stuff

@@
 
-% Title of the paper, and the short title which is used in the headers.
-% Keep the title short and informative.
 \title[The Kepler Smear Campaign]{The \kepler Smear Campaign I: An Asteroseismic Catalogue of Bright Red Giants}
 
-% The list of authors, and the short list which is used in the headers.
-% If you need two or more lines of authors, add an extra line using \newauthor
+% This author list is not final! If you think you should be in a different position please do not hesitate to say so.
 \author[B. J. S. Pope et al.]{Benjamin J. S. Pope,$^{1,2,3}$\thanks{E-mail: benjamin.pope@nyu.edu}
@@
 Timothy R. White,$^{5,8}$\newauthor
-Daniel Huber,$^{9,10,11}$ et al
+Daniel Huber,$^{9,10,11}$
+Ashley Chontos,$^{9}$
+Victor Silva Aguirre,$^{5}$
+Victoria Antoci,$^{5}$ et al
 \\
@@
 
-% Enter the current year, for the copyright statements etc.
-\pubyear{2017}
+\pubyear{2018}
 
@@
 
-%We have made all new data products and software discussed in this paper publicly available, and encourage interested readers to use these in their own research.
+We have made all new data products and software discussed in this paper publicly available, and encourage interested readers to use these in their own research.
 
@@
 
-\section*{Acknowledgements}
+\section*{Acknowledgements} % add your acknowledgements text here!
 
-This research made use of NASA's Astrophysics Data System; the SIMBAD database, operated at CDS, Strasbourg, France; the IPython package \citep{PER-GRA:2007}; SciPy \citep{jones_scipy_2001}; and Astropy, a community-developed core Python package for Astronomy \citep{2013A&A...558A..33A}.
-Some of the data presented in this paper were obtained from the Mikulski Archive for Space Telescopes (MAST).
-STScI is operated by the Association of Universities for Research in Astronomy, Inc., under NASA contract NAS5-26555.
-Support for MAST for non-HST data is provided by the NASA Office of Space Science via grant NNX13AC07G and by other grants and contracts.
-We acknowledge the support of the Group of Eight universities and the German Academic Exchange Service through the Go8 Australia-Germany Joint Research Co-operation Scheme.
-
+This work was performed in part under contract with the Jet Propulsion Laboratory (JPL) funded by NASA through the Sagan Fellowship Program executed by the NASA Exoplanet Science Institute.
 B.P.
@@
 BP and TW would like to acknowledge the Gadigal people of the Eora Nation and the Norongerragal and Gweagal peoples of the Tharawal Nation as the traditional owners of the land at the University of Sydney and the Sutherland Shire on which some of this work was carried out, and pay their respects to their knowledge, and their elders past, present and future.
+
+This research made use of NASA's Astrophysics Data System; the SIMBAD database, operated at CDS, Strasbourg, France; the IPython package \citep{PER-GRA:2007}; SciPy \citep{jones_scipy_2001}; and Astropy, a community-developed core Python package for Astronomy \citep{2013A&A...558A..33A}.
+Some of the data presented in this paper were obtained from the Mikulski Archive for Space Telescopes (MAST).
+STScI is operated by the Association of Universities for Research in Astronomy, Inc., under NASA contract NAS5-26555.
+Support for MAST for non-HST data is provided by the NASA Office of Space Science via grant NNX13AC07G and by other grants and contracts.
+We acknowledge the support of the Group of Eight universities and the German Academic Exchange Service through the Go8 Australia-Germany Joint Research Co-operation Scheme.
 

### 2018-07-24 paper/ms.tex
misc

@@
 Victor Silva Aguirre,$^{5}$
-Victoria Antoci,$^{5}$ et al
+Victoria Antoci,$^{5}$ and friends
 \\
@@
 B.P.
-acknowledges support from Balliol College and the Clarendon Fund.
+also acknowledges support from Balliol College and the Clarendon Fund.
 D.H.
@@
 
-BP acknowledges being on the traditional territory of the Lenape Nations and, today, recognize that Manhattan continues to be the home to many Algonkian peoples.
+BP acknowledges being on the traditional territory of the Lenape Nations and, today, we recognize that Manhattan continues to be the home to many Algonkian peoples.
 We thank the Lenape peoples for allowing us to carry out this work on the Lenape original homelands at New York University.

### 2018-07-24 paper/ms.tex
open science

@@
 We believe in open science, and have therefore made all substantive products of this research available to the interested reader.
-All code used to produce smear light curves is available under a GPL~v3 license at \url{https://github.com/benjaminpope/keplersmear}.
+All code used to produce smear light curves is available under a GPL~v3 license at \url{github.com/benjaminpope/keplersmear}.
 All smear light curves, both including the red giant sample studied in detail in Section~\ref{rgs}, and other stars as discussed in Section~\ref{other}, can be downloaded from the Mikulski Archive for Space Telescopes (MAST) as a High-Level Science Product.
 TRES spectra are available from \textcolor{red}{somewhere}, and all asteroseismic parameters and derived stellar parameters for the red giants in Section~\ref{rgs} are provided in an online-only table as Supplementary Material to this paper.
+
+All smear light curves in this paper, as well as the \LaTeX{} source code used to produce this document, can be found
+at \url{github.com/benjaminpope/smearcampaign}.
 
@@
 
-BP acknowledges being on the traditional territory of the Lenape Nations and, today, we recognize that Manhattan continues to be the home to many Algonkian peoples.
+BP acknowledges being on the traditional territory of the Lenape Nations and, today, we grecognize that Manhattan continues to be the home to many Algonkian peoples.
 We thank the Lenape peoples for allowing us to carry out this work on the Lenape original homelands at New York University.

### 2018-07-24 paper/ms.tex
van eylen

@@
 It has yielded the first detection of gravity-mode period spacings in a red giant \citep{rggmodes}, enabling probes of interior rotation of red giants \citep{rggmoderotation} and distinguishing between hydrogen- and helium-burning cores \citep{rggmodehelium}.
-It has also permitted the determination of ages and fundamental parameters of main-sequence stars \citep{silvaages}, including planet-hosting stars \citep{huberplanetages,silvaplanetages}, revealing the most ancient known planetary system, dating back to the earliest stages of the galaxy \citep{ancientplanets}.
+It has also permitted the determination of ages and fundamental parameters of main-sequence stars \citep{silvaages}, including planet-hosting stars \citep{huberplanetages,silvaplanetages,2018MNRAS.479.4786V}, revealing the most ancient known planetary system, dating back to the earliest stages of the galaxy \citep{ancientplanets}.
 By comparing asteroseismic stellar ages to stellar rotation periods, \citet{angusgyro} have shown that gyrochronology models cannot fit the data with a single relation, leading \citet{vansadersgyro} to suggest a qualitative change in dynamo mechanism as stars age through the main sequence.

### 2018-07-24 paper/ms.tex
spelling

@@
 In this Paper, we focus in particular on a subset of these consisting of 60~red giants for which we detect solar-like oscillations.
-Using high-resolution spectroscopy from the Tillinghast Reflector Echelle Spectrograph (TRES) together with asteroseismic modelling, we constrain the masses and evolutionary states of these benchmark red giants.
+Using high-resolution spectroscopy from the Tillinghast Reflector \'{E}chelle Spectrograph (TRES) together with asteroseismic modelling, we constrain the masses and evolutionary states of these benchmark red giants.
 All source code, light curves, TRES spectra, and asteroseismic and stellar parameters are publicly available as a \kepler legacy sample.
@@
 For eclipsing binaries, we present the results of light-curve modelling to precisely determine their parameters.
-Finally, for the oscillating red giants, which constitute the bulk of the sample, we determine the asteroseismic parameters \numax and \Dnu, and therefore stellar masses and \logg measurements; and we and obtain high-resolution spectroscopy with the Tillinghast Reflector Echelle Spectrograph (TRES), from whose spectra we derive stellar parameters and elemental abundances constrained by asteroseismic parameters.
+Finally, for the oscillating red giants, which constitute the bulk of the sample, we determine the asteroseismic parameters \numax and \Dnu, and therefore stellar masses and \logg measurements; and we and obtain high-resolution spectroscopy with the Tillinghast Reflector \'{E}chelle Spectrograph (TRES), from whose spectra we derive stellar parameters and elemental abundances constrained by asteroseismic parameters.
 We discuss the potential for these as benchmark stars for other stellar surveys, in particular \gaia.
@@
 
-For the whole red giant sample, we have obtained high-resolution spectroscopy with the Tillinghast Reflector Echelle Spectrograph (TRES) in order to constrain stellar parameters and elemental abundances.
+For the whole red giant sample, we have obtained high-resolution spectroscopy with the Tillinghast Reflector \'{E}chelle Spectrograph (TRES) in order to constrain stellar parameters and elemental abundances.
 Operating with spectral resolving power $R=44 000$, we obtain signal-to-noise ratios of \textcolor{red}{something} per resolution element.

### 2018-07-24 paper/ms.tex
jofre papers

@@
 It is necessary to calibrate such a study against benchmark stars with very precisely-determined parameters, which in practice means requires nearby bright stars that are amenable to very high signal-to-noise spectroscopy plus asteroseismology \citep{creeveybenchmark},  parallaxes \citep{hawkinsbenchmarks}, and/or interferometry \citep{casagrandebenchmark,creeveybenchmark2}.
+This is especially important in the context of the \gaia mission \citep{gaia}, which has recently put out its second data release of 1,692,919,135 sources, including 1,331,909,727 with parallaxes \citep{gaiadr2}.
+These data will form the basis of many large surveys and it is vital that they are calibrated correctly.
+To this end, 34~FGK stars have been chosen as \gaia-ESO benchmark stars for which metallicities \citep{gaiabenchmark1}, effective temperatures and surface gravities \citep{gaiabenchmark3}, and relative abundances of $\alpha$ and iron-peak elements \citep{gaiabenchmark4} have been determined.
+This has been accompanied by the release of high resolution spectra \citep{gaiabenchmark2} and formed the basis of extensions to lower metallicities \citep{gaiabenchmark5}, stellar twin studies \citep{gaiabenchmarktwins} and comparisons of stellar abundance determination pipelines \citep{gaiabenchmarkabundances}.
 

### 2018-07-24 paper/ms.tex
more structure

@@
 This sample is biased towards red giants and hot stars, containing only a few FG dwarfs.
-We find no transiting planets, but detect $M$~new eclipsing binaries, and solar-like oscillations in $N$~red giants.
+We find no transiting planets, but detect \textcolor{red}{$M$}~new eclipsing binaries, and solar-like oscillations in \textcolor{red}{$N$}~red giants.
 We do not model hot stars or FG dwarfs in great detail, but provide some discussion and initial classification of interesting variability.
@@
 \label{method}
+
+In this Section we will discuss the methods used for characterizing our new benchmark stars.
+We have obtained smear light curves for our sample of red giant stars with the \texttt{keplersmear} pipeline as described in Section~\ref{photometry}, performed asteroseismology on all of these to extract \numax and therefore \logg as described in Section~\ref{asteroseismology}, and combined these with TRES spectra to obtain chemical abundances as described in Section~\ref{spectroscopy}.
 
@@
 
+\section{Asteroseismology}
+\label{asteroseismology}
+
+\textcolor{red}{Guy - can you describe your pipeline here?}
+
 \subsection{Spectroscopy}
@@
 
-For the whole red giant sample, we have obtained high-resolution spectroscopy with the Tillinghast Reflector \'{E}chelle Spectrograph (TRES) in order to constrain stellar parameters and elemental abundances.
+For the whole red giant sample, we have obtained high-resolution spectroscopy with TRES in order to constrain stellar parameters and elemental abundances.
 Operating with spectral resolving power $R=44 000$, we obtain signal-to-noise ratios of \textcolor{red}{something} per resolution element.

### 2018-07-24 paper/ms.tex
stuff

@@
 Should I redo this?}.
+
 \subsection{Asteroseismology}
@@
 
-For all \textcolor{red}{N} red giants identified in this sample, we have attempted to extract the asteroseismic parameters \numax and $\langle \Dnu \rangle$.
+\textcolor{red}{Guy - can you describe your pipeline here?}
+
+For all \textcolor{red}{N} red giants identified in this sample, we have attempted to extract the asteroseismic parameters \numax and $\langle \Dnu \rangle$ \citep{KB95,2013ARA&A..51..353C}.
 These constrain fundamental stellar parameters independently from spectroscopic or interferometric measurements:
@@
 \begin{equation}
+\label{scaling}
 \numax \propto \dfrac{g}{g_{\sun}} \cdot \dfrac{\teff}{\teff_{\sun}}^{\dfrac{1}{2}}
@@
 
-\section{Asteroseismology}
-\label{asteroseismology}
-
-\textcolor{red}{Guy - can you describe your pipeline here?}
+Once \numax has been estimated, we use the asteroseismic scaling relation for \numax \citep[Equation~\ref{scaling};][]{KB95} to estimate \logg in order to inform extraction of chemical abundances from spectra.
+Using the initial spectroscopic estimate of \Teff, which is not significantly informed by \numax, we propagate uncertainties in \numax with Monte Carlo sampling.
 
@@
 Operating with spectral resolving power $R=44 000$, we obtain signal-to-noise ratios of \textcolor{red}{something} per resolution element.
+
+\textcolor{red}{Keith - can you describe how you got the abundances here?}
 
@@
 \label{other}
+
+\textcolor{red}{Ashley/Dan/Vichi?}
 

### 2018-07-24 paper/ms.tex
stuff

@@
 Once \numax has been estimated, we use the asteroseismic scaling relation for \numax \citep[Equation~\ref{scaling};][]{KB95} to estimate \logg in order to inform extraction of chemical abundances from spectra.
-Using the initial spectroscopic estimate of \Teff, which is not significantly informed by \numax, we propagate uncertainties in \numax with Monte Carlo sampling.
+Using the initial spectroscopic estimate of \teff, which is not significantly informed by \numax, we propagate uncertainties in \numax with Monte Carlo sampling.
 

### 2018-07-25 paper/ms.tex
minor
pipelines

@@
 
-\textcolor{red}{Guy - can you describe your pipeline here?}
+\textcolor{red}{Guy - can you describe your pipeline in more detail here?}
 
@@
 Operating with spectral resolving power $R=44 000$, we obtain signal-to-noise ratios of \textcolor{red}{something} per resolution element.
+From this observing run we have 35 unique targets with seismic \logg and spectra.
 
-\textcolor{red}{Keith - can you describe how you got the abundances here?}
+\textcolor{red}{Keith - can you describe in more detail how you got the abundances here?}
+
+We initially run the Stellar Parameter Classification \citep[SPC:][]{spc} code to determine \teff and \logg, using the SPC \teff to inform the asteroseismic estimation of \logg from \numax.
+For deriving abundances, \teff is fixed from the results of an initial SPC fit, while \logg is fixed to the seismic values.
+The spectroscopic parameters $v_{\text{mic}}$, and broadening (convolution by $V_{\text{mac}}$, $v_{\sin{i}}$ and the instrumental line profile) as well as [Fe/H] and all chemical abundances are derived using the Brussels Automatic Code for Characterizing High accUracy Spectra \citep[BACCHUS:][]{bacchus}.
 

### 2018-07-25 paper/ms.tex
more for hawkins pipeline
arcturus
include keith's abundance tables in the paper

@@
 The spectroscopic parameters $v_{\text{mic}}$, and broadening (convolution by $V_{\text{mac}}$, $v_{\sin{i}}$ and the instrumental line profile) as well as [Fe/H] and all chemical abundances are derived using the Brussels Automatic Code for Characterizing High accUracy Spectra \citep[BACCHUS:][]{bacchus}.
+This is performed both with and without a line-by-line differential approach with respect to Arcturus ($\alpha$~Bo\"{o}tis) using the method described by \citet{gaiabenchmark4} and the Arcturus abundances from \citep{hawkinsapogee}.
+The results of these calculations are presented in Tables~\ref{table1},~\ref{table2} and~\ref{table3}.
+We note that no abundances for oxygen could be reliably derived for any of the stars in our spectroscopic sample.
+
+\input{abundances_1.tex}
+\input{abundances_2.tex}
+\input{abundances_3.tex}
 

### 2018-07-25 paper/ms.tex
and stellar properties too
rename
fixes

--- 2018-07-25 paper/ms.tex
@@
 For deriving abundances, \teff is fixed from the results of an initial SPC fit, while \logg is fixed to the seismic values.
-The spectroscopic parameters $v_{\text{mic}}$, and broadening (convolution by $V_{\text{mac}}$, $v_{\sin{i}}$ and the instrumental line profile) as well as [Fe/H] and all chemical abundances are derived using the Brussels Automatic Code for Characterizing High accUracy Spectra \citep[BACCHUS:][]{bacchus}.
+The spectroscopic parameters $v_{\text{mic}}$, and broadening (convolution by $V_{\text{mac}}$, $v_{\sin{i}}$ and the instrumental line profile) as well as [Fe/H] and all chemical abundances are derived using the Brussels Automatic Code for Characterizing High accUracy Spectra \citep[BACCHUS:][]{bacchus}, and the results from this calculation are displayed in Table~\ref{stellar_props}.
+Individual elemental abundances are extracted both with and without a line-by-line differential approach with respect to Arcturus ($\alpha$~Bo\"{o}tis) using the method described by \citet{gaiabenchmark4} and the Arcturus abundances from \citep{hawkinsapogee}.
+The results of these calculations are presented in Tables~\ref{elems1},~\ref{elems2} and~\ref{elems3}.
+We note that no abundances for oxygen could be reliably derived for any of the stars in our spectroscopic sample.
+
+\input{stellar_props.tex}
+
+\input{abundances_1.tex}
+\input{abundances_2.tex}
+\input{abundances_3.tex}
 

### 2018-07-25 paper/ms.tex
abundance study initial draft done

@@
 For the whole red giant sample, we have obtained high-resolution spectroscopy with TRES in order to constrain stellar parameters and elemental abundances.
-Operating with spectral resolving power $R=44 000$, we obtain signal-to-noise ratios of \textcolor{red}{something} per resolution element.
-From this observing run we have 35 unique targets with seismic \logg and spectra.
-
-\textcolor{red}{Keith - can you describe in more detail how you got the abundances here?}
+Operating with spectral resolving power $R=44 000$, we obtain signal-to-noise ratios of tens to hundreds per resolution element.
+We note that this resolution and SNR are sufficient for an exploratory study, but for more detailed analysis it will be desirable to use APOGEE or similar instruments at higher resolution and SNR.
+From this observing run we have 35 unique targets with seismic \logg and spectra, one more star than the \gaia-ESO benchmark set and a significant addition to the ensemble of bright red giants with asteroseismic parameter determinations.
 

### 2018-07-25 paper/ms.tex
add suzanne

@@
 Victor Silva Aguirre,$^{5}$
-Victoria Antoci,$^{5}$ and friends
+Victoria Antoci,$^{5}$\newauthor
+Suzanne Aigrain,$^{3}$ and friends
 \\

### 2018-07-25 paper/ms.tex
correcting error

--- 2018-07-25 paper/ms.tex
@@
 Victor Silva Aguirre,$^{5}$
-Victoria Antoci,$^{5}$ and friends
+Victoria Antoci,$^{5}$\newauthor
+Suzanne Aigrain,$^{3}$g and friends
 \\
@@
 The very flat top of this function helps avoid significant variation with position, while still smoothly rolling off at the edges to avoid discontinuous artefacts.
-We calculate this on a grid of $10\times$ subsampled points in time so that the sharply varying edge changes column weights smoothly as a function of centroid.
+We calculate this on a grid of $10\,\times$ subsampled points in pixel space so that the sharply varying edge changes column weights smoothly as a function of centroid.
 We extract photometry using apertures with a range of widths $w \in\{1.5,~2,~3,~4,~5\}$ pixels.

### 2018-07-26 paper/ms.tex
differential abundances

@@
 Individual elemental abundances are extracted both with and without a line-by-line differential approach with respect to Arcturus ($\alpha$~Bo\"{o}tis) using the method described by \citet{gaiabenchmark4} and the Arcturus abundances from \citep{hawkinsapogee}.
-The results of these calculations are presented in Tables~\ref{elems1},~\ref{elems2} and~\ref{elems3}.
-We note that no abundances for oxygen could be reliably derived for any of the stars in our spectroscopic sample.
+The results of these absolute abundance calculations are presented in Tables~\ref{elems1},~\ref{elems2} and~\ref{elems3}.
+Because for most elements Arcturus differential abundances are not available, these are provided as supplementary online-only material.
+No abundances for oxygen could be reliably derived for any of the stars in our spectroscopic sample by either method.
 

### 2018-07-26 paper/ms.tex
asteroseismic analysis

@@
 In the following, we will use the light curves with the lowest 6.5~hr Combined Differential Photometric Precision (CDPP) \citep{cdpp} out of all apertures, as calculated with the \textsc{k2sc} implementation \citep{k2sc}.
-\textcolor{red}{This is primitive - how do we justify this?
-We only did it because we didn't have anything cleverer, but now we do.
-Should I redo this?}.
+This is not necessarily the optimal choice for all red giants, especially those with oscillations on a 6.5~h timescale, but is a reasonable proxy nevertheless for white noise and leads to satisfactory results upon visual inspection of the present sample.
 
@@
 \label{asteroseismology}
-
-\textcolor{red}{Guy - can you describe your pipeline in more detail here?}
 
@@
 
-We obtain good estimates of these asteroseismic parameters for \textcolor{red}{35} targets.
-In the remainder of cases, we find that the very-low-frequency ($\lesssim 2\muHz$) oscillations are affected by filter artefacts from detrending, and we are not able to obtain good estimates for these stars.
-\textcolor{red}{Should we try with these?}
+We obtain good estimates of these asteroseismic parameters for 35 targets, presented in Table~\ref{astero_table}.
+In many of the remainder of cases, we find that the very-low-frequency ($\lesssim 2\muHz$) oscillations are affected by filter artefacts from detrending, and we are not able to obtain good estimates for these stars.
 
@@
 Using the initial spectroscopic estimate of \teff, which is not significantly informed by \numax, we propagate uncertainties in \numax with Monte Carlo sampling.
+
+For eight stars, we find that the asteroseismic fit is unsatisfactory: for BD+39~388 we cannot detect the expected oscillations; BD+43~3064 there are significant peaks but these are not consistent with the pattern expected from a red giant; for HD~179959 and HD~187217 we suspect contamination with the oscillations of a second giant, which is hard to remove from smear light curves; while for HD~188629, HD~188639 and HD~188875 we can extract a \numax but not a robust \Dnu.
+One star in our sample, the retired~A star HD~185351, has a mode envelope that is not well fit by our model.
+The smear light curve for this star has already been published by \citet{2017MNRAS.464.3713H}, who showed with detailed asteroseismic modelling that it had a zero-age main sequence mass of $\sim 1.60 \msun$ and used it to calibrate the convective overshoot parameter for low-luminosity red giants.
+The bulk asteroseismic modelling presented here should therefore be considered to be superseded by the more detailed model of \citet{2017MNRAS.464.3713H}.
+
+\input{astero_table.tex}
 
@@
 We note that this resolution and SNR are sufficient for an exploratory study, but for more detailed analysis it will be desirable to use APOGEE or similar instruments at higher resolution and SNR.
-From this observing run we have 35 unique targets with seismic \logg and spectra, one more star than the \gaia-ESO benchmark set and a significant addition to the ensemble of bright red giants with asteroseismic parameter determinations.
+From this observing run we have~35 unique targets with seismic \logg and spectra, one more star than the \gaia-ESO benchmark set and a significant addition to the ensemble of bright red giants with asteroseismic parameter determinations.
+These are unfortunately not the same~35 unique targets as for the asteroseismic analysis presented above in Section~\ref{asteroseismology}: due to observing constraints, we were unable to obtain spectra for BD+42~315, BD+48~290, HD~176209, HD~183354, HD~189636, or HD~189750.
 
-We initially run the Stellar Parameter Classification \citep[SPC:][]{spc} code to determine \teff and \logg, using the SPC \teff to inform the asteroseismic estimation of \logg from \numax.
+To derive stellar parameters from our TRES spectra, we initially run the Stellar Parameter Classification \citep[SPC:][]{spc} code to determine \teff and \logg, using the SPC \teff to inform the asteroseismic estimation of \logg from \numax.
 For deriving abundances, \teff is fixed from the results of an initial SPC fit, while \logg is fixed to the seismic values.

### 2018-07-26 paper/ms.tex
typo

@@
 Victoria Antoci,$^{5}$\newauthor
-Suzanne Aigrain,$^{3}$g and friends
+Suzanne Aigrain,$^{3}$ and friends
 \\

### 2018-07-26 paper/ms.tex
addition to paper spectra section

@@
 For deriving abundances, \teff is fixed from the results of an initial SPC fit, while \logg is fixed to the seismic values.
-The spectroscopic parameters $v_{\text{mic}}$, and broadening (convolution by $V_{\text{mac}}$, $v_{\sin{i}}$ and the instrumental line profile) as well as [Fe/H] and all chemical abundances are derived using the Brussels Automatic Code for Characterizing High accUracy Spectra \citep[BACCHUS:][]{bacchus}, and the results from this calculation are displayed in Table~\ref{stellar_props}.
-Individual elemental abundances are extracted both with and without a line-by-line differential approach with respect to Arcturus ($\alpha$~Bo\"{o}tis) using the method described by \citet{gaiabenchmark4} and the Arcturus abundances from \citep{hawkinsapogee}.
-The results of these absolute abundance calculations are presented in Tables~\ref{elems1},~\ref{elems2} and~\ref{elems3}.
+The other stellar atmospheric parameters including the microturbulent velocity ($v_{\text{mic}}$), and broadening (convolution by $V_{\text{mac}}$, $v_{\sin{i}}$ and the instrumental line profile) as well as [Fe/H] and chemical abundances for 20 chemical species are derived using the Brussels Automatic Code for Characterizing High accUracy Spectra \citep[BACCHUS:][]{bacchus}, and the results from this calculation are displayed in Table~\ref{stellar_props}.
+BACCHUS uses an interpolation scheme through a grid of MARCS model atmospheres \citep{Gustafsson2008} in combination with TURBOSPECTRUM \citep{Alvarez1998, Plez2012}.
+For the calculation of synthetic spectra, atomic line information has been taken from the fifth version of the Gaia-ESO linelist (Heiter et al., in preparation).
+Additionally we used the molecular species for CH \citep{Masseron2014}, CN, NH, OH, MgH  C$_{2}$ (T.
+Masseron, private communication).
+The SiH molecular information is adopted from the Kurucz linelists and the information for TiO, ZrO, FeH, CaH from B.
+Plez (private communication).
+
+Individual elemental abundances are derived by first fixing the stellar atmospheric parameters to those determined above.
+Spectra are then synthesized  in regions centered around an absorption  feature of the element we want to derive.
+The spectra generated will have different [X/Fe] values.
+A $\chi^2$ minimization procedure is then done to derive the best fitting abundance for each line.
+The reported abundances are the median [X/Fe] value of the various line regions for a given element.
+To achieve the most precise abundances we have derived them using  both with and without a line-by-line differential approach with respect to Arcturus ($\alpha$~Bo\"{o}tis) using the method described by \citet{gaiabenchmark4} and the Arcturus abundances from \citep{hawkinsapogee}.
+The results of these absolute abundance calculations {\bf without the line-by-line differential analysis implemented?}, are presented in Tables~\ref{elems1},~\ref{elems2} and~\ref{elems3}.
 Because for most elements Arcturus differential abundances are not available, these are provided as supplementary online-only material.
@@
 \label{rgs}
-
+\subsection{Chemical Composition}
+place [X/Fe] vs [Fe/H] diagrams here and discuss which Galactic populations these stars come from.
+May also want to discuss how these span the typical Galactic populations and can act as benchmark stars for APOGEE or other large surveys
 \subsection{Other Stars}

### 2018-07-26 paper/ms.tex
all stars now listed

--- 2018-07-26 paper/ms.tex
@@
 \usepackage{ae,aecompl}
+\usepackage{longtable}
 
@@
 A number of these lay just at the edge of a detector, with the result that in some cadences the centroid of the star did not lie on the chip; light curves from these targets were found to be of extremely low quality and all of these objects were discarded.
-After applying these criteria we obtained a list of \textcolor{red}{101} targets.
+After applying these criteria we obtained a list of \textcolor{red}{101} targets, which are listed in Table~\ref{all_stars} in order of their \kepler magnitude $Kp$ together with their spectral type from SIMBAD, the quarters for which they were observed, the seasons for which they were on silicon (some did not even land on silicon for all seasons) and whether spectroscopy is available as in Section~\ref{spectroscopy} and Table~\ref{stellar_props}.
 Aside from the restriction on stars falling on the edge of a chip, the addition of these objects to conventionally-observed stars makes the \kepler survey magnitude-complete down to $Kp=8$.
@@
 This is not necessarily the optimal choice for all red giants, especially those with oscillations on a 6.5~h timescale, but is a reasonable proxy nevertheless for white noise and leads to satisfactory results upon visual inspection of the present sample.
+
+\input{all_stars.tex}
+\input{all_Stars2.tex}
 

### 2018-07-30 paper/ms.tex
untrack
space
include hr diagram and gaia distances

@@
 
+\begin{figure*}
+\noindent\includegraphics[width=15cm,keepaspectratio]{gaia_kepler_hr.png}
+
+\caption{\label{hrdiagram}
+Hertzsprung-Russell diagram of the Smear Campaign stars (orange and teal) situated in the entire \kepler sample (black), using the Bedell \texttt{gaia-kepler.fun} crossmatch and calibrated distances from \citet{gaiadists}.
+The smear sample includes giants and hot main-sequence stars.
+Those giants for which TRES spectroscopy have been obtained are highlighted in teal.}
+\end{figure*}
+
 \input{all_stars.tex}
@@
 \label{rgs}
+
 \subsection{Chemical Composition}
@@
 May also want to discuss how these span the typical Galactic populations and can act as benchmark stars for APOGEE or other large surveys
+
 \subsection{Other Stars}
@@
 
+This work has made use of data from the European Space Agency (ESA) mission
+{\it Gaia} (\url{https://www.cosmos.esa.int/gaia}), processed by the {\it Gaia}
+Data Processing and Analysis Consortium (DPAC,
+\url{https://www.cosmos.esa.int/web/gaia/dpac/consortium}). Funding for the DPAC
+has been provided by national institutions, in particular the institutions
+participating in the {\it Gaia} Multilateral Agreement. This work made use of the gaia-kepler.fun crossmatch database created by Megan Bedell.
+
 This research made use of NASA's Astrophysics Data System; the SIMBAD database, operated at CDS, Strasbourg, France; the IPython package \citep{PER-GRA:2007}; SciPy \citep{jones_scipy_2001}; and Astropy, a community-developed core Python package for Astronomy \citep{2013A&A...558A..33A}.

### 2018-07-30 paper/ms.tex
url

@@
 \caption{\label{hrdiagram}
-Hertzsprung-Russell diagram of the Smear Campaign stars (orange and teal) situated in the entire \kepler sample (black), using the Bedell \texttt{gaia-kepler.fun} crossmatch and calibrated distances from \citet{gaiadists}.
+Hertzsprung-Russell diagram of the Smear Campaign stars (orange and teal) situated in the entire \kepler sample (black), using the Bedell \url{gaia-kepler.fun} crossmatch and calibrated distances from \citet{gaiadists}.
 The smear sample includes giants and hot main-sequence stars.
@@
 has been provided by national institutions, in particular the institutions
-participating in the {\it Gaia} Multilateral Agreement. This work made use of the gaia-kepler.fun crossmatch database created by Megan Bedell.
+participating in the {\it Gaia} Multilateral Agreement. This work made use of the \url{gaia-kepler.fun} crossmatch database created by Megan Bedell.
 

### 2018-07-30 paper/ms.tex
dr2

@@
 \caption{\label{hrdiagram}
-Hertzsprung-Russell diagram of the Smear Campaign stars (orange and teal) situated in the entire \kepler sample (black), using the Bedell \url{gaia-kepler.fun} crossmatch and calibrated distances from \citet{gaiadists}.
+Hertzsprung-Russell diagram of the Smear Campaign stars (orange and teal) situated in the entire \kepler sample (black), using the Bedell \url{gaia-kepler.fun} crossmatch and \gaia~DR2 calibrated distances from \citet{gaiadists}.
 The smear sample includes giants and hot main-sequence stars.

### 2018-07-30 paper/ms.tex
102

@@
 \begin{abstract}
-Here we present the first data release of the \kepler Smear Campaign, using collateral `smear' data obtained by \kepler to reconstruct light curves of 101~stars too bright to have been otherwise observed.
+Here we present the first data release of the \kepler Smear Campaign, using collateral `smear' data obtained by \kepler to reconstruct light curves of 102~stars too bright to have been otherwise observed.
 We describe the pipeline developed to extract and calibrate these light curves, and show that we attain photometric precision comparable to stars ordinarily more observed in the nominal \kepler mission.
@@
 A number of these lay just at the edge of a detector, with the result that in some cadences the centroid of the star did not lie on the chip; light curves from these targets were found to be of extremely low quality and all of these objects were discarded.
-After applying these criteria we obtained a list of \textcolor{red}{101} targets, which are listed in Table~\ref{all_stars} in order of their \kepler magnitude $Kp$ together with their spectral type from SIMBAD, the quarters for which they were observed, the seasons for which they were on silicon (some did not even land on silicon for all seasons) and whether spectroscopy is available as in Section~\ref{spectroscopy} and Table~\ref{stellar_props}.
+After applying these criteria we obtained a list of 102 targets, which are listed in Table~\ref{all_stars} in order of their \kepler magnitude $Kp$ together with their spectral type from SIMBAD, the quarters for which they were observed, the seasons for which they were on silicon (some did not even land on silicon for all seasons) and whether spectroscopy is available as in Section~\ref{spectroscopy} and Table~\ref{stellar_props}.
 Aside from the restriction on stars falling on the edge of a chip, the addition of these objects to conventionally-observed stars makes the \kepler survey magnitude-complete down to $Kp=8$.

### 2018-07-30 paper/ms.tex
number of quarters

@@
 In \citet{smear}, we demonstrated a method for extracting precise light curves of bright stars in \kepler and K2, and presented light curves of a small number of variable stars as examples to illustrate this method.
-In this Paper we present light curves of all unobserved or significantly under-observed stars brighter than $V=8$ in the \kepler field.
+In this Paper we present light curves of all unobserved or significantly under-observed stars brighter than $Kp=9$ in the \kepler field.
 This sample is biased towards red giants and hot stars, containing only a few FG dwarfs.
@@
 
-We selected as our sample all stars on-silicon in \kepler with $Kp<8$ which were unobserved for more than $10$ quarters \textcolor{red}{Tim: what was your cutoff in quarters for `underobserved' stars?}, including those stars which were entirely unobserved.
+We selected as our sample all stars on-silicon in \kepler with $Kp<9$ which were unobserved for more than $8$ quarters, including those stars which were entirely unobserved.
 A number of these lay just at the edge of a detector, with the result that in some cadences the centroid of the star did not lie on the chip; light curves from these targets were found to be of extremely low quality and all of these objects were discarded.

### 2018-07-30 paper/ms.tex
text about tables and figure

@@
 A number of these lay just at the edge of a detector, with the result that in some cadences the centroid of the star did not lie on the chip; light curves from these targets were found to be of extremely low quality and all of these objects were discarded.
-After applying these criteria we obtained a list of 102 targets, which are listed in Table~\ref{all_stars} in order of their \kepler magnitude $Kp$ together with their spectral type from SIMBAD, the quarters for which they were observed, the seasons for which they were on silicon (some did not even land on silicon for all seasons) and whether spectroscopy is available as in Section~\ref{spectroscopy} and Table~\ref{stellar_props}.
-Aside from the restriction on stars falling on the edge of a chip, the addition of these objects to conventionally-observed stars makes the \kepler survey magnitude-complete down to $Kp=8$.
+After applying these criteria we obtained a list of 102 targets, which are listed in Table~\ref{all_stars} in order of their \kepler magnitude $Kp$ together with their spectral type from SIMBAD, \gaia~DR2 source identifiers, apparent~$G$ magnitudes and distances from \citet{gaiadists}, the quarters for which the stars were observed, the seasons for which they were on silicon (some did not even land on silicon for all seasons), and whether spectroscopy is available as in Section~\ref{spectroscopy} and Table~\ref{stellar_props}.
+Aside from the restriction on stars falling on the edge of a chip, the addition of these objects to conventionally-observed stars makes the \kepler survey magnitude-complete down to $Kp=9$.
+In Figure~\ref{hrdiagram} we show these stars on a colour-magnitude diagram in \gaia $Bp-Rp$ and absolute~$G$ magnitudes using \gaia~DR2 calibrated distances from \citet{gaiadists}, and situate these in context with the entire \kepler sample from the Bedell \url{gaia-kepler.fun} crossmatch.
 
@@
 \caption{\label{hrdiagram}
-Hertzsprung-Russell diagram of the Smear Campaign stars (orange and teal) situated in the entire \kepler sample (black), using the Bedell \url{gaia-kepler.fun} crossmatch and \gaia~DR2 calibrated distances from \citet{gaiadists}.
+\gaia colour-magnitude diagram of the Smear Campaign stars (orange and teal) situated in the entire \kepler sample (black), using the Bedell \url{gaia-kepler.fun} crossmatch and \gaia~DR2 calibrated distances from \citet{gaiadists}.
 The smear sample includes giants and hot main-sequence stars.

### 2018-08-07 paper/ms.tex
supplementary material

@@
 The smear sample includes giants and hot main-sequence stars.
-Those giants for which TRES spectroscopy have been obtained are highlighted in teal.}
+Those giants for which TRES spectroscopy have been obtained are highlighted in teal.
+An interactive version of this diagram is available as supplementary material from the journal or at \url{benjaminpope.github.io/data/cmd_smear.html}.}
 \end{figure*}

### 2018-08-08 paper/ms.tex
typos in star names

@@
 From this observing run we have~35 unique targets with seismic \logg and spectra, one more star than the \gaia-ESO benchmark set and a significant addition to the ensemble of bright red giants with asteroseismic parameter determinations.
-These are unfortunately not the same~35 unique targets as for the asteroseismic analysis presented above in Section~\ref{asteroseismology}: due to observing constraints, we were unable to obtain spectra for BD+42~315, BD+48~290, HD~176209, HD~183354, HD~189636, or HD~189750.
+These are unfortunately not the same~35 unique targets as for the asteroseismic analysis presented above in Section~\ref{asteroseismology}: due to observing constraints, we were unable to obtain spectra for BD+42~315, BD+48~290, HD~176209, HD~182354, HD~189636, or HD~189750.
 

### 2018-08-09 paper/ms.tex
hump and spike stars

@@
 
+\subsection{Classical Pulsators}
+
+Two stars in the sample show the `hump-and-spike' morphology in their power spectra (a broad `hump' of low-amplitude oscillations dominated by one high amplitude coherent oscillation): HD~186155 (HR~7495), and HD~183362 (HR~7403), respectively the third brightest and $37^{th}$-brightest stars on silicon and the brightest two stars that show this effect.
+\citet{2018MNRAS.474.2774S} have recently claimed the hump-and-spike power spectra as evidence for Rossby modes.
+The F5 star HD~186155, identified by SIMBAD as having a giant spectral type of F5II-III, is shown by its \gaia distance to in fact lie on the main sequence.
+With an absolute $G$~mag of 1.402, it is significantly fainter than the bright B3e star HD~183362 at $G = -2.576$.
+
 \textcolor{red}{Ashley/Dan/Vichi?}

### 2018-08-09 paper/ms.tex
text

@@
 
-Two stars in the sample show the `hump-and-spike' morphology in their power spectra (a broad `hump' of low-amplitude oscillations dominated by one high amplitude coherent oscillation): HD~186155 (HR~7495), and HD~183362 (HR~7403), respectively the third brightest and $37^{th}$-brightest stars on silicon and the brightest two stars that show this effect.
+Two stars in the sample show the `hump-and-spike' morphology in their power spectra (a broad `hump' of low-amplitude oscillations dominated by one high amplitude coherent oscillation): HD~186155 (HR~7495), and HD~183362 (HR~7403), respectively the third brightest and $37^{\text{th}}$-brightest stars on silicon and the brightest two stars that show this effect.
 \citet{2018MNRAS.474.2774S} have recently claimed the hump-and-spike power spectra as evidence for Rossby modes.

### 2018-08-09 paper/ms.tex
not the bit about it being bright
antoci
add jie and tim as coauthors

@@
 Victoria Antoci,$^{5}$\newauthor
-Suzanne Aigrain,$^{3}$ and friends
+Suzanne Aigrain,$^{3}$ 
+Timothy R. Bedding,$^{10,5}$
+Jie Yu,$^{10,5}$ and friends
 \\
@@
 The F5 star HD~186155, identified by SIMBAD as having a giant spectral type of F5II-III, is shown by its \gaia distance to in fact lie on the main sequence.
-With an absolute $G$~mag of 1.402, it is significantly fainter than the bright B3e star HD~183362 at $G = -2.576$.
+The other example is the B3e star HD~183362 at $G = -2.576$.
+A detailed study of these stars will be presented by Antoci et al., in prep.
 

### 2018-08-10 paper/ms.tex
comment on G0 dwarf

@@
 In Figure~\ref{hrdiagram} we show these stars on a colour-magnitude diagram in \gaia $Bp-Rp$ and absolute~$G$ magnitudes using \gaia~DR2 calibrated distances from \citet{gaiadists}, and situate these in context with the entire \kepler sample from the Bedell \url{gaia-kepler.fun} crossmatch.
+From the HR diagram, we identify 64 of these objects as evolved systems, and the remaining~38 lie on the main sequence.
+One of the main sequence objects, BD+43~3068 is a G0 dwarf with a $G$ magnitude of 8.267944 and a distance of $53.8 \pm 0.1$~pc, and it is therefore surprising that it was not included in the nominal \kepler survey as a Solar analogue: it is possible that it was previously misidentified as a giant.
+Regrettably, it is only possible to reconstruct a light curve with the 30~minute long cadence and therefore it is not possible to do asteroseismology on this bright, nearby solar-like star.
 

### 2018-08-10 paper/ms.tex
caption

@@
 \caption{\label{hrdiagram}
-\gaia colour-magnitude diagram of the Smear Campaign stars (orange and teal) situated in the entire \kepler sample (black), using the Bedell \url{gaia-kepler.fun} crossmatch and \gaia~DR2 calibrated distances from \citet{gaiadists}.
+\gaia colour-magnitude diagram of the Smear Campaign stars (orange and teal) situated in sample of \kepler stars with \gaia parallax $\text{SNR} > 25$ (black), using the Bedell \url{gaia-kepler.fun} crossmatch and \gaia~DR2 calibrated distances from \citet{gaiadists}.
 The smear sample includes giants and hot main-sequence stars.

### 2018-08-10 paper/ms.tex
seasons

@@
 A number of these lay just at the edge of a detector, with the result that in some cadences the centroid of the star did not lie on the chip; light curves from these targets were found to be of extremely low quality and all of these objects were discarded.
-After applying these criteria we obtained a list of 102 targets, which are listed in Table~\ref{all_stars} in order of their \kepler magnitude $Kp$ together with their spectral type from SIMBAD, \gaia~DR2 source identifiers, apparent~$G$ magnitudes and distances from \citet{gaiadists}, the quarters for which the stars were observed, the seasons for which they were on silicon (some did not even land on silicon for all seasons), and whether spectroscopy is available as in Section~\ref{spectroscopy} and Table~\ref{stellar_props}.
-Aside from the restriction on stars falling on the edge of a chip, the addition of these objects to conventionally-observed stars makes the \kepler survey magnitude-complete down to $Kp=9$.
+After applying these criteria we obtained a list of 102 targets, which are listed in Table~\ref{all_stars} in order of their \kepler magnitude $Kp$ together with their spectral type from SIMBAD, \gaia~DR2 source identifiers, apparent~$G$ magnitudes and distances from \citet{gaiadists}, the quarters for which the stars were observed, and whether spectroscopy is available as in Section~\ref{spectroscopy} and Table~\ref{stellar_props}.
+The \kepler satellite rotates between quarters, so that it cycles through four orientation `seasons' each rotated from the last by $90^{\circ}$.
+Some stars did not land on silicon for all seasons: we have only one season of HD~179394; two for HD~187277, HD~226754, V554~Lyr, and BD+47~2891; and three for BD+43~3064.
+Aside from the restriction on stars falling on the edge of a chip like tihs or otherwise, the addition of our sample to the conventionally-observed stars makes the \kepler survey magnitude-complete down to $Kp=9$.
 In Figure~\ref{hrdiagram} we show these stars on a colour-magnitude diagram in \gaia $Bp-Rp$ and absolute~$G$ magnitudes using \gaia~DR2 calibrated distances from \citet{gaiadists}, and situate these in context with the entire \kepler sample from the Bedell \url{gaia-kepler.fun} crossmatch.

### 2018-08-10 paper/ms.tex
add amalie to authors
init red clump star section
remove newpage
new sections

@@
 Timothy R. Bedding,$^{10,5}$
-Jie Yu,$^{10,5}$ and friends
+Jie Yu,$^{10,5}$ 
+Amalie Stokholm,$^{5}$\newauthor
+and friends
 \\
@@
 By comparing asteroseismic stellar ages to stellar rotation periods, \citet{angusgyro} have shown that gyrochronology models cannot fit the data with a single relation, leading \citet{vansadersgyro} to suggest a qualitative change in dynamo mechanism as stars age through the main sequence.
-\newpage
 
@@
 \subsection{Chemical Composition}
+\label{chemical}
 place [X/Fe] vs [Fe/H] diagrams here and discuss which Galactic populations these stars come from.
@@
 
-\subsection{Other Stars}
-\label{other}
+\subsection{Red Clump Stars}
+\label{clumpstars}
+
+From visual inspection of the power spectra, HD 181069, HD 183124, HD 182354, HD 182692, and HD 180658 are seen to be core helium-burning red clump stars.
 
 \subsection{Classical Pulsators}
+\label{pulsators}
 
@@
 \textcolor{red}{Ashley/Dan/Vichi?}
+
+\subsection{Eclipsing Binaries}
+\label{ebs}
 

### 2018-08-10 paper/ms.tex
typo in acknowledgement

@@
 
-BP acknowledges being on the traditional territory of the Lenape Nations and, today, we grecognize that Manhattan continues to be the home to many Algonkian peoples.
+BP acknowledges being on the traditional territory of the Lenape Nations and, today, we recognize that Manhattan continues to be the home to many Algonkian peoples.
 We thank the Lenape peoples for allowing us to carry out this work on the Lenape original homelands at New York University.

### 2018-08-10 paper/ms.tex
newpage issue

@@
 Two stars in the sample show the `hump-and-spike' morphology in their power spectra (a broad `hump' of low-amplitude oscillations dominated by one high amplitude coherent oscillation): HD~186155 (HR~7495), and HD~183362 (HR~7403), respectively the third brightest and $37^{\text{th}}$-brightest stars on silicon and the brightest two stars that show this effect.
+Another star with a hump-and-spike spectrum is Boyajian's~Star, which shows deep enigmatic dips in brightness \citep{2016MNRAS.457.3988B}, and has faded both throughout the \kepler mission \citep{2016ApJ...830L..39M} and in relation to Harvard photographic plates from 1890 onwards \citep{2016ApJ...822L..34S}.
+It is unclear whether the explanation of the hump-and-spike phenomenon will shed light on the strange behaviour of Boyajian's~Star, but it may be relevant.
 \citet{2018MNRAS.474.2774S} have recently claimed the hump-and-spike power spectra as evidence for Rossby modes.
@@
 \label{conclusions}
+\newpage
 

### 2018-08-10 paper/ms.tex
more citations for boyajian's star

@@
 Another star with a hump-and-spike spectrum is Boyajian's~Star, which shows deep enigmatic dips in brightness \citep{2016MNRAS.457.3988B}, and has faded both throughout the \kepler mission \citep{2016ApJ...830L..39M} and in relation to Harvard photographic plates from 1890 onwards \citep{2016ApJ...822L..34S}.
+The dimming, which is chromatic in the manner expected of heterogeneous clouds of circumstellar dust in the line of sight \citep{2018ApJ...853..130D,2018arXiv180608842B}, has been ascribed to various causes \citep[reviewed in][]{2018RNAAS...2a..16W}, most notably a cloud of exocomets surrounding the star \citep[e.g.][]{2018MNRAS.473.5286W}.
 It is unclear whether the explanation of the hump-and-spike phenomenon will shed light on the strange behaviour of Boyajian's~Star, but it may be relevant.
@@
 \label{conclusions}
-\newpage
 

### 2018-08-10 paper/ms.tex
reformat
subsubsection

@@
 
-\subsection{Chemical Composition}
+\subsubsection{Chemical Composition}
 \label{chemical}
@@
 
-\subsection{Red Clump Stars}
+\subsubsection{Red Clump Stars}
 \label{clumpstars}
@@
 
-\subsection{Classical Pulsators}
+\subsection{Main Sequence Pulsators}
 \label{pulsators}
@@
 Two stars in the sample show the `hump-and-spike' morphology in their power spectra (a broad `hump' of low-amplitude oscillations dominated by one high amplitude coherent oscillation): HD~186155 (HR~7495), and HD~183362 (HR~7403), respectively the third brightest and $37^{\text{th}}$-brightest stars on silicon and the brightest two stars that show this effect.
-Another star with a hump-and-spike spectrum is Boyajian's~Star, which shows deep enigmatic dips in brightness \citep{2016MNRAS.457.3988B}, and has faded both throughout the \kepler mission \citep{2016ApJ...830L..39M} and in relation to Harvard photographic plates from 1890 onwards \citep{2016ApJ...822L..34S}.
-The dimming, which is chromatic in the manner expected of heterogeneous clouds of circumstellar dust in the line of sight \citep{2018ApJ...853..130D,2018arXiv180608842B}, has been ascribed to various causes \citep[reviewed in][]{2018RNAAS...2a..16W}, most notably a cloud of exocomets surrounding the star \citep[e.g.][]{2018MNRAS.473.5286W}.
-It is unclear whether the explanation of the hump-and-spike phenomenon will shed light on the strange behaviour of Boyajian's~Star, but it may be relevant.
 \citet{2018MNRAS.474.2774S} have recently claimed the hump-and-spike power spectra as evidence for Rossby modes.
@@
 A detailed study of these stars will be presented by Antoci et al., in prep.
+
+Another star with a hump-and-spike spectrum is Boyajian's~Star, which shows deep enigmatic dips in brightness \citep{2016MNRAS.457.3988B}, and has faded both throughout the \kepler mission \citep{2016ApJ...830L..39M} and in relation to Harvard photographic plates from 1890 onwards \citep{2016ApJ...822L..34S}.
+The dimming, which is chromatic in the manner expected of heterogeneous clouds of circumstellar dust in the line of sight \citep{2018ApJ...853..130D,2018arXiv180608842B}, has been ascribed to various causes \citep[reviewed in][]{2018RNAAS...2a..16W}, most notably a cloud of exocomets surrounding the star \citep[e.g.][]{2018MNRAS.473.5286W}.
+It is unclear whether the explanation of the hump-and-spike phenomenon will shed light on the strange behaviour of Boyajian's~Star, but it may be relevant.
 
@@
 All code used to produce smear light curves is available under a GPL~v3 license at \url{github.com/benjaminpope/keplersmear}.
-All smear light curves, both including the red giant sample studied in detail in Section~\ref{rgs}, and other stars as discussed in Section~\ref{other}, can be downloaded from the Mikulski Archive for Space Telescopes (MAST) as a High-Level Science Product.
+All smear light curves, both including the red giant sample studied in detail in Section~\ref{rgs}, and main sequence stars as discussed in Sections~\ref{pulsators} and~\ref{ebs}, can be downloaded from the Mikulski Archive for Space Telescopes (MAST) as a High-Level Science Product.
 TRES spectra are available from \textcolor{red}{somewhere}, and all asteroseismic parameters and derived stellar parameters for the red giants in Section~\ref{rgs} are provided in an online-only table as Supplementary Material to this paper.

### 2018-08-10 paper/ms.tex
add in tim's figure

@@
 
-From visual inspection of the power spectra, HD 181069, HD 183124, HD 182354, HD 182692, and HD 180658 are seen to be core helium-burning red clump stars.
+From visual inspection of the power spectra, HD~181069, HD~183124, HD~182354, HD~182692, and HD~180658 are seen to be core helium-burning red clump stars.
+A power spectrum of the best example of these, HD~183124, is shown in Figure~\ref{HD_183124}.
+
+\begin{figure*}
+\noindent\includegraphics[width=19cm,keepaspectratio]{HD_183124.png}
+
+\caption{\label{HD_183124}
+Power spectrum (left) and \'{e}chelle diagram (right) of the solar-like oscillations of the red clump star HD~183124.
+The modes in the power spectrum used for the \'{e}chelle diagram are highlighted with blue dots.
+In the \'{e}chelle diagram we see the characteristic pattern of `bumped' modes from avoided crossings between the comb of \emph{p}-modes and \emph{g}-mode oscillations with a period spacing of $\Delta \Pi = 300.1~\text{s}$.}
+\end{figure*}
 

### 2018-08-10 paper/ms.tex
edit abstract

@@
 Here we present the first data release of the \kepler Smear Campaign, using collateral `smear' data obtained by \kepler to reconstruct light curves of 102~stars too bright to have been otherwise observed.
-We describe the pipeline developed to extract and calibrate these light curves, and show that we attain photometric precision comparable to stars ordinarily more observed in the nominal \kepler mission.
-In this Paper, we focus in particular on a subset of these consisting of 60~red giants for which we detect solar-like oscillations.
-Using high-resolution spectroscopy from the Tillinghast Reflector \'{E}chelle Spectrograph (TRES) together with asteroseismic modelling, we constrain the masses and evolutionary states of these benchmark red giants.
+We describe the pipeline developed to extract and calibrate these light curves, and show that we attain photometric precision comparable to stars observed ordinarily in the nominal \kepler mission.
+In this Paper, we focus in particular on a subset of these consisting of 64~red giants for which we detect solar-like oscillations.
+Using high-resolution spectroscopy from the Tillinghast Reflector \'{E}chelle Spectrograph (TRES) together with asteroseismic modelling, we obtain the masses and evolutionary states of~27 of these red giant and red clump stars as benchmarks.
 All source code, light curves, TRES spectra, and asteroseismic and stellar parameters are publicly available as a \kepler legacy sample.
@@
 has been provided by national institutions, in particular the institutions
-participating in the {\it Gaia} Multilateral Agreement. This work made use of the \url{gaia-kepler.fun} crossmatch database created by Megan Bedell.
+participating in the {\it Gaia} Multilateral Agreement. This work has in particular made use of the \url{gaia-kepler.fun} crossmatch database created by Megan Bedell.
 

### 2018-08-10 paper/ms.tex
add bedding citation

@@
 A power spectrum of the best example of these, HD~183124, is shown in Figure~\ref{HD_183124}.
+Clump stars differ significantly in their core structure from stars on the hydrogen shell burning red giant sequence, with the consequence that they can be distinguished from hydrogen-shell burning giants asteroseismologically due to their much higher \emph{g}-mode period spacings \citep{rggmodehelium}.
 

### 2018-08-10 paper/ms.tex
init clump

--- 2018-08-10 paper/ms.tex
@@
 
-From visual inspection of the power spectra, HD~181069, HD~183124, HD~182354, HD~182692, and HD~180658 are seen to be core helium-burning red clump stars.
-A power spectrum of the best example of these, HD~183124, is shown in Figure~\ref{HD_183124}.
+Red clump stars, which burn helium in their cores, differ significantly in their core structure from stars on the hydrogen shell burning red giant sequence.
+They can therefore be distinguished from hydrogen-shell burning giants asteroseismologically, due to their much higher \emph{g}-mode period spacings \citep{rggmodehelium}.
+The moniker `red clump' arises from the fact that such stars can have a very narrow range of luminosities, so that they appear as a clump in the HR diagram \citep{2016ARA&A..54...95G}.
+This property makes them useful standard candles to which distances can be accurately computed from photometry.
+Red clump stars have been used to calibrate the \gaia survey's parallaxes at long distances \citep{2017A&A...598L...4D,2017MNRAS.471..722H,2018A&A...609A.116R}.
+\gaia~DR2 parallaxes have a zero-point offset of $\sim 0.03$~mas \citep{gaiadr2parallax}, and in particular hierarchical models of the ensemble of \gaia clump stars can be used to accurately estimate this and thereby improve the accuracy of \gaia distances greater than a few~kpc (Hawkins et al., in prep.).
+
+From visual inspection of the power spectra, HD~181069, HD~183124, HD~182354, HD~182692, and HD~180658 are seen to be red clump stars.
+A power spectrum of the best example of these, HD~183124, together with an \'{e}chelle diagram used to estimate its \emph{g}-mode period spacing, is shown in Figure~\ref{HD_183124}.
 

### 2018-08-13 paper/ms.tex
round out red clump section
hipparcos

@@
 
-\subsection{Photometry}
-\label{photometry}
+\subsection{Sample}
+\label{sample}
 
@@
 Some stars did not land on silicon for all seasons: we have only one season of HD~179394; two for HD~187277, HD~226754, V554~Lyr, and BD+47~2891; and three for BD+43~3064.
-Aside from the restriction on stars falling on the edge of a chip like tihs or otherwise, the addition of our sample to the conventionally-observed stars makes the \kepler survey magnitude-complete down to $Kp=9$.
+Aside from the restriction on stars falling on the edge of a chip like this or otherwise, the addition of our sample to the conventionally-observed stars makes the \kepler survey magnitude-complete down to $Kp=9$.
+
 In Figure~\ref{hrdiagram} we show these stars on a colour-magnitude diagram in \gaia $Bp-Rp$ and absolute~$G$ magnitudes using \gaia~DR2 calibrated distances from \citet{gaiadists}, and situate these in context with the entire \kepler sample from the Bedell \url{gaia-kepler.fun} crossmatch.
+While \gaia parallaxes for very bright stars can be subject to systematic error, we have compared these to those found by \emph{Hipparcos} \citep{vanleeuwen07b}, and found close agreement for the brightest stars, with a scatter that increases with magnitude.
 From the HR diagram, we identify 64 of these objects as evolved systems, and the remaining~38 lie on the main sequence.
@@
 Regrettably, it is only possible to reconstruct a light curve with the 30~minute long cadence and therefore it is not possible to do asteroseismology on this bright, nearby solar-like star.
+
+\subsection{Photometry}
+\label{photometry}
 
@@
 A power spectrum of the best example of these, HD~183124, together with an \'{e}chelle diagram used to estimate its \emph{g}-mode period spacing, is shown in Figure~\ref{HD_183124}.
+While precise characterization of these stars to the necessary degree is beyond the scope of this paper, they are ideal candidates for anchoring models of the mass and metallicity dependence of red clump properties for calibrating \gaia and other distance measures.
 

### 2018-08-13 paper/ms.tex
timescale

@@
 
-For all \textcolor{red}{N} red giants identified in this sample, we have attempted to extract the asteroseismic parameters \numax and $\langle \Dnu \rangle$ \citep{KB95,2013ARA&A..51..353C}.
+While~64 red giants have been identified in this sample, for some of these, by visual inspection it is clear that the timescale of their variability is of the same order as a \kepler quarter and they are thus badly affected by systematics and systematics correction.
+From the 35 giants for which there is shorter-timescale variability, we have attempted to extract the asteroseismic parameters \numax and $\langle \Dnu \rangle$ \citep{KB95,2013ARA&A..51..353C}.
 These constrain fundamental stellar parameters independently from spectroscopic or interferometric measurements:

### 2018-08-13 paper/ms.tex
more on bias

@@
 In Figure~\ref{hrdiagram} we show these stars on a colour-magnitude diagram in \gaia $Bp-Rp$ and absolute~$G$ magnitudes using \gaia~DR2 calibrated distances from \citet{gaiadists}, and situate these in context with the entire \kepler sample from the Bedell \url{gaia-kepler.fun} crossmatch.
+The smear targets in this diagram appear to have not merely higher apparent brightnesses than the general \kepler population, but also higher intrinsic luminosities.
+While this could simply arise from being selected for their apparent brightness, it is worth considering whether this is because of a bias in their parallax measurements.
 While \gaia parallaxes for very bright stars can be subject to systematic error, we have compared these to those found by \emph{Hipparcos} \citep{vanleeuwen07b}, and found close agreement for the brightest stars, with a scatter that increases with magnitude.
+We therefore suggest that parallax bias is not the reason for the smear sample sitting above the remainder of the \kepler sample.
+
 From the HR diagram, we identify 64 of these objects as evolved systems, and the remaining~38 lie on the main sequence.

### 2018-08-15 paper/ms.tex
add stars
assess contamination

@@
 
+Because the smear data are collected along an entire CCD~column, there is the risk of contamination from sufficiently bright sources.
+This is especially true in doing asteroseismology of red giants, where the low-amplitude stochastically-excited oscillations can be washed out in a power spectrum by the coherent high amplitude variations of a classical pulsator, even if the background star is much fainter.
+We can assess the importance of this contamination by considering the differences between odd and even quarters: because the \kepler satellite rotates $90^{\circ}$ between successive quarters, any contaminant will lie in the same column as a smear target only every second quarter, falling in the other quarters in the same row but not necessarily the same column.
+We have therefore generated Lomb-Scargle periodograms \citep{lomb,scargle} of each light curve, clipped for outliers, and considering only odd and even quarters, and visually inspected these for significant differences.
+In the great majority of cases they closely resemble one another, indicating that contamination is at worst a minor effect.
+In the case of HD~181878, a red giant, there is clear and significant contamination from a $\delta$~Scuti variable, as is seen in Figure~\ref{contamination}.
+
+\begin{figure}
+\noindent\includegraphics[width=8cm,keepaspectratio]{contam_HD_181778.png}
+
+\caption{\label{contamination}
+Power spectra of odd and even quarters of HD~181778.
+It is clear from inspection that while odd quarters have the power spectrum expected of a giant star, even quarters have very high amplitude coherent oscillations typical of a $\delta$~Scuti variable.}
+\end{figure}
+
 \input{all_stars.tex}
@@
 May also want to discuss how these span the typical Galactic populations and can act as benchmark stars for APOGEE or other large surveys
+
+Two of the stars in our sample also appear in the Hypatia catalogue of stellar abundances \citep{hypatia}: HD~185351 and HD~175740.
+The abundances reported here for HD~185351 are consistent within the large errorbars of both surveys with those reported in Hypatia, while for HD~175740 they are not.
+\textcolor{red}{Keith - what's going on here?
+Check this?}
 

### 2018-08-15 paper/ms.tex
halo photometry

@@
 The result of these two target selection constraints is that photometry was obtained for only \textcolor{red}{a small number} of saturated stars in the \kepler field, while many bright targets were ignored.
+In the K2 mission \citep{k2early}, very saturated stars have been observed with `halo photometry' using unsaturated pixels in a specially-determined region around bright stars, including the Pleiades \citep{halo}, Aldebaran \citep{aldebaran}, and $\rho$~Leonis \citep{rholeo}.
+Unfortunately, in the legacy \kepler sample, photometry of such saturated stars was rarely attempted.
 

### 2018-08-16 paper/ms.tex
timothy van reeth as coauthor

@@
 Amalie Stokholm,$^{5}$\newauthor
+Timothy van Reeth,$^{5,10}$
 and friends
@@
 
-From the HR diagram, we identify 64 of these objects as evolved systems, and the remaining~38 lie on the main sequence.
+We identify the evolutionary state of objects in the main sequence versus evolved stars first from the \gaia colour-magnitude diagram in Figure~\ref{hrdiagram}.
+Taking a cutoff in \gaia $Bp-Rp < 1$, we identify 64 of these objects as evolved systems, and the remaining~38 lie apparently on the main sequence.
+
 One of the main sequence objects, BD+43~3068 is a G0 dwarf with a $G$ magnitude of 8.267944 and a distance of $53.8 \pm 0.1$~pc, and it is therefore surprising that it was not included in the nominal \kepler survey as a Solar analogue: it is possible that it was previously misidentified as a giant.
 Regrettably, it is only possible to reconstruct a light curve with the 30~minute long cadence and therefore it is not possible to do asteroseismology on this bright, nearby solar-like star.
+This light curve shows neither rotational modulation (as determined by its featureless autocorrelation) nor evidence of transits.
+
+Considering objects lying photometrically on the main sequence, from the \kepler power spectrum we identify solar-like oscillations in HD~182354 and HD~176209 at frequencies consistent with them being subgiants.
+\textcolor{red}{Get frequencies}.
 
@@
 
-\subsection{Main Sequence Pulsators}
+\subsection{Main Sequence Stars}
+\label{mainseq}
+
+\subsubsection{Classical Pulsators}
 \label{pulsators}
@@
 
-\subsection{Eclipsing Binaries}
+\subsubsection{Eclipsing Binaries}
 \label{ebs}

### 2018-08-17 paper/ms.tex
added variability analysis

@@
 
+For all the main sequence stars in our sample, we visually inspected light curves and power spectra to determine their variability class.
+In the following subsections, we will briefly comment on some of the findings.
+As main sequence variables are so diverse, and suited to varied science cases, we have attempted only a very preliminary study of these stars in this paper, leaving detailed analysis to future work.
+
 \subsubsection{Classical Pulsators}
 \label{pulsators}
+The sample contains many $\delta\,\text{Sct}$ and $\gamma\,\text{Dor}$ variables, and several hybrid pulsators. \textcolor{red}{Simon - add text here.}
+Including hotter stars, we also detect SPB pulsations in \textcolor{red}{some stars - Conny/Tim van Reeth?}.
+
+\subsubsection{Hump and Spike Stars}
+\label{hs}
 
@@
 \label{ebs}
+We detect some eclipsing binaries \textcolor{red}{Ben - finish this.}
 

### 2018-08-17 paper/ms.tex
added variability analysis
hedge

@@
 We identify the evolutionary state of objects in the main sequence versus evolved stars first from the \gaia colour-magnitude diagram in Figure~\ref{hrdiagram}.
-Taking a cutoff in \gaia $Bp-Rp < 1$, we identify 64 of these objects as evolved systems, and the remaining~38 lie apparently on the main sequence.
+Taking a cutoff in \gaia $Bp-Rp < 1$, we identify 64 of these objects as clearly evolved systems, and the remaining~38 lie apparently on the main sequence.
 

### 2018-08-20 paper/ms.tex
tim edits phase 1

@@
 
-The \kepler Space Telescope, operated by NASA, was launched in 2009 to obtain photometry of hundreds of thousands of stars in a field in Cygnus-Lyra, in order to detect a statistically-useful sample of transiting exoplanets \citep{2010Sci...327..977B}.
+% The \kepler Space Telescope, operated by NASA, was launched in 2009 to obtain photometry of hundreds of thousands of stars in a field in Cygnus-Lyra, in order to detect a statistically-useful sample of transiting exoplanets \citep{2010Sci...327..977B}.
 It achieved this primary goal, showing that exoplanets are common around Sun-like stars \citep{2013ApJ...766...81F,2013PNAS..11019273P,2014ApJ...795...64F}, though with the failure of two reaction wheels, the mission was cut short and there remain substantial uncertainties on these estimates.
@@
 
-Beyond searching for planets, \kepler has revolutionized the field of asteroseismology \citep{2010PASP..122..131G}.
+% Beyond searching for planets, 
+\kepler has revolutionized the field of asteroseismology for solar-like oscillations \citep{2010PASP..122..131G}.
 It has yielded the first detection of gravity-mode period spacings in a red giant \citep{rggmodes}, enabling probes of interior rotation of red giants \citep{rggmoderotation} and distinguishing between hydrogen- and helium-burning cores \citep{rggmodehelium}.
@@
 
-A major outcome of the \kepler asteroseismology programme is a legacy sample of extremely well characterized stars which can serve as benchmarks for future work \citep{keplerlegacy1,keplerlegacy2}.
+A major outcome of the \kepler asteroseismology programme is a legacy sample of extremely well characterized stars that can serve as benchmarks for future work \citep{keplerlegacy1,keplerlegacy2}.
 As well as asteroseismology, by also using optical interferometry, it has been possible to determine fundamental parameters of main-sequence and giant stars with unprecedented precision \citep{huber12,thetacygwhite,white15}.
@@
 
-Brighter \kepler stars are therefore ideal benchmark targets, as photometry can be most easily complemented by \hipparcos parallaxes, interferometric diameters, and high resolution spectroscopy.  
+Brighter \kepler stars are therefore ideal benchmark targets, since photometry can be most easily complemented by \hipparcos parallaxes, interferometric diameters, and high resolution spectroscopy.  
 Unfortunately, the \kepler field was deliberately placed to minimize overall the number of saturated stars, so that only a dozen stars brighter than~6th~magnitude landed on silicon \citep{2010ApJ...713L..79K}.
-This was because stars brighter than $Kp \sim 11$ saturate the CCD detector, spilling electrons up and down their column on the CCD and rendering these pixels otherwise unusable.
+This was because stars brighter than $Kp \sim 11$ saturate the CCD detector, spilling electrons up and down their column on the CCD and rendering those pixels otherwise unusable.
 Furthermore, due to the limited availablility of bandwidth to download data from the satellite, only a fraction \textcolor{red}{What fraction?} of pixels on the \kepler detector are actually downloaded, these being allocated via a competitive proposal process.
@@
 
-\citet{orig_smear} noted that there is a way to obtain photometry of every target on-silicon in \kepler using a data channel normally used for calibration, even if active pixels were not allocated and downloaded.
-\kepler employs an inter-line transfer CCD as its detector, which successively shuffles each row of pixels down to the edges of the chip where they are ultimately read out.
-Because the \kepler camera lacks a shutter, the detector is exposed to light during the readout process, with the result that fluxes in each pixel are biased up by light collected from objects in the same column.
+\citet{orig_smear} noted a way to obtain photometry of every target on-silicon in \kepler using a data channel normally used for calibration, even if active pixels were not allocated and downloaded.
+\kepler employs an inter-line transfer CCD as its detector, which successively shuffles each row of pixels down to the edges of the chip to be read out.
+Because the \kepler camera lacks a shutter, the detector is exposed to light during the readout process, with the result that fluxes in each pixel are contaminated by light collected from objects in the same column.
 This is a particularly serious issue for faint objects in the same detector column as brighter stars, and it is important to calibrate this at each readout stage.
-Six rows of blank `masked' pixels are allocated in each column to measure the smear bias; furthermore, six `virtual' rows are recorded at the end of the readout, with the result that twelve rows of pixels sample the smear bias in each column.
+Six rows of blank `masked' pixels were allocated in each column to measure the smear bias; furthermore, six `virtual' rows were recorded at the end of the readout, with the result that twelve rows of pixels sample the smear bias in each column.
 \citet{orig_smear} realized that these encode the light curves of bright targets in a 1D projection of the star field.
-The masked and virtual smear registers each receive $\sim 1/1034$ of the incident flux in each column; if this is dominated by the light from a single star, the flux combining both smear registers is equivalent to that of a star $\sim 6.8$~times fainter.
+The masked and virtual smear registers each receive $\sim 1/1034$ of the incident flux in each column.
+If this is dominated by the light from a single star, the flux combining both smear registers is equivalent to that of a star $\sim 6.8$~times fainter.
 
 In \citet{smear}, we demonstrated a method for extracting precise light curves of bright stars in \kepler and K2, and presented light curves of a small number of variable stars as examples to illustrate this method.
-In this Paper we present light curves of all unobserved or significantly under-observed stars brighter than $Kp=9$ in the \kepler field.
-This sample is biased towards red giants and hot stars, containing only a few FG dwarfs.
-We find no transiting planets, but detect \textcolor{red}{$M$}~new eclipsing binaries, and solar-like oscillations in \textcolor{red}{$N$}~red giants.
+In this paper we present smear light curves of all unobserved or significantly under-observed stars brighter than $Kp=9$ in the \kepler field.
+This sample mostly consists of red giants and hot stars, containing only a few FG dwarfs.
+We find no transiting planets, but detect \textcolor{red}{$M$}~new eclipsing binaries, and measure solar-like oscillations in 34~red giants.
 We do not model hot stars or FG dwarfs in great detail, but provide some discussion and initial classification of interesting variability.
 For eclipsing binaries, we present the results of light-curve modelling to precisely determine their parameters.
-Finally, for the oscillating red giants, which constitute the bulk of the sample, we determine the asteroseismic parameters \numax and \Dnu, and therefore stellar masses and \logg measurements; and we and obtain high-resolution spectroscopy with the Tillinghast Reflector \'{E}chelle Spectrograph (TRES), from whose spectra we derive stellar parameters and elemental abundances constrained by asteroseismic parameters.
+For the oscillating red giants that constitute the bulk of the sample, we determine the asteroseismic parameters \numax and \Dnu, and therefore stellar masses and \logg measurements; and we and obtain high-resolution spectroscopy with the Tillinghast Reflector \'{E}chelle Spectrograph (TRES), from whose spectra we derive stellar parameters and elemental abundances constrained by asteroseismic parameters.
 We discuss the potential for these as benchmark stars for other stellar surveys, in particular \gaia.

### 2018-08-20 paper/ms.tex
more tim edits

@@
 
-In this Section we will discuss the methods used for characterizing our new benchmark stars.
 We have obtained smear light curves for our sample of red giant stars with the \texttt{keplersmear} pipeline as described in Section~\ref{photometry}, performed asteroseismology on all of these to extract \numax and therefore \logg as described in Section~\ref{asteroseismology}, and combined these with TRES spectra to obtain chemical abundances as described in Section~\ref{spectroscopy}.
@@
 
-We selected as our sample all stars on-silicon in \kepler with $Kp<9$ which were unobserved for more than $8$ quarters, including those stars which were entirely unobserved.
-A number of these lay just at the edge of a detector, with the result that in some cadences the centroid of the star did not lie on the chip; light curves from these targets were found to be of extremely low quality and all of these objects were discarded.
+We selected as our sample all stars on-silicon in \kepler with $Kp<9$ that were targeted for fewer than $8$ quarters, including those stars that were entirely unobserved.
+A number of these lay at the edge of a detector, with the result that in some cadences the centroid of the star did not lie on the chip; light curves from these targets were found to be of extremely low quality and all of these objects were discarded.
 After applying these criteria we obtained a list of 102 targets, which are listed in Table~\ref{all_stars} in order of their \kepler magnitude $Kp$ together with their spectral type from SIMBAD, \gaia~DR2 source identifiers, apparent~$G$ magnitudes and distances from \citet{gaiadists}, the quarters for which the stars were observed, and whether spectroscopy is available as in Section~\ref{spectroscopy} and Table~\ref{stellar_props}.

### 2018-08-23 paper/ms.tex
equations
addition to paper chemical part with new plots

@@
 \label{scaling}
-\numax \propto \dfrac{g}{g_{\sun}} \cdot \dfrac{\teff}{\teff_{\sun}}^{\dfrac{1}{2}}
+\numax \propto \dfrac{g}{g_{\sun}} \cdot \left(\dfrac{\teff}{\teff_{\sun}}\right)^{\dfrac{1}{2}}
 \end{equation}
@@
 \begin{equation}
-\langle \Dnu \rangle \propto \sqrt{\langle \rho \rangle} = \sqrt{\dfrac{M}{\msun} (\dfrac{R}{\rsun})^{-3}}
+\langle \Dnu \rangle \propto \sqrt{\langle \rho \rangle} = \sqrt{\dfrac{M}{\msun} \left(\dfrac{R}{\rsun}\right)^{-3}}
 \end{equation}
@@
 The reported abundances are the median [X/Fe] value of the various line regions for a given element.
+{ \bf Ben: Maybe remove this if we do not actually implement line-by-line differential; Do we have a TRES Arcturus spectrum.} Abundance uncertainties reported are the standard error in the line-by-line abundance ratios.
+Where only one line exists for a given element, we conservatively assume the standard error is 0.10~dex.
+In principle, these uncertainties are underestimated because there they do not include the errors driven by imperfect stellar parameter values and other systematic errors arising from incorrect line list data upon other things.
+We do note, however, thus use of asteroseismology really reduces the uncertainties caused by the stellar parameters \citep[see][for a longer discussion on this]{hawkinsapogee}.
 To achieve the most precise abundances we have derived them using  both with and without a line-by-line differential approach with respect to Arcturus ($\alpha$~Bo\"{o}tis) using the method described by \citet{gaiabenchmark4} and the Arcturus abundances from \citep{hawkinsapogee}.
@@
 \label{chemical}
-place [X/Fe] vs [Fe/H] diagrams here and discuss which Galactic populations these stars come from.
+The chemical compositions for each star were measured in the $\alpha$ (Mg, Ti, Si, Ca), odd-Z (Al, Na, Cu, Sc, V), Fe-peak (Fe, Ni, Zn, Co, Cr, Mn), and neutron capture (Sr, Y, Zr, Ba, La, Nd, Eu) elemental families.
+This was done to asses the Galactic populations from which these stars are drawn from.
+The first thing to note is that the metallicity, which are tabulated in Table~\ref{stellar_props}, are to high (with $-0.51<$~[M/H]~$<$ +0.14~dex) to be considered drawn from the Galactic halo, whose peak metallicity is around --1.20 \cite[e.g.][]{Chiba2000}.
+Furthermore, the distance distribution, noted in Table~\ref{all_stars}, indicates that all stars are located within a few~kpc of the Sun and thus are not apart of the Galactic bulge.
+These alone allow us to predict that theses stars are drawn from only the Galactic thick and thin disks.
+We provide a detailed chemical abundance analysis below to support this claim.\\
+{\bf $\alpha$ elements:}\\
+\begin{figure*}
+\noindent\includegraphics[width=\textwidth,keepaspectratio]{Pope_spectra_alphaele.pdf}
+
+\caption{\label{alphael}
+The [Mg/Fe], [Si/Fe], [Ca/Fe], and [Ti/Fe], [Al/Fe], [Na/Fe] abundance ratios as a function of iron on the top and bottom rows, respectively for our stars (black cirlces).
+We also illustrate a representative sample of Galactic disk stars from \citet[open red square,][]{Bensby2014} and \citet[open orange triangles,][]{Adibekyan2012}.
+}
+\end{figure*}
+The $\alpha$ elements are thought to form in  variety ways during internal fusion within a star while it evolves over its life.
+These elements are then largely dispersed into the interstellar medium through Type~II supernovae (SNII) \citep{Matteucci2001}.
+The most important of these diagrams are those including the abundances of the $\alpha$ elements as a function of metallicity.
+It has been shown by many studies \citep[e.g.][and references therein]{Edvardsson1993, Adibekyan2012, Feltzing2013, Bensby2014}, that the Galactic thick disk and thin disk separate in the $\alpha$ elements, where the thick disk is enhanced in [Mg, Si, Ca, Ti/Fe] compared to the Galactic thin disk at a given metallicity.
+In Fig.~\ref{alphael}, we display the [Mg, Si, Ca, Ti/Fe] abundance ratios as a function of [Fe/H] for our stars (black circles) compared\footnote{We note that there are likely systematics between our [X/Fe] abundance scale and those of our comparison samples.
+We do not have the relevant data, which include several stars in common with these studies but observed with the TRES spectrograph, to asses the level of systematics.}  to representative disk stars from \cite[open red square,][]{Bensby2014} and \cite[open orange triangles,][]{Adibekyan2012}.
+
+For most of the stars in our sample, the [Mg, Ti, Ca/Fe] abundance ratios are enhanced.
+The commonly used [$\alpha$/Fe] abundance ratio is the average of Mg, Ti, Si, Ca (thus it is ([Mg/Fe] + [Ca/Fe] + [Si/Fe] + [Ti/Fe] / 4.0) ) is also enhanced in most stars.
+This is consistent with most stars belonging to the Galactic thick disk.
+Though there are a handful of stars where the typical [$\alpha$/Fe] ratio is solar.
+\\ 
+{\bf Odd-Z elements:}\\
+The odd-Z elements Na and Al are also shown in  Fig.~\ref{alphael}. These elements are significantly enhanced 
+\\
+{\bf Fe-peak elements:}\\
+XX
+\\ 
+{\bf Neutron capture elements:}\\
+XX
+
+%place [X/Fe] vs [Fe/H] diagrams here and discuss which Galactic populations these stars come from.
 May also want to discuss how these span the typical Galactic populations and can act as benchmark stars for APOGEE or other large surveys

### 2018-08-24 paper/ms.tex
authors

--- 2018-08-20 paper/ms.tex
@@
 Timothy van Reeth,$^{5,10}$
+David W. Latham,$^{12}$,
+Allyson Bieryla,$^{12}$
 and friends
@@
 $^{10}$Sydney Institute for Astronomy (SIfA), School of Physics, University of Sydney, NSW 2006, Australia\\
-$^{11}$SETI Institute, 189 Bernardo Avenue, Mountain View, CA 94043, USA
+$^{11}$SETI Institute, 189 Bernardo Avenue, Mountain View, CA 94043, USA\\
+$^{12}$Harvard-Smithsonian Center for Astrophysics, Cambridge, MA 02138, USA
 }

### 2018-08-25 paper/ms.tex
astropy

@@
 
-This research made use of NASA's Astrophysics Data System; the SIMBAD database, operated at CDS, Strasbourg, France; the IPython package \citep{PER-GRA:2007}; SciPy \citep{jones_scipy_2001}; and Astropy, a community-developed core Python package for Astronomy \citep{2013A&A...558A..33A}.
+This research made use of NASA's Astrophysics Data System; the SIMBAD database, operated at CDS, Strasbourg, France; the IPython package \citep{PER-GRA:2007}; SciPy \citep{jones_scipy_2001}; and Astropy, a community-developed core Python package for Astronomy \citep{astropy}.
 Some of the data presented in this paper were obtained from the Mikulski Archive for Space Telescopes (MAST).

### 2018-08-27 paper/ms.tex
some latham changes

@@
 Allyson Bieryla,$^{12}$
+Gilbert A. Esquerdo,$^{12}$ %\newauthor
 and friends
@@
 $^{11}$SETI Institute, 189 Bernardo Avenue, Mountain View, CA 94043, USA\\
-$^{12}$Harvard-Smithsonian Center for Astrophysics, Cambridge, MA 02138, USA
+$^{12}$Harvard-Smithsonian Center for Astrophysics, 60 Garden Street, Cambridge, MA 02138, USA
 }
@@
 \begin{abstract}
-Here we present the first data release of the \kepler Smear Campaign, using collateral `smear' data obtained by \kepler to reconstruct light curves of 102~stars too bright to have been otherwise observed.
-We describe the pipeline developed to extract and calibrate these light curves, and show that we attain photometric precision comparable to stars observed ordinarily in the nominal \kepler mission.
+Here we present the first data release of the \kepler Smear Campaign, using collateral `smear' data obtained by \kepler to reconstruct light curves of 102~stars too bright to have been otherwise targeted.
+We describe the pipeline developed to extract and calibrate these light curves, and show that we attain photometric precision comparable to stars analyzed by the standard pipeline in the nominal \kepler mission.
 In this Paper, we focus in particular on a subset of these consisting of 64~red giants for which we detect solar-like oscillations.
-Using high-resolution spectroscopy from the Tillinghast Reflector \'{E}chelle Spectrograph (TRES) together with asteroseismic modelling, we obtain the masses and evolutionary states of~27 of these red giant and red clump stars as benchmarks.
+Using high-resolution spectroscopy from the Tillinghast Reflector \'{E}chelle Spectrograph (TRES) together with asteroseismic modelling, we obtain the stellar densities and derive masses, radii and ages of~34 of these red giant and red clump stars as benchmarks.
 All source code, light curves, TRES spectra, and asteroseismic and stellar parameters are publicly available as a \kepler legacy sample.
@@
 It has yielded the first detection of gravity-mode period spacings in a red giant \citep{rggmodes}, enabling probes of interior rotation of red giants \citep{rggmoderotation} and distinguishing between hydrogen- and helium-burning cores \citep{rggmodehelium}.
-It has also permitted the determination of ages and fundamental parameters of main-sequence stars \citep{silvaages}, including planet-hosting stars \citep{huberplanetages,silvaplanetages,2018MNRAS.479.4786V}, revealing the most ancient known planetary system, dating back to the earliest stages of the galaxy \citep{ancientplanets}.
+It has also permitted the determination of ages and fundamental parameters of main-sequence stars as cool as the Sun and hotter \citep{silvaages}, including planet-hosting stars \citep{huberplanetages,silvaplanetages,2018MNRAS.479.4786V}, revealing the most ancient known planetary system, dating back to the earliest stages of the galaxy \citep{ancientplanets}.
 By comparing asteroseismic stellar ages to stellar rotation periods, \citet{angusgyro} have shown that gyrochronology models cannot fit the data with a single relation, leading \citet{vansadersgyro} to suggest a qualitative change in dynamo mechanism as stars age through the main sequence.
@@
 Likewise by combining with spectroscopy, \citet{hawkinsapogee} have been able to produce a large sample of stars with precise elemental abundances by fitting spectroscopic data with \logg and \teff fixed to asteroseismically-determined values.
-It is necessary to calibrate such a study against benchmark stars with very precisely-determined parameters, which in practice means requires nearby bright stars that are amenable to very high signal-to-noise spectroscopy plus asteroseismology \citep{creeveybenchmark},  parallaxes \citep{hawkinsbenchmarks}, and/or interferometry \citep{casagrandebenchmark,creeveybenchmark2}.
+It is necessary to calibrate such a study against benchmark stars with very precisely-determined parameters, which in practice requires nearby bright stars that are amenable to very high signal-to-noise spectroscopy plus asteroseismology \citep{creeveybenchmark}, parallaxes \citep{hawkinsbenchmarks}, and/or interferometry \citep{casagrandebenchmark,creeveybenchmark2}.
 This is especially important in the context of the \gaia mission \citep{gaia}, which has recently put out its second data release of 1,692,919,135 sources, including 1,331,909,727 with parallaxes \citep{gaiadr2}.
 These data will form the basis of many large surveys and it is vital that they are calibrated correctly.
-To this end, 34~FGK stars have been chosen as \gaia-ESO benchmark stars for which metallicities \citep{gaiabenchmark1}, effective temperatures and surface gravities \citep{gaiabenchmark3}, and relative abundances of $\alpha$ and iron-peak elements \citep{gaiabenchmark4} have been determined.
+To this end, 34~FGK stars including both giants and dwarfs have been chosen as \gaia-ESO benchmark stars for which metallicities \citep{gaiabenchmark1}, effective temperatures and asteroseismic surface gravities \citep{gaiabenchmark3}, and relative abundances of $\alpha$ and iron-peak elements \citep{gaiabenchmark4} have been determined.
+This includes only four main sequence stars much cooler than the Sun, due to the paucity of such stars with asteroseismology.
 This has been accompanied by the release of high resolution spectra \citep{gaiabenchmark2} and formed the basis of extensions to lower metallicities \citep{gaiabenchmark5}, stellar twin studies \citep{gaiabenchmarktwins} and comparisons of stellar abundance determination pipelines \citep{gaiabenchmarkabundances}.
 
-Brighter \kepler stars are therefore ideal benchmark targets, since photometry can be most easily complemented by \hipparcos parallaxes, interferometric diameters, and high resolution spectroscopy.  
-Unfortunately, the \kepler field was deliberately placed to minimize overall the number of saturated stars, so that only a dozen stars brighter than~6th~magnitude landed on silicon \citep{2010ApJ...713L..79K}.
-This was because stars brighter than $Kp \sim 11$ saturate the CCD detector, spilling electrons up and down their column on the CCD and rendering those pixels otherwise unusable.
-Furthermore, due to the limited availablility of bandwidth to download data from the satellite, only a fraction \textcolor{red}{What fraction?} of pixels on the \kepler detector are actually downloaded, these being allocated via a competitive proposal process.
+Brighter \kepler stars are therefore ideal benchmark targets, since photometry can be most easily complemented by \gaia parallaxes, interferometric diameters, and high resolution spectroscopy.  
+Unfortunately, the \kepler field was deliberately placed to minimize overall the number of extremely bright stars on the detectors, so that only a dozen stars brighter than~6th~magnitude landed on silicon \citep{2010ApJ...713L..79K}.
+This was because stars brighter than $Kp \sim 11$ saturate the CCD detectors, with their flux distributed along a bleed column and rendering those pixels otherwise unusable.
+Furthermore, due to the limited availablility of bandwidth to download data from the satellite, only a fraction \textcolor{red}{What fraction?} of pixels on the \kepler detectors are actually downloaded.
 The result of these two target selection constraints is that photometry was obtained for only \textcolor{red}{a small number} of saturated stars in the \kepler field, while many bright targets were ignored.
@@
 For the oscillating red giants that constitute the bulk of the sample, we determine the asteroseismic parameters \numax and \Dnu, and therefore stellar masses and \logg measurements; and we and obtain high-resolution spectroscopy with the Tillinghast Reflector \'{E}chelle Spectrograph (TRES), from whose spectra we derive stellar parameters and elemental abundances constrained by asteroseismic parameters.
-We discuss the potential for these as benchmark stars for other stellar surveys, in particular \gaia.
+These asteroseismic constraints can be compared to those from \gaia, offering the opportunity both to test asteroseismic scaling relations and combine both datasets to refine the benchmark star properties further.
 
@@
 
-We selected as our sample all stars on-silicon in \kepler with $Kp<9$ that were targeted for fewer than $8$ quarters, including those stars that were entirely unobserved.
+We selected as our sample all stars on-silicon in \kepler with $Kp<9$ that were targeted for fewer than an arbitrary $8$ quarters, including those stars that were entirely unobserved.
 A number of these lay at the edge of a detector, with the result that in some cadences the centroid of the star did not lie on the chip; light curves from these targets were found to be of extremely low quality and all of these objects were discarded.
-After applying these criteria we obtained a list of 102 targets, which are listed in Table~\ref{all_stars} in order of their \kepler magnitude $Kp$ together with their spectral type from SIMBAD, \gaia~DR2 source identifiers, apparent~$G$ magnitudes and distances from \citet{gaiadists}, the quarters for which the stars were observed, and whether spectroscopy is available as in Section~\ref{spectroscopy} and Table~\ref{stellar_props}.
+After applying these criteria we obtained a list of 102 targets, which are listed in Table~\ref{all_stars} in order of their \kepler magnitude $Kp$ together with their spectral type from SIMBAD, \gaia~DR2 source identifiers, apparent~$G$ magnitudes and distances from \citet{gaiadists}, the quarters for which the stars were observed, and whether spectroscopy is available in Section~\ref{spectroscopy} and Table~\ref{stellar_props}.
 The \kepler satellite rotates between quarters, so that it cycles through four orientation `seasons' each rotated from the last by $90^{\circ}$.

### 2018-08-27 paper/ms.tex
edits

@@
 This was because stars brighter than $Kp \sim 11$ saturate the CCD detectors, with their flux distributed along a bleed column and rendering those pixels otherwise unusable.
-Furthermore, due to the limited availablility of bandwidth to download data from the satellite, only a fraction \textcolor{red}{What fraction?} of pixels on the \kepler detectors are actually downloaded.
+Furthermore, due to the limited availablility of bandwidth to download data from the spacecraft, only a fraction \textcolor{red}{What fraction?} of pixels on the \kepler detectors are actually downloaded.
 The result of these two target selection constraints is that photometry was obtained for only \textcolor{red}{a small number} of saturated stars in the \kepler field, while many bright targets were ignored.
@@
 After applying these criteria we obtained a list of 102 targets, which are listed in Table~\ref{all_stars} in order of their \kepler magnitude $Kp$ together with their spectral type from SIMBAD, \gaia~DR2 source identifiers, apparent~$G$ magnitudes and distances from \citet{gaiadists}, the quarters for which the stars were observed, and whether spectroscopy is available in Section~\ref{spectroscopy} and Table~\ref{stellar_props}.
-The \kepler satellite rotates between quarters, so that it cycles through four orientation `seasons' each rotated from the last by $90^{\circ}$.
+The \kepler spacecraft rotates between quarters, so that it cycles through four orientation `seasons' each rotated from the last by $90^{\circ}$.
 Some stars did not land on silicon for all seasons: we have only one season of HD~179394; two for HD~187277, HD~226754, V554~Lyr, and BD+47~2891; and three for BD+43~3064.
@@
 This is especially true in doing asteroseismology of red giants, where the low-amplitude stochastically-excited oscillations can be washed out in a power spectrum by the coherent high amplitude variations of a classical pulsator, even if the background star is much fainter.
-We can assess the importance of this contamination by considering the differences between odd and even quarters: because the \kepler satellite rotates $90^{\circ}$ between successive quarters, any contaminant will lie in the same column as a smear target only every second quarter, falling in the other quarters in the same row but not necessarily the same column.
+We can assess the importance of this contamination by considering the differences between odd and even quarters: because the \kepler spacecraft rotates $90^{\circ}$ between successive quarters, any contaminant will lie in the same column as a smear target only every second quarter, falling in the other quarters in the same row but not necessarily the same column.
 We have therefore generated Lomb-Scargle periodograms \citep{lomb,scargle} of each light curve, clipped for outliers, and considering only odd and even quarters, and visually inspected these for significant differences.

### 2018-08-27 paper/ms.tex
phrasing

@@
 Some stars did not land on silicon for all seasons: we have only one season of HD~179394; two for HD~187277, HD~226754, V554~Lyr, and BD+47~2891; and three for BD+43~3064.
-Aside from the restriction on stars falling on the edge of a chip like this or otherwise, the addition of our sample to the conventionally-observed stars makes the \kepler survey magnitude-complete down to $Kp=9$.
+\textcolor{red}{Aside from the restriction on stars falling on the edge of a chip}, the addition of our sample to the conventionally-observed stars makes the \kepler survey magnitude-complete down to $Kp=9$.
 
-In Figure~\ref{hrdiagram} we show these stars on a colour-magnitude diagram in \gaia $Bp-Rp$ and absolute~$G$ magnitudes using \gaia~DR2 calibrated distances from \citet{gaiadists}, and situate these in context with the entire \kepler sample from the Bedell \url{gaia-kepler.fun} crossmatch.
+In Figure~\ref{hrdiagram} we show these stars on a colour-magnitude diagram in \gaia $Bp-Rp$ and absolute~$G$ magnitudes using \gaia~DR2 calibrated distances from \citet{gaiadists}, overlaid on the \kepler sample from the Bedell \url{gaia-kepler.fun} crossmatch.
 The smear targets in this diagram appear to have not merely higher apparent brightnesses than the general \kepler population, but also higher intrinsic luminosities.

### 2018-08-27 paper/ms.tex
phrasing

@@
 \caption{\label{hrdiagram}
-\gaia colour-magnitude diagram of the Smear Campaign stars (orange and teal) situated in sample of \kepler stars with \gaia parallax $\text{SNR} > 25$ (black), using the Bedell \url{gaia-kepler.fun} crossmatch and \gaia~DR2 calibrated distances from \citet{gaiadists}.
+\gaia colour-magnitude diagram of the Smear Campaign stars (orange and teal) overlaid on the sample of \kepler stars with \gaia parallax $\text{SNR} > 25$ (black), using the Bedell \url{gaia-kepler.fun} crossmatch and \gaia~DR2 calibrated distances from \citet{gaiadists}.
 The smear sample includes giants and hot main-sequence stars.

### 2018-08-27 paper/ms.tex
rearrange slightly

@@
 Allyson Bieryla,$^{12}$
-Gilbert A. Esquerdo,$^{12}$ %\newauthor
+Gilbert A. Esquerdo,$^{12}$\newauthor
 and friends
@@
 A major outcome of the \kepler asteroseismology programme is a legacy sample of extremely well characterized stars that can serve as benchmarks for future work \citep{keplerlegacy1,keplerlegacy2}.
-As well as asteroseismology, by also using optical interferometry, it has been possible to determine fundamental parameters of main-sequence and giant stars with unprecedented precision \citep{huber12,thetacygwhite,white15}.
-Likewise by combining with spectroscopy, \citet{hawkinsapogee} have been able to produce a large sample of stars with precise elemental abundances by fitting spectroscopic data with \logg and \teff fixed to asteroseismically-determined values.
+In conjunction with spectroscopy, \citet{hawkinsapogee} have been able to produce a large sample of stars with precise elemental abundances by fitting spectroscopic data with \logg and \teff fixed to asteroseismically-determined values.
 It is necessary to calibrate such a study against benchmark stars with very precisely-determined parameters, which in practice requires nearby bright stars that are amenable to very high signal-to-noise spectroscopy plus asteroseismology \citep{creeveybenchmark}, parallaxes \citep{hawkinsbenchmarks}, and/or interferometry \citep{casagrandebenchmark,creeveybenchmark2}.
@@
 This has been accompanied by the release of high resolution spectra \citep{gaiabenchmark2} and formed the basis of extensions to lower metallicities \citep{gaiabenchmark5}, stellar twin studies \citep{gaiabenchmarktwins} and comparisons of stellar abundance determination pipelines \citep{gaiabenchmarkabundances}.
+Furthermore, by combining asteroseismology with optical interferometry, it has been possible to determine fundamental parameters of main-sequence and giant stars with unprecedented precision \citep{huber12,thetacygwhite,white15}.
 

### 2018-08-27 paper/ms.tex
sign error

@@
 We identify the evolutionary state of objects in the main sequence versus evolved stars first from the \gaia colour-magnitude diagram in Figure~\ref{hrdiagram}.
-Taking a cutoff in \gaia $Bp-Rp < 1$, we identify 64 of these objects as clearly evolved systems, and the remaining~38 lie apparently on the main sequence.
+Taking a cutoff in \gaia $Bp-Rp > 1$, we identify 64 of these objects as clearly evolved systems, and the remaining~38 lie apparently on the main sequence.
 

### 2018-08-27 paper/ms.tex
careful re definition

@@
 While~64 red giants have been identified in this sample, for some of these, by visual inspection it is clear that the timescale of their variability is of the same order as a \kepler quarter and they are thus badly affected by systematics and systematics correction.
-From the 35 giants for which there is shorter-timescale variability, we have attempted to extract the asteroseismic parameters \numax and $\langle \Dnu \rangle$ \citep{KB95,2013ARA&A..51..353C}.
-These constrain fundamental stellar parameters independently from spectroscopic or interferometric measurements:
+From the 34 giants for which there is high-SNR shorter-timescale variability, we have attempted to extract the asteroseismic parameters \numax and $\langle \Dnu \rangle$ \citep{KB95,2013ARA&A..51..353C}.
+These constrain fundamental stellar parameters as through these scaling relations:
 

### 2018-08-27 paper/ms.tex
typo

@@
 
-For eight stars, we find that the asteroseismic fit is unsatisfactory: for BD+39~388 we cannot detect the expected oscillations; BD+43~3064 there are significant peaks but these are not consistent with the pattern expected from a red giant; for HD~179959 and HD~187217 we suspect contamination with the oscillations of a second giant, which is hard to remove from smear light curves; while for HD~188629, HD~188639 and HD~188875 we can extract a \numax but not a robust \Dnu.
+For eight stars, we find that the asteroseismic fit is unsatisfactory: for BD+39~388 we cannot detect the expected oscillations; for BD+43~3064 there are significant peaks but these are not consistent with the pattern expected from a red giant; for HD~179959 and HD~187217 we suspect contamination with the oscillations of a second giant, which is hard to remove from smear light curves; while for HD~188629, HD~188639 and HD~188875 we can extract a \numax but not a robust \Dnu.
 One star in our sample, the retired~A star HD~185351, has a mode envelope that is not well fit by our model.

### 2018-08-27 paper/ms.tex
oops

@@
 Operating with spectral resolving power $R=44 000$, we obtain signal-to-noise ratios of tens to hundreds per resolution element.
-We note that this resolution and SNR are sufficient for an exploratory study, but for more detailed analysis it will be desirable to use APOGEE or similar instruments at higher resolution and SNR.
-From this observing run we have~35 unique targets with seismic \logg and spectra, one more star than the \gaia-ESO benchmark set and a significant addition to the ensemble of bright red giants with asteroseismic parameter determinations.
-These are unfortunately not the same~35 unique targets as for the asteroseismic analysis presented above in Section~\ref{asteroseismology}: due to observing constraints, we were unable to obtain spectra for BD+42~315, BD+48~290, HD~176209, HD~182354, HD~189636, or HD~189750.
+We note that this resolution and SNR are sufficient for an exploratory study, but for more detailed analysis it will be desirable to use APOGEE or similar instruments to obtain greater spectral coverage.
+From this observing run we have~34 unique targets with seismic \logg and spectra, one more star than the \gaia-ESO benchmark set and a significant addition to the ensemble of bright red giants with asteroseismic parameter determinations.
+These are unfortunately not the same~34 unique targets as for the asteroseismic analysis presented above in Section~\ref{asteroseismology}: due to observing constraints, we were unable to obtain spectra for BD+42~315, BD+48~290, HD~176209, HD~182354, HD~189636, or HD~189750.
 

### 2018-08-27 paper/ms.tex
full numbers

@@
 From this observing run we have~34 unique targets with seismic \logg and spectra, one more star than the \gaia-ESO benchmark set and a significant addition to the ensemble of bright red giants with asteroseismic parameter determinations.
-These are unfortunately not the same~34 unique targets as for the asteroseismic analysis presented above in Section~\ref{asteroseismology}: due to observing constraints, we were unable to obtain spectra for BD+42~315, BD+48~290, HD~176209, HD~182354, HD~189636, or HD~189750.
+These are unfortunately not the same~34 unique targets as for the asteroseismic analysis presented above in Section~\ref{asteroseismology}: due to observing constraints, we were unable to obtain spectra for BD+42~3150, BD+48~2904, HD~176209, HD~182354, HD~189636AB, or HD~189750.
 

### 2018-08-27 paper/ms.tex
phrasing

@@
 Where only one line exists for a given element, we conservatively assume the standard error is 0.10~dex.
-In principle, these uncertainties are underestimated because there they do not include the errors driven by imperfect stellar parameter values and other systematic errors arising from incorrect line list data upon other things.
+In principle, these uncertainties are underestimated because there they do not include the errors driven by imperfect stellar parameter values and other systematic errors arising, for instance, from incorrect line list data.
 We do note, however, thus use of asteroseismology really reduces the uncertainties caused by the stellar parameters \citep[see][for a longer discussion on this]{hawkinsapogee}.

### 2018-08-27 paper/ms.tex
globular cluster metallicity?

@@
 The chemical compositions for each star were measured in the $\alpha$ (Mg, Ti, Si, Ca), odd-Z (Al, Na, Cu, Sc, V), Fe-peak (Fe, Ni, Zn, Co, Cr, Mn), and neutron capture (Sr, Y, Zr, Ba, La, Nd, Eu) elemental families.
-This was done to asses the Galactic populations from which these stars are drawn from.
-The first thing to note is that the metallicity, which are tabulated in Table~\ref{stellar_props}, are to high (with $-0.51<$~[M/H]~$<$ +0.14~dex) to be considered drawn from the Galactic halo, whose peak metallicity is around --1.20 \cite[e.g.][]{Chiba2000}.
+This was done to asses the Galactic populations from which these stars are drawn.
+The first thing to note is that the metallicities, which are tabulated in Table~\ref{stellar_props}, are too high (with $-0.51<$~[M/H]~$<$ +0.14~dex) to be considered drawn from the Galactic halo, whose peak metallicity is around $\sim -1.50$ \cite[e.g.][]{Chiba2000}.
 Furthermore, the distance distribution, noted in Table~\ref{all_stars}, indicates that all stars are located within a few~kpc of the Sun and thus are not apart of the Galactic bulge.

### 2018-08-27 paper/ms.tex
typo
exofop

@@
 Furthermore, the distance distribution, noted in Table~\ref{all_stars}, indicates that all stars are located within a few~kpc of the Sun and thus are not apart of the Galactic bulge.
-These alone allow us to predict that theses stars are drawn from only the Galactic thick and thin disks.
+These alone allow us to predict that these stars are drawn from only the Galactic thick and thin disks.
 We provide a detailed chemical abundance analysis below to support this claim.\\
@@
 All smear light curves, both including the red giant sample studied in detail in Section~\ref{rgs}, and main sequence stars as discussed in Sections~\ref{pulsators} and~\ref{ebs}, can be downloaded from the Mikulski Archive for Space Telescopes (MAST) as a High-Level Science Product.
-TRES spectra are available from \textcolor{red}{somewhere}, and all asteroseismic parameters and derived stellar parameters for the red giants in Section~\ref{rgs} are provided in an online-only table as Supplementary Material to this paper.
+TRES spectra will be made available from the ExoFOP-TESS website, and all asteroseismic parameters and derived stellar parameters for the red giants in Section~\ref{rgs} are provided in an online-only table as Supplementary Material to this paper.
 

### 2018-08-29 paper/ms.tex
lpv section init
Revert "typo"
This reverts commit 431b81bedd3f5d8f3f3bb40cb8bcbcbffe43756f.

@@
 Furthermore, the distance distribution, noted in Table~\ref{all_stars}, indicates that all stars are located within a few~kpc of the Sun and thus are not apart of the Galactic bulge.
-These alone allow us to predict that these stars are drawn from only the Galactic thick and thin disks.
+These alone allow us to predict that theses stars are drawn from only the Galactic thick and thin disks.
 We provide a detailed chemical abundance analysis below to support this claim.\\
@@
 
+\subsubsection{Long Period Variables}
+\label{lpvs}
+
 \subsection{Main Sequence Stars}
@@
 acknowledges support by the Australian Research Council's Discovery Projects funding scheme (project number DE140101364) and support by the NASA Grant NNX14AB92G issued through the \emph{Kepler} Participating Scientist Program.
+DWL acknowledges partial support from the Kepler Extended Mission under NASA Cooperative Agreement NNX13AB58A with the Smithsonian Astrophysical Observatory.
 

### 2018-08-29 paper/ms.tex
no observed col

@@
 
-We selected as our sample all stars on-silicon in \kepler with $Kp<9$ that were targeted for fewer than an arbitrary $8$ quarters, including those stars that were entirely unobserved.
+We selected as our sample all stars on-silicon in \kepler with $Kp<9$ that were targeted for fewer than an arbitrary $8$ quarters, the majority of which were previously entirely missing.
+Sixteen stars were to some extent observed conventionally: HD~174020 was targeted in LC for Q2, 6, 10, and 14; HD~175841 for Q11-12, 14-16, with SC for Q3; HD~176582 for Q12-13; HD~178090 for Q1, 3, and 10; HD~180682 for Q0, 3, and 7; HD~181069 for Q1, 10, 13, 14, and 17; HD~181878 for Q14-17; HD~182694 for Q2; HD~183124 for even quarters; HD~185351 for Q1-3 and with SC for Q16; HD~186155 for only Q1; HD~187217 for Q14-17; HD~188252 for only Q13; HD~189013 with SC for Q3 as a $\gamma$~Dor; V380~Cyg for Q11 and with SC for Q7, 9, 10, 12-17; and V819~Cyg for Q14, 16 and 17.
 A number of these lay at the edge of a detector, with the result that in some cadences the centroid of the star did not lie on the chip; light curves from these targets were found to be of extremely low quality and all of these objects were discarded.

### 2018-08-29 paper/ms.tex
note TRES spectra with tick mark
m giant and odd/even illustration

@@
 In the great majority of cases they closely resemble one another, indicating that contamination is at worst a minor effect.
-In the case of HD~181878, a red giant, there is clear and significant contamination from a $\delta$~Scuti variable, as is seen in Figure~\ref{contamination}.
+In the case of HD~181878, a red giant, there is clear and significant contamination from an M~giant, as is seen in Figure~\ref{contamination}.
 
@@
 Power spectra of odd and even quarters of HD~181778.
-It is clear from inspection that while odd quarters have the power spectrum expected of a giant star, even quarters have very high amplitude coherent oscillations typical of a $\delta$~Scuti variable.}
+It is clear from inspection that while odd quarters have the power spectrum expected of a giant star, even quarters have very high amplitude coherent oscillations typical of an M~giant.}
 \end{figure}

### 2018-09-04 paper/ms.tex
jofre author

@@
 Gilbert A. Esquerdo,$^{12}$\newauthor
+Paula Jofr\'{e},$^{13}$
 and friends
@@
 $^{11}$SETI Institute, 189 Bernardo Avenue, Mountain View, CA 94043, USA\\
-$^{12}$Harvard-Smithsonian Center for Astrophysics, 60 Garden Street, Cambridge, MA 02138, USA
+$^{12}$Harvard-Smithsonian Center for Astrophysics, 60 Garden Street, Cambridge, MA 02138, USA\\
+$^{13}$N\'{u}cleo de Astronom\'{i}a, Facultad de Ingenier\'{i}a y Ciencias, Universidad Diego Portales, Ej\'{e}rcito 441, Santiago De, Chile
 }
@@
 By comparing asteroseismic stellar ages to stellar rotation periods, \citet{angusgyro} have shown that gyrochronology models cannot fit the data with a single relation, leading \citet{vansadersgyro} to suggest a qualitative change in dynamo mechanism as stars age through the main sequence.
+\newpage
 

### 2018-09-06 paper/ms.tex
some edits

@@
 % Beyond searching for planets, 
-\kepler has revolutionized the field of asteroseismology for solar-like oscillations \citep{2010PASP..122..131G}.
-It has yielded the first detection of gravity-mode period spacings in a red giant \citep{rggmodes}, enabling probes of interior rotation of red giants \citep{rggmoderotation} and distinguishing between hydrogen- and helium-burning cores \citep{rggmodehelium}.
+\kepler has revolutionized the field of asteroseismology for solar-like oscillations \citep{2010PASP..122..131G,2010ApJ...713L.169C}.
+It has yielded the detection of gravity-mode period spacings in a red giant \citep{rggmodes,2014A&A...572L...5M}, enabling probes of interior rotation of red giants \citep{rggmoderotation,2012A&A...548A..10M} and distinguishing between hydrogen- and helium-burning cores \citep{rggmodehelium,2012A&A...540A.143M}.
 It has also permitted the determination of ages and fundamental parameters of main-sequence stars as cool as the Sun and hotter \citep{silvaages}, including planet-hosting stars \citep{huberplanetages,silvaplanetages,2018MNRAS.479.4786V}, revealing the most ancient known planetary system, dating back to the earliest stages of the galaxy \citep{ancientplanets}.
@@
 For eclipsing binaries, we present the results of light-curve modelling to precisely determine their parameters.
-For the oscillating red giants that constitute the bulk of the sample, we determine the asteroseismic parameters \numax and \Dnu, and therefore stellar masses and \logg measurements; and we and obtain high-resolution spectroscopy with the Tillinghast Reflector \'{E}chelle Spectrograph (TRES), from whose spectra we derive stellar parameters and elemental abundances constrained by asteroseismic parameters.
+For the oscillating red giants that constitute the bulk of the sample, we determine the asteroseismic parameters \numax and \Dnu, and therefore stellar masses and \logg measurements.
+We have also obtained high-resolution optical spectroscopy of 63~objects, predominantly giants, with the Tillinghast Reflector \'{E}chelle Spectrograph (TRES).
+For the~34 stars with both spectroscopy and asteroseismic parameters we derive fundamental stellar parameters and elemental abundances.
 These asteroseismic constraints can be compared to those from \gaia, offering the opportunity both to test asteroseismic scaling relations and combine both datasets to refine the benchmark star properties further.
@@
 In the case of HD~181878, a red giant, there is clear and significant contamination from an M~giant, as is seen in Figure~\ref{contamination}.
+Likewise HD~183383 shows two different stars, depending on the quarter: some parts are likely from an ellipsoidal variable with a period of 6.46 days, other parts are from an RR Lyrae pulsator.
 

### 2018-09-06 paper/ms.tex
hawkins is apokasc

@@
 A major outcome of the \kepler asteroseismology programme is a legacy sample of extremely well characterized stars that can serve as benchmarks for future work \citep{keplerlegacy1,keplerlegacy2}.
-In conjunction with spectroscopy, \citet{hawkinsapogee} have been able to produce a large sample of stars with precise elemental abundances by fitting spectroscopic data with \logg and \teff fixed to asteroseismically-determined values.
+Asteroseismological studies with \kepler complement other probes of stellar physics well: for example, the APOKASC sample of~1916 spectroscopically- and asteroseismically-characterized red giant stars \citep{2014ApJS..215...19P}.
+For this APOKASC sample, \citet{hawkinsapogee} have been able to extract precise elemental abundances by fitting spectroscopic data with \logg and \teff fixed to asteroseismically-determined values.
 It is necessary to calibrate such a study against benchmark stars with very precisely-determined parameters, which in practice requires nearby bright stars that are amenable to very high signal-to-noise spectroscopy plus asteroseismology \citep{creeveybenchmark}, parallaxes \citep{hawkinsbenchmarks}, and/or interferometry \citep{casagrandebenchmark,creeveybenchmark2}.

### 2018-09-06 paper/ms.tex
past tense

@@
 A number of these lay at the edge of a detector, with the result that in some cadences the centroid of the star did not lie on the chip; light curves from these targets were found to be of extremely low quality and all of these objects were discarded.
-After applying these criteria we obtained a list of 102 targets, which are listed in Table~\ref{all_stars} in order of their \kepler magnitude $Kp$ together with their spectral type from SIMBAD, \gaia~DR2 source identifiers, apparent~$G$ magnitudes and distances from \citet{gaiadists}, the quarters for which the stars were observed, and whether spectroscopy is available in Section~\ref{spectroscopy} and Table~\ref{stellar_props}.
+After applying these criteria we obtained a list of 102 targets, which are listed in Table~\ref{all_stars} with their \kepler magnitude $Kp$ together with their spectral type from SIMBAD, \gaia~DR2 apparent~$G$ magnitudes and $Bp-Rp$ colours, \gaia~DR2 calibrated distances from \citet{gaiadists}, variability classification and availability of TRES spectroscopy.
 The \kepler spacecraft rotates between quarters, so that it cycles through four orientation `seasons' each rotated from the last by $90^{\circ}$.
@@
 
-In Figure~\ref{hrdiagram} we show these stars on a colour-magnitude diagram in \gaia $Bp-Rp$ and absolute~$G$ magnitudes using \gaia~DR2 calibrated distances from \citet{gaiadists}, overlaid on the \kepler sample from the Bedell \url{gaia-kepler.fun} crossmatch.
+Figure~\ref{hrdiagram} shows these stars on a colour-magnitude diagram in \gaia $Bp-Rp$ and absolute~$G$ magnitudes using \gaia~DR2 calibrated distances from \citet{gaiadists}, overlaid on the \kepler sample from the Bedell \url{gaia-kepler.fun} crossmatch.
 The smear targets in this diagram appear to have not merely higher apparent brightnesses than the general \kepler population, but also higher intrinsic luminosities.
@@
 Regrettably, it is only possible to reconstruct a light curve with the 30~minute long cadence and therefore it is not possible to do asteroseismology on this bright, nearby solar-like star.
-This light curve shows neither rotational modulation (as determined by its featureless autocorrelation) nor evidence of transits.
+This light curve shows neither rotational modulation (as determined by its featureless autocorrelation) nor evidence for transits.
 
-Considering objects lying photometrically on the main sequence, from the \kepler power spectrum we identify solar-like oscillations in HD~182354 and HD~176209 at frequencies consistent with them being subgiants.
+Considering objects lying photometrically on the main sequence, from the \kepler power spectrum we identify solar-like oscillations in HD~182354 and HD~176209 at frequencies consistent with them being subgiants or contaminated with flux from red giants.
 \textcolor{red}{Get frequencies}.
@@
 
-In preparing light curves of the \kepler smear stars, we follow the methods described in \citet{smear}, with some improvements.
-We select using RA and Dec values from the \kepler Input Catalog (KIC) \citep{kic}, and query MAST to find the corresponding mean pixel position for a given \kepler quarter.
-We measure the centroid of smear columns in the vicinity, and use these values to do raw aperture photometry.
-We find that the cosine-bell aperture used for raw photometry in \citet{smear} can in some light curves introduce position-dependent systematics and jumps.
-We instead in this work apply a super-Gaussian aperture, $A \propto \exp{\dfrac{-(x-x_0)}{w} ^ 4}$, where $x_0$ is the centroid and $w$ a width in pixels.
+In preparing light curves of the \kepler smear stars, we have followed the methods described in \citet{smear}, with some improvements.
+We selected our input RA and Dec values from the \kepler Input Catalog (KIC) \citep{kic}, and queried MAST to find the corresponding mean pixel position for a given \kepler quarter.
+We then measured the centroid of smear columns in the vicinity, and used these values to do raw aperture photometry.
+We found that the cosine-bell aperture used for raw photometry in \citet{smear} can in some light curves introduce position-dependent systematics and jumps.
+We instead in this work have applied a super-Gaussian aperture, $A \propto \exp{\dfrac{-(x-x_0)}{w} ^ 4}$, where $x_0$ is the centroid and $w$ a width in pixels.
 The very flat top of this function helps avoid significant variation with position, while still smoothly rolling off at the edges to avoid discontinuous artefacts.
-We calculate this on a grid of $10\,\times$ subsampled points in pixel space so that the sharply varying edge changes column weights smoothly as a function of centroid.
-We extract photometry using apertures with a range of widths $w \in\{1.5,~2,~3,~4,~5\}$ pixels.
+This is calculated on a grid of $10\,\times$ subsampled points in pixel space so that the sharply varying edge changes column weights smoothly as a function of centroid.
+We have then extracted photometry using apertures with a range of widths $w \in\{1.5,~2,~3,~4,~5\}$ pixels.
 
-From this raw photometry we subtract a background light curve, which corrects for time-varying global systematics.
-Whereas in \citet{smear} we then subtract a background estimate chosen manually, for this larger set of light curves, we now choose the lowest $25\%$ of pixels by median flux as being unlikely to be contaminated by stars, and take our background level to be the median of this at each time sample.
+From this raw photometry a background light curve was subtracted, which corrects for time-varying global systematics.
+Whereas in \citet{smear} we subtracted a background estimate chosen manually, for this larger set of light curves, we have now chosen the lowest $25\%$ of pixels by median flux as being unlikely to be contaminated by stars, and taken our background level to be the median of this at each time sample.
 To denoise this, we fit a Gaussian Process with a 30-day timescale squared exponential kernel using \textsc{george} \citep{hodlr}, and our final background light curve is taken to be the posterior mean of this GP.
@@
 The dominant source of residual systematic errors in nominal \kepler time series is a common-mode variation primarily due to thermal changes on board the spacecraft, an issue which is traditionally dealt with by identifying and fitting a linear combination of systematic modes \citep{pdc0,pdc1,pdc2,petigura}.
-We adopt the same approach here, using the \kepler Pre-search Data Conditioning (PDC) Cotrending Basis Vectors (CBVs) available from MAST, finding least-squares fits of  either the first~4 or~8 CBVs to each light curve.
-We note that this can subtract astrophysical signals on long timescales, such that we use and recommend 4~CBV light curves for stars with variability on timescales longer than $\sim 5$ days, but otherwise use the 8~CBV light curves.
+We have adopted the same approach here, using the \kepler Pre-search Data Conditioning (PDC) Cotrending Basis Vectors (CBVs) available from MAST, finding least-squares fits of either the first~4 or~8 CBVs to each light curve.
+This can subtract astrophysical signals on long timescales, such that we use and recommend 4~CBV light curves for stars with variability on timescales longer than $\sim 5$ days, or indeed raw uncorrected lightcurves for stars variable at high amplitude on $\sim$~quarter timescales, but otherwise we recommend the 8~CBV light curves.
 There is some room for improvement here by simultaneously modelling astrophysical and instrumental variations, but this is beyond the scope of this paper.

### 2018-09-06 paper/ms.tex
more text into past tense

@@
 While~64 red giants have been identified in this sample, for some of these, by visual inspection it is clear that the timescale of their variability is of the same order as a \kepler quarter and they are thus badly affected by systematics and systematics correction.
-From the 34 giants for which there is high-SNR shorter-timescale variability, we have attempted to extract the asteroseismic parameters \numax and $\langle \Dnu \rangle$ \citep{KB95,2013ARA&A..51..353C}.
+In Table~\ref{all_stars} we have noted these as `long-period variables' (LPVs), without specifically meaning these are LPVs by a particular astrophysical definition, and they are discussed further in Section~\ref{lpvs}.
+For the~34 giants for which there is high-SNR shorter-timescale variability, we have attempted to extract the asteroseismic parameters \numax and $\langle \Dnu \rangle$ \citep{KB95,2013ARA&A..51..353C}.
 These constrain fundamental stellar parameters as through these scaling relations:
@@
 
-We follow the method of \citet{2016AN....337..774D}, obtaining a Lomb-Scargle periodogram of the smoothed time series according to the method of \citet{2011MNRAS.414L...6G}.
-We then conduct a Markov Chain Monte Carlo fit to this, applying the combined granulation and oscillation model of \citet{2014A&A...570A..41K}, consisting of two Harvey profiles for the granulation \citep{1985ESASP.235..199H}, a Gaussian envelope for the stellar oscillations, and a white noise background for instrumental noise.
-We find that the marginal posterior distribution for the Gaussian envelope is well-approximated by a single Gaussian, and take its median and standard deviation to be our estimates for \numax and its uncertainty.
+We have followed the method of \citet{2016AN....337..774D}, obtaining a Lomb-Scargle periodogram of the smoothed time series according to the method of \citet{2011MNRAS.414L...6G}.
+The posterior distribution of the asteroseismic parameters is obtained with a Markov Chain Monte Carlo fit to the smoothed periodogram, applying the combined granulation and oscillation model of \citet{2014A&A...570A..41K}.
+This consists of two Harvey profiles for the granulation \citep{1985ESASP.235..199H}, a Gaussian envelope for the stellar oscillations, and a white noise background for instrumental noise.
+The marginal posterior distribution for the oscillation envelope is well-approximated by a single Gaussian, and we have taken its median and standard deviation to be our estimates for \numax and its uncertainty.
 
-To estimate \Dnu, we divide the power spectrum through by the granulation and noise models to obtain a signal-to-noise spectrum, and fit a sum of Lorentzians separated by mean large (\Dnu) and small (\dnu) separations to the part of this spectrum in the vicinity of \numax.
+To estimate \Dnu, we have divided the power spectrum through by the granulation and noise models to obtain a signal-to-noise spectrum, and fit a sum of Lorentzians separated by mean large (\Dnu) and small (\dnu) separations to the part of this spectrum in the vicinity of \numax.
 In practice, for this dataset, \dnu is poorly constrained, but mean $\langle \Dnu \rangle$ is typically well-constrained and its posterior marginal distribution is well-represented by a single Gaussian as with \numax.
 
-We obtain good estimates of these asteroseismic parameters for 35 targets, presented in Table~\ref{astero_table}.
-In many of the remainder of cases, we find that the very-low-frequency ($\lesssim 2\muHz$) oscillations are affected by filter artefacts from detrending, and we are not able to obtain good estimates for these stars.
+We obtain good estimates of these asteroseismic parameters for 34 targets, presented in Table~\ref{astero_table}.
+In the remainder of cases, as noted above, we find that the very-low-frequency ($\lesssim 2\muHz$) oscillations are affected by filter artefacts from detrending, and we are not able to obtain good estimates for these stars.
 
-Once \numax has been estimated, we use the asteroseismic scaling relation for \numax \citep[Equation~\ref{scaling};][]{KB95} to estimate \logg in order to inform extraction of chemical abundances from spectra.
-Using the initial spectroscopic estimate of \teff, which is not significantly informed by \numax, we propagate uncertainties in \numax with Monte Carlo sampling.
+Once \numax has been estimated, we have used the asteroseismic scaling relation for \numax \citep[Equation~\ref{scaling};][]{KB95} to estimate \logg in order to inform extraction of chemical abundances from spectra.
+Using the initial spectroscopic estimate of \teff, which is not significantly informed by \numax, uncertainties in \numax are propagated with Monte Carlo sampling.
 
-For eight stars, we find that the asteroseismic fit is unsatisfactory: for BD+39~388 we cannot detect the expected oscillations; for BD+43~3064 there are significant peaks but these are not consistent with the pattern expected from a red giant; for HD~179959 and HD~187217 we suspect contamination with the oscillations of a second giant, which is hard to remove from smear light curves; while for HD~188629, HD~188639 and HD~188875 we can extract a \numax but not a robust \Dnu.
+For eight stars, we have found that the asteroseismic fit is unsatisfactory: for BD+39~388 we cannot detect the expected oscillations; for BD+43~3064 there are significant peaks but these are not consistent with the pattern expected from a red giant; for HD~179959 and HD~187217 we suspect contamination with the oscillations of a second giant, which is hard to remove from smear light curves; while for HD~188629, HD~188639 and HD~188875 we can extract a \numax but not a robust \Dnu.
 One star in our sample, the retired~A star HD~185351, has a mode envelope that is not well fit by our model.
@@
 For the whole red giant sample, we have obtained high-resolution spectroscopy with TRES in order to constrain stellar parameters and elemental abundances.
-Operating with spectral resolving power $R=44 000$, we obtain signal-to-noise ratios of tens to hundreds per resolution element.
-We note that this resolution and SNR are sufficient for an exploratory study, but for more detailed analysis it will be desirable to use APOGEE or similar instruments to obtain greater spectral coverage.
+Operating with spectral resolving power $R=44 000$, we have obtained spectra with signal-to-noise ratios (SNRs) of tens to hundreds per resolution element.
+This resolution and SNR are sufficient for an exploratory study, but for more detailed analysis it will be desirable to use APOGEE or similar instruments to obtain greater spectral coverage.
 From this observing run we have~34 unique targets with seismic \logg and spectra, one more star than the \gaia-ESO benchmark set and a significant addition to the ensemble of bright red giants with asteroseismic parameter determinations.
-These are unfortunately not the same~34 unique targets as for the asteroseismic analysis presented above in Section~\ref{asteroseismology}: due to observing constraints, we were unable to obtain spectra for BD+42~3150, BD+48~2904, HD~176209, HD~182354, HD~189636AB, or HD~189750.
+Due to observing constraints, we were unable to obtain spectra for BD+42~3150, BD+48~2904, HD~176209, HD~182354, HD~189636AB, or HD~189750.
+% figure out this discrepancy?
 
-To derive stellar parameters from our TRES spectra, we initially run the Stellar Parameter Classification \citep[SPC:][]{spc} code to determine \teff and \logg, using the SPC \teff to inform the asteroseismic estimation of \logg from \numax.
+To derive stellar parameters from our TRES spectra, we initially ran the Stellar Parameter Classification \citep[SPC:][]{spc} code to determine \teff and \logg, using the SPC \teff to inform the asteroseismic estimation of \logg from \numax.
 For deriving abundances, \teff is fixed from the results of an initial SPC fit, while \logg is fixed to the seismic values.

### 2018-09-08 paper/ms.tex
venn diagram and conclusions

@@
 \newcommand{\kepler}{\emph{Kepler}\xspace}
+\newcommand{\ktwo}{\emph{K2}\xspace}
 \newcommand{\hipparcos}{\emph{Hipparcos}\xspace}
@@
 The result of these two target selection constraints is that photometry was obtained for only \textcolor{red}{a small number} of saturated stars in the \kepler field, while many bright targets were ignored.
-In the K2 mission \citep{k2early}, very saturated stars have been observed with `halo photometry' using unsaturated pixels in a specially-determined region around bright stars, including the Pleiades \citep{halo}, Aldebaran \citep{aldebaran}, and $\rho$~Leonis \citep{rholeo}.
+In the \ktwo mission \citep{k2early}, very saturated stars have been observed with `halo photometry' using unsaturated pixels in a specially-determined region around bright stars, including the Pleiades \citep{halo}, Aldebaran \citep{aldebaran}, and $\rho$~Leonis \citep{rholeo}.
 Unfortunately, in the legacy \kepler sample, photometry of such saturated stars was rarely attempted.
@@
 
-In \citet{smear}, we demonstrated a method for extracting precise light curves of bright stars in \kepler and K2, and presented light curves of a small number of variable stars as examples to illustrate this method.
+In \citet{smear}, we demonstrated a method for extracting precise light curves of bright stars in \kepler and \ktwo, and presented light curves of a small number of variable stars as examples to illustrate this method.
 In this paper we present smear light curves of all unobserved or significantly under-observed stars brighter than $Kp=9$ in the \kepler field.
@@
 After applying these criteria we obtained a list of 102 targets, which are listed in Table~\ref{all_stars} with their \kepler magnitude $Kp$ together with their spectral type from SIMBAD, \gaia~DR2 apparent~$G$ magnitudes and $Bp-Rp$ colours, \gaia~DR2 calibrated distances from \citet{gaiadists}, variability classification and availability of TRES spectroscopy.
+A Venn diagram of the sample, noting the availablilty of asteroseismic fits Section~\ref{asteroseismology} and spectroscopy (Section~\ref{spectroscopy}) is displayed in Figure~\ref{venn}.
 The \kepler spacecraft rotates between quarters, so that it cycles through four orientation `seasons' each rotated from the last by $90^{\circ}$.
@@
 The smear targets in this diagram appear to have not merely higher apparent brightnesses than the general \kepler population, but also higher intrinsic luminosities.
-While this could simply arise from being selected for their apparent brightness, it is worth considering whether this is because of a bias in their parallax measurements.
+While this could simply arise from being selected for their apparent brightness, it is {}worth considering whether this is because of a bias in their parallax measurements.
 While \gaia parallaxes for very bright stars can be subject to systematic error, we have compared these to those found by \emph{Hipparcos} \citep{vanleeuwen07b}, and found close agreement for the brightest stars, with a scatter that increases with magnitude.
@@
 \end{figure*}
+
+\begin{figure}
+\noindent\includegraphics[width=8cm,keepaspectratio]{venn.png}
+\caption{\label{venn}
+Venn diagram showing the overall structure of the \kepler Smear Campaign sample, showing the subsets for which TRES spectroscopy and asteroseismology are available and their overlap.}
+\end{figure}
+\newpage % hack because the venn diagram doesn't work
 
@@
 
-Two stars in the sample show the `hump-and-spike' morphology in their power spectra (a broad `hump' of low-amplitude oscillations dominated by one high amplitude coherent oscillation): HD~186155 (HR~7495), and HD~183362 (HR~7403), respectively the third brightest and $37^{\text{th}}$-brightest stars on silicon and the brightest two stars that show this effect.
+Two stars in the sample show the `hump-and-spike' morphology in their power spectra (a broad `hump' of low-amplitude oscillations dominated by one high amplitude coherent oscillation toward the high frequency end of this band): HD~186155 (HR~7495), and HD~183362 (HR~7403), respectively the third brightest and $37^{\text{th}}$-brightest stars on silicon and the brightest two stars that show this effect.
 \citet{2018MNRAS.474.2774S} have recently claimed the hump-and-spike power spectra as evidence for Rossby modes.
@@
 \label{conclusions}
+
+The \kepler Smear Campaign establishes a legacy sample of~102 very bright stars, with \kepler light curves that in almost all cases reveal astrophysically interesting variability.
+The virtue of these bright stars is that they can be studied with interferometry, and more easily with spectroscopy than fainter targets, permitting especially detailed characterization.
+We have therefore obtained detailed abundances of a subset of the red giants in this sample, particularly with a view to determining their provenance in the Galactic thick and thin disk populations.
+The science that can be done both with this sample and with this method are, however, considerably broader: while we have not attempted it in this paper, a compelling next step is to use interferometric diameter measurements and to further constrain the red giant parameters, and compare these to the constraints from \gaia.
+Any tension between these measurements will help test and refine the asteroseismic scaling relations, and better models will propagate through to smaller systematic uncertainties in large samples of stars too faint for interferometry.
+Further improvements will be revealed by the detailed modelling of individual oscillation frequencies in these giants to infer interior structure such as convective overshoot, which is at the time of writing an active topic of research.
+For the lower-frequency M~giants classed as LPVs in this paper, extending the systematics correction and quarter-stitching algorithms to more robustly correct their light curves without removing real signal will allow similar asteroseismic analysis, for a sample of stars that are much less well understood than their higher-frequency counterparts.
+
+The \kepler Smear Campaign has another natural extension: while many saturated stars in \ktwo have now been observed with `halo' apertures including their unsaturated pixels, many were not, either because they were fainter than the typical $Kp \lesssim 6.5$ limit, or because in Campaigns~0-3 and~5 no such apertures were selected.
+There is therefore the potential for a \ktwo Smear Campaign to complete the \ktwo sample down to fainter magnitudes, complementing the very brightest stars studied with halo photometry.
 

### 2018-09-10 paper/ms.tex
now has section on classical pulsators

@@
 Timothy R. White,$^{5,8}$\newauthor
-Daniel Huber,$^{9,10,11}$
-Ashley Chontos,$^{9}$
+Timothy R. Bedding,$^{9,5}$
+Allyson Bieryla,$^{10}$
+David W. Latham,$^{10}$,
+Conny Aerts,$^{11,12,13}$\newauthor
+Suzanne Aigrain,$^{3}$ 
+Victoria Antoci,$^{5}$
+Dominic Bowman,$^{11,12,13}$
+Ashley Chontos,$^{9}$\newauthor
+Gilbert A. Esquerdo,$^{10}$
+Daniel Huber,$^{14,15,9}$
+Paula Jofr\'{e},$^{16}$
+Simon Murphy,$^{5,9}$\newauthor
+Timothy van Reeth,$^{5,9}$
 Victor Silva Aguirre,$^{5}$
-Victoria Antoci,$^{5}$\newauthor
-Suzanne Aigrain,$^{3}$ 
-Timothy R. Bedding,$^{10,5}$
-Jie Yu,$^{10,5}$ 
-Amalie Stokholm,$^{5}$\newauthor
-Timothy van Reeth,$^{5,10}$
-David W. Latham,$^{12}$,
-Allyson Bieryla,$^{12}$
-Gilbert A. Esquerdo,$^{12}$\newauthor
-Paula Jofr\'{e},$^{13}$
+Amalie Stokholm,$^{5}$
+Jie Yu,$^{9,5}$ \newauthor
 and friends
@@
 $^{8}$Research School of Astronomy and Astrophysics, Mount Stromlo Observatory, The Australian National University, Canberra, ACT 2611, Australia\\
-$^{9}$Institute for Astronomy, University of Hawai‘i, 2680 Woodlawn Drive, Honolulu, HI 96822, USA\\
-$^{10}$Sydney Institute for Astronomy (SIfA), School of Physics, University of Sydney, NSW 2006, Australia\\
-$^{11}$SETI Institute, 189 Bernardo Avenue, Mountain View, CA 94043, USA\\
-$^{12}$Harvard-Smithsonian Center for Astrophysics, 60 Garden Street, Cambridge, MA 02138, USA\\
-$^{13}$N\'{u}cleo de Astronom\'{i}a, Facultad de Ingenier\'{i}a y Ciencias, Universidad Diego Portales, Ej\'{e}rcito 441, Santiago De, Chile
+$^{9}$Sydney Institute for Astronomy (SIfA), School of Physics, University of Sydney, NSW 2006, Australia\\
+$^{10}$Harvard-Smithsonian Center for Astrophysics, 60 Garden Street, Cambridge, MA 02138, USA\\
+$^{11}$Institute of Astronomy, KU Leuven, Celestijnenlaan 200D, B-3001 Leuven, Belgium\\
+$^{12}$Department of Astrophysics, IMAPP, Radboud University Nijmegen, P.O. Box 9010, 6500 GL Nijmegen, The Netherlands\\
+$^{13}$Kavli Institute for Theoretical Physics, University of California, Santa Barbara, CA 93106, USA\\
+$^{14}$Institute for Astronomy, University of Hawai'i, 2680 Woodlawn Drive, Honolulu, HI 96822, USA\\
+$^{15}$SETI Institute, 189 Bernardo Avenue, Mountain View, CA 94043, USA\\
+$^{16}$N\'{u}cleo de Astronom\'{i}a, Facultad de Ingenier\'{i}a y Ciencias, Universidad Diego Portales, Ej\'{e}rcito 441, Santiago De, Chile\\
 }
@@
 \end{figure}
-\newpage % hack because the venn diagram doesn't work
 
@@
 \label{pulsators}
-The sample contains many $\delta\,\text{Sct}$ and $\gamma\,\text{Dor}$ variables, and several hybrid pulsators. \textcolor{red}{Simon - add text here.}
-Including hotter stars, we also detect SPB pulsations in \textcolor{red}{some stars - Conny/Tim van Reeth?}.
+
+Amongst our sample are pulsating stars of spectral type~B,~A, and~F, with their names, properties and variability class listed in Table~\ref{all_stars}.
+The coherent g-mode pulsations in samples of B, A, and F stars observed by \kepler previously showed these stars to be near-rigid rotators \citep{kurtz2014,saio15,triana15,vanreeth15,vanreeth16,vanreeth18,murphy16,schmid16,moravveji16,ouazzani17,papics17,aerts17,szewczuk18}.
+These studies cover about 70 stars so far.
+However, the vast majority of intermediate-mass stars observed by Kepler have yet to be subjected to in-depth asteroseismic analyses and modelling of their interior properties.
+One of the valuable outputs of our current work includes the reduced light curves of several early-B stars, which were only scarcely targeted in the nominal \kepler mission.
+The few that were monitored did not reveal suitable oscillation frequency patterns to achieve a unique mode identification, which is a requirement to perform asteroseismic modelling.
+The investigation of pulsation modes in high-mass stars using high-quality \kepler smear data combined with high-precision spectroscopy to identify the modes \citep[Chapter 6]{aertsbook} is an exciting prospect for asteroseismology, as the interior physics of these stars are largely unknown, yet they play a pivotal role in stellar and galactic evolution.
+The in-depth asteroseismic analysis of the smear data for the~B~stars in this work is beyond the scope of the current paper, as it requires additional ground-based follow-up spectroscopy.
+Such studies will be the subject of future work.
 
@@
 \citet{2018MNRAS.474.2774S} have recently claimed the hump-and-spike power spectra as evidence for Rossby modes.
-The F5 star HD~186155, identified by SIMBAD as having a giant spectral type of F5II-III, is shown by its \gaia distance to in fact lie on the main sequence.
+The F5 star HD~186155, identified by SIMBAD as having a giant spectral type of F5II-III, is shown by its \gaia distance to in fact lie on the main {}sequence.
 The other example is the B3e star HD~183362 at $G = -2.576$.

### 2018-09-10 paper/ms.tex
more about hump and spike stars

@@
 
-Two stars in the sample show the `hump-and-spike' morphology in their power spectra (a broad `hump' of low-amplitude oscillations dominated by one high amplitude coherent oscillation toward the high frequency end of this band): HD~186155 (HR~7495), and HD~183362 (HR~7403), respectively the third brightest and $37^{\text{th}}$-brightest stars on silicon and the brightest two stars that show this effect.
+Several stars in the sample show the `hump-and-spike' morphology in their power spectra (a broad `hump' of low-amplitude oscillations dominated by one high amplitude coherent oscillation toward the high frequency end of this band): HD~186155 (HR~7495), 14~Cyg (HD~185872, HR~7483), HD~189178 (HR~7628), HD~183362 (HR~7403), and HD~184787.
+Of these, HD~186155 and 14~Cyg are the third brightest and sixth-brightest stars on silicon, making these the brightest stars that show this effect.
 \citet{2018MNRAS.474.2774S} have recently claimed the hump-and-spike power spectra as evidence for Rossby modes.
-The F5 star HD~186155, identified by SIMBAD as having a giant spectral type of F5II-III, is shown by its \gaia distance to in fact lie on the main {}sequence.
+The F5 star HD~186155, identified by SIMBAD as having a giant spectral type of F5II-III, is shown by its \gaia distance to in fact lie on the main sequence.
 The other example is the B3e star HD~183362 at $G = -2.576$.

### 2018-09-10 paper/ms.tex
wording

@@
 Several stars in the sample show the `hump-and-spike' morphology in their power spectra (a broad `hump' of low-amplitude oscillations dominated by one high amplitude coherent oscillation toward the high frequency end of this band): HD~186155 (HR~7495), 14~Cyg (HD~185872, HR~7483), HD~189178 (HR~7628), HD~183362 (HR~7403), and HD~184787.
-Of these, HD~186155 and 14~Cyg are the third brightest and sixth-brightest stars on silicon, making these the brightest stars that show this effect.
+Of these, HD~186155 and 14~Cyg are the third-- and sixth--brightest stars on silicon, making these the brightest stars that show this effect.
 \citet{2018MNRAS.474.2774S} have recently claimed the hump-and-spike power spectra as evidence for Rossby modes.
 The F5 star HD~186155, identified by SIMBAD as having a giant spectral type of F5II-III, is shown by its \gaia distance to in fact lie on the main sequence.
-The other example is the B3e star HD~183362 at $G = -2.576$.
 A detailed study of these stars will be presented by Antoci et al., in prep.

### 2018-09-10 paper/ms.tex
redid gaia match more rigorously

@@
 Amongst our sample are pulsating stars of spectral type~B,~A, and~F, with their names, properties and variability class listed in Table~\ref{all_stars}.
+
+Several stars have a more complex classification than can be adequately noted in Table~\ref{all_stars}: HD~189684 is listed as an ellipsoidal variable, but also shows evidence for $\gamma$\,Dor variability.
+HD~185397 and HD~186255 are listed as $\gamma$\,Dor/$\delta$\,Sct hybrids, but may in fact simply be $\delta$\,Sct variables with nonlinear combination frequencies, and a detailed frequency analysis will be required to distinguish between these possibilities.
+HD~184788 shows acombination of two rotational modulation signals with base frequencies: 0.0885 and~$0.1966 c/d$.
+HD~184875 is a $\gamma$\,Dor but also shows evidence for an unknown contaminant.
+V554~Lyr and V2079~Cyg are both known $\alpha^2$\,CVn variables, and the latter also shows a weak $\delta$\,Sct signal.
+The detection of rotational modulation in the chemically-peculiar HD~175132 suggests its reclassification as an $\alpha^2$\,CVn variable.
+
 The coherent g-mode pulsations in samples of B, A, and F stars observed by \kepler previously showed these stars to be near-rigid rotators \citep{kurtz2014,saio15,triana15,vanreeth15,vanreeth16,vanreeth18,murphy16,schmid16,moravveji16,ouazzani17,papics17,aerts17,szewczuk18}.
@@
 Of these, HD~186155 and 14~Cyg are the third-- and sixth--brightest stars on silicon, making these the brightest stars that show this effect.
+The identification for HD~189178 is tentative, as the spectrum also resembles that of an SPB star, while for HD~184787 there is long term variability consistent with contamination.
+The other hump-and-spike identifications seem secure.
 \citet{2018MNRAS.474.2774S} have recently claimed the hump-and-spike power spectra as evidence for Rossby modes.

### 2018-09-10 paper/ms.tex
put in the relevant numbers in the introduction

@@
 This was because stars brighter than $Kp \sim 11$ saturate the CCD detectors, with their flux distributed along a bleed column and rendering those pixels otherwise unusable.
-Furthermore, due to the limited availablility of bandwidth to download data from the spacecraft, only a fraction \textcolor{red}{What fraction?} of pixels on the \kepler detectors are actually downloaded.
-The result of these two target selection constraints is that photometry was obtained for only \textcolor{red}{a small number} of saturated stars in the \kepler field, while many bright targets were ignored.
+Furthermore, due to the limited availablility of bandwidth to download data from the spacecraft, only $\sim 5.7\%$ of pixels on the \kepler detectors are actually downloaded in any one Quarter \citep{2010ApJ...713L..87Jd}.
+The result of these two target selection constraints is that photometry was obtained for most of the mission for only~35 stars brighter than $Kp<7$ in the \kepler field, while~17 targets in this range were observed for less than half the mission and~29 targets brighter than this threshold were entirely ignored.
+The availability of \kepler data remains significantly incomplete down to fainter magnitudes, and in this work we consider $Kp=9$ to be an arbitrary cutoff for bright stars of interest.
 In the \ktwo mission \citep{k2early}, very saturated stars have been observed with `halo photometry' using unsaturated pixels in a specially-determined region around bright stars, including the Pleiades \citep{halo}, Aldebaran \citep{aldebaran}, and $\rho$~Leonis \citep{rholeo}.
@@
 
-In \citet{smear}, we demonstrated a method for extracting precise light curves of bright stars in \kepler and \ktwo, and presented light curves of a small number of variable stars as examples to illustrate this method.
+In \citet{smear}, we demonstrated a method for extracting precise light curves of bright stars in \kepler and \ktwo from these collateral data, and presented light curves of a small number of variable stars as examples to illustrate this method.
 In this paper we present smear light curves of all unobserved or significantly under-observed stars brighter than $Kp=9$ in the \kepler field.
-This sample mostly consists of red giants and hot stars, containing only a few FG dwarfs.
+This sample mostly consists of red giants and hot stars, containing only one~G dwarf.
 We find no transiting planets, but detect \textcolor{red}{$M$}~new eclipsing binaries, and measure solar-like oscillations in 34~red giants.
-We do not model hot stars or FG dwarfs in great detail, but provide some discussion and initial classification of interesting variability.
+We do not model main sequence stars in great detail, but provide some discussion and initial classification of interesting variability.
 For eclipsing binaries, we present the results of light-curve modelling to precisely determine their parameters.
@@
 Some stars did not land on silicon for all seasons: we have only one season of HD~179394; two for HD~187277, HD~226754, V554~Lyr, and BD+47~2891; and three for BD+43~3064.
-\textcolor{red}{Aside from the restriction on stars falling on the edge of a chip}, the addition of our sample to the conventionally-observed stars makes the \kepler survey magnitude-complete down to $Kp=9$.
+The addition of our sample to the conventionally-observed stars makes the \kepler survey magnitude-complete down to $Kp=9$ for all stars on-silicon.
 
@@
 HD~184875 is a $\gamma$\,Dor but also shows evidence for an unknown contaminant.
-V554~Lyr and V2079~Cyg are both known $\alpha^2$\,CVn variables, and the latter also shows a weak $\delta$\,Sct signal.
+V554~Lyr and V2079~Cyg are both known $\alpha^2$\,CVn variables, which are chemically peculiar stars with strong magnetic fields that show rotational modulation.
+V2079~Cyg also shows a weak $\delta$\,Sct signal.
 The detection of rotational modulation in the chemically-peculiar HD~175132 suggests its reclassification as an $\alpha^2$\,CVn variable.

### 2018-09-10 paper/ms.tex
initialize new eclipsing binary section

@@
 
-\subsubsection{Eclipsing Binaries}
+\subsubsection{Binaries}
 \label{ebs}
-We detect some eclipsing binaries \textcolor{red}{Ben - finish this.}
+
+We detect BD+47~2825 as a new eclipsing binary system, and recover light curves for the previously-known eclipsing binaries HD~186994, V2083~Cyg, and V380~Cyg.
+The known binary system HD~189684 is newly identified as showing ellipsoidal variability, but does not show evidence of eclipses.
+\textcolor{red}{Finish this section?}
 

### 2018-09-10 paper/ms.tex
descope ebs

@@
 This sample mostly consists of red giants and hot stars, containing only one~G dwarf.
-We find no transiting planets, but detect \textcolor{red}{$M$}~new eclipsing binaries, and measure solar-like oscillations in 34~red giants.
+We find no transiting planets, but detect one new eclipsing binary, and measure solar-like oscillations in 34~red giants.
 We do not model main sequence stars in great detail, but provide some discussion and initial classification of interesting variability.
-For eclipsing binaries, we present the results of light-curve modelling to precisely determine their parameters.
 For the oscillating red giants that constitute the bulk of the sample, we determine the asteroseismic parameters \numax and \Dnu, and therefore stellar masses and \logg measurements.
@@
 The known binary system HD~189684 is newly identified as showing ellipsoidal variability, but does not show evidence of eclipses.
-\textcolor{red}{Finish this section?}
+We do not attempt detailed analysis of their variability in this paper.
 

### 2018-09-10 paper/ms.tex
bedding corrections

@@
 This was because stars brighter than $Kp \sim 11$ saturate the CCD detectors, with their flux distributed along a bleed column and rendering those pixels otherwise unusable.
-Furthermore, due to the limited availablility of bandwidth to download data from the spacecraft, only $\sim 5.7\%$ of pixels on the \kepler detectors are actually downloaded in any one Quarter \citep{2010ApJ...713L..87Jd}.
+Furthermore, due to the limited availablility of bandwidth to download data from the spacecraft, only $\sim 5.7\%$ of pixels on the \kepler detectors are actually downloaded in any one Quarter \citep{2010ApJ...713L..87J}.
 The result of these two target selection constraints is that photometry was obtained for most of the mission for only~35 stars brighter than $Kp<7$ in the \kepler field, while~17 targets in this range were observed for less than half the mission and~29 targets brighter than this threshold were entirely ignored.
@@
 \kepler employs an inter-line transfer CCD as its detector, which successively shuffles each row of pixels down to the edges of the chip to be read out.
-Because the \kepler camera lacks a shutter, the detector is exposed to light during the readout process, with the result that fluxes in each pixel are contaminated by light collected from objects in the same column.
-This is a particularly serious issue for faint objects in the same detector column as brighter stars, and it is important to calibrate this at each readout stage.
+Because the \kepler camera lacks a shutter, the detector is exposed to light during the readout process, with the result that fluxes in each pixel are contaminated by light collected from stars in the same column.
+This is a particularly serious issue for faint stars in the same detector column as brighter stars, and it is important to calibrate this at each readout stage.
 Six rows of blank `masked' pixels were allocated in each column to measure the smear bias; furthermore, six `virtual' rows were recorded at the end of the readout, with the result that twelve rows of pixels sample the smear bias in each column.
@@
 For the oscillating red giants that constitute the bulk of the sample, we determine the asteroseismic parameters \numax and \Dnu, and therefore stellar masses and \logg measurements.
-We have also obtained high-resolution optical spectroscopy of 63~objects, predominantly giants, with the Tillinghast Reflector \'{E}chelle Spectrograph (TRES).
+We have also obtained high-resolution optical spectroscopy of 63~stars, predominantly giants, with the Tillinghast Reflector \'{E}chelle Spectrograph (TRES).
 For the~34 stars with both spectroscopy and asteroseismic parameters we derive fundamental stellar parameters and elemental abundances.
@@
 Sixteen stars were to some extent observed conventionally: HD~174020 was targeted in LC for Q2, 6, 10, and 14; HD~175841 for Q11-12, 14-16, with SC for Q3; HD~176582 for Q12-13; HD~178090 for Q1, 3, and 10; HD~180682 for Q0, 3, and 7; HD~181069 for Q1, 10, 13, 14, and 17; HD~181878 for Q14-17; HD~182694 for Q2; HD~183124 for even quarters; HD~185351 for Q1-3 and with SC for Q16; HD~186155 for only Q1; HD~187217 for Q14-17; HD~188252 for only Q13; HD~189013 with SC for Q3 as a $\gamma$~Dor; V380~Cyg for Q11 and with SC for Q7, 9, 10, 12-17; and V819~Cyg for Q14, 16 and 17.
-A number of these lay at the edge of a detector, with the result that in some cadences the centroid of the star did not lie on the chip; light curves from these targets were found to be of extremely low quality and all of these objects were discarded.
+A number of these lay at the edge of a detector, with the result that in some cadences the centroid of the star did not lie on the chip; light curves from these targets were found to be of extremely low quality and all of these stars were discarded.
 After applying these criteria we obtained a list of 102 targets, which are listed in Table~\ref{all_stars} with their \kepler magnitude $Kp$ together with their spectral type from SIMBAD, \gaia~DR2 apparent~$G$ magnitudes and $Bp-Rp$ colours, \gaia~DR2 calibrated distances from \citet{gaiadists}, variability classification and availability of TRES spectroscopy.
@@
 
-Figure~\ref{hrdiagram} shows these stars on a colour-magnitude diagram in \gaia $Bp-Rp$ and absolute~$G$ magnitudes using \gaia~DR2 calibrated distances from \citet{gaiadists}, overlaid on the \kepler sample from the Bedell \url{gaia-kepler.fun} crossmatch.
+Figure~\ref{hrdiagram} shows these stars on a colour-magnitude diagram using \gaia $Bp-Rp$ and absolute~$G$ magnitudes and \gaia~DR2 calibrated distances \citep{gaiadists}, overlaid on the \kepler sample from the Bedell \url{gaia-kepler.fun} crossmatch.
 The smear targets in this diagram appear to have not merely higher apparent brightnesses than the general \kepler population, but also higher intrinsic luminosities.
@@
 
-We identify the evolutionary state of objects in the main sequence versus evolved stars first from the \gaia colour-magnitude diagram in Figure~\ref{hrdiagram}.
-Taking a cutoff in \gaia $Bp-Rp > 1$, we identify 64 of these objects as clearly evolved systems, and the remaining~38 lie apparently on the main sequence.
+We identify the evolutionary state of stars in the main sequence versus evolved stars first from the \gaia colour-magnitude diagram in Figure~\ref{hrdiagram}.
+Taking a cutoff in \gaia $Bp-Rp > 1$, we identify 64 of these stars as clearly evolved systems, and the remaining~38 lie apparently on the main sequence.
 
-One of the main sequence objects, BD+43~3068 is a G0 dwarf with a $G$ magnitude of 8.267944 and a distance of $53.8 \pm 0.1$~pc, and it is therefore surprising that it was not included in the nominal \kepler survey as a Solar analogue: it is possible that it was previously misidentified as a giant.
+The coolest main sequence star, BD+43~3068, is a G0 dwarf with a $G$ magnitude of 8.3 and a distance of $53.8 \pm 0.1$~pc, and it is therefore surprising that it was not included in the nominal \kepler survey as a solar analogue.
+It is possible that it was previously misidentified as a giant.
 Regrettably, it is only possible to reconstruct a light curve with the 30~minute long cadence and therefore it is not possible to do asteroseismology on this bright, nearby solar-like star.
-This light curve shows neither rotational modulation (as determined by its featureless autocorrelation) nor evidence for transits.
+Its light curve shows neither rotational modulation (as determined by its featureless autocorrelation) nor evidence for transits.
 
-Considering objects lying photometrically on the main sequence, from the \kepler power spectrum we identify solar-like oscillations in HD~182354 and HD~176209 at frequencies consistent with them being subgiants or contaminated with flux from red giants.
+Considering stars lying close to the main sequence, from the \kepler power spectrum we identify solar-like oscillations in HD~182354 and HD~176209 at frequencies consistent with them being subgiants or contaminated with flux from red giants.
 \textcolor{red}{Get frequencies}.
@@
 
-Because the smear data are collected along an entire CCD~column, there is the risk of contamination from sufficiently bright sources.
+Because the smear data are collected along an entire CCD~column, there is the risk of contamination from other bright stars.
 This is especially true in doing asteroseismology of red giants, where the low-amplitude stochastically-excited oscillations can be washed out in a power spectrum by the coherent high amplitude variations of a classical pulsator, even if the background star is much fainter.
@@
 
-While~64 red giants have been identified in this sample, for some of these, by visual inspection it is clear that the timescale of their variability is of the same order as a \kepler quarter and they are thus badly affected by systematics and systematics correction.
+Among the~64 red giants identified in this sample, for~30 the timescale of their variability is of the same order as a \kepler quarter and they are thus badly affected by systematics and systematics correction.
 In Table~\ref{all_stars} we have noted these as `long-period variables' (LPVs), without specifically meaning these are LPVs by a particular astrophysical definition, and they are discussed further in Section~\ref{lpvs}.
 For the~34 giants for which there is high-SNR shorter-timescale variability, we have attempted to extract the asteroseismic parameters \numax and $\langle \Dnu \rangle$ \citep{KB95,2013ARA&A..51..353C}.
-These constrain fundamental stellar parameters as through these scaling relations:
+These constrain fundamental stellar parameters through the approximate scaling relations:
 
@@
 \begin{equation}
-\langle \Dnu \rangle \propto \sqrt{\langle \rho \rangle} = \sqrt{\dfrac{M}{\msun} \left(\dfrac{R}{\rsun}\right)^{-3}}
+\langle \Dnu \rangle \propto \sqrt{\langle \rho \rangle} = \sqrt{M {R}^{-3}}
 \end{equation}
@@
 To estimate \Dnu, we have divided the power spectrum through by the granulation and noise models to obtain a signal-to-noise spectrum, and fit a sum of Lorentzians separated by mean large (\Dnu) and small (\dnu) separations to the part of this spectrum in the vicinity of \numax.
-In practice, for this dataset, \dnu is poorly constrained, but mean $\langle \Dnu \rangle$ is typically well-constrained and its posterior marginal distribution is well-represented by a single Gaussian as with \numax.
+In practice, for this dataset, \dnu is not constrained, but mean $\langle \Dnu \rangle$ is typically well-constrained and its posterior marginal distribution is well-represented by a single Gaussian as with \numax.
 
@@
 
-Once \numax has been estimated, we have used the asteroseismic scaling relation for \numax \citep[Equation~\ref{scaling};][]{KB95} to estimate \logg in order to inform extraction of chemical abundances from spectra.
+Once \numax has been estimated, we have used Equation~\ref{scaling}, the asteroseismic scaling relation for \numax \citep{1991ApJ...368..599B,KB95}, to estimate \logg in order to inform extraction of chemical abundances from spectra.
 Using the initial spectroscopic estimate of \teff, which is not significantly informed by \numax, uncertainties in \numax are propagated with Monte Carlo sampling.
@@
 For eight stars, we have found that the asteroseismic fit is unsatisfactory: for BD+39~388 we cannot detect the expected oscillations; for BD+43~3064 there are significant peaks but these are not consistent with the pattern expected from a red giant; for HD~179959 and HD~187217 we suspect contamination with the oscillations of a second giant, which is hard to remove from smear light curves; while for HD~188629, HD~188639 and HD~188875 we can extract a \numax but not a robust \Dnu.
-One star in our sample, the retired~A star HD~185351, has a mode envelope that is not well fit by our model.
-The smear light curve for this star has already been published by \citet{2017MNRAS.464.3713H}, who showed with detailed asteroseismic modelling that it had a zero-age main sequence mass of $\sim 1.60 \msun$ and used it to calibrate the convective overshoot parameter for low-luminosity red giants.
-The bulk asteroseismic modelling presented here should therefore be considered to be superseded by the more detailed model of \citet{2017MNRAS.464.3713H}.
+One star in our sample, HD~185351, has a mode envelope that is not well fit by our model.
+The smear light curve for this star has already been published by \citet{2017MNRAS.464.3713H}, who showed with detailed asteroseismic modelling that it had a zero-age main sequence mass of $\sim 1.60 \msun$ (a so-called `retired~A star') and used it to calibrate the convective overshoot parameter for low-luminosity red giants.
+The global asteroseismic modelling presented here should therefore be considered to be superseded by the more detailed model of \citet{2017MNRAS.464.3713H}.
 
@@
 
-For the whole red giant sample, we have obtained high-resolution spectroscopy with TRES in order to constrain stellar parameters and elemental abundances.
+We have obtained high-resolution spectroscopy with TRES for~63 stars, mainly giants, in order to constrain stellar parameters and elemental abundances.
 Operating with spectral resolving power $R=44 000$, we have obtained spectra with signal-to-noise ratios (SNRs) of tens to hundreds per resolution element.
-This resolution and SNR are sufficient for an exploratory study, but for more detailed analysis it will be desirable to use APOGEE or similar instruments to obtain greater spectral coverage.
+Although this resolution and SNR are sufficient for an exploratory study, for more detailed analysis it will be desirable to use APOGEE or similar instruments to obtain greater spectral coverage.
 From this observing run we have~34 unique targets with seismic \logg and spectra, one more star than the \gaia-ESO benchmark set and a significant addition to the ensemble of bright red giants with asteroseismic parameter determinations.
@@
 \label{chemical}
-The chemical compositions for each star were measured in the $\alpha$ (Mg, Ti, Si, Ca), odd-Z (Al, Na, Cu, Sc, V), Fe-peak (Fe, Ni, Zn, Co, Cr, Mn), and neutron capture (Sr, Y, Zr, Ba, La, Nd, Eu) elemental families.
-This was done to asses the Galactic populations from which these stars are drawn.
-The first thing to note is that the metallicities, which are tabulated in Table~\ref{stellar_props}, are too high (with $-0.51<$~[M/H]~$<$ +0.14~dex) to be considered drawn from the Galactic halo, whose peak metallicity is around $\sim -1.50$ \cite[e.g.][]{Chiba2000}.
+The chemical composition for each star was measured in the $\alpha$ (Mg, Ti, Si, Ca), odd-Z (Al, Na, Cu, Sc, V), Fe-peak (Fe, Ni, Zn, Co, Cr, Mn), and neutron capture (Sr, Y, Zr, Ba, La, Nd, Eu) elemental families.
+This was done to asses the Galactic populations to which these stars belong.
+The first thing to note is that the metallicities, which are tabulated in Table~\ref{stellar_props}, are too high (with $-0.51<$~[M/H]~$<$ +0.14~dex) to be belong to the Galactic halo, whose peak metallicity is around $\sim -1.50$ \cite[e.g.][]{Chiba2000}.
 Furthermore, the distance distribution, noted in Table~\ref{all_stars}, indicates that all stars are located within a few~kpc of the Sun and thus are not apart of the Galactic bulge.
-These alone allow us to predict that theses stars are drawn from only the Galactic thick and thin disks.
+Thus, these stars are drawn from only the Galactic thick and thin disks.
 We provide a detailed chemical abundance analysis below to support this claim.\\
@@
 \end{figure*}
-The $\alpha$ elements are thought to form in  variety ways during internal fusion within a star while it evolves over its life.
-These elements are then largely dispersed into the interstellar medium through Type~II supernovae (SNII) \citep{Matteucci2001}.
-The most important of these diagrams are those including the abundances of the $\alpha$ elements as a function of metallicity.
+The $\alpha$ elements are largely dispersed into the interstellar medium through Type~II supernovae (SNII) \citep{Matteucci2001}.
 It has been shown by many studies \citep[e.g.][and references therein]{Edvardsson1993, Adibekyan2012, Feltzing2013, Bensby2014}, that the Galactic thick disk and thin disk separate in the $\alpha$ elements, where the thick disk is enhanced in [Mg, Si, Ca, Ti/Fe] compared to the Galactic thin disk at a given metallicity.
-In Fig.~\ref{alphael}, we display the [Mg, Si, Ca, Ti/Fe] abundance ratios as a function of [Fe/H] for our stars (black circles) compared\footnote{We note that there are likely systematics between our [X/Fe] abundance scale and those of our comparison samples.
-We do not have the relevant data, which include several stars in common with these studies but observed with the TRES spectrograph, to asses the level of systematics.}  to representative disk stars from \cite[open red square,][]{Bensby2014} and \cite[open orange triangles,][]{Adibekyan2012}.
+In Fig.~\ref{alphael}, we display the [Mg, Si, Ca, Ti/Fe] abundance ratios as a function of [Fe/H] for our stars (black circles) compared\footnote{There are likely to be systematics between our [X/Fe] abundance scale and those of our comparison samples.}  to representative disk stars from \cite[open red square]{Bensby2014} and \cite[open orange triangles]{Adibekyan2012}.
 
@@
 
-Red clump stars, which burn helium in their cores, differ significantly in their core structure from stars on the hydrogen shell burning red giant sequence.
-They can therefore be distinguished from hydrogen-shell burning giants asteroseismologically, due to their much higher \emph{g}-mode period spacings \citep{rggmodehelium}.
-The moniker `red clump' arises from the fact that such stars can have a very narrow range of luminosities, so that they appear as a clump in the HR diagram \citep{2016ARA&A..54...95G}.
+Red clump stars, which burn helium in their cores, can be distinguished from hydrogen-shell burning giants asteroseismologically, via their much higher \emph{g}-mode period spacings \citep{rggmodehelium}.
+The term `red clump' arises from the fact that such stars can have a very narrow range of luminosities, so that they appear as a clump in the HR diagram \citep{2016ARA&A..54...95G}.
 This property makes them useful standard candles to which distances can be accurately computed from photometry.
@@
 
-From visual inspection of the power spectra, HD~181069, HD~183124, HD~182354, HD~182692, and HD~180658 are seen to be red clump stars.
+From inspection of the power spectra, HD~181069, HD~183124, HD~182354, HD~182692, and HD~180658 are seen to be red clump stars.
 A power spectrum of the best example of these, HD~183124, together with an \'{e}chelle diagram used to estimate its \emph{g}-mode period spacing, is shown in Figure~\ref{HD_183124}.
-While precise characterization of these stars to the necessary degree is beyond the scope of this paper, they are ideal candidates for anchoring models of the mass and metallicity dependence of red clump properties for calibrating \gaia and other distance measures.
+While precise characterization of these stars is beyond the scope of this paper, they are ideal candidates for anchoring models of the mass and metallicity dependence of red clump properties for calibrating \gaia and other distance measures.
 
@@
 
-For all the main sequence stars in our sample, we visually inspected light curves and power spectra to determine their variability class.
+For all the main sequence stars in our sample, we inspected light curves and power spectra to determine their variability class.
 In the following subsections, we will briefly comment on some of the findings.
-As main sequence variables are so diverse, and suited to varied science cases, we have attempted only a very preliminary study of these stars in this paper, leaving detailed analysis to future work.
+Since main sequence variables are so diverse, and the relevant scientific questions so varied, we have attempted only a very preliminary study of these stars in this paper, leaving detailed analysis to future work.
 
@@
 The other hump-and-spike identifications seem secure.
-\citet{2018MNRAS.474.2774S} have recently claimed the hump-and-spike power spectra as evidence for Rossby modes.
+\citet{2018MNRAS.474.2774S} have recently interpreted the hump-and-spike power spectra as evidence for Rossby modes.
 The F5 star HD~186155, identified by SIMBAD as having a giant spectral type of F5II-III, is shown by its \gaia distance to in fact lie on the main sequence.
@@
 
-Another star with a hump-and-spike spectrum is Boyajian's~Star, which shows deep enigmatic dips in brightness \citep{2016MNRAS.457.3988B}, and has faded both throughout the \kepler mission \citep{2016ApJ...830L..39M} and in relation to Harvard photographic plates from 1890 onwards \citep{2016ApJ...822L..34S}.
+Another star with a hump-and-spike spectrum is Boyajian's~Star (KIC~8462852), which shows deep enigmatic dips in brightness \citep{2016MNRAS.457.3988B}, and has faded both throughout the \kepler mission \citep{2016ApJ...830L..39M} and in relation to Harvard photographic plates from 1890 onwards \citep{2016ApJ...822L..34S}.
 The dimming, which is chromatic in the manner expected of heterogeneous clouds of circumstellar dust in the line of sight \citep{2018ApJ...853..130D,2018arXiv180608842B}, has been ascribed to various causes \citep[reviewed in][]{2018RNAAS...2a..16W}, most notably a cloud of exocomets surrounding the star \citep[e.g.][]{2018MNRAS.473.5286W}.

### 2018-09-12 paper/ms.tex
simon murphy section

@@
 
-Amongst our sample are pulsating stars of spectral type~B,~A, and~F, with their names, properties and variability class listed in Table~\ref{all_stars}.
+Our sample includes pulsating stars of spectral type~B,~A, and~F, with their names, properties and variability class listed in Table~\ref{all_stars}.
+
+Among the hot-star sample are 5 $\delta$\,Sct stars, which show p-mode pulsation.
+These oscillation modes have particularly long lifetimes and stable frequencies, making them precise stellar clocks with periods of $\sim$2\,hr.
+These can be used to search for binarity and to obtain orbital parameters from photometry alone \citep{shibahashi&kurtz2012}.
+We used the phase-modulation method of \citet{murphyetal2014} to investigate whether any of these $\delta$\,Sct stars were binaries.
+Any phase modulation is converted into a light arrival-time delay, and if a star is a binary, the time delays of each mode should vary in unison.
+Nearly 350 PM binaries are known in the full \textit{Kepler} dataset \citep{murphyetal2018}.
+
+In four of the five targets we found evidence for binarity, while in the fifth (HD\,185397) there was some time-delay variation but there was no agreement between different modes so it is not of binary origin.
+Of the others, HD\,175841 and HD\,177781 are likely very long-period binaries, with periods far exceeding the Kepler datasets of $\sim$1470\,d.
+HD\,181521 appears to be an eccentric binary with a period of at least 1000\,d, but there is only 1 maximum and 1 minimum in the time-delay curve (cf.
+\citep{murphy&shibahashi2015}), so a unique orbital solution was unobtainable.
+Finally, HD\,186255 is likely a binary with a period of $\sim$415\,d, but there is a slight aperiodicity in the time delays, likely caused by beating between pulsation modes that are not well-separated in the frequency.
+That, coupled with the fact that this star is on the failed Module 3 and is therefore missing data every 4th quarter (i.e.
+$\sim$93 of every 372.5\,d), makes the binary classification uncertain.
+If indeed this is a 415-d binary, the time delays are consistent with a companion of minimum mass $\sim$0.45\,M$_{\odot}$ in an orbit of moderate eccentricity ($\sim$0.15).
 
@@
 HD~185397 and HD~186255 are listed as $\gamma$\,Dor/$\delta$\,Sct hybrids, but may in fact simply be $\delta$\,Sct variables with nonlinear combination frequencies, and a detailed frequency analysis will be required to distinguish between these possibilities.
-HD~184788 shows acombination of two rotational modulation signals with base frequencies: 0.0885 and~$0.1966 c/d$.
+HD~184788 shows a combination of two rotational modulation signals with base frequencies: 0.0885 and~$0.1966 c/d$.
 HD~184875 is a $\gamma$\,Dor but also shows evidence for an unknown contaminant.

### 2018-09-12 paper/ms.tex
small changes

@@
 We describe the pipeline developed to extract and calibrate these light curves, and show that we attain photometric precision comparable to stars analyzed by the standard pipeline in the nominal \kepler mission.
-In this Paper, we focus in particular on a subset of these consisting of 64~red giants for which we detect solar-like oscillations.
+In this Paper, we focus in particular on a subset of these consisting of 66~red giants for which we detect solar-like oscillations.
 Using high-resolution spectroscopy from the Tillinghast Reflector \'{E}chelle Spectrograph (TRES) together with asteroseismic modelling, we obtain the stellar densities and derive masses, radii and ages of~34 of these red giant and red clump stars as benchmarks.
@@
 We identify the evolutionary state of stars in the main sequence versus evolved stars first from the \gaia colour-magnitude diagram in Figure~\ref{hrdiagram}.
-Taking a cutoff in \gaia $Bp-Rp > 1$, we identify 64 of these stars as clearly evolved systems, and the remaining~38 lie apparently on the main sequence.
+Taking a cutoff in \gaia $Bp-Rp > 1$, we identify 66 of these stars as evolved systems, and the remaining~36 lie apparently on the main sequence.
 
@@
 
-Among the~64 red giants identified in this sample, for~30 the timescale of their variability is of the same order as a \kepler quarter and they are thus badly affected by systematics and systematics correction.
+Among the~66 red giants identified in this sample, for~32 the timescale of their variability is of the same order as a \kepler quarter and they are thus badly affected by systematics and systematics correction.
 In Table~\ref{all_stars} we have noted these as `long-period variables' (LPVs), without specifically meaning these are LPVs by a particular astrophysical definition, and they are discussed further in Section~\ref{lpvs}.

### 2018-09-13 paper/ms.tex
neither heartbeat nor eruptive

@@
 
+Two other stars whose variability we classify as rotational modulation, HD~176582 (B5V) and HD~179395 (B9), have very short periods (1.58~d and 1.83~d respectively) and phase stability throughout the \kepler observations.
+While HD~176582 is listed as an eruptive variable by \citet{2016ApJ...829...23D}, this appears to be a misclassification considering the full \kepler smear light curve.
+Both stars show periods shorter than the shortest `heartbeat' binaries with tidally-induced pulsations from \citet{2012ApJ...753...86T}, and neither star is known to be chemically-peculiar.
+We suggest that it is possible that these are nevertheless $\alpha^2$\,CVn variables.
+
 The coherent g-mode pulsations in samples of B, A, and F stars observed by \kepler previously showed these stars to be near-rigid rotators \citep{kurtz2014,saio15,triana15,vanreeth15,vanreeth16,vanreeth18,murphy16,schmid16,moravveji16,ouazzani17,papics17,aerts17,szewczuk18}.

### 2018-09-14 paper/ms.tex
simon and conny agree that it is chemically peculiar spot variation

@@
 While HD~176582 is listed as an eruptive variable by \citet{2016ApJ...829...23D}, this appears to be a misclassification considering the full \kepler smear light curve.
-Both stars show periods shorter than the shortest `heartbeat' binaries with tidally-induced pulsations from \citet{2012ApJ...753...86T}, and neither star is known to be chemically-peculiar.
-We suggest that it is possible that these are nevertheless $\alpha^2$\,CVn variables.
+Both stars show periods shorter than the shortest `heartbeat' binaries with tidally-induced pulsations from \citet{2012ApJ...753...86T}.
+Moreover, the variability periods are short enough that for a binary origin we would expect orbits to be circularized \citep{2000A&A...354..881D}.
+While neither star is known to be chemically-peculiar, we suggest that it is possible that these are nevertheless $\alpha^2$\,CVn variables.
 

### 2018-09-17 paper/ms.tex
bowman

@@
 Victoria Antoci,$^{5}$
-Dominic Bowman,$^{11,12,13}$
+Dominic Bowman,$^{11}$
 Ashley Chontos,$^{9}$\newauthor
@@
 DWL acknowledges partial support from the Kepler Extended Mission under NASA Cooperative Agreement NNX13AB58A with the Smithsonian Astrophysical Observatory.
+The research leading to these results has received funding from the European Research Council (ERC) under the European Union's Horizon 2020 research and innovation programme (grant agreement No670519: MAMSIE).
 

### 2018-09-17 paper/ms.tex
bowman fixes

@@
 Victoria Antoci,$^{5}$
-Dominic Bowman,$^{11}$
+Dominic M. Bowman,$^{11}$
 Ashley Chontos,$^{9}$\newauthor
@@
 
-\subsubsection{Classical Pulsators}
-\label{pulsators}
-
 Our sample includes pulsating stars of spectral type~B,~A, and~F, with their names, properties and variability class listed in Table~\ref{all_stars}.
@@
 Of these, HD~186155 and 14~Cyg are the third-- and sixth--brightest stars on silicon, making these the brightest stars that show this effect.
-The identification for HD~189178 is tentative, as the spectrum also resembles that of an SPB star, while for HD~184787 there is long term variability consistent with contamination.
+The identification for HD~189178 is tentative, as the spectrum also shows evidence of SPB pulsations, and for HD~183362 for $\gamma$\,Dor pulsations, while for HD~184787 there is long term variability consistent with contamination.
 The other hump-and-spike identifications seem secure.
@@
 All code used to produce smear light curves is available under a GPL~v3 license at \url{github.com/benjaminpope/keplersmear}.
-All smear light curves, both including the red giant sample studied in detail in Section~\ref{rgs}, and main sequence stars as discussed in Sections~\ref{pulsators} and~\ref{ebs}, can be downloaded from the Mikulski Archive for Space Telescopes (MAST) as a High-Level Science Product.
+All smear light curves, both including the red giant sample studied in detail in Section~\ref{rgs}, and main sequence stars as discussed in Sections~\ref{mainseq} and~\ref{ebs}, can be downloaded from the Mikulski Archive for Space Telescopes (MAST) as a High-Level Science Product.
 TRES spectra will be made available from the ExoFOP-TESS website, and all asteroseismic parameters and derived stellar parameters for the red giants in Section~\ref{rgs} are provided in an online-only table as Supplementary Material to this paper.

### 2018-09-20 paper/ms.tex
a2cvn from bowman

@@
 
-Two other stars whose variability we classify as rotational modulation, HD~176582 (B5V) and HD~179395 (B9), have very short periods (1.58~d and 1.83~d respectively) and phase stability throughout the \kepler observations.
+There are two stars whose variability we classify as $\alpha^2$\,CVn  HD~176582 (B5V) and HD~179395 (B9), but which are not previously known to be chemically-peculiar.
+have very short periods (1.58~d and 1.83~d respectively) and phase stability throughout the \kepler observations.
 While HD~176582 is listed as an eruptive variable by \citet{2016ApJ...829...23D}, this appears to be a misclassification considering the full \kepler smear light curve.
@@
 Moreover, the variability periods are short enough that for a binary origin we would expect orbits to be circularized \citep{2000A&A...354..881D}.
-While neither star is known to be chemically-peculiar, we suggest that it is possible that these are nevertheless $\alpha^2$\,CVn variables.
+While neither star is known to be chemically-peculiar, we suggest that it is likely that these are nevertheless $\alpha^2$\,CVn variables.
 

### 2018-09-20 paper/ms.tex
a2cvn from bowman

@@
 Moreover, the variability periods are short enough that for a binary origin we would expect orbits to be circularized \citep{2000A&A...354..881D}.
-While neither star is known to be chemically-peculiar, we suggest that it is likely that these are nevertheless $\alpha^2$\,CVn variables.
+We suggest that it is likely that these are nevertheless $\alpha^2$\,CVn variables, and that it will be valuable to study these stars spectroscopically for signs of chemical peculiarity.
 

### 2018-10-03 paper/ms.tex
new spectroscopy

@@
 
-The coherent g-mode pulsations in samples of B, A, and F stars observed by \kepler previously showed these stars to be near-rigid rotators \citep{kurtz2014,saio15,triana15,vanreeth15,vanreeth16,vanreeth18,murphy16,schmid16,moravveji16,ouazzani17,papics17,aerts17,szewczuk18}.
+The coherent g-mode pulsations in samples of B, A, and F stars observed by \kepler previously showed these stars to be near-rigid rotators \citep{kurtz2014,saio15,triana15,vanreeth15,vanreeth16,vanreeth18,murphy16,schmid16,moravveji16,ouazzani17,papics17,aerts17,szewczuk18,2018arXiv180907779A}.
 These studies cover about 70 stars so far.

### 2018-10-03 paper/ms.tex
remove hd 189636

@@
 After applying these criteria we obtained a list of 102 targets, which are listed in Table~\ref{all_stars} with their \kepler magnitude $Kp$ together with their spectral type from SIMBAD, \gaia~DR2 apparent~$G$ magnitudes and $Bp-Rp$ colours, \gaia~DR2 calibrated distances from \citet{gaiadists}, variability classification and availability of TRES spectroscopy.
-A Venn diagram of the sample, noting the availablilty of asteroseismic fits Section~\ref{asteroseismology} and spectroscopy (Section~\ref{spectroscopy}) is displayed in Figure~\ref{venn}.
 The \kepler spacecraft rotates between quarters, so that it cycles through four orientation `seasons' each rotated from the last by $90^{\circ}$.
@@
 
-\begin{figure}
-\noindent\includegraphics[width=8cm,keepaspectratio]{venn.png}
-\caption{\label{venn}
-Venn diagram showing the overall structure of the \kepler Smear Campaign sample, showing the subsets for which TRES spectroscopy and asteroseismology are available and their overlap.}
-\end{figure}
+% \begin{figure}
+% \noindent\includegraphics[width=8cm,keepaspectratio]{venn.png}
+% \caption{\label{venn}
+% Venn diagram showing the overall structure of the \kepler Smear Campaign sample, showing the subsets for which TRES spectroscopy and asteroseismology are available and their overlap.}
+% \end{figure}
 

### 2018-10-25 paper/ms.tex
turn off hyperref for the moment

@@
 \usepackage{xspace}
-\usepackage{hyperref}
 
@@
 We describe the pipeline developed to extract and calibrate these light curves, and show that we attain photometric precision comparable to stars analyzed by the standard pipeline in the nominal \kepler mission.
-In this Paper, we focus in particular on a subset of these consisting of 66~red giants for which we detect solar-like oscillations.
-Using high-resolution spectroscopy from the Tillinghast Reflector \'{E}chelle Spectrograph (TRES) together with asteroseismic modelling, we obtain the stellar densities and derive masses, radii and ages of~34 of these red giant and red clump stars as benchmarks.
-All source code, light curves, TRES spectra, and asteroseismic and stellar parameters are publicly available as a \kepler legacy sample.
+In this Paper, we focus in particular on a subset of these consisting of 66~red giants for which we detect solar-like oscillations.y All source code, light curves, TRES spectra, and asteroseismic and stellar parameters are publicly available as a \kepler legacy sample.
 \end{abstract}
@@
 We can assess the importance of this contamination by considering the differences between odd and even quarters: because the \kepler spacecraft rotates $90^{\circ}$ between successive quarters, any contaminant will lie in the same column as a smear target only every second quarter, falling in the other quarters in the same row but not necessarily the same column.
-We have therefore generated Lomb-Scargle periodograms \citep{lomb,scargle} of each light curve, clipped for outliers, and considering only odd and even quarters, and visually inspected these for significant differences.
+We have therefore generated Lomb-Scargle periodograms \citep{lomb,scargle} of each light curve, clipped for outliers, and considering only odd and even quarters, and both visually inspected these for significant differences.
 In the great majority of cases they closely resemble one another, indicating that contamination is at worst a minor effect.
+In order to better quantify this, we compute the inner product of  normalized periodograms of the odd and even quarters each smoothed with a 3-element Gaussian kernel.
+If this overlap integral is 1, then the power spectra are identical; substantial departures from unity may be caused by real nonstationary or long-period stellar variation, noise, or gain or contamination differences between the seasons.
+We find that the distribution of overlaps is strongly peaked around $\sim 0.91$, with a tail of 22 stars showing overlap $< 0.9$.
+We investigate these further, finding that in not all of these cases is there an obvious problem, for example the classical pulsator HD~175841 in which amplitudes of several pulsations have changed but the overall distribution seems very similar, in which we conclude that the variation is probably astrophysical or an artefact of our data processing.
+
 In the case of HD~181878, a red giant, there is clear and significant contamination from an M~giant, as is seen in Figure~\ref{contamination}.
 Likewise HD~183383 shows two different stars, depending on the quarter: some parts are likely from an ellipsoidal variable with a period of 6.46 days, other parts are from an RR Lyrae pulsator.
+Between seasons, there is an extra hump of power near the red giant oscillations in HD~175740; extra low frequency power in HD~180658; one coherent peak in  HD~182694; high frequency contamination in HD~181597 possibly from an EB; and a very significant difference in amplitude between seasons for BD~+39~3882.
+In other cases visual inspection does not show severe contamination, but in all cases we recommend that users of these light curves carefully check for differences between odd and even quarters.
 
@@
 It is clear from inspection that while odd quarters have the power spectrum expected of a giant star, even quarters have very high amplitude coherent oscillations typical of an M~giant.}
+\end{figure}
+
+\begin{figure}
+\noindent\includegraphics[width=8cm,keepaspectratio]{contam.eps}
+
+\caption{\label{contamination2}
+Histogram over overlap integrals of smoothed periodograms of odd and even quarters for each star in the sample.
+The peak at $\sim 0.91$ contains normal stars with limited contamination; we investigate the 22 stars with overlaps below 0.9 for which there is a significant risk of contamination.}
 \end{figure}
@@
 
-BP acknowledges being on the traditional territory of the Lenape Nations and, today, we recognize that Manhattan continues to be the home to many Algonkian peoples.
-We thank the Lenape peoples for allowing us to carry out this work on the Lenape original homelands at New York University.
-BP and TW would like to acknowledge the Gadigal people of the Eora Nation and the Norongerragal and Gweagal peoples of the Tharawal Nation as the traditional owners of the land at the University of Sydney and the Sutherland Shire on which some of this work was carried out, and pay their respects to their knowledge, and their elders past, present and future.
+BP acknowledges being on the traditional territory of the Lenape Nations and recognizes that Manhattan continues to be the home to many Algonkian peoples.
+We give blessings and thanks to the Lenape people and Lenape Nations in recognition that we are carrying out this work on their indigenous homelands.
+We would like to acknowledge the Gadigal people of the Eora Nation and the Norongerragal and Gweagal peoples of the Tharawal Nation as the traditional owners of the land at the University of Sydney and the Sutherland Shire on which some of this work was carried out, and pay their respects to their knowledge, and their elders past, present and future.
 

### 2018-10-26 paper/ms.tex
amalie figure

@@
 
+\textcolor{red}{Paragraph on stellar modelling by Amalie}
+
+\begin{figure*}
+\noindent\includegraphics[width=17cm,keepaspectratio]{different_constraints_fullsample_ove02.pdf}
+
+\caption{\label{masses}
+Using asteroseismic constraints (left) and asteroseismic and spectroscopic constraints jointly (right) we infer the masses of each star in the asteroseismic sample of giants.}
+\end{figure*}
+
 \subsubsection{Chemical Composition}

### 2018-11-10 paper/ms.tex
fixed broken hyperref
updated tex and figure for stellar abundances

@@
 It has also permitted the determination of ages and fundamental parameters of main-sequence stars as cool as the Sun and hotter \citep{silvaages}, including planet-hosting stars \citep{huberplanetages,silvaplanetages,2018MNRAS.479.4786V}, revealing the most ancient known planetary system, dating back to the earliest stages of the galaxy \citep{ancientplanets}.
-By comparing asteroseismic stellar ages to stellar rotation periods, \citet{angusgyro} have shown that gyrochronology models cannot fit the data with a single relation, leading \citet{vansadersgyro} to suggest a qualitative change in dynamo mechanism as stars age through the main sequence.
+%By comparing asteroseismic stellar ages to stellar rotation periods, \citet{angusgyro} have shown that gyrochronology models cannot fit the data with a single relation, leading~\citet{vansadersgyro}~to suggest a qualitative change in dynamo mechanism as stars age through the main sequence.
+\newpage
 
@@
 The reported abundances are the median [X/Fe] value of the various line regions for a given element.
-{ \bf Ben: Maybe remove this if we do not actually implement line-by-line differential; Do we have a TRES Arcturus spectrum.} Abundance uncertainties reported are the standard error in the line-by-line abundance ratios.
+Abundance uncertainties reported are the standard error in the line-by-line abundance ratios.
 Where only one line exists for a given element, we conservatively assume the standard error is 0.10~dex.
@@
 We do note, however, thus use of asteroseismology really reduces the uncertainties caused by the stellar parameters \citep[see][for a longer discussion on this]{hawkinsapogee}.
+
 To achieve the most precise abundances we have derived them using  both with and without a line-by-line differential approach with respect to Arcturus ($\alpha$~Bo\"{o}tis) using the method described by \citet{gaiabenchmark4} and the Arcturus abundances from \citep{hawkinsapogee}.
-The results of these absolute abundance calculations {\bf without the line-by-line differential analysis implemented?}, are presented in Tables~\ref{elems1},~\ref{elems2} and~\ref{elems3}.
-Because for most elements Arcturus differential abundances are not available, these are provided as supplementary online-only material.
+Choosing this method means we do not derive the abundances for neutron capture  elements (e.g.
+Sr, Y, Zr, Ba, La, Nd, Eu) in a differential way because there are no estimated values for these elements at the appropriate benchmark parameters of Arcturus.
+For these elements we instead derive the chemical abundances in an aboslute way where the solar abundances of \cite{Asplund2005} are assumed.
+The uncertainty in the abundances are taken a the line-by-line dispersion or assumed to be 0.10 when just one line is available.
 No abundances for oxygen could be reliably derived for any of the stars in our spectroscopic sample by either method.
 
+{\bf Ben the tables should be remade to do Mg, Ti, Si, Ca, Al, V, Fe, Ni in on Table called differential abundances and second table of Sr, Y, Zr, Ba, La, Nd, Eu which is for the non-differential neutron capture} The results of these absolute abundance calculations {\bf without the line-by-line differential analysis implemented?}, are presented in Tables~\ref{elems1},~\ref{elems2} and~\ref{elems3}.
+Because for most  Arcturus differential abundances are not available, these are provided as supplementary online-only material.
 \input{stellar_props.tex}
@@
 
-\subsubsection{Chemical Composition}
+\subsubsection{Chemical Compositions}
 \label{chemical}
-The chemical composition for each star was measured in the $\alpha$ (Mg, Ti, Si, Ca), odd-Z (Al, Na, Cu, Sc, V), Fe-peak (Fe, Ni, Zn, Co, Cr, Mn), and neutron capture (Sr, Y, Zr, Ba, La, Nd, Eu) elemental families.
-This was done to asses the Galactic populations to which these stars belong.
+The chemical composition for each star was measured in the $\alpha$ (Mg, Ti, Si, Ca), odd-Z (Al, V) and Fe-peak (Fe, Ni) elemental families in a differential way with respect to Arcturus.
+The chemical composition for the neutron capture elements were are shown in Fig.~\ref{fig:ncap}, and are derived not differentially with respect to Arcturus.
+The elemental abundance rations were measured in order to asses the Galactic populations to which these stars belong.
 The first thing to note is that the metallicities, which are tabulated in Table~\ref{stellar_props}, are too high (with $-0.51<$~[M/H]~$<$ +0.14~dex) to be belong to the Galactic halo, whose peak metallicity is around $\sim -1.50$ \cite[e.g.][]{Chiba2000}.
@@
 We provide a detailed chemical abundance analysis below to support this claim.\\
-{\bf $\alpha$ elements:}\\
+
+%\begin{figure*}
+%\noindent\includegraphics[width=\textwidth,keepaspectratio]{Pope_spectra_alphaele.pdf}
+%
+%\caption{\label{alphael}
+%The [Mg/Fe], [Si/Fe], [Ca/Fe], and [Ti/Fe], [Al/Fe], [Na/Fe] abundance ratios as a function of iron on the top and bottom rows, respectively for our stars (black cirlces).
+We also illustrate a representative sample of Galactic disk stars from \citet[open red square,][]{Bensby2014} and \citet[open orange triangles,][]{Adibekyan2012}.
+}
+%\end{figure*}
+
 \begin{figure*}
-\noindent\includegraphics[width=\textwidth,keepaspectratio]{Pope_spectra_alphaele.pdf}
+\noindent\includegraphics[width=0.7\textwidth,keepaspectratio]{chem_pope.png}
 
 \caption{\label{alphael}
-The [Mg/Fe], [Si/Fe], [Ca/Fe], and [Ti/Fe], [Al/Fe], [Na/Fe] abundance ratios as a function of iron on the top and bottom rows, respectively for our stars (black cirlces).
-We also illustrate a representative sample of Galactic disk stars from \citet[open red square,][]{Bensby2014} and \citet[open orange triangles,][]{Adibekyan2012}.
+The [Mg/Fe], [Si/Fe], [Ti/Fe], [V/Fe] (left panel) and [Al/Fe], [Ca/Fe], [Ni/Fe], [Cr/Fe] (right panel) abundance ratios as a function of iron for our stars (black circles).
+We also show a representative sample of Galactic disk stars from \citet[open red square,][]{Bensby2014}, \citet[open orange squares,][]{Adibekyan2012}, \citet[light green circles][]{Battistini2015}.
+These elemental ratios give a representative example of the chemical composition of our sample and show they are consistent with the Galactic disk population.
+} %Mg was chosen as an illustrative $\alpha$-element.
 }
 \end{figure*}
-The $\alpha$ elements are largely dispersed into the interstellar medium through Type~II supernovae (SNII) \citep{Matteucci2001}.
+One of the primary ways to distinguish, in a chemical sense, whether the stars in our sample are drawn from the Galactic disk(s), bulge or halo, we can explore the ratio of their $\alpha$-elements to Fe.
+The $\alpha$ elements are formed during He burning (e.g.
+Mg, Ti, Si, Ca) and largely dispersed into the interstellar medium through Type~II supernovae (SNII) \citep{Matteucci2001}.
 It has been shown by many studies \citep[e.g.][and references therein]{Edvardsson1993, Adibekyan2012, Feltzing2013, Bensby2014}, that the Galactic thick disk and thin disk separate in the $\alpha$ elements, where the thick disk is enhanced in [Mg, Si, Ca, Ti/Fe] compared to the Galactic thin disk at a given metallicity.
-In Fig.~\ref{alphael}, we display the [Mg, Si, Ca, Ti/Fe] abundance ratios as a function of [Fe/H] for our stars (black circles) compared\footnote{There are likely to be systematics between our [X/Fe] abundance scale and those of our comparison samples.}  to representative disk stars from \cite[open red square]{Bensby2014} and \cite[open orange triangles]{Adibekyan2012}.
+In Fig.~\ref{alphael}, we display the [Mg/Fe] abundance ratio as a function of [Fe/H] for our stars (black circles) compared\footnote{There may to be systematics between our [X/Fe] abundance scale and those of our comparison samples.}  to representative thick and thin disk stars from \cite[open red square]{Bensby2014} and \cite[open orange triangles]{Adibekyan2012}.
 
-For most of the stars in our sample, the [Mg, Ti, Ca/Fe] abundance ratios are enhanced.
+For most of the stars in our sample, the [Mg/Fe] abundance ratios are enhanced.
+This is equally true in all of the $\alpha$-elements except Ca where the is a much larger spread.
 The commonly used [$\alpha$/Fe] abundance ratio is the average of Mg, Ti, Si, Ca (thus it is ([Mg/Fe] + [Ca/Fe] + [Si/Fe] + [Ti/Fe] / 4.0) ) is also enhanced in most stars.
-This is consistent with most stars belonging to the Galactic thick disk.
-Though there are a handful of stars where the typical [$\alpha$/Fe] ratio is solar.
-\\ 
-{\bf Odd-Z elements:}\\
-The odd-Z elements Na and Al are also shown in  Fig.~\ref{alphael}. These elements are significantly enhanced 
-\\
-{\bf Fe-peak elements:}\\
-XX
-\\ 
-{\bf Neutron capture elements:}\\
-XX
+This is consistent with most of the stars observed here belonging to the Galactic disk with a slight (of the order $\sim$0.15~dex) enhancement in the $\alpha$-elements.
+Fig.~\ref{alphael} clearly rule out the Galactic bulge (which would require the sample to be significantly more $\alpha$-enriched given their metallicity) and the Galactic halo (given that the stars would need to be significantly more metal-poor).
+%Though there are a handful of stars where the typical [$\alpha$/Fe] ratio is solar.
+
+In addition, to the $\alpha$ and odd-Z elements we also derived the chemical abundance for several neutron capture elements including Sr, Zr, La, Eu (left panel of Fig~\ref{fig:ncap}) as well as Y, Ba, and Nd (right panel of Fig.~\ref{fig:ncap}).
+It is clear from Fig.~\ref{fig:ncap}  that the chemical abundance ratio of neutron each neutron capture element is consistent with the Galactic disk population.
+We do however observe that the Ba of our sample is slight enhanced while the Y of our sample is slightly compared to the general disk population of \cite{Bensby2014}.
+However, we conclude in all elemental abundance ratios studied our sample most closely resembles the Galactic disk.
+\begin{figure*}
+\noindent\includegraphics[width=0.7\textwidth,keepaspectratio]{chem_ncap_pope.pdf}
+
+\caption{\label{fig:ncap}
+The [Mg/Fe], [Si/Fe], [Ti/Fe], [V/Fe] (left panel) and [Al/Fe], [Ca/Fe], [Ni/Fe], [Cr/Fe] (right panel) abundance ratios as a function of iron for our stars (black circles).
+We also show a representative sample of Galactic disk stars from \citet[open red square,][]{Bensby2014}, \citet[green circles][]{Battistini2016}.
+These elemental ratios give a representive example of the chemical composition of our sample and show they are consistent with the Galactic disk population.
+} %Mg was chosen as an illustrative $\alpha$-element.
+}
+\end{figure*}
+
+We note that one of the stars (HD~175740) can also be found in the Hypatia catalogue \citep{hypatia}.
+The chemical abundance ratios in each element are consistent, within the uncertainties (of order $\sim$0.10--0.15~dex for most elemental abundance ratios in Hypatia and up to $\sim$0.05~dex here).
+
+%We note that two of the stars in our sample also appear in the Hypatia catalogue of stellar abundances \citep{hypatia}: HD~185351 and HD~175740.
+The abundances reported here for HD~185351 are consistent within the large errorbars of both surveys with those reported in Hypatia, while for HD~175740 they are not.
+\textcolor{red}{Keith - what's going on here?
+Check this?}
 
@@
 May also want to discuss how these span the typical Galactic populations and can act as benchmark stars for APOGEE or other large surveys
-
-Two of the stars in our sample also appear in the Hypatia catalogue of stellar abundances \citep{hypatia}: HD~185351 and HD~175740.
-The abundances reported here for HD~185351 are consistent within the large errorbars of both surveys with those reported in Hypatia, while for HD~175740 they are not.
-\textcolor{red}{Keith - what's going on here?
-Check this?}
 
@@
 
+%\appendix
+%\section{Full Chemical Analysis}
+%The chemical composition for each star was measured in the $\alpha$ (Mg, Ti, Si, Ca), odd-Z (Al, Cu, Sc, V), Fe-peak (Fe, Ni, Zn, Co, Cr, Mn), and neutron capture (Sr, Y, Zr, Ba, La, Nd, Eu) elemental families.
+In Fig.~\ref{fig:alphael}, we show the chemical abundance pattern of [Mg/Fe] as a function of metallicity of our sample (in black) as well two representative Galactic disk samples.
+It is clear from that figure that our sample is largely drawn from the Galactic disk from a chemical perspective.
+Below we provide further evidence of this with other elements across three families.
+%
+%In Fig.~\ref{fig:alphael_appendix}, we display the abundances of the remaining $\alpha$-elements (including Ti, Si, Ca) as well as the odd-Z elements (Al, Cu, Sc, V).
+In Fig.~\ref{fig:Fepeak_appendix} we show the Fe-peak elements (Fe, Ni, Zn, Co, Cr, Mn) and in Fig.~\ref{fig:ncapture_appendix}  we show the Neutron-Capture elements.
+In each diagram we plot the [X/Fe] abundance ration as a function of metallicity.
+For reference, the typical chemical abundances pattern in the Galactic disk is shown for each element and are taken from Bensby2014, Adibekyan2012,
+
 \section*{Acknowledgements} % add your acknowledgements text here!

### 2018-11-11 paper/ms.tex
typos

@@
 The chemical composition for each star was measured in the $\alpha$ (Mg, Ti, Si, Ca), odd-Z (Al, V) and Fe-peak (Fe, Ni) elemental families in a differential way with respect to Arcturus.
-The chemical composition for the neutron capture elements were are shown in Fig.~\ref{fig:ncap}, and are derived not differentially with respect to Arcturus.
-The elemental abundance rations were measured in order to asses the Galactic populations to which these stars belong.
-The first thing to note is that the metallicities, which are tabulated in Table~\ref{stellar_props}, are too high (with $-0.51<$~[M/H]~$<$ +0.14~dex) to be belong to the Galactic halo, whose peak metallicity is around $\sim -1.50$ \cite[e.g.][]{Chiba2000}.
-Furthermore, the distance distribution, noted in Table~\ref{all_stars}, indicates that all stars are located within a few~kpc of the Sun and thus are not apart of the Galactic bulge.
+The chemical composition for the neutron capture elements are shown in Fig.~\ref{fig:ncap}, and are derived not differentially with respect to Arcturus.
+The elemental abundance ratios were measured in order to assess the Galactic populations to which these stars belong.
+The first thing to note is that the metallicities, which are tabulated in Table~\ref{stellar_props}, are too high (with $-0.51<$~[M/H]~$<$ +0.14~dex) to belong to the Galactic halo, whose peak metallicity is around $\sim -1.50$ \cite[e.g.][]{Chiba2000}.
+Furthermore, the distance distribution, noted in Table~\ref{all_stars}, indicates that all stars are located within a few~kpc of the Sun and are not apart of the Galactic bulge.
 Thus, these stars are drawn from only the Galactic thick and thin disks.
@@
 We also show a representative sample of Galactic disk stars from \citet[open red square,][]{Bensby2014}, \citet[open orange squares,][]{Adibekyan2012}, \citet[light green circles][]{Battistini2015}.
-These elemental ratios give a representative example of the chemical composition of our sample and show they are consistent with the Galactic disk population.
+These elemental ratios show that the chemical composition of our sample is consistent with the Galactic disk population.
 } %Mg was chosen as an illustrative $\alpha$-element.
@@
 \end{figure*}
-One of the primary ways to distinguish, in a chemical sense, whether the stars in our sample are drawn from the Galactic disk(s), bulge or halo, we can explore the ratio of their $\alpha$-elements to Fe.
+One of the primary ways to determine, in a chemical sense, whether the stars in our sample are drawn from the Galactic disk(s), bulge or halo, is with the ratio of their $\alpha$-elements to Fe.
 The $\alpha$ elements are formed during He burning (e.g.
@@
 For most of the stars in our sample, the [Mg/Fe] abundance ratios are enhanced.
-This is equally true in all of the $\alpha$-elements except Ca where the is a much larger spread.
-The commonly used [$\alpha$/Fe] abundance ratio is the average of Mg, Ti, Si, Ca (thus it is ([Mg/Fe] + [Ca/Fe] + [Si/Fe] + [Ti/Fe] / 4.0) ) is also enhanced in most stars.
-This is consistent with most of the stars observed here belonging to the Galactic disk with a slight (of the order $\sim$0.15~dex) enhancement in the $\alpha$-elements.
+This is true for all of the $\alpha$-elements except Ca where the is a much larger spread.
+The commonly used [$\alpha$/Fe] abundance ratio, the average of Mg, Ti, Si, Ca (thus it is ([Mg/Fe] + [Ca/Fe] + [Si/Fe] + [Ti/Fe] / 4) ), is also enhanced in most stars.
+This is consistent with most of the stars observed here belonging to the Galactic disk with a slight (of order $\sim$0.15~dex) enhancement in the $\alpha$-elements.
 Fig.~\ref{alphael} clearly rule out the Galactic bulge (which would require the sample to be significantly more $\alpha$-enriched given their metallicity) and the Galactic halo (given that the stars would need to be significantly more metal-poor).
@@
 It is clear from Fig.~\ref{fig:ncap}  that the chemical abundance ratio of neutron each neutron capture element is consistent with the Galactic disk population.
-We do however observe that the Ba of our sample is slight enhanced while the Y of our sample is slightly compared to the general disk population of \cite{Bensby2014}.
-However, we conclude in all elemental abundance ratios studied our sample most closely resembles the Galactic disk.
+We do however observe that the Ba of our sample is slightly enhanced while the Y of our sample is slightly compared to the general disk population of \cite{Bensby2014}.
+However, we conclude all elemental abundance ratios studied our sample most closely resemble the Galactic disk.
 \begin{figure*}

### 2018-11-11 paper/ms.tex
typos

@@
 The chemical composition for each star was measured in the $\alpha$ (Mg, Ti, Si, Ca), odd-Z (Al, V) and Fe-peak (Fe, Ni) elemental families in a differential way with respect to Arcturus.
-The chemical composition for the neutron capture elements are shown in Fig.~\ref{fig:ncap}, and are derived not differentially with respect to Arcturus.
+The chemical composition for the neutron capture elements are shown in Fig.~\ref{fig:ncap}, and are derived in absolute terms and not differentially with respect to Arcturus.
 The elemental abundance ratios were measured in order to assess the Galactic populations to which these stars belong.

### 2018-11-12 paper/ms.tex
keith affiliation and wording

@@
 Guy R. Davies,$^{4,5}$
-Keith Hawkins,$^{6,7}$
-Timothy R. White,$^{5,8}$\newauthor
-Timothy R. Bedding,$^{9,5}$
-Allyson Bieryla,$^{10}$
-David W. Latham,$^{10}$,
-Conny Aerts,$^{11,12,13}$\newauthor
+Keith Hawkins,$^{6}$
+Timothy R. White,$^{5,7}$\newauthor
+Timothy R. Bedding,$^{8,5}$
+Allyson Bieryla,$^{9}$
+David W. Latham,$^{9}$,
+Conny Aerts,$^{10,11,12}$\newauthor
 Suzanne Aigrain,$^{3}$ 
 Victoria Antoci,$^{5}$
-Dominic M. Bowman,$^{11}$
-Ashley Chontos,$^{9}$\newauthor
-Gilbert A. Esquerdo,$^{10}$
-Daniel Huber,$^{14,15,9}$
-Paula Jofr\'{e},$^{16}$
-Simon Murphy,$^{5,9}$\newauthor
-Timothy van Reeth,$^{5,9}$
+Dominic M. Bowman,$^{10}$
+Ashley Chontos,$^{8}$\newauthor
+Gilbert A. Esquerdo,$^{9}$
+Daniel Huber,$^{13,14,8}$
+Paula Jofr\'{e},$^{15}$
+Simon Murphy,$^{5,8}$\newauthor
+Timothy van Reeth,$^{5,8}$
 Victor Silva Aguirre,$^{5}$
 Amalie Stokholm,$^{5}$
-Jie Yu,$^{9,5}$ \newauthor
+Jie Yu,$^{8,5}$ \newauthor
 and friends
@@
 $^{6}$Department of Astronomy, The University of Texas at Austin, 2515 Speedway Boulevard, Austin, TX 78712, USA\\
-$^{7}$Department of Astronomy, Columbia University, 550 W 120th St, New York, NY 10027, USA\\
-$^{8}$Research School of Astronomy and Astrophysics, Mount Stromlo Observatory, The Australian National University, Canberra, ACT 2611, Australia\\
-$^{9}$Sydney Institute for Astronomy (SIfA), School of Physics, University of Sydney, NSW 2006, Australia\\
-$^{10}$Harvard-Smithsonian Center for Astrophysics, 60 Garden Street, Cambridge, MA 02138, USA\\
-$^{11}$Institute of Astronomy, KU Leuven, Celestijnenlaan 200D, B-3001 Leuven, Belgium\\
-$^{12}$Department of Astrophysics, IMAPP, Radboud University Nijmegen, P.O. Box 9010, 6500 GL Nijmegen, The Netherlands\\
-$^{13}$Kavli Institute for Theoretical Physics, University of California, Santa Barbara, CA 93106, USA\\
-$^{14}$Institute for Astronomy, University of Hawai'i, 2680 Woodlawn Drive, Honolulu, HI 96822, USA\\
-$^{15}$SETI Institute, 189 Bernardo Avenue, Mountain View, CA 94043, USA\\
-$^{16}$N\'{u}cleo de Astronom\'{i}a, Facultad de Ingenier\'{i}a y Ciencias, Universidad Diego Portales, Ej\'{e}rcito 441, Santiago De, Chile\\
+$^{7}$Research School of Astronomy and Astrophysics, Mount Stromlo Observatory, The Australian National University, Canberra, ACT 2611, Australia\\
+$^{8}$Sydney Institute for Astronomy (SIfA), School of Physics, University of Sydney, NSW 2006, Australia\\
+$^{9}$Harvard-Smithsonian Center for Astrophysics, 60 Garden Street, Cambridge, MA 02138, USA\\
+$^{10}$Institute of Astronomy, KU Leuven, Celestijnenlaan 200D, B-3001 Leuven, Belgium\\
+$^{11}$Department of Astrophysics, IMAPP, Radboud University Nijmegen, P.O. Box 9010, 6500 GL Nijmegen, The Netherlands\\
+$^{12}$Kavli Institute for Theoretical Physics, University of California, Santa Barbara, CA 93106, USA\\
+$^{13}$Institute for Astronomy, University of Hawai'i, 2680 Woodlawn Drive, Honolulu, HI 96822, USA\\
+$^{14}$SETI Institute, 189 Bernardo Avenue, Mountain View, CA 94043, USA\\
+$^{15}$N\'{u}cleo de Astronom\'{i}a, Facultad de Ingenier\'{i}a y Ciencias, Universidad Diego Portales, Ej\'{e}rcito 441, Santiago De, Chile\\
 }
@@
 It is clear from Fig.~\ref{fig:ncap}  that the chemical abundance ratio of neutron each neutron capture element is consistent with the Galactic disk population.
-We do however observe that the Ba of our sample is slightly enhanced while the Y of our sample is slightly compared to the general disk population of \cite{Bensby2014}.
-However, we conclude all elemental abundance ratios studied our sample most closely resemble the Galactic disk.
+We do however observe that the Ba of our sample is slightly enhanced while the Y of our sample is slightly reduced relative to the general disk population of \cite{Bensby2014}.
+Nevertheless, we conclude all elemental abundance ratios studied our sample most closely resemble the Galactic disk.
 \begin{figure*}

### 2018-11-12 paper/ms.tex
Affiliations

@@
 Keith Hawkins,$^{6}$
-Timothy R. White,$^{5,7}$\newauthor
+Timothy R. White,$^{7,5}$\newauthor
 Timothy R. Bedding,$^{8,5}$
@@
 Dominic M. Bowman,$^{10}$
-Ashley Chontos,$^{8}$\newauthor
+Ashley Chontos,$^{13}$\newauthor
 Gilbert A. Esquerdo,$^{9}$
@@
 Paula Jofr\'{e},$^{15}$
-Simon Murphy,$^{5,8}$\newauthor
-Timothy van Reeth,$^{5,8}$
+Simon Murphy,$^{8,5}$\newauthor
+Timothy van Reeth,$^{8,5}$
 Victor Silva Aguirre,$^{5}$
@@
 We describe the pipeline developed to extract and calibrate these light curves, and show that we attain photometric precision comparable to stars analyzed by the standard pipeline in the nominal \kepler mission.
-In this Paper, we focus in particular on a subset of these consisting of 66~red giants for which we detect solar-like oscillations.y All source code, light curves, TRES spectra, and asteroseismic and stellar parameters are publicly available as a \kepler legacy sample.
+In this Paper, we focus in particular on a subset of these consisting of 66~red giants for which we detect solar-like oscillations.
+All source code, light curves, TRES spectra, and asteroseismic and stellar parameters are publicly available as a \kepler legacy sample.
 \end{abstract}
@@
 
-%We note that two of the stars in our sample also appear in the Hypatia catalogue of stellar abundances \citep{hypatia}: HD~185351 and HD~175740.
-The abundances reported here for HD~185351 are consistent within the large errorbars of both surveys with those reported in Hypatia, while for HD~175740 they are not.
-\textcolor{red}{Keith - what's going on here?
-Check this?}
-
 %place [X/Fe] vs [Fe/H] diagrams here and discuss which Galactic populations these stars come from.

### 2018-11-18 paper/ms.tex
amalie section done

@@
 
-\textcolor{red}{Paragraph on stellar modelling by Amalie}
+We determined physical properties such as mass, radius, and age for the 33 red giants from their atmospheric and asteroseismic observables (see Table ) using the BAyesian STellar Algorithm \citep[\textsc{basta}][]{silvaaguirre2015,silvaaguirre2017}.
+\textsc{basta} compares the observed properties with predictions from theoretical models of stellar evolution, in this case the recently updated BaSTI (a Bag of Stellar Tracks and Isochrones) stellar models and isochrones library \citep{Hidalgo:2018dy} with overshooting and no mass-loss.
+
+The spectroscopic properties we fit are the effective temperature \teff, the metallicity \feh, and the surface gravities \logg from Table~\ref{stellar_props}.
+These are accompanied by the global asteroseismic properties \Dnu and \numax from Table~\ref{astero_table}.
+Theoretical predictions of \Dnu and \numax are computed using the asteroseismic scaling relation for any point along an evolutionary track or isochrone.
+For the solar values, we adopt $\nu_{\text{max, }\odot}=3090$~$\mu$Hz, $\Delta\nu_{\odot}=135.1$~$\mu$Hz \citep{huber2011}, and $T_{\text{eff, }\odot}=5777$~K.
+
+The accuracy of the asteroseismic scaling relations across different metallicities, effective temperatures, and evolutionary status is currently an active discussion within the field of asteroseismology \citep[see][]{white2011,belkacem2011,sharma2016,viani2017}.
+We apply the correction by \cite{Serenelli:2017cn} to the large frequency separation relation in Equation~\ref{Dnuscaling} as it has been shown to reproduce the results of a number of classical age determination for the open clusters M67 \citep{stello2016} and NGC~6819 \citep{casagrande2016}.
+
+We compare the solutions found using this set of fitting parameter with those found using only spectroscopic input in Figure~\ref{masses}, and we find that the change in median stellar parameters between the two results is small for all analyzed red giants.
+However, in the comparison plot it becomes visible how adding the asteroseismic constraints to the fit narrows down the parameter space and thus decrease the derived uncertainties.
 

### 2018-11-21 paper/ms.tex
new abundances from madeline and keith
keith comment implemented, removed

@@
 
-{\bf Ben the tables should be remade to do Mg, Ti, Si, Ca, Al, V, Fe, Ni in on Table called differential abundances and second table of Sr, Y, Zr, Ba, La, Nd, Eu which is for the non-differential neutron capture} The results of these absolute abundance calculations {\bf without the line-by-line differential analysis implemented?}, are presented in Tables~\ref{elems1},~\ref{elems2} and~\ref{elems3}.
-Because for most  Arcturus differential abundances are not available, these are provided as supplementary online-only material.
 \input{stellar_props.tex}
@@
 \input{abundances_2.tex}
-\input{abundances_3.tex}
 

### 2018-11-21 paper/ms.tex
remove rubric
indigenous acknowledgement

@@
 Considering stars lying close to the main sequence, from the \kepler power spectrum we identify solar-like oscillations in HD~182354 and HD~176209 at frequencies consistent with them being subgiants or contaminated with flux from red giants.
-\textcolor{red}{Get frequencies}.
 
@@
 
-\textcolor{red}{Ashley/Dan/Vichi?}
-
 \subsubsection{Binaries}
@@
 We give blessings and thanks to the Lenape people and Lenape Nations in recognition that we are carrying out this work on their indigenous homelands.
-We would like to acknowledge the Gadigal people of the Eora Nation and the Norongerragal and Gweagal peoples of the Tharawal Nation as the traditional owners of the land at the University of Sydney and the Sutherland Shire on which some of this work was carried out, and pay their respects to their knowledge, and their elders past, present and future.
+We would like to acknowledge the Gadigal Clan of the Eora Nation as the traditional owners of the land on which the University of Sydney is built and on which some of this work was carried out, and pay their respects to their knowledge, and their elders past, present and future.
 

### 2018-11-21 paper/ms.tex
remove comments
author list

@@
 Timothy R. White,$^{7,5}$\newauthor
-Timothy R. Bedding,$^{8,5}$
-Allyson Bieryla,$^{9}$
-David W. Latham,$^{9}$,
-Conny Aerts,$^{10,11,12}$\newauthor
-Suzanne Aigrain,$^{3}$ 
+Allyson Bieryla,$^{8}$
+David W. Latham,$^{8}$,
+Conny Aerts,$^{9,10,11}$
+Suzanne Aigrain,$^{3}$ \newauthor
 Victoria Antoci,$^{5}$
+Timothy R. Bedding,$^{12,5}$
 Dominic M. Bowman,$^{10}$
 Ashley Chontos,$^{13}$\newauthor
-Gilbert A. Esquerdo,$^{9}$
+Gilbert A. Esquerdo,$^{8}$
 Daniel Huber,$^{13,14,8}$
 Paula Jofr\'{e},$^{15}$
-Simon Murphy,$^{8,5}$\newauthor
-Timothy van Reeth,$^{8,5}$
+Simon Murphy,$^{12,5}$\newauthor
+Timothy van Reeth,$^{12,5}$
 Victor Silva Aguirre,$^{5}$
 Amalie Stokholm,$^{5}$
-Jie Yu,$^{8,5}$ \newauthor
-and friends
+Jie Yu$^{12,5}$ 
 \\
@@
 $^{7}$Research School of Astronomy and Astrophysics, Mount Stromlo Observatory, The Australian National University, Canberra, ACT 2611, Australia\\
-$^{8}$Sydney Institute for Astronomy (SIfA), School of Physics, University of Sydney, NSW 2006, Australia\\
-$^{9}$Harvard-Smithsonian Center for Astrophysics, 60 Garden Street, Cambridge, MA 02138, USA\\
-$^{10}$Institute of Astronomy, KU Leuven, Celestijnenlaan 200D, B-3001 Leuven, Belgium\\
-$^{11}$Department of Astrophysics, IMAPP, Radboud University Nijmegen, P.O. Box 9010, 6500 GL Nijmegen, The Netherlands\\
-$^{12}$Kavli Institute for Theoretical Physics, University of California, Santa Barbara, CA 93106, USA\\
+$^{8}$Harvard-Smithsonian Center for Astrophysics, 60 Garden Street, Cambridge, MA 02138, USA\\
+$^{9}$Institute of Astronomy, KU Leuven, Celestijnenlaan 200D, B-3001 Leuven, Belgium\\
+$^{10}$Department of Astrophysics, IMAPP, Radboud University Nijmegen, P.O. Box 9010, 6500 GL Nijmegen, The Netherlands\\
+$^{11}$Kavli Institute for Theoretical Physics, University of California, Santa Barbara, CA 93106, USA\\
+$^{12}$Sydney Institute for Astronomy (SIfA), School of Physics, University of Sydney, NSW 2006, Australia\\
 $^{13}$Institute for Astronomy, University of Hawai'i, 2680 Woodlawn Drive, Honolulu, HI 96822, USA\\
@@
 
-%\begin{figure*}
-%\noindent\includegraphics[width=\textwidth,keepaspectratio]{Pope_spectra_alphaele.pdf}
-%
-%\caption{\label{alphael}
-%The [Mg/Fe], [Si/Fe], [Ca/Fe], and [Ti/Fe], [Al/Fe], [Na/Fe] abundance ratios as a function of iron on the top and bottom rows, respectively for our stars (black cirlces).
-We also illustrate a representative sample of Galactic disk stars from \citet[open red square,][]{Bensby2014} and \citet[open orange triangles,][]{Adibekyan2012}.
-}
-%\end{figure*}
-
 \begin{figure*}
@@
 The chemical abundance ratios in each element are consistent, within the uncertainties (of order $\sim$0.10--0.15~dex for most elemental abundance ratios in Hypatia and up to $\sim$0.05~dex here).
-
-%place [X/Fe] vs [Fe/H] diagrams here and discuss which Galactic populations these stars come from.
-May also want to discuss how these span the typical Galactic populations and can act as benchmark stars for APOGEE or other large surveys
 
@@
 
-%\appendix
-%\section{Full Chemical Analysis}
-%The chemical composition for each star was measured in the $\alpha$ (Mg, Ti, Si, Ca), odd-Z (Al, Cu, Sc, V), Fe-peak (Fe, Ni, Zn, Co, Cr, Mn), and neutron capture (Sr, Y, Zr, Ba, La, Nd, Eu) elemental families.
-In Fig.~\ref{fig:alphael}, we show the chemical abundance pattern of [Mg/Fe] as a function of metallicity of our sample (in black) as well two representative Galactic disk samples.
-It is clear from that figure that our sample is largely drawn from the Galactic disk from a chemical perspective.
-Below we provide further evidence of this with other elements across three families.
-%
-%In Fig.~\ref{fig:alphael_appendix}, we display the abundances of the remaining $\alpha$-elements (including Ti, Si, Ca) as well as the odd-Z elements (Al, Cu, Sc, V).
-In Fig.~\ref{fig:Fepeak_appendix} we show the Fe-peak elements (Fe, Ni, Zn, Co, Cr, Mn) and in Fig.~\ref{fig:ncapture_appendix}  we show the Neutron-Capture elements.
-In each diagram we plot the [X/Fe] abundance ration as a function of metallicity.
-For reference, the typical chemical abundances pattern in the Galactic disk is shown for each element and are taken from Bensby2014, Adibekyan2012,
-
 \section*{Acknowledgements} % add your acknowledgements text here!

### 2018-11-21 paper/ms.tex
Author list

@@
 Timothy R. White,$^{7,5}$\newauthor
+Amalie Stokholm,$^{5}$
 Allyson Bieryla,$^{8}$
 David W. Latham,$^{8}$,
-Conny Aerts,$^{9,10,11}$
-Suzanne Aigrain,$^{3}$ \newauthor
+Conny Aerts,$^{9,10,11}$\newauthor
+Suzanne Aigrain,$^{3}$ 
 Victoria Antoci,$^{5}$
 Timothy R. Bedding,$^{12,5}$
-Dominic M. Bowman,$^{10}$
-Ashley Chontos,$^{13}$\newauthor
+Dominic M. Bowman,$^{10}$\newauthor
+Ashley Chontos,$^{13}$
 Gilbert A. Esquerdo,$^{8}$
 Daniel Huber,$^{13,14,8}$
-Paula Jofr\'{e},$^{15}$
-Simon Murphy,$^{12,5}$\newauthor
+Paula Jofr\'{e},$^{15}$\newauthor
+Simon Murphy,$^{12,5}$
 Timothy van Reeth,$^{12,5}$
 Victor Silva Aguirre,$^{5}$
-Amalie Stokholm,$^{5}$
 Jie Yu$^{12,5}$ 

### 2018-11-22 paper/ms.tex
author list
add madeline

@@
 Allyson Bieryla,$^{8}$
-David W. Latham,$^{8}$,
+David W. Latham,$^{8}$wb
 Conny Aerts,$^{9,10,11}$\newauthor
@@
 Simon Murphy,$^{12,5}$
+Madeline Lucy,$^{6}$
 Timothy van Reeth,$^{12,5}$

### 2018-11-22 paper/ms.tex
remove typo
author list

--- 2018-11-21 paper/ms.tex
@@
 Allyson Bieryla,$^{8}$
-David W. Latham,$^{8}$,
+David W. Latham,$^{8}$
 Conny Aerts,$^{9,10,11}$\newauthor
@@
 Paula Jofr\'{e},$^{15}$\newauthor
+Madeline Lucy,$^{6}$
 Simon Murphy,$^{12,5}$
-Timothy van Reeth,$^{12,5}$
+Timothy van Reeth,$^{12,5}$\newauthor
 Victor Silva Aguirre,$^{5}$

### 2018-12-01 paper/ms.tex
lucey

@@
 Paula Jofr\'{e},$^{15}$\newauthor
-Madeline Lucy,$^{6}$
+Madeline Lucey,$^{6}$
 Simon Murphy,$^{12,5}$

### 2018-12-04 paper/ms.tex
bedding revisions complete

--- 2018-11-22 paper/ms.tex
@@
 Gilbert A. Esquerdo,$^{8}$
-Daniel Huber,$^{13,14,8}$
-Paula Jofr\'{e},$^{15}$\newauthor
-Madeline Lucy,$^{6}$
-Simon Murphy,$^{12,5}$
+Daniel Huber,$^{13}$
+Paula Jofr\'{e},$^{14}$\newauthor
+Madeline Lucey,$^{6}$
+Simon J. Murphy,$^{12,5}$
 Timothy van Reeth,$^{12,5}$\newauthor
@@
 $^{13}$Institute for Astronomy, University of Hawai'i, 2680 Woodlawn Drive, Honolulu, HI 96822, USA\\
-$^{14}$SETI Institute, 189 Bernardo Avenue, Mountain View, CA 94043, USA\\
-$^{15}$N\'{u}cleo de Astronom\'{i}a, Facultad de Ingenier\'{i}a y Ciencias, Universidad Diego Portales, Ej\'{e}rcito 441, Santiago De, Chile\\
+$^{14}$N\'{u}cleo de Astronom\'{i}a, Facultad de Ingenier\'{i}a y Ciencias, Universidad Diego Portales, Ej\'{e}rcito 441, Santiago De, Chile\\
 }
@@
 \begin{abstract}
-Here we present the first data release of the \kepler Smear Campaign, using collateral `smear' data obtained by \kepler to reconstruct light curves of 102~stars too bright to have been otherwise targeted.
+We present the first data release of the \kepler Smear Campaign, using collateral `smear' data obtained in the \kepler four-year mission to reconstruct light curves of 102~stars too bright to have been otherwise targeted.
 We describe the pipeline developed to extract and calibrate these light curves, and show that we attain photometric precision comparable to stars analyzed by the standard pipeline in the nominal \kepler mission.
-In this Paper, we focus in particular on a subset of these consisting of 66~red giants for which we detect solar-like oscillations.
+In this Paper, we focus on 66~red giants for which we detect solar-like oscillations, characterizing 34 of these in detail with spectroscopic chemical abundances and asteroseismic masses as benchmark stars.
+We also classify the whole sample, finding nearly all to be variable, with classical pulsations and binary effects.
 All source code, light curves, TRES spectra, and asteroseismic and stellar parameters are publicly available as a \kepler legacy sample.
@@
 \kepler has revolutionized the field of asteroseismology for solar-like oscillations \citep{2010PASP..122..131G,2010ApJ...713L.169C}.
-It has yielded the detection of gravity-mode period spacings in a red giant \citep{rggmodes,2014A&A...572L...5M}, enabling probes of interior rotation of red giants \citep{rggmoderotation,2012A&A...548A..10M} and distinguishing between hydrogen- and helium-burning cores \citep{rggmodehelium,2012A&A...540A.143M}.
-It has also permitted the determination of ages and fundamental parameters of main-sequence stars as cool as the Sun and hotter \citep{silvaages}, including planet-hosting stars \citep{huberplanetages,silvaplanetages,2018MNRAS.479.4786V}, revealing the most ancient known planetary system, dating back to the earliest stages of the galaxy \citep{ancientplanets}.
-%By comparing asteroseismic stellar ages to stellar rotation periods, \citet{angusgyro} have shown that gyrochronology models cannot fit the data with a single relation, leading~\citet{vansadersgyro}~to suggest a qualitative change in dynamo mechanism as stars age through the main sequence.
-\newpage
+It has yielded the detection of gravity-mode period spacings for red giants \citep{rggmodes,2014A&A...572L...5M}, enabling probes of interior rotation \citep{rggmoderotation,2012A&A...548A..10M,2012ApJ...756...19D} and distinguishing between hydrogen- and helium-burning cores \citep{rggmodehelium,2012A&A...540A.143M}.
+It has also permitted the determination of ages and fundamental parameters of cool main-sequence stars \citep{silvaages}, including planet-hosting stars \citep{huberplanetages,silvaplanetages,2016MNRAS.456.2183D,2018MNRAS.479.4786V}.
+%revealing the most ancient known planetary system, dating back to the earliest stages of the galaxy \citep{ancientplanets}.
+%By comparing asteroseismic stellar ages to stellar rotation periods, \citet{angusgyro} have shown that gyrochronology models cannot fit the data with a single relation, leading~\citet{vansadersgyro}~to suggest a qualitative change in dynamo mechanism as stars age through the main-sequence.
 
-A major outcome of the \kepler asteroseismology programme is a legacy sample of extremely well characterized stars that can serve as benchmarks for future work \citep{keplerlegacy1,keplerlegacy2}.
+A major outcome of the \kepler asteroseismology programme is a legacy sample of extremely well characterized stars that can serve as benchmarks for future work \citep{keplerlegacy1,keplerlegacy2,silvaplanetages,2016MNRAS.456.2183D}.
 Asteroseismological studies with \kepler complement other probes of stellar physics well: for example, the APOKASC sample of~1916 spectroscopically- and asteroseismically-characterized red giant stars \citep{2014ApJS..215...19P}.
@@
 To this end, 34~FGK stars including both giants and dwarfs have been chosen as \gaia-ESO benchmark stars for which metallicities \citep{gaiabenchmark1}, effective temperatures and asteroseismic surface gravities \citep{gaiabenchmark3}, and relative abundances of $\alpha$ and iron-peak elements \citep{gaiabenchmark4} have been determined.
-This includes only four main sequence stars much cooler than the Sun, due to the paucity of such stars with asteroseismology.
+This includes only four main-sequence stars much cooler than the Sun, due to the paucity of such stars with asteroseismology.
 This has been accompanied by the release of high resolution spectra \citep{gaiabenchmark2} and formed the basis of extensions to lower metallicities \citep{gaiabenchmark5}, stellar twin studies \citep{gaiabenchmarktwins} and comparisons of stellar abundance determination pipelines \citep{gaiabenchmarkabundances}.
@@
 We find no transiting planets, but detect one new eclipsing binary, and measure solar-like oscillations in 34~red giants.
-We do not model main sequence stars in great detail, but provide some discussion and initial classification of interesting variability.
+We do not model main-sequence stars in great detail, but provide some discussion and initial classification of interesting variability.
 For the oscillating red giants that constitute the bulk of the sample, we determine the asteroseismic parameters \numax and \Dnu, and therefore stellar masses and \logg measurements.
@@
 
-We selected as our sample all stars on-silicon in \kepler with $Kp<9$ that were targeted for fewer than an arbitrary $8$ quarters, the majority of which were previously entirely missing.
-Sixteen stars were to some extent observed conventionally: HD~174020 was targeted in LC for Q2, 6, 10, and 14; HD~175841 for Q11-12, 14-16, with SC for Q3; HD~176582 for Q12-13; HD~178090 for Q1, 3, and 10; HD~180682 for Q0, 3, and 7; HD~181069 for Q1, 10, 13, 14, and 17; HD~181878 for Q14-17; HD~182694 for Q2; HD~183124 for even quarters; HD~185351 for Q1-3 and with SC for Q16; HD~186155 for only Q1; HD~187217 for Q14-17; HD~188252 for only Q13; HD~189013 with SC for Q3 as a $\gamma$~Dor; V380~Cyg for Q11 and with SC for Q7, 9, 10, 12-17; and V819~Cyg for Q14, 16 and 17.
+We selected all stars on-silicon in \kepler with $Kp<9$ that were targeted for fewer than $8$ quarters.
+The majority of these were not previously targeted at all, but sixteen stars were to some extent observed conventionally: HD~174020 was targeted in LC for Q2, 6, 10, and 14; HD~175841 for Q11-12, 14-16, with SC for Q3; HD~176582 for Q12-13; HD~178090 for Q1, 3, and 10; HD~180682 for Q0, 3, and 7; HD~181069 for Q1, 10, 13, 14, and 17; HD~181878 for Q14-17; HD~182694 for Q2; HD~183124 for even quarters; HD~185351 for Q1-3 and with SC for Q16; HD~186155 for only Q1; HD~187217 for Q14-17; HD~188252 for only Q13; HD~189013 with SC for Q3 as a $\gamma$~Dor; V380~Cyg for Q11 and with SC for Q7, 9, 10, 12-17; and V819~Cyg for Q14, 16 and 17.
 A number of these lay at the edge of a detector, with the result that in some cadences the centroid of the star did not lie on the chip; light curves from these targets were found to be of extremely low quality and all of these stars were discarded.
-After applying these criteria we obtained a list of 102 targets, which are listed in Table~\ref{all_stars} with their \kepler magnitude $Kp$ together with their spectral type from SIMBAD, \gaia~DR2 apparent~$G$ magnitudes and $Bp-Rp$ colours, \gaia~DR2 calibrated distances from \citet{gaiadists}, variability classification and availability of TRES spectroscopy.
+After applying these criteria we obtained a list of 102 targets, which are listed in Table~\ref{all_stars} with their \kepler magnitude $Kp$, together with their spectral type from SIMBAD, \gaia~DR2 apparent~$G$ magnitudes and $Bp-Rp$ colours, \gaia~DR2 calibrated distances from \citet{gaiadists}, variability classification and availability of TRES spectroscopy.
 The \kepler spacecraft rotates between quarters, so that it cycles through four orientation `seasons' each rotated from the last by $90^{\circ}$.
-Some stars did not land on silicon for all seasons: we have only one season of HD~179394; two for HD~187277, HD~226754, V554~Lyr, and BD+47~2891; and three for BD+43~3064.
+Some stars were not on silicon for all seasons: we have only one season of HD~179394; two for HD~187277, HD~226754, V554~Lyr, and BD+47~2891; and three for BD+43~3064.
 The addition of our sample to the conventionally-observed stars makes the \kepler survey magnitude-complete down to $Kp=9$ for all stars on-silicon.
@@
 Figure~\ref{hrdiagram} shows these stars on a colour-magnitude diagram using \gaia $Bp-Rp$ and absolute~$G$ magnitudes and \gaia~DR2 calibrated distances \citep{gaiadists}, overlaid on the \kepler sample from the Bedell \url{gaia-kepler.fun} crossmatch.
-The smear targets in this diagram appear to have not merely higher apparent brightnesses than the general \kepler population, but also higher intrinsic luminosities.
+The smear targets in this diagram selected to have higher apparent brightnesses than the general \kepler population, appear also to have higher intrinsic luminosities.
 While this could simply arise from being selected for their apparent brightness, it is {}worth considering whether this is because of a bias in their parallax measurements.
-While \gaia parallaxes for very bright stars can be subject to systematic error, we have compared these to those found by \emph{Hipparcos} \citep{vanleeuwen07b}, and found close agreement for the brightest stars, with a scatter that increases with magnitude.
-We therefore suggest that parallax bias is not the reason for the smear sample sitting above the remainder of the \kepler sample.
+While \gaia parallaxes for very bright stars can be subject to systematic error, we have compared to \emph{Hipparcos} \citep{vanleeuwen07b}, and found close agreement for the brightest stars, with a scatter that increases with magnitude.
+We therefore suggest that parallax bias is not the reason for the smear sample sitting above the majority of the \kepler sample.
 
-We identify the evolutionary state of stars in the main sequence versus evolved stars first from the \gaia colour-magnitude diagram in Figure~\ref{hrdiagram}.
-Taking a cutoff in \gaia $Bp-Rp > 1$, we identify 66 of these stars as evolved systems, and the remaining~36 lie apparently on the main sequence.
+We identify the evolutionary state of main-sequence versus evolved stars from the \gaia colour-magnitude diagram in Figure~\ref{hrdiagram}.
+Taking a cutoff in \gaia $Bp-Rp > 1$, we identify 66 of these stars as evolved systems, and the remaining~36 lie on the main-sequence.
 
-The coolest main sequence star, BD+43~3068, is a G0 dwarf with a $G$ magnitude of 8.3 and a distance of $53.8 \pm 0.1$~pc, and it is therefore surprising that it was not included in the nominal \kepler survey as a solar analogue.
-It is possible that it was previously misidentified as a giant.
-Regrettably, it is only possible to reconstruct a light curve with the 30~minute long cadence and therefore it is not possible to do asteroseismology on this bright, nearby solar-like star.
+The coolest main-sequence star, BD+43~3068 (SAO~47785), is a G0 dwarf with a $G$ magnitude of 8.3 and a distance of $53.8 \pm 0.1$~pc, and it is therefore surprising that it was not included in the nominal \kepler survey as a solar analogue.
+It is only possible to reconstruct a light curve with the 30~minute long cadence and therefore it is not possible to do asteroseismology on this bright, nearby solar-like star.
 Its light curve shows neither rotational modulation (as determined by its featureless autocorrelation) nor evidence for transits.
 
-Considering stars lying close to the main sequence, from the \kepler power spectrum we identify solar-like oscillations in HD~182354 and HD~176209 at frequencies consistent with them being subgiants or contaminated with flux from red giants.
+Considering stars lying close to the main-sequence, from the \kepler power spectrum we identify solar-like oscillations in HD~182354 and HD~176209 at frequencies consistent with them being subgiants or contaminated with flux from red giants.
 
@@
 
-In preparing light curves of the \kepler smear stars, we have followed the methods described in \citet{smear}, with some improvements.
-We selected our input RA and Dec values from the \kepler Input Catalog (KIC) \citep{kic}, and queried MAST to find the corresponding mean pixel position for a given \kepler quarter.
+In generating light curves of the \kepler smear stars, we have followed the methods described by \citet{smear}, with some improvements.
+We selected our input RA and Dec values from the \kepler Input Catalog (KIC) \citep{kic}, and queried MAST to find the corresponding mean pixel position for each \kepler quarter.
 We then measured the centroid of smear columns in the vicinity, and used these values to do raw aperture photometry.
-We found that the cosine-bell aperture used for raw photometry in \citet{smear} can in some light curves introduce position-dependent systematics and jumps.
-We instead in this work have applied a super-Gaussian aperture, $A \propto \exp{\dfrac{-(x-x_0)}{w} ^ 4}$, where $x_0$ is the centroid and $w$ a width in pixels.
+We found that the cosine-bell aperture used for raw photometry by \citet{smear} can sometimes introduce position-dependent systematics and jumps.
+We instead used a super-Gaussian aperture, $A \propto \exp{\dfrac{-(x-x_0)}{w} ^ 4}$, where $x_0$ is the centroid and $w$ is the width in pixels.
 The very flat top of this function helps avoid significant variation with position, while still smoothly rolling off at the edges to avoid discontinuous artefacts.
-This is calculated on a grid of $10\,\times$ subsampled points in pixel space so that the sharply varying edge changes column weights smoothly as a function of centroid.
-We have then extracted photometry using apertures with a range of widths $w \in\{1.5,~2,~3,~4,~5\}$ pixels.
+The super-Gaussian is calculated on a grid of $10\,\times$ subsampled points in pixel space so that the sharply varying edge changes column weights smoothly as a function of centroid.
+We then extracted photometry using apertures with a range of widths $w \in\{1.5,~2,~3,~4,~5\}$ pixels.
 
-From this raw photometry a background light curve was subtracted, which corrects for time-varying global systematics.
-Whereas in \citet{smear} we subtracted a background estimate chosen manually, for this larger set of light curves, we have now chosen the lowest $25\%$ of pixels by median flux as being unlikely to be contaminated by stars, and taken our background level to be the median of this at each time sample.
-To denoise this, we fit a Gaussian Process with a 30-day timescale squared exponential kernel using \textsc{george} \citep{hodlr}, and our final background light curve is taken to be the posterior mean of this GP.
+From this raw photometry a background light curve was subtracted, correcting for time-varying global systematics.
+Whereas in \citet{smear} we subtracted a background estimated manually, for this larger set of light curves, we have chosen the lowest $25\%$ of pixels by median flux as being unlikely to be contaminated by stars, and taken our background level to be the median of this at each time sample.
+To reduce the noise in this background model, we fitted a Gaussian Process with a 30-day timescale squared exponential kernel using \textsc{george} \citep{hodlr}, and our final background light curve is taken to be the posterior mean of this GP.
 
-The dominant source of residual systematic errors in nominal \kepler time series is a common-mode variation primarily due to thermal changes on board the spacecraft, an issue which is traditionally dealt with by identifying and fitting a linear combination of systematic modes \citep{pdc0,pdc1,pdc2,petigura}.
+The dominant source of residual systematic errors in nominal \kepler time series is a common-mode variation primarily due to thermal changes on board the spacecraft, an issue that is traditionally dealt with by identifying and fitting a linear combination of systematic modes \citep{pdc0,pdc1,pdc2,petigura}.
 We have adopted the same approach here, using the \kepler Pre-search Data Conditioning (PDC) Cotrending Basis Vectors (CBVs) available from MAST, finding least-squares fits of either the first~4 or~8 CBVs to each light curve.
-This can subtract astrophysical signals on long timescales, such that we use and recommend 4~CBV light curves for stars with variability on timescales longer than $\sim 5$ days, or indeed raw uncorrected lightcurves for stars variable at high amplitude on $\sim$~quarter timescales, but otherwise we recommend the 8~CBV light curves.
+This can remove astrophysical signals having long timescales, and so we use and recommend 4~CBV light curves for stars with variability on timescales longer than $\sim 5$ days, or indeed raw uncorrected lightcurves for stars variable at high amplitude on $\sim$~quarter timescales, but otherwise we recommend the 8~CBV light curves.
 There is some room for improvement here by simultaneously modelling astrophysical and instrumental variations, but this is beyond the scope of this paper.
-In the following, we will use the light curves with the lowest 6.5~hr Combined Differential Photometric Precision (CDPP) \citep{cdpp} out of all apertures, as calculated with the \textsc{k2sc} implementation \citep{k2sc}.
-This is not necessarily the optimal choice for all red giants, especially those with oscillations on a 6.5~h timescale, but is a reasonable proxy nevertheless for white noise and leads to satisfactory results upon visual inspection of the present sample.
+In the following, we use the light curves with the lowest 6.5~hr Combined Differential Photometric Precision (CDPP) \citep{cdpp} out of all apertures, as calculated with the \textsc{k2sc} CDPP implementation \citep{k2sc}.
+This is not necessarily the optimal choice for all red giants, especially those with oscillations on a 6.5~h timescale, but is a reasonable proxy for white noise and leads to satisfactory results upon visual inspection of the present sample.
 
@@
 Because the smear data are collected along an entire CCD~column, there is the risk of contamination from other bright stars.
-This is especially true in doing asteroseismology of red giants, where the low-amplitude stochastically-excited oscillations can be washed out in a power spectrum by the coherent high amplitude variations of a classical pulsator, even if the background star is much fainter.
-We can assess the importance of this contamination by considering the differences between odd and even quarters: because the \kepler spacecraft rotates $90^{\circ}$ between successive quarters, any contaminant will lie in the same column as a smear target only every second quarter, falling in the other quarters in the same row but not necessarily the same column.
-We have therefore generated Lomb-Scargle periodograms \citep{lomb,scargle} of each light curve, clipped for outliers, and considering only odd and even quarters, and both visually inspected these for significant differences.
+This is especially true when doing asteroseismology of red giants, where the low-amplitude stochastically-excited oscillations can be washed out in a power spectrum by the coherent high amplitude variations of a classical pulsator, even if the background star is much fainter.
+We can assess the importance of this contamination by considering the differences between odd and even quarters: because the \kepler spacecraft rotates $90^{\circ}$ between successive quarters, any contaminant will lie in the same column as a smear target only every second quarter.
+We have therefore generated Lomb-Scargle periodograms \citep{lomb,scargle} of each light curve, after clipping for outliers.
+We consider only odd and even quarters separately, and also the full combined time series.
 In the great majority of cases they closely resemble one another, indicating that contamination is at worst a minor effect.
-In order to better quantify this, we compute the inner product of  normalized periodograms of the odd and even quarters each smoothed with a 3-element Gaussian kernel.
+In order to better quantify this, we computed the inner product of normalized periodograms of the odd and even quarters, each smoothed with a 3-element Gaussian kernel.
 If this overlap integral is 1, then the power spectra are identical; substantial departures from unity may be caused by real nonstationary or long-period stellar variation, noise, or gain or contamination differences between the seasons.
-We find that the distribution of overlaps is strongly peaked around $\sim 0.91$, with a tail of 22 stars showing overlap $< 0.9$.
-We investigate these further, finding that in not all of these cases is there an obvious problem, for example the classical pulsator HD~175841 in which amplitudes of several pulsations have changed but the overall distribution seems very similar, in which we conclude that the variation is probably astrophysical or an artefact of our data processing.
+We found that the distribution of overlaps (Figure~\ref{contamination2}) is strongly peaked around $\sim 0.91$, with a tail of 22 stars showing overlap $< 0.9$.
+We investigate these further, finding that in some of these cases  there was no obvious problem.
+For example, the classical pulsator HD~175841 showed amplitude changes of several pulsations but the overall distribution seemed very similar, from which we conclude that the variation is probably astrophysical.
 
@@
 Histogram over overlap integrals of smoothed periodograms of odd and even quarters for each star in the sample.
-The peak at $\sim 0.91$ contains normal stars with limited contamination; we investigate the 22 stars with overlaps below 0.9 for which there is a significant risk of contamination.}
+The peak at $\sim 0.91$ contains normal stars with limited contamination; we investigate the 22 stars with overlaps below 0.9 for which there is a significant possibility of contamination.}
 \end{figure}
@@
 
-Among the~66 red giants identified in this sample, for~32 the timescale of their variability is of the same order as a \kepler quarter and they are thus badly affected by systematics and systematics correction.
-In Table~\ref{all_stars} we have noted these as `long-period variables' (LPVs), without specifically meaning these are LPVs by a particular astrophysical definition, and they are discussed further in Section~\ref{lpvs}.
-For the~34 giants for which there is high-SNR shorter-timescale variability, we have attempted to extract the asteroseismic parameters \numax and $\langle \Dnu \rangle$ \citep{KB95,2013ARA&A..51..353C}.
+Among the~66 red giants identified in this sample, for~32 the timescale of their variability is similar to the length of a \kepler quarter and they are thus badly affected by systematics and systematics correction.
+In Table~\ref{all_stars} we have noted these as `long-period variables' (LPVs).
+For the~34 giants for with high-SNR shorter-timescale variability, we have attempted to extract the asteroseismic parameters \numax and $\langle \Dnu \rangle$ \citep{KB95,2013ARA&A..51..353C}.
 These constrain fundamental stellar parameters through the approximate scaling relations:
@@
 \begin{equation}
+\label{Dnuscaling}
 \langle \Dnu \rangle \propto \sqrt{\langle \rho \rangle} = \sqrt{M {R}^{-3}}
@@
 We have followed the method of \citet{2016AN....337..774D}, obtaining a Lomb-Scargle periodogram of the smoothed time series according to the method of \citet{2011MNRAS.414L...6G}.
-The posterior distribution of the asteroseismic parameters is obtained with a Markov Chain Monte Carlo fit to the smoothed periodogram, applying the combined granulation and oscillation model of \citet{2014A&A...570A..41K}.
-This consists of two Harvey profiles for the granulation \citep{1985ESASP.235..199H}, a Gaussian envelope for the stellar oscillations, and a white noise background for instrumental noise.
+The posterior distribution of the asteroseismic parameters was obtained with a Markov Chain Monte Carlo fit to the smoothed periodogram, applying the combined granulation and oscillation model of \citet{2014A&A...570A..41K}.
+This consists of two Harvey profiles for the granulation \citep{1985ESASP.235..199H}, a Gaussian envelope for the stellar oscillations, and a white noise background for photon noise.
 The marginal posterior distribution for the oscillation envelope is well-approximated by a single Gaussian, and we have taken its median and standard deviation to be our estimates for \numax and its uncertainty.
 
-To estimate \Dnu, we have divided the power spectrum through by the granulation and noise models to obtain a signal-to-noise spectrum, and fit a sum of Lorentzians separated by mean large (\Dnu) and small (\dnu) separations to the part of this spectrum in the vicinity of \numax.
-In practice, for this dataset, \dnu is not constrained, but mean $\langle \Dnu \rangle$ is typically well-constrained and its posterior marginal distribution is well-represented by a single Gaussian as with \numax.
+To estimate \Dnu, we divided the power spectrum by the granulation and noise models to obtain a signal-to-noise spectrum, and fit a sum of Lorentzians separated by mean large (\Dnu) and small (\dnu) separations to the part of this spectrum in the vicinity of \numax.
+For this dataset, \dnu is not constrained, but mean $\langle \Dnu \rangle$ is typically well-constrained and its posterior marginal distribution is well-represented by a single Gaussian.
 
-We obtain good estimates of these asteroseismic parameters for 34 targets, presented in Table~\ref{astero_table}.
-In the remainder of cases, as noted above, we find that the very-low-frequency ($\lesssim 2\muHz$) oscillations are affected by filter artefacts from detrending, and we are not able to obtain good estimates for these stars.
+We obtained good estimates of these asteroseismic parameters for 34 targets, presented in Table~\ref{astero_table}.
+In the remainder of cases, as noted above, very-low-frequency ($\lesssim 2\muHz$) oscillations are affected by filter artefacts from detrending, and we were not able to obtain good estimates for these stars.
 
-Once \numax has been estimated, we have used Equation~\ref{scaling}, the asteroseismic scaling relation for \numax \citep{1991ApJ...368..599B,KB95}, to estimate \logg in order to inform extraction of chemical abundances from spectra.
-Using the initial spectroscopic estimate of \teff, which is not significantly informed by \numax, uncertainties in \numax are propagated with Monte Carlo sampling.
+We have used Equation~\ref{scaling}, the asteroseismic scaling relation for \numax \citep{1991ApJ...368..599B,KB95}, to estimate \logg in order to inform extraction of chemical abundances from spectra.
+Using the initial spectroscopic estimate of \teff, which is not dependent on \numax, uncertainties in \numax were propagated with Monte Carlo sampling.
 
-For eight stars, we have found that the asteroseismic fit is unsatisfactory: for BD+39~388 we cannot detect the expected oscillations; for BD+43~3064 there are significant peaks but these are not consistent with the pattern expected from a red giant; for HD~179959 and HD~187217 we suspect contamination with the oscillations of a second giant, which is hard to remove from smear light curves; while for HD~188629, HD~188639 and HD~188875 we can extract a \numax but not a robust \Dnu.
-One star in our sample, HD~185351, has a mode envelope that is not well fit by our model.
-The smear light curve for this star has already been published by \citet{2017MNRAS.464.3713H}, who showed with detailed asteroseismic modelling that it had a zero-age main sequence mass of $\sim 1.60 \msun$ (a so-called `retired~A star') and used it to calibrate the convective overshoot parameter for low-luminosity red giants.
+For eight stars, we found that the asteroseismic fit is unsatisfactory: for BD+39~388 we cannot detect the expected oscillations; for BD+43~3064 there are significant peaks but these are not consistent with the pattern expected from a red giant; for HD~179959 and HD~187217 we suspect contamination with the oscillations of a second giant, which is hard to remove from smear light curves; for HD~188629, HD~188639 and HD~188875 we can extract a \numax but not a robust \Dnu.
+The `retired~A star' HD~185351 \citep[studied by][]{2014ApJ...794...15J}, has a mode envelope that is not well fit by our model.
+The smear light curve for this star has already been published by \citet{2017MNRAS.464.3713H}, who showed with detailed asteroseismic modelling that it had a zero-age main-sequence mass of $\sim 1.60 \msun$ (a so-called `retired~A star') and used it to calibrate the convective overshoot parameter for low-luminosity red giants.
 The global asteroseismic modelling presented here should therefore be considered to be superseded by the more detailed model of \citet{2017MNRAS.464.3713H}.
@@
 Operating with spectral resolving power $R=44 000$, we have obtained spectra with signal-to-noise ratios (SNRs) of tens to hundreds per resolution element.
-Although this resolution and SNR are sufficient for an exploratory study, for more detailed analysis it will be desirable to use APOGEE or similar instruments to obtain greater spectral coverage.
-From this observing run we have~34 unique targets with seismic \logg and spectra, one more star than the \gaia-ESO benchmark set and a significant addition to the ensemble of bright red giants with asteroseismic parameter determinations.
-Due to observing constraints, we were unable to obtain spectra for BD+42~3150, BD+48~2904, HD~176209, HD~182354, HD~189636AB, or HD~189750.
+Although this resolution and SNR are sufficient for an exploratory study, a more detailed analysis will require APOGEE or a similar instrument to obtain greater spectral coverage.
+From this observing run we have~33 unique targets with seismic \logg and spectra, the same as in the \gaia-ESO benchmark set and a significant addition to the ensemble of bright red giants with asteroseismic parameter determinations.
+%Due to observing constraints, we were unable to obtain spectra for BD+42~3150, BD+48~2904, HD~176209, HD~182354, HD~189636AB, or HD~189750.
 % figure out this discrepancy?
 
-To derive stellar parameters from our TRES spectra, we initially ran the Stellar Parameter Classification \citep[SPC:][]{spc} code to determine \teff and \logg, using the SPC \teff to inform the asteroseismic estimation of \logg from \numax.
-For deriving abundances, \teff is fixed from the results of an initial SPC fit, while \logg is fixed to the seismic values.
-The other stellar atmospheric parameters including the microturbulent velocity ($v_{\text{mic}}$), and broadening (convolution by $V_{\text{mac}}$, $v_{\sin{i}}$ and the instrumental line profile) as well as [Fe/H] and chemical abundances for 20 chemical species are derived using the Brussels Automatic Code for Characterizing High accUracy Spectra \citep[BACCHUS:][]{bacchus}, and the results from this calculation are displayed in Table~\ref{stellar_props}.
+To derive stellar parameters from our TRES spectra, we initially ran the Stellar Parameter Classification code \citep[SPC:][]{spc} to determine \teff and \logg, using the SPC \teff to inform the asteroseismic estimation of \logg from \numax.
+For deriving abundances, \teff was fixed from the results of an initial SPC fit, while \logg was fixed to the seismic values.
+The other stellar atmospheric parameters including the microturbulent velocity ($v_{\text{mic}}$), broadening (convolution by $V_{\text{mac}}$, $v_{\sin{i}}$ and the instrumental line profile), as well as [Fe/H] and chemical abundances for 20 chemical species were derived using the Brussels Automatic Code for Characterizing High accUracy Spectra \citep[BACCHUS:][]{bacchus}.
+The results from this calculation are displayed in Table~\ref{stellar_props}.
 BACCHUS uses an interpolation scheme through a grid of MARCS model atmospheres \citep{Gustafsson2008} in combination with TURBOSPECTRUM \citep{Alvarez1998, Plez2012}.
 For the calculation of synthetic spectra, atomic line information has been taken from the fifth version of the Gaia-ESO linelist (Heiter et al., in preparation).
-Additionally we used the molecular species for CH \citep{Masseron2014}, CN, NH, OH, MgH  C$_{2}$ (T.
+Additionally, we used the molecular species for CH \citep{Masseron2014}, CN, NH, OH, MgH  C$_{2}$ (T.
 Masseron, private communication).
-The SiH molecular information is adopted from the Kurucz linelists and the information for TiO, ZrO, FeH, CaH from B.
+The SiH molecular information was adopted from the Kurucz linelists and the information for TiO, ZrO, FeH, CaH from B.
 Plez (private communication).
 
-Individual elemental abundances are derived by first fixing the stellar atmospheric parameters to those determined above.
-Spectra are then synthesized  in regions centered around an absorption  feature of the element we want to derive.
-The spectra generated will have different [X/Fe] values.
-A $\chi^2$ minimization procedure is then done to derive the best fitting abundance for each line.
-The reported abundances are the median [X/Fe] value of the various line regions for a given element.
+Individual elemental abundances were derived by first fixing the stellar atmospheric parameters to those determined above.
+Spectra were then synthesized in regions centered around an absorption feature of the element in question with different [X/Fe] values.
+A $\chi^2$ minimization procedure was then done to derive the best fitting abundance for each line.
+The reported abundances are the median [X/Fe] value of the various line regions for each element.
 Abundance uncertainties reported are the standard error in the line-by-line abundance ratios.
-Where only one line exists for a given element, we conservatively assume the standard error is 0.10~dex.
-In principle, these uncertainties are underestimated because there they do not include the errors driven by imperfect stellar parameter values and other systematic errors arising, for instance, from incorrect line list data.
-We do note, however, thus use of asteroseismology really reduces the uncertainties caused by the stellar parameters \citep[see][for a longer discussion on this]{hawkinsapogee}.
+Where only one line exists for a given element, we conservatively assumed the standard error is 0.10~dex.
+In principle, these uncertainties are underestimated because there they do not include the errors driven by imperfect stellar parameters and other systematic errors arising, for instance, from incorrect line list data.
+We do note, however, thus use of asteroseismology greatly reduces the uncertainties caused by the stellar parameters \citep[see][for a longer discussion on this]{hawkinsapogee}.
 
-To achieve the most precise abundances we have derived them using both with and without a line-by-line differential approach with respect to Arcturus ($\alpha$~Bo\"{o}tis) using the method described by \citet{gaiabenchmark4} and the Arcturus abundances from \citep{hawkinsapogee}.
+To achieve the most precise abundances we have derived them both with and without a line-by-line differential approach with respect to Arcturus ($\alpha$~Bo\"{o}tis), using the method described by \citet{gaiabenchmark4} and the Arcturus abundances from \citep{hawkinsapogee}.
 Choosing this method means we do not derive the abundances for neutron capture  elements (e.g.
 Sr, Y, Zr, Ba, La, Nd, Eu) in a differential way because there are no estimated values for these elements at the appropriate benchmark parameters of Arcturus.
-For these elements we instead derive the chemical abundances in an aboslute way where the solar abundances of \cite{Asplund2005} are assumed.
-The uncertainty in the abundances are taken a the line-by-line dispersion or assumed to be 0.10 when just one line is available.
+For these elements we instead derived the chemical abundances in an absolute way, where the solar abundances of \cite{Asplund2005} were assumed.
+The uncertainty in the abundances are taken as the line-by-line dispersion, or assumed to be 0.10 when just one line is available.
 No abundances for oxygen could be reliably derived for any of the stars in our spectroscopic sample by either method.
@@
 
-We determined physical properties such as mass, radius, and age for the 33 red giants from their atmospheric and asteroseismic observables (see Table ) using the BAyesian STellar Algorithm \citep[\textsc{basta}][]{silvaaguirre2015,silvaaguirre2017}.
+We determined the mass, radius, and age for the 33 red giants from their atmospheric and asteroseismic observables (see Table ) using the BAyesian STellar Algorithm \citep[\textsc{basta}][]{silvaaguirre2015,silvaaguirre2017}.
 \textsc{basta} compares the observed properties with predictions from theoretical models of stellar evolution, in this case the recently updated BaSTI (a Bag of Stellar Tracks and Isochrones) stellar models and isochrones library \citep{Hidalgo:2018dy} with overshooting and no mass-loss.
 
-The spectroscopic properties we fit are the effective temperature \teff, the metallicity \feh, and the surface gravities \logg from Table~\ref{stellar_props}.
+The spectroscopic properties are the effective temperature \teff, the metallicity \feh, and the surface gravities \logg from Table~\ref{stellar_props}.
 These are accompanied by the global asteroseismic properties \Dnu and \numax from Table~\ref{astero_table}.
-Theoretical predictions of \Dnu and \numax are computed using the asteroseismic scaling relation for any point along an evolutionary track or isochrone.
-For the solar values, we adopt $\nu_{\text{max, }\odot}=3090$~$\mu$Hz, $\Delta\nu_{\odot}=135.1$~$\mu$Hz \citep{huber2011}, and $T_{\text{eff, }\odot}=5777$~K.
+Theoretical predictions of \Dnu and \numax were computed using the asteroseismic scaling relation for any point along an evolutionary track or isochrone.
+For the solar values, we adopted $\nu_{\text{max, }\odot}=3090$~$\mu$Hz, $\Delta\nu_{\odot}=135.1$~$\mu$Hz \citep{huber2011}, and $T_{\text{eff, }\odot}=5777$~K.
 
-The accuracy of the asteroseismic scaling relations across different metallicities, effective temperatures, and evolutionary status is currently an active discussion within the field of asteroseismology \citep[see][]{white2011,belkacem2011,sharma2016,viani2017}.
-We apply the correction by \cite{Serenelli:2017cn} to the large frequency separation relation in Equation~\ref{Dnuscaling} as it has been shown to reproduce the results of a number of classical age determination for the open clusters M67 \citep{stello2016} and NGC~6819 \citep{casagrande2016}.
+The accuracy of the asteroseismic scaling relations across different metallicities, effective temperatures, and evolutionary status is currently under discussion \citep[see][]{white2011,belkacem2011,sharma2016,viani2017}.
+We applied the correction by \cite{Serenelli:2017cn} to the large frequency separation relation in Equation~\ref{Dnuscaling} as it has been shown to reproduce the results of a number of classical age determination for the open clusters M67 \citep{stello2016} and NGC~6819 \citep{casagrande2016}.
 
 We compare the solutions found using this set of fitting parameter with those found using only spectroscopic input in Figure~\ref{masses}, and we find that the change in median stellar parameters between the two results is small for all analyzed red giants.
-However, in the comparison plot it becomes visible how adding the asteroseismic constraints to the fit narrows down the parameter space and thus decrease the derived uncertainties.
+However, in the comparison plot it becomes clear that adding the asteroseismic constraints to the fit narrows down the parameter space and thus decreases the uncertainties.
 
@@
 The chemical composition for each star was measured in the $\alpha$ (Mg, Ti, Si, Ca), odd-Z (Al, V) and Fe-peak (Fe, Ni) elemental families in a differential way with respect to Arcturus.
-The chemical composition for the neutron capture elements are shown in Fig.~\ref{fig:ncap}, and are derived in absolute terms and not differentially with respect to Arcturus.
-The elemental abundance ratios were measured in order to assess the Galactic populations to which these stars belong.
-The first thing to note is that the metallicities, which are tabulated in Table~\ref{stellar_props}, are too high (with $-0.51<$~[M/H]~$<$ +0.14~dex) to belong to the Galactic halo, whose peak metallicity is around $\sim -1.50$ \cite[e.g.][]{Chiba2000}.
-Furthermore, the distance distribution, noted in Table~\ref{all_stars}, indicates that all stars are located within a few~kpc of the Sun and are not apart of the Galactic bulge.
+The chemical composition for the neutron-capture elements are shown in Fig.~\ref{fig:ncap}, and were derived in absolute terms rather than differentially with respect to Arcturus.
+The elemental abundance ratios were measured in order to determine the Galactic populations to which these stars belong.
+The metallicities, which are tabulated in Table~\ref{stellar_props}, are too high (with $-0.51<$~[M/H]~$<$ +0.14~dex) to belong to the Galactic halo, whose peak metallicity is around $\sim -1.50$ \cite[e.g.][]{Chiba2000}.
+Furthermore, the distance distribution (Table~\ref{all_stars}) indicates that all stars are located within a few~kpc of the Sun and are not apart of the Galactic bulge.
 Thus, these stars are drawn from only the Galactic thick and thin disks.
@@
 \end{figure*}
+
 One of the primary ways to determine, in a chemical sense, whether the stars in our sample are drawn from the Galactic disk(s), bulge or halo, is with the ratio of their $\alpha$-elements to Fe.
@@
 Mg, Ti, Si, Ca) and largely dispersed into the interstellar medium through Type~II supernovae (SNII) \citep{Matteucci2001}.
-It has been shown by many studies \citep[e.g.][and references therein]{Edvardsson1993, Adibekyan2012, Feltzing2013, Bensby2014}, that the Galactic thick disk and thin disk separate in the $\alpha$ elements, where the thick disk is enhanced in [Mg, Si, Ca, Ti/Fe] compared to the Galactic thin disk at a given metallicity.
-In Fig.~\ref{alphael}, we display the [Mg/Fe] abundance ratio as a function of [Fe/H] for our stars (black circles) compared\footnote{There may to be systematics between our [X/Fe] abundance scale and those of our comparison samples.} to representative thick and thin disk stars from \cite[open red square]{Bensby2014} and \cite[open orange triangles]{Adibekyan2012}.
+It has been shown by many studies \citep[e.g.][and references therein]{Edvardsson1993, Adibekyan2012, Feltzing2013, Bensby2014}, that the Galactic thick and thin disks separate in the $\alpha$ elements, where the thick disk is enhanced in [Mg, Si, Ca, Ti/Fe] compared to the Galactic thin disk at a given metallicity.
+In Fig.~\ref{alphael}, we display the [Mg/Fe] abundance ratio as a function of [Fe/H] for our stars (black circles), compared\footnote{There may to be systematics between our [X/Fe] abundance scale and those of our comparison samples.} to representative thick and thin disk stars from \cite[open red squares]{Bensby2014} and \cite[open orange triangles]{Adibekyan2012}.
 
@@
 The commonly used [$\alpha$/Fe] abundance ratio, the average of Mg, Ti, Si, Ca (thus it is ([Mg/Fe] + [Ca/Fe] + [Si/Fe] + [Ti/Fe] / 4) ), is also enhanced in most stars.
-This is consistent with most of the stars observed here belonging to the Galactic disk with a slight (of order $\sim$0.15~dex) enhancement in the $\alpha$-elements.
+This is consistent with most of the stars observed here belonging to the Galactic disks with a slight (of order $\sim$0.15~dex) enhancement in the $\alpha$-elements.
 Fig.~\ref{alphael} clearly rule out the Galactic bulge (which would require the sample to be significantly more $\alpha$-enriched given their metallicity) and the Galactic halo (given that the stars would need to be significantly more metal-poor).
@@
 In addition, to the $\alpha$ and odd-Z elements we also derived the chemical abundance for several neutron capture elements including Sr, Zr, La, Eu (left panel of Fig~\ref{fig:ncap}) as well as Y, Ba, and Nd (right panel of Fig.~\ref{fig:ncap}).
-It is clear from Fig.~\ref{fig:ncap}  that the chemical abundance ratio of neutron each neutron capture element is consistent with the Galactic disk population.
-We do however observe that the Ba of our sample is slightly enhanced while the Y of our sample is slightly reduced relative to the general disk population of \cite{Bensby2014}.
+It is clear from Fig.~\ref{fig:ncap}  that the chemical abundance ratio of each neutron capture element is consistent with the Galactic disk population.
+The Ba of our sample is slightly enhanced, however, while the Y of our sample is slightly reduced relative to the general disk population of \cite{Bensby2014}.
 Nevertheless, we conclude all elemental abundance ratios studied our sample most closely resemble the Galactic disk.
@@
 Red clump stars have been used to calibrate the \gaia survey's parallaxes at long distances \citep{2017A&A...598L...4D,2017MNRAS.471..722H,2018A&A...609A.116R}.
-\gaia~DR2 parallaxes have a zero-point offset of $\sim 0.03$~mas \citep{gaiadr2parallax}, and in particular hierarchical models of the ensemble of \gaia clump stars can be used to accurately estimate this and thereby improve the accuracy of \gaia distances greater than a few~kpc (Hawkins et al., in prep.).
+\gaia~DR2 parallaxes have a zero-point offset of $\sim 0.03$~mas \citep{gaiadr2parallax}, and hierarchical models of the ensemble of \gaia clump stars can be used to accurately estimate this and thereby improve the accuracy of \gaia distances greater than a few~kpc (Hawkins et al., in prep.).
 
 From inspection of the power spectra, HD~181069, HD~183124, HD~182354, HD~182692, and HD~180658 are seen to be red clump stars.
-A power spectrum of the best example of these, HD~183124, together with an \'{e}chelle diagram used to estimate its \emph{g}-mode period spacing, is shown in Figure~\ref{HD_183124}.
+A power spectrum of the best example of these, HD~183124, together with a period \'{e}chelle diagram used to estimate its \emph{g}-mode period spacing, are shown in Figure~\ref{HD_183124}.
 While precise characterization of these stars is beyond the scope of this paper, they are ideal candidates for anchoring models of the mass and metallicity dependence of red clump properties for calibrating \gaia and other distance measures.
@@
 \caption{\label{HD_183124}
-Power spectrum (left) and \'{e}chelle diagram (right) of the solar-like oscillations of the red clump star HD~183124.
-The modes in the power spectrum used for the \'{e}chelle diagram are highlighted with blue dots.
-In the \'{e}chelle diagram we see the characteristic pattern of `bumped' modes from avoided crossings between the comb of \emph{p}-modes and \emph{g}-mode oscillations with a period spacing of $\Delta \Pi = 300.1~\text{s}$.}
+Power spectrum (left) and period \'{e}chelle diagram (right) of the solar-like oscillations of the red clump star HD~183124.
+The modes in the power spectrum used for the period \'{e}chelle diagram are highlighted with blue dots.
+In the period \'{e}chelle diagram we see the characteristic pattern of `bumped' modes from avoided crossings between the comb of \emph{p}-modes and \emph{g}-mode oscillations with a period spacing of $\Delta \Pi = 300.1~\text{s}$.}
 \end{figure*}
 
-\subsubsection{Long Period Variables}
-\label{lpvs}
-
-\subsection{Main Sequence Stars}
+\subsection{Main-Sequence Stars}
 \label{mainseq}
 
-For all the main sequence stars in our sample, we inspected light curves and power spectra to determine their variability class.
+For all the main-sequence stars in our sample, we inspected light curves and power spectra to determine their variability class.
 In the following subsections, we will briefly comment on some of the findings.
-Since main sequence variables are so diverse, and the relevant scientific questions so varied, we have attempted only a very preliminary study of these stars in this paper, leaving detailed analysis to future work.
+Since main-sequence variables are diverse, and the relevant scientific questions varied, we have attempted only a very preliminary study of these stars in this paper, leaving detailed analysis to future work.
 
-Our sample includes pulsating stars of spectral type~B,~A, and~F, with their names, properties and variability class listed in Table~\ref{all_stars}.
+Our sample includes pulsating stars of spectral types~B,~A, and~F, as listed in Table~\ref{all_stars}.
 
-Among the hot-star sample are 5 $\delta$\,Sct stars, which show p-mode pulsation.
+The sample includes 5 $\delta$\,Sct stars, which show p-mode pulsation.
 These oscillation modes have particularly long lifetimes and stable frequencies, making them precise stellar clocks with periods of $\sim$2\,hr.
 These can be used to search for binarity and to obtain orbital parameters from photometry alone \citep{shibahashi&kurtz2012}.
-We used the phase-modulation method of \citet{murphyetal2014} to investigate whether any of these $\delta$\,Sct stars were binaries.
-Any phase modulation is converted into a light arrival-time delay, and if a star is a binary, the time delays of each mode should vary in unison.
+We used the phase-modulation (PM) method of \citet{murphyetal2014} to investigate whether any of these $\delta$\,Sct stars are binaries.
+Any phase modulation is converted into a light arrival-time (R\o mer) delay, and for a binary, the time delays of each mode should vary in unison.
 Nearly 350 PM binaries are known in the full \textit{Kepler} dataset \citep{murphyetal2018}.
@@
 In four of the five targets we found evidence for binarity, while in the fifth (HD\,185397) there was some time-delay variation but there was no agreement between different modes so it is not of binary origin.
-Of the others, HD\,175841 and HD\,177781 are likely very long-period binaries, with periods far exceeding the Kepler datasets of $\sim$1470\,d.
-HD\,181521 appears to be an eccentric binary with a period of at least 1000\,d, but there is only 1 maximum and 1 minimum in the time-delay curve (cf.
-\citep{murphy&shibahashi2015}), so a unique orbital solution was unobtainable.
-Finally, HD\,186255 is likely a binary with a period of $\sim$415\,d, but there is a slight aperiodicity in the time delays, likely caused by beating between pulsation modes that are not well-separated in the frequency.
-That, coupled with the fact that this star is on the failed Module 3 and is therefore missing data every 4th quarter (i.e.
+Of the others, HD\,175841 and HD\,177781 are probably very long-period binaries, with periods far exceeding the Kepler datasets of $\sim$1470\,d.
+HD\,181521 appears to be an eccentric binary with a period of at least 1000\,d, but there is only 1 maximum and 1 minimum in the time-delay curve (\citep[cf.][]{murphy&shibahashi2015}), so a unique orbital solution was unobtainable.
+Finally, HD\,186255 is probably a binary with a period of $\sim$415\,d (Figure~\ref{pm}), but there is a slight aperiodicity in the time delays, likely caused by beating between pulsation modes that are not well-separated in the frequency.
+That, coupled with the fact that this star falls on the failed Module 3 and is therefore missing data every 4th quarter (i.e.
 $\sim$93 of every 372.5\,d), makes the binary classification uncertain.
-If indeed this is a 415-d binary, the time delays are consistent with a companion of minimum mass $\sim$0.45\,M$_{\odot}$ in an orbit of moderate eccentricity ($\sim$0.15).
+If this is indeed a 415-d binary, the time delays are consistent with a companion of minimum mass $\sim$0.45\,M$_{\odot}$ in an orbit of moderate eccentricity ($\sim$0.15).
+
+\begin{figure*}
+\noindent\includegraphics[width=19cm,keepaspectratio]{HD186255_time-delay_plot.png}
+
+\caption{\label{pm}
+Time delay as a function of time for the $\delta$\,Sct star HD~186255, calculated for three of its oscillation modes ($f_2$, $f_5$, and $f_8$) and their average.
+These vary in unison, but with a small amplitude, and are possibly indicative of a low-mass or highly inclined companion.}
+\end{figure*}
 
@@
 
-There are two stars whose variability we classify as $\alpha^2$\,CVn  HD~176582 (B5V) and HD~179395 (B9), but which are not previously known to be chemically-peculiar.
-have very short periods (1.58~d and 1.83~d respectively) and phase stability throughout the \kepler observations.
+There are two stars whose variability we classify as $\alpha^2$\,CVn, namely HD~176582 (B5V) and HD~179395 (B9), but which are not previously known to be chemically-peculiar.
+They have very short periods (1.58~d and 1.83~d respectively) and phase stability throughout the \kepler observations.
 While HD~176582 is listed as an eruptive variable by \citet{2016ApJ...829...23D}, this appears to be a misclassification considering the full \kepler smear light curve.
@@
 Moreover, the variability periods are short enough that for a binary origin we would expect orbits to be circularized \citep{2000A&A...354..881D}.
-We suggest that it is likely that these are nevertheless $\alpha^2$\,CVn variables, and that it will be valuable to study these stars spectroscopically for signs of chemical peculiarity.
+We suggest that these are nevertheless $\alpha^2$\,CVn variables, and that it will be valuable to study these stars spectroscopically for signs of chemical peculiarity.
 
@@
 The investigation of pulsation modes in high-mass stars using high-quality \kepler smear data combined with high-precision spectroscopy to identify the modes \citep[Chapter 6]{aertsbook} is an exciting prospect for asteroseismology, as the interior physics of these stars are largely unknown, yet they play a pivotal role in stellar and galactic evolution.
-The in-depth asteroseismic analysis of the smear data for the~B~stars in this work is beyond the scope of the current paper, as it requires additional ground-based follow-up spectroscopy.
-Such studies will be the subject of future work.
+The in-depth asteroseismic analysis of the smear data for the~B~stars requires additional ground-based follow-up spectroscopy and will be the subject of future work.
 
@@
 
-Several stars in the sample show the `hump-and-spike' morphology in their power spectra (a broad `hump' of low-amplitude oscillations dominated by one high amplitude coherent oscillation toward the high frequency end of this band): HD~186155 (HR~7495), 14~Cyg (HD~185872, HR~7483), HD~189178 (HR~7628), HD~183362 (HR~7403), and HD~184787.
+Several stars in the sample show the `hump-and-spike' morphology in their power spectra \citep[][a broad `hump' of low-amplitude oscillations dominated by one high amplitude coherent oscillation toward the high frequency end of this band]{2013MNRAS.431.2240B,2014MNRAS.441.3543B,2017MNRAS.467.1830B,2018MNRAS.474.2774S}: these are marked `H+S' in Table~\ref{stellar_props}.
+%HD~186155 (HR~7495), 14~Cyg (HD~185872, HR~7483), HD~189178 (HR~7628), HD~183362 (HR~7403), and HD~184787. 
 Of these, HD~186155 and 14~Cyg are the third-- and sixth--brightest stars on silicon, making these the brightest stars that show this effect.
@@
 \citet{2018MNRAS.474.2774S} have recently interpreted the hump-and-spike power spectra as evidence for Rossby modes.
-The F5 star HD~186155, identified by SIMBAD as having a giant spectral type of F5II-III, is shown by its \gaia distance to in fact lie on the main sequence.
+The F5 star HD~186155, identified by SIMBAD as having a giant spectral type of F5II-III, is shown by its \gaia distance to in fact lie on the main-sequence.
 A detailed study of these stars will be presented by Antoci et al., in prep.
@@
 
-\subsubsection{Binaries}
+\subsubsection{Eclipsing Binaries}
 \label{ebs}
 
-We detect BD+47~2825 as a new eclipsing binary system, and recover light curves for the previously-known eclipsing binaries HD~186994, V2083~Cyg, and V380~Cyg.
-The known binary system HD~189684 is newly identified as showing ellipsoidal variability, but does not show evidence of eclipses.
+We detect BD+47~2825 as a new eclipsing binary system, and obtained light curves for the previously-known eclipsing binaries HD~186994 \citep{2016AJ....151..101A}, V2083~Cyg \citep{2012MNRAS.421.1196Z}, and V380~Cyg \citep{2003A&A...399.1115C}.
+The known spectroscopic binary system HD~189684 \citep{2008MNRAS.389..869E} is newly identified as showing ellipsoidal variability, but does not show evidence of eclipses.
 We do not attempt detailed analysis of their variability in this paper.
@@
 
-We believe in open science, and have therefore made all substantive products of this research available to the interested reader.
+To facilitate open science, we have made the products of this research available online.
 All code used to produce smear light curves is available under a GPL~v3 license at \url{github.com/benjaminpope/keplersmear}.
-All smear light curves, both including the red giant sample studied in detail in Section~\ref{rgs}, and main sequence stars as discussed in Sections~\ref{mainseq} and~\ref{ebs}, can be downloaded from the Mikulski Archive for Space Telescopes (MAST) as a High-Level Science Product.
+All smear light curves, both including the red giant sample studied in detail in Section~\ref{rgs}, and main-sequence stars as discussed in Sections~\ref{mainseq} and~\ref{ebs}, can be downloaded from the Mikulski Archive for Space Telescopes (MAST) as a High-Level Science Product.
 TRES spectra will be made available from the ExoFOP-TESS website, and all asteroseismic parameters and derived stellar parameters for the red giants in Section~\ref{rgs} are provided in an online-only table as Supplementary Material to this paper.
@@
 The virtue of these bright stars is that they can be studied with interferometry, and more easily with spectroscopy than fainter targets, permitting especially detailed characterization.
-We have therefore obtained detailed abundances of a subset of the red giants in this sample, particularly with a view to determining their provenance in the Galactic thick and thin disk populations.
-The science that can be done both with this sample and with this method are, however, considerably broader: while we have not attempted it in this paper, a compelling next step is to use interferometric diameter measurements and to further constrain the red giant parameters, and compare these to the constraints from \gaia.
+These stars will also be bright enough to be re-observed with high precision by the Transiting Exoplanet Survey Satellite \citep[][TESS;]{tess}.
+We have obtained detailed abundances of a subset of the red giants in this sample, with a view to confirming their membership of the Galactic thick and thin disk populations.
+A compelling next step is to use interferometric diameter measurements and to further constrain the red giant parameters, and compare these to the constraints from \gaia.
 Any tension between these measurements will help test and refine the asteroseismic scaling relations, and better models will propagate through to smaller systematic uncertainties in large samples of stars too faint for interferometry.
-Further improvements will be revealed by the detailed modelling of individual oscillation frequencies in these giants to infer interior structure such as convective overshoot, which is at the time of writing an active topic of research.
+Further improvements will be revealed by the detailed modelling of individual oscillation frequencies in these giants to infer interior structure such as convective overshoot.
 For the lower-frequency M~giants classed as LPVs in this paper, extending the systematics correction and quarter-stitching algorithms to more robustly correct their light curves without removing real signal will allow similar asteroseismic analysis, for a sample of stars that are much less well understood than their higher-frequency counterparts.
@@
 D.H.
-acknowledges support by the Australian Research Council's Discovery Projects funding scheme (project number DE140101364) and support by the NASA Grant NNX14AB92G issued through the \emph{Kepler} Participating Scientist Program.
+acknowledges support by the National Aeronautics and Space Administration through the K2 Guest Observer Program (NNX17AF76G, 80NSSC18K0362) and the National Science Foundation (AST-1717000).
 DWL acknowledges partial support from the Kepler Extended Mission under NASA Cooperative Agreement NNX13AB58A with the Smithsonian Astrophysical Observatory.
 The research leading to these results has received funding from the European Research Council (ERC) under the European Union's Horizon 2020 research and innovation programme (grant agreement No670519: MAMSIE).
+Funding for the Stellar Astrophysics Centre is provided by The Danish National Research Foundation (Grant agreement no.: DNRF106).
 
@@
 has been provided by national institutions, in particular the institutions
-participating in the {\it Gaia} Multilateral Agreement. This work has in particular made use of the \url{gaia-kepler.fun} crossmatch database created by Megan Bedell.
+participating in the {\it Gaia} Multilateral Agreement. This work has made use of the \url{gaia-kepler.fun} crossmatch database created by Megan Bedell.
 

### 2018-12-04 paper/ms.tex
vsa changes

@@
 Timothy R. Bedding,$^{12,5}$
-Dominic M. Bowman,$^{10}$\newauthor
+Dominic M. Bowman,$^{9}$\newauthor
 Ashley Chontos,$^{13}$
@@
 We found that the cosine-bell aperture used for raw photometry by \citet{smear} can sometimes introduce position-dependent systematics and jumps.
-We instead used a super-Gaussian aperture, $A \propto \exp{\dfrac{-(x-x_0)}{w} ^ 4}$, where $x_0$ is the centroid and $w$ is the width in pixels.
+We instead used a super-Gaussian aperture,
+
+\begin{equation}
+A \propto \exp{\dfrac{-(x-x_0)}{w} ^ 4},
+\end{equation}
+\noindent where $x_0$ is the centroid and $w$ is the width in pixels.
 The very flat top of this function helps avoid significant variation with position, while still smoothly rolling off at the edges to avoid discontinuous artefacts.
@@
 Whereas in \citet{smear} we subtracted a background estimated manually, for this larger set of light curves, we have chosen the lowest $25\%$ of pixels by median flux as being unlikely to be contaminated by stars, and taken our background level to be the median of this at each time sample.
-To reduce the noise in this background model, we fitted a Gaussian Process with a 30-day timescale squared exponential kernel using \textsc{george} \citep{hodlr}, and our final background light curve is taken to be the posterior mean of this GP.
+To reduce the noise in this background model, we fitted a Gaussian Process (GP) with a 30-day timescale squared exponential kernel using \textsc{george} \citep{hodlr}, and our final background light curve is taken to be the posterior mean of this GP.
 
@@
 \label{scaling}
-\numax \propto \dfrac{g}{g_{\sun}} \cdot \left(\dfrac{\teff}{\teff_{\sun}}\right)^{\dfrac{1}{2}}
+\numax \propto \dfrac{g}{g_{\sun}} \cdot \left(\dfrac{\teff}{\teff_{\sun}}\right)^{\dfrac{1}{2}},
 \end{equation}
@@
 \label{Dnuscaling}
-\langle \Dnu \rangle \propto \sqrt{\langle \rho \rangle} = \sqrt{M {R}^{-3}}
+\langle \Dnu \rangle \propto \sqrt{\langle \rho \rangle} = \sqrt{M {R}^{-3}}.
 \end{equation}
@@
 The research leading to these results has received funding from the European Research Council (ERC) under the European Union's Horizon 2020 research and innovation programme (grant agreement No670519: MAMSIE).
-Funding for the Stellar Astrophysics Centre is provided by The Danish National Research Foundation (Grant agreement no.: DNRF106).
+V.S.A.
+acknowledges support the Independent Research Fund Denmark (Research grant 7027-00096B).
+Funding for the Stellar Astrophysics Centre is provided by The Danish National Research Foundation (Grant agreement No.~DNRF106).
 

### 2018-12-04 paper/ms.tex
bieryla changes

@@
 We describe the pipeline developed to extract and calibrate these light curves, and show that we attain photometric precision comparable to stars analyzed by the standard pipeline in the nominal \kepler mission.
-In this Paper, we focus on 66~red giants for which we detect solar-like oscillations, characterizing 34 of these in detail with spectroscopic chemical abundances and asteroseismic masses as benchmark stars.
+In this paper, we focus on 66~red giants for which we detect solar-like oscillations, characterizing 34 of these in detail with spectroscopic chemical abundances and asteroseismic masses as benchmark stars.
 We also classify the whole sample, finding nearly all to be variable, with classical pulsations and binary effects.
@@
 For the oscillating red giants that constitute the bulk of the sample, we determine the asteroseismic parameters \numax and \Dnu, and therefore stellar masses and \logg measurements.
-We have also obtained high-resolution optical spectroscopy of 63~stars, predominantly giants, with the Tillinghast Reflector \'{E}chelle Spectrograph (TRES).
+We have also obtained high-resolution optical spectroscopy of 63~stars, predominantly giants, with the Tillinghast Reflector \'{E}chelle Spectrograph \citep[TRES;][]{2007RMxAC..28..129S}.
 For the~34 stars with both spectroscopy and asteroseismic parameters we derive fundamental stellar parameters and elemental abundances.
@@
 We have obtained high-resolution spectroscopy with TRES for~63 stars, mainly giants, in order to constrain stellar parameters and elemental abundances.
-Operating with spectral resolving power $R=44 000$, we have obtained spectra with signal-to-noise ratios (SNRs) of tens to hundreds per resolution element.
+Operating with spectral resolving power $R=44 000$, we have obtained spectra with a mean signal-to-noise ratio (SNRs) of $\sim 100$  per resolution element.
 Although this resolution and SNR are sufficient for an exploratory study, a more detailed analysis will require APOGEE or a similar instrument to obtain greater spectral coverage.
@@
 The metallicities, which are tabulated in Table~\ref{stellar_props}, are too high (with $-0.51<$~[M/H]~$<$ +0.14~dex) to belong to the Galactic halo, whose peak metallicity is around $\sim -1.50$ \cite[e.g.][]{Chiba2000}.
-Furthermore, the distance distribution (Table~\ref{all_stars}) indicates that all stars are located within a few~kpc of the Sun and are not apart of the Galactic bulge.
+Furthermore, the distance distribution (Table~\ref{all_stars}) indicates that all stars are located within a few~kpc of the Sun and are not part of the Galactic bulge.
 Thus, these stars are drawn from only the Galactic thick and thin disks.

### 2018-12-05 paper/ms.tex
jofre changes

@@
 \usepackage{longtable}
+\usepackage{ulem}
 
@@
 These data will form the basis of many large surveys and it is vital that they are calibrated correctly.
-To this end, 34~FGK stars including both giants and dwarfs have been chosen as \gaia-ESO benchmark stars for which metallicities \citep{gaiabenchmark1}, effective temperatures and asteroseismic surface gravities \citep{gaiabenchmark3}, and relative abundances of $\alpha$ and iron-peak elements \citep{gaiabenchmark4} have been determined.
+To this end, 36~FGK stars including both giants and dwarfs have been chosen as \gaia benchmark stars for which metallicities \citep{gaiabenchmark1,2018RNAAS...2c.152J}, effective temperatures and asteroseismic surface gravities \citep{gaiabenchmark3}, and relative abundances of $\alpha$ and iron-peak elements \citep{gaiabenchmark4} have been determined.
 This includes only four main-sequence stars much cooler than the Sun, due to the paucity of such stars with asteroseismology.
@@
 In the \ktwo mission \citep{k2early}, very saturated stars have been observed with `halo photometry' using unsaturated pixels in a specially-determined region around bright stars, including the Pleiades \citep{halo}, Aldebaran \citep{aldebaran}, and $\rho$~Leonis \citep{rholeo}.
-Unfortunately, in the legacy \kepler sample, photometry of such saturated stars was rarely attempted.
+Unfortunately, in the four-year \kepler sample, photometry of such saturated stars was rarely attempted.
 
@@
 Although this resolution and SNR are sufficient for an exploratory study, a more detailed analysis will require APOGEE or a similar instrument to obtain greater spectral coverage.
-From this observing run we have~33 unique targets with seismic \logg and spectra, the same as in the \gaia-ESO benchmark set and a significant addition to the ensemble of bright red giants with asteroseismic parameter determinations.
+From this observing run we have~33 unique targets with seismic \logg and spectra, comparable to the 36 of the \gaia benchmark set \citep{2018RNAAS...2c.152J} and a significant addition to the ensemble of bright red giants with asteroseismic parameter determinations.
 %Due to observing constraints, we were unable to obtain spectra for BD+42~3150, BD+48~2904, HD~176209, HD~182354, HD~189636AB, or HD~189750.
@@
 For deriving abundances, \teff was fixed from the results of an initial SPC fit, while \logg was fixed to the seismic values.
-The other stellar atmospheric parameters including the microturbulent velocity ($v_{\text{mic}}$), broadening (convolution by $V_{\text{mac}}$, $v_{\sin{i}}$ and the instrumental line profile), as well as [Fe/H] and chemical abundances for 20 chemical species were derived using the Brussels Automatic Code for Characterizing High accUracy Spectra \citep[BACCHUS:][]{bacchus}.
+The other stellar atmospheric parameters including the microturbulent velocity ($v_{\text{mic}}$), broadening (convolution by $v_{\text{mac}}$, $v_{\sin{i}}$ and the instrumental line profile), as well as [Fe/H] and chemical abundances for 20 chemical species were derived using the Brussels Automatic Code for Characterizing High accUracy Spectra \citep[BACCHUS:][]{bacchus}.
 The results from this calculation are displayed in Table~\ref{stellar_props}.
@@
 
-To achieve the most precise abundances we have derived them both with and without a line-by-line differential approach with respect to Arcturus ($\alpha$~Bo\"{o}tis), using the method described by \citet{gaiabenchmark4} and the Arcturus abundances from \citep{hawkinsapogee}.
+To achieve the most precise abundances we have derived them both with and without a line-by-line differential approach with respect to Arcturus ($\alpha$~Bo\"{o}tis), using the method described by \citet{hawkinsapogee} and the Arcturus abundances from \citep{gaiabenchmark4}.
 Choosing this method means we do not derive the abundances for neutron capture  elements (e.g.
@@
 We compare the solutions found using this set of fitting parameter with those found using only spectroscopic input in Figure~\ref{masses}, and we find that the change in median stellar parameters between the two results is small for all analyzed red giants.
-However, in the comparison plot it becomes clear that adding the asteroseismic constraints to the fit narrows down the parameter space and thus decreases the uncertainties.
+However, in the comparison plot it becomes clear that adding the asteroseismic constraints to the fit reduces the posterior uncertainty in stellar mass.
 
@@
 One of the primary ways to determine, in a chemical sense, whether the stars in our sample are drawn from the Galactic disk(s), bulge or halo, is with the ratio of their $\alpha$-elements to Fe.
-The $\alpha$ elements are formed during He burning (e.g.
+The $\alpha$ elements are formed after He burning (e.g.
 Mg, Ti, Si, Ca) and largely dispersed into the interstellar medium through Type~II supernovae (SNII) \citep{Matteucci2001}.
@@
 The investigation of pulsation modes in high-mass stars using high-quality \kepler smear data combined with high-precision spectroscopy to identify the modes \citep[Chapter 6]{aertsbook} is an exciting prospect for asteroseismology, as the interior physics of these stars are largely unknown, yet they play a pivotal role in stellar and galactic evolution.
-The in-depth asteroseismic analysis of the smear data for the~B~stars requires additional ground-based follow-up spectroscopy and will be the subject of future work.
+The in-depth asteroseismic analysis of the smear data for the~B~stars will be the subject of future work.
 
@@
 Funding for the Stellar Astrophysics Centre is provided by The Danish National Research Foundation (Grant agreement No.~DNRF106).
+PJ acknowledges FONDECYT Iniciaci\'on grant 11170174.
 

### 2018-12-05 paper/ms.tex
jofre changes
changes

@@
 We describe the pipeline developed to extract and calibrate these light curves, and show that we attain photometric precision comparable to stars analyzed by the standard pipeline in the nominal \kepler mission.
-In this paper, we focus on 66~red giants for which we detect solar-like oscillations, characterizing 34 of these in detail with spectroscopic chemical abundances and asteroseismic masses as benchmark stars.
+In this paper, aside from publishing the light curves of these stars, we focus on 66~red giants for which we detect solar-like oscillations, characterizing 34 of these in detail with spectroscopic chemical abundances and asteroseismic masses as benchmark stars.
 We also classify the whole sample, finding nearly all to be variable, with classical pulsations and binary effects.
@@
 % Beyond searching for planets, 
-\kepler has revolutionized the field of asteroseismology for solar-like oscillations \citep{2010PASP..122..131G,2010ApJ...713L.169C}.
-It has yielded the detection of gravity-mode period spacings for red giants \citep{rggmodes,2014A&A...572L...5M}, enabling probes of interior rotation \citep{rggmoderotation,2012A&A...548A..10M,2012ApJ...756...19D} and distinguishing between hydrogen- and helium-burning cores \citep{rggmodehelium,2012A&A...540A.143M}.
+\kepler has revolutionized the field of asteroseismology both for solar-like oscillations \citep{2010PASP..122..131G,2010ApJ...713L.169C} and for coherent heat-engine driven oscillations \citep{2018arXiv180907779A}.
+It has yielded the detection of gravity-dominated mixed mode period spacings for red giants \citep{rggmodes,2014A&A...572L...5M}, enabling probes of interior rotation \citep{rggmoderotation,2012A&A...548A..10M,2012ApJ...756...19D} and distinguishing between hydrogen- and helium-burning cores \citep{rggmodehelium,2012A&A...540A.143M}.
 It has also permitted the determination of ages and fundamental parameters of cool main-sequence stars \citep{silvaages}, including planet-hosting stars \citep{huberplanetages,silvaplanetages,2016MNRAS.456.2183D,2018MNRAS.479.4786V}.
+\kepler gravity-mode asteroseismology has also been used to derive the internal rotation profiles of intermediate mass stars \citep{2015ApJ...810...16T,2018A&A...618A..24V}.
 %revealing the most ancient known planetary system, dating back to the earliest stages of the galaxy \citep{ancientplanets}.
@@
 
-In the case of HD~181878, a red giant, there is clear and significant contamination from an M~giant, as is seen in Figure~\ref{contamination}.
+In the case of HD~181878, a red giant, there is clear and significant contamination from a star with several low-frequency pulsations, as is seen in Figure~\ref{contamination}.
 Likewise HD~183383 shows two different stars, depending on the quarter: some parts are likely from an ellipsoidal variable with a period of 6.46 days, other parts are from an RR Lyrae pulsator.
@@
 Power spectra of odd and even quarters of HD~181778.
-It is clear from inspection that while odd quarters have the power spectrum expected of a giant star, even quarters have very high amplitude coherent oscillations typical of an M~giant.}
+It is clear from inspection that while odd quarters have the power spectrum expected of a giant star, even quarters have very high amplitude coherent oscillations.}
 \end{figure}
@@
 
-Among the~66 red giants identified in this sample, for~32 the timescale of their variability is similar to the length of a \kepler quarter and they are thus badly affected by systematics and systematics correction.
+Among the~66 red giants identified in this sample, for~32 the timescale of their variability is similar to the length of a \kepler quarter and they are thus badly affected by systematics which are hard to correct with the CBV approah.
 In Table~\ref{all_stars} we have noted these as `long-period variables' (LPVs).
@@
 
-We have used Equation~\ref{scaling}, the asteroseismic scaling relation for \numax \citep{1991ApJ...368..599B,KB95}, to estimate \logg in order to inform extraction of chemical abundances from spectra.
-Using the initial spectroscopic estimate of \teff, which is not dependent on \numax, uncertainties in \numax were propagated with Monte Carlo sampling.
-
 For eight stars, we found that the asteroseismic fit is unsatisfactory: for BD+39~388 we cannot detect the expected oscillations; for BD+43~3064 there are significant peaks but these are not consistent with the pattern expected from a red giant; for HD~179959 and HD~187217 we suspect contamination with the oscillations of a second giant, which is hard to remove from smear light curves; for HD~188629, HD~188639 and HD~188875 we can extract a \numax but not a robust \Dnu.
@@
 Operating with spectral resolving power $R=44 000$, we have obtained spectra with a mean signal-to-noise ratio (SNRs) of $\sim 100$  per resolution element.
-Although this resolution and SNR are sufficient for an exploratory study, a more detailed analysis will require APOGEE or a similar instrument to obtain greater spectral coverage.
+%Although this resolution and SNR are sufficient for an exploratory study, a more detailed analysis will require APOGEE or a similar instrument to obtain greater spectral coverage.
 From this observing run we have~33 unique targets with seismic \logg and spectra, comparable to the 36 of the \gaia benchmark set \citep{2018RNAAS...2c.152J} and a significant addition to the ensemble of bright red giants with asteroseismic parameter determinations.
@@
 % figure out this discrepancy?
+
+We have used Equation~\ref{scaling}, the asteroseismic scaling relation for \numax \citep{1991ApJ...368..599B,KB95}, to estimate \logg in order to inform extraction of chemical abundances from spectra.
+Using the initial spectroscopic estimate of \teff, which is not dependent on \numax, uncertainties in \numax were propagated with Monte Carlo sampling.
 
@@
 Abundance uncertainties reported are the standard error in the line-by-line abundance ratios.
-Where only one line exists for a given element, we conservatively assumed the standard error is 0.10~dex.
+Where only one line exists for a given element, we assumed the standard error to be 0.10~dex.
 In principle, these uncertainties are underestimated because there they do not include the errors driven by imperfect stellar parameters and other systematic errors arising, for instance, from incorrect line list data.
-We do note, however, thus use of asteroseismology greatly reduces the uncertainties caused by the stellar parameters \citep[see][for a longer discussion on this]{hawkinsapogee}.
+We do note, however, the use of asteroseismology to determine \logg greatly reduces the uncertainties caused by the stellar parameters \citep[see][for a longer discussion on this]{hawkinsapogee}.
 
-To achieve the most precise abundances we have derived them both with and without a line-by-line differential approach with respect to Arcturus ($\alpha$~Bo\"{o}tis), using the method described by \citet{hawkinsapogee} and the Arcturus abundances from \citep{gaiabenchmark4}.
+To achieve the most precise abundances we have derived them both with and without a line-by-line differential approach with respect to Arcturus ($\alpha$~Bo\"{o}tis), using the method described by \citet{hawkinsapogee} and the Arcturus abundances from \citet{gaiabenchmark4}.
 Choosing this method means we do not derive the abundances for neutron capture  elements (e.g.
@@
 For these elements we instead derived the chemical abundances in an absolute way, where the solar abundances of \cite{Asplund2005} were assumed.
-The uncertainty in the abundances are taken as the line-by-line dispersion, or assumed to be 0.10 when just one line is available.
+The uncertainty in the abundances are either the line-by-line dispersion, or assumed to be 0.10 when just one line is available.
 No abundances for oxygen could be reliably derived for any of the stars in our spectroscopic sample by either method.
@@
 
-We determined the mass, radius, and age for the 33 red giants from their atmospheric and asteroseismic observables (see Table ) using the BAyesian STellar Algorithm \citep[\textsc{basta}][]{silvaaguirre2015,silvaaguirre2017}.
+We determined the mass, radius, and age for the 33 red giants from their atmospheric and asteroseismic observables (see Table~\ref{astero_table}) using the BAyesian STellar Algorithm \citep[\textsc{basta}][]{silvaaguirre2015,silvaaguirre2017}.
 \textsc{basta} compares the observed properties with predictions from theoretical models of stellar evolution, in this case the recently updated BaSTI (a Bag of Stellar Tracks and Isochrones) stellar models and isochrones library \citep{Hidalgo:2018dy} with overshooting and no mass-loss.
@@
 The [Mg/Fe], [Si/Fe], [Ti/Fe], [V/Fe] (left panel) and [Al/Fe], [Ca/Fe], [Ni/Fe], [Cr/Fe] (right panel) abundance ratios as a function of iron for our stars (black circles).
-We also show a representative sample of Galactic disk stars from \citet[open red square,][]{Bensby2014}, \citet[open orange squares,][]{Adibekyan2012}, \citet[light green circles][]{Battistini2015}.
+We also show a representative sample of Galactic disk stars from \citet[open red squares]{Bensby2014}, \citet[open orange squares]{Adibekyan2012}, and \citet[light green circles]{Battistini2015}.
 These elemental ratios show that the chemical composition of our sample is consistent with the Galactic disk population.

### 2018-12-05 paper/ms.tex
aerts affiliation

@@
 David W. Latham,$^{8}$
-Conny Aerts,$^{9,10,11}$\newauthor
+Conny Aerts,$^{9,10}$\newauthor
 Suzanne Aigrain,$^{3}$ 
 Victoria Antoci,$^{5}$
-Timothy R. Bedding,$^{12,5}$
+Timothy R. Bedding,$^{11,5}$
 Dominic M. Bowman,$^{9}$\newauthor
-Ashley Chontos,$^{13}$
+Ashley Chontos,$^{12}$
 Gilbert A. Esquerdo,$^{8}$
-Daniel Huber,$^{13}$
-Paula Jofr\'{e},$^{14}$\newauthor
+Daniel Huber,$^{12}$
+Paula Jofr\'{e},$^{13}$\newauthor
 Madeline Lucey,$^{6}$
-Simon J. Murphy,$^{12,5}$
-Timothy van Reeth,$^{12,5}$\newauthor
+Simon J. Murphy,$^{11,5}$
+Timothy van Reeth,$^{11,5}$\newauthor
 Victor Silva Aguirre,$^{5}$
-Jie Yu$^{12,5}$ 
+Jie Yu$^{11,5}$ 
 \\
@@
 $^{10}$Department of Astrophysics, IMAPP, Radboud University Nijmegen, P.O. Box 9010, 6500 GL Nijmegen, The Netherlands\\
-$^{11}$Kavli Institute for Theoretical Physics, University of California, Santa Barbara, CA 93106, USA\\
-$^{12}$Sydney Institute for Astronomy (SIfA), School of Physics, University of Sydney, NSW 2006, Australia\\
-$^{13}$Institute for Astronomy, University of Hawai'i, 2680 Woodlawn Drive, Honolulu, HI 96822, USA\\
-$^{14}$N\'{u}cleo de Astronom\'{i}a, Facultad de Ingenier\'{i}a y Ciencias, Universidad Diego Portales, Ej\'{e}rcito 441, Santiago De, Chile\\
+$^{11}$Sydney Institute for Astronomy (SIfA), School of Physics, University of Sydney, NSW 2006, Australia\\
+$^{12}$Institute for Astronomy, University of Hawai'i, 2680 Woodlawn Drive, Honolulu, HI 96822, USA\\
+$^{13}$N\'{u}cleo de Astronom\'{i}a, Facultad de Ingenier\'{i}a y Ciencias, Universidad Diego Portales, Ej\'{e}rcito 441, Santiago De, Chile\\
 }
@@
 %By comparing asteroseismic stellar ages to stellar rotation periods, \citet{angusgyro} have shown that gyrochronology models cannot fit the data with a single relation, leading~\citet{vansadersgyro}~to suggest a qualitative change in dynamo mechanism as stars age through the main-sequence.
+\newpage
 
@@
 We have adopted the same approach here, using the \kepler Pre-search Data Conditioning (PDC) Cotrending Basis Vectors (CBVs) available from MAST, finding least-squares fits of either the first~4 or~8 CBVs to each light curve.
-This can remove astrophysical signals having long timescales, and so we use and recommend 4~CBV light curves for stars with variability on timescales longer than $\sim 5$ days, or indeed raw uncorrected lightcurves for stars variable at high amplitude on $\sim$~quarter timescales, but otherwise we recommend the 8~CBV light curves.
+This can remove astrophysical signals having long timescales, and so we use and recommend 4~CBV light curves for stars with variability on timescales longer than $\sim 5$ days, or indeed raw uncorrected light curves for stars variable at high amplitude on $\sim$~quarter timescales, but otherwise we recommend the 8~CBV light curves.
 There is some room for improvement here by simultaneously modelling astrophysical and instrumental variations, but this is beyond the scope of this paper.

### 2018-12-05 paper/ms.tex
vsa references

@@
 Mg, Ti, Si, Ca) and largely dispersed into the interstellar medium through Type~II supernovae (SNII) \citep{Matteucci2001}.
-It has been shown by many studies \citep[e.g.][and references therein]{Edvardsson1993, Adibekyan2012, Feltzing2013, Bensby2014}, that the Galactic thick and thin disks separate in the $\alpha$ elements, where the thick disk is enhanced in [Mg, Si, Ca, Ti/Fe] compared to the Galactic thin disk at a given metallicity.
+%It has been shown by many studies \citep[e.g.][and references therein]{Edvardsson1993, Adibekyan2012, Feltzing2013, Bensby2014}, that the Galactic thick and thin disks separate in the $\alpha$ elements, where the thick disk is enhanced in [Mg, Si, Ca, Ti/Fe] compared to the Galactic thin disk at a given metallicity.
+The Galactic disk can be chemically dissected into a low- and a high-alpha component that have different vertical and age structure \citep[see e.g.][]{2016ApJ...823...30B,2017A&A...608L...1H,2018MNRAS.475.5487S}, and are commonly associated with the thin and the thick disk \citep[e.g.][and references therein]{Edvardsson1993, Adibekyan2012, Feltzing2013, Bensby2014}.
+At a given metallicity, the thick disk is enhanced in [Mg, Si, Ca, Ti/Fe] compared to the Galactic thin disk.
+
 In Fig.~\ref{alphael}, we display the [Mg/Fe] abundance ratio as a function of [Fe/H] for our stars (black circles), compared\footnote{There may to be systematics between our [X/Fe] abundance scale and those of our comparison samples.} to representative thick and thin disk stars from \cite[open red squares]{Bensby2014} and \cite[open orange triangles]{Adibekyan2012}.

### 2018-12-05 paper/ms.tex
vsa revisions and duplicated references

@@
 It has yielded the detection of gravity-dominated mixed mode period spacings for red giants \citep{rggmodes,2014A&A...572L...5M}, enabling probes of interior rotation \citep{rggmoderotation,2012A&A...548A..10M,2012ApJ...756...19D} and distinguishing between hydrogen- and helium-burning cores \citep{rggmodehelium,2012A&A...540A.143M}.
-It has also permitted the determination of ages and fundamental parameters of cool main-sequence stars \citep{silvaages}, including planet-hosting stars \citep{huberplanetages,silvaplanetages,2016MNRAS.456.2183D,2018MNRAS.479.4786V}.
-\kepler gravity-mode asteroseismology has also been used to derive the internal rotation profiles of intermediate mass stars \citep{2015ApJ...810...16T,2018A&A...618A..24V}.
+It has also permitted the determination of ages and fundamental parameters of cool main-sequence stars \citep{silvaages}, including planet-hosting stars \citep{huberplanetages,silvaaguirre2015,2016MNRAS.456.2183D,2018MNRAS.479.4786V}.
+\kepler gravity-mode asteroseismology has also been used to derive the internal rotation profiles of intermediate mass stars \citep{triana15,vanreeth18}.
 %revealing the most ancient known planetary system, dating back to the earliest stages of the galaxy \citep{ancientplanets}.
@@
 
-A major outcome of the \kepler asteroseismology programme is a legacy sample of extremely well characterized stars that can serve as benchmarks for future work \citep{keplerlegacy1,keplerlegacy2,silvaplanetages,2016MNRAS.456.2183D}.
+A major outcome of the \kepler asteroseismology programme is a legacy sample of extremely well characterized stars that can serve as benchmarks for future work \citep{keplerlegacy1,silvaaguirre2017,silvaaguirre2015,2016MNRAS.456.2183D}.
 Asteroseismological studies with \kepler complement other probes of stellar physics well: for example, the APOKASC sample of~1916 spectroscopically- and asteroseismically-characterized red giant stars \citep{2014ApJS..215...19P}.

### 2018-12-05 paper/ms.tex
italics
removed 176209 as an interloper A star

@@
 \newcommand{\rsun}{\mbox{$\mathrm{R}_{\sun}$}\xspace}
-\newcommand{\kepler}{\emph{Kepler}\xspace}
-\newcommand{\ktwo}{\emph{K2}\xspace}
-\newcommand{\hipparcos}{\emph{Hipparcos}\xspace}
-\newcommand{\gaia}{\emph{Gaia}\xspace}
+\newcommand{\kepler}{\textit{Kepler}\xspace}
+\newcommand{\ktwo}{\textit{K2}\xspace}
+\newcommand{\hipparcos}{\textit{Hipparcos}\xspace}
+\newcommand{\gaia}{\textit{Gaia}\xspace}
 
@@
 
-\title[The Kepler Smear Campaign]{The \kepler Smear Campaign I: An Asteroseismic Catalogue of Bright Red Giants}
+\title[The Kepler Smear Campaign]{The \textit{Kepler} Smear Campaign I: An Asteroseismic Catalogue of Bright Red Giants}
 
@@
 While this could simply arise from being selected for their apparent brightness, it is {}worth considering whether this is because of a bias in their parallax measurements.
-While \gaia parallaxes for very bright stars can be subject to systematic error, we have compared to \emph{Hipparcos} \citep{vanleeuwen07b}, and found close agreement for the brightest stars, with a scatter that increases with magnitude.
+While \gaia parallaxes for very bright stars can be subject to systematic error, we have compared to \hipparcos \citep{vanleeuwen07b}, and found close agreement for the brightest stars, with a scatter that increases with magnitude.
 We therefore suggest that parallax bias is not the reason for the smear sample sitting above the majority of the \kepler sample.
@@
 
-Red clump stars, which burn helium in their cores, can be distinguished from hydrogen-shell burning giants asteroseismologically, via their much higher \emph{g}-mode period spacings \citep{rggmodehelium}.
+Red clump stars, which burn helium in their cores, can be distinguished from hydrogen-shell burning giants asteroseismologically, via their much higher \textit{g}-mode period spacings \citep{rggmodehelium}.
 The term `red clump' arises from the fact that such stars can have a very narrow range of luminosities, so that they appear as a clump in the HR diagram \citep{2016ARA&A..54...95G}.
@@
 From inspection of the power spectra, HD~181069, HD~183124, HD~182354, HD~182692, and HD~180658 are seen to be red clump stars.
-A power spectrum of the best example of these, HD~183124, together with a period \'{e}chelle diagram used to estimate its \emph{g}-mode period spacing, are shown in Figure~\ref{HD_183124}.
+A power spectrum of the best example of these, HD~183124, together with a period \'{e}chelle diagram used to estimate its \textit{g}-mode period spacing, are shown in Figure~\ref{HD_183124}.
 While precise characterization of these stars is beyond the scope of this paper, they are ideal candidates for anchoring models of the mass and metallicity dependence of red clump properties for calibrating \gaia and other distance measures.
@@
 The modes in the power spectrum used for the period \'{e}chelle diagram are highlighted with blue dots.
-In the period \'{e}chelle diagram we see the characteristic pattern of `bumped' modes from avoided crossings between the comb of \emph{p}-modes and \emph{g}-mode oscillations with a period spacing of $\Delta \Pi = 300.1~\text{s}$.}
+In the period \'{e}chelle diagram we see the characteristic pattern of `bumped' modes from avoided crossings between the comb of \textit{p}-modes and \textit{g}-mode oscillations with a period spacing of $\Delta \Pi = 300.1~\text{s}$.}
 \end{figure*}

### 2018-12-05 paper/ms.tex
new asteroseismic figure

@@
 
-\begin{figure*}
-\noindent\includegraphics[width=17cm,keepaspectratio]{different_constraints_fullsample_ove02.pdf}
+\begin{figure}
+% \noindent\includegraphics[width=17cm,keepaspectratio]{different_constraints_fullsample_ove02.pdf}
+\noindent\includegraphics[width=8.5cm,keepaspectratio]{different_constraints_ben.pdf}
 
 \caption{\label{masses}
-Using asteroseismic constraints (left) and asteroseismic and spectroscopic constraints jointly (right) we infer the masses of each star in the asteroseismic sample of giants.}
-\end{figure*}
+Using asteroseismic constraints only (red) and asteroseismic and spectroscopic constraints jointly (blue) we infer the masses of each star in the asteroseismic sample of giants.}
+\end{figure}
 

### 2018-12-06 paper/ms.tex
typo

@@
 
-Among the~66 red giants identified in this sample, for~32 the timescale of their variability is similar to the length of a \kepler quarter and they are thus badly affected by systematics which are hard to correct with the CBV approah.
+Among the~66 red giants identified in this sample, for~32 the timescale of their variability is similar to the length of a \kepler quarter and they are thus badly affected by systematics which are hard to correct with the CBV approach.
 In Table~\ref{all_stars} we have noted these as `long-period variables' (LPVs).

### 2018-12-06 paper/ms.tex
typos

@@
 
-We compare the solutions found using this set of fitting parameter with those found using only spectroscopic input in Figure~\ref{masses}, and we find that the change in median stellar parameters between the two results is small for all analyzed red giants.
-However, in the comparison plot it becomes clear that adding the asteroseismic constraints to the fit reduces the posterior uncertainty in stellar mass.
+We compare the solutions found using this set of fitting parameters with those found using only asteroseismic input in Figure~\ref{masses}, and we find that the change in median stellar parameters between the two results is small for all analyzed red giants.
+However, in the comparison plot it becomes clear that adding the spectroscopic constraints to the fit reduces the posterior uncertainty in stellar mass.
 
@@
 Of the others, HD\,175841 and HD\,177781 are probably very long-period binaries, with periods far exceeding the Kepler datasets of $\sim$1470\,d.
-HD\,181521 appears to be an eccentric binary with a period of at least 1000\,d, but there is only 1 maximum and 1 minimum in the time-delay curve (\citep[cf.][]{murphy&shibahashi2015}), so a unique orbital solution was unobtainable.
+HD\,181521 appears to be an eccentric binary with a period of at least 1000\,d, but there is only 1 maximum and 1 minimum in the time-delay curve \citep[cf.][]{murphy&shibahashi2015}, so a unique orbital solution was unobtainable.
 Finally, HD\,186255 is probably a binary with a period of $\sim$415\,d (Figure~\ref{pm}), but there is a slight aperiodicity in the time delays, likely caused by beating between pulsation modes that are not well-separated in the frequency.
@@
 This work was performed in part under contract with the Jet Propulsion Laboratory (JPL) funded by NASA through the Sagan Fellowship Program executed by the NASA Exoplanet Science Institute.
-B.P.
-also acknowledges support from Balliol College and the Clarendon Fund.
-D.H.
-acknowledges support by the National Aeronautics and Space Administration through the K2 Guest Observer Program (NNX17AF76G, 80NSSC18K0362) and the National Science Foundation (AST-1717000).
+BJSP also acknowledges support from Balliol College and the Clarendon Fund.
+DH acknowledges support by the National Aeronautics and Space Administration through the K2 Guest Observer Program (NNX17AF76G, 80NSSC18K0362) and the National Science Foundation (AST-1717000).
+TRW acknowledges the support of the Australian Research Council (grant DP150100250).
 DWL acknowledges partial support from the Kepler Extended Mission under NASA Cooperative Agreement NNX13AB58A with the Smithsonian Astrophysical Observatory.
 The research leading to these results has received funding from the European Research Council (ERC) under the European Union's Horizon 2020 research and innovation programme (grant agreement No670519: MAMSIE).
-V.S.A.
-acknowledges support the Independent Research Fund Denmark (Research grant 7027-00096B).
+VSA acknowledges support the Independent Research Fund Denmark (Research grant 7027-00096B).
 Funding for the Stellar Astrophysics Centre is provided by The Danish National Research Foundation (Grant agreement No.~DNRF106).
@@
 
-BP acknowledges being on the traditional territory of the Lenape Nations and recognizes that Manhattan continues to be the home to many Algonkian peoples.
+BJSP acknowledges being on the traditional territory of the Lenape Nations and recognizes that Manhattan continues to be the home to many Algonkian peoples.
 We give blessings and thanks to the Lenape people and Lenape Nations in recognition that we are carrying out this work on their indigenous homelands.

### 2018-12-06 paper/ms.tex
quarters observed

@@
 We selected all stars on-silicon in \kepler with $Kp<9$ that were targeted for fewer than $8$ quarters.
-The majority of these were not previously targeted at all, but sixteen stars were to some extent observed conventionally: HD~174020 was targeted in LC for Q2, 6, 10, and 14; HD~175841 for Q11-12, 14-16, with SC for Q3; HD~176582 for Q12-13; HD~178090 for Q1, 3, and 10; HD~180682 for Q0, 3, and 7; HD~181069 for Q1, 10, 13, 14, and 17; HD~181878 for Q14-17; HD~182694 for Q2; HD~183124 for even quarters; HD~185351 for Q1-3 and with SC for Q16; HD~186155 for only Q1; HD~187217 for Q14-17; HD~188252 for only Q13; HD~189013 with SC for Q3 as a $\gamma$~Dor; V380~Cyg for Q11 and with SC for Q7, 9, 10, 12-17; and V819~Cyg for Q14, 16 and 17.
+The majority of these were not previously targeted at all, but sixteen stars were to some extent observed conventionally: these are listed in Table~\ref{quarters}.
 A number of these lay at the edge of a detector, with the result that in some cadences the centroid of the star did not lie on the chip; light curves from these targets were found to be of extremely low quality and all of these stars were discarded.
@@
 The addition of our sample to the conventionally-observed stars makes the \kepler survey magnitude-complete down to $Kp=9$ for all stars on-silicon.
+
+\input{quarters.tex}
 
@@
 
-Because the smear data are collected along an entire CCD~column, there is the risk of contamination from other bright stars.
-This is especially true when doing asteroseismology of red giants, where the low-amplitude stochastically-excited oscillations can be washed out in a power spectrum by the coherent high amplitude variations of a classical pulsator, even if the background star is much fainter.
-We can assess the importance of this contamination by considering the differences between odd and even quarters: because the \kepler spacecraft rotates $90^{\circ}$ between successive quarters, any contaminant will lie in the same column as a smear target only every second quarter.
+We can assess the importance of this contamination by considering differences between quarters.
+Because the Kepler spacecraft rotates $90^\circ$ between successive quarters, stars are observed on different CCD modules with the exception of stars on the central Module 13.
+Minor variations in the precise alignment of each CCD mean that the contribution from contaminating stars varies from quarter to quarter.
+Differences are clearer for Module 13, where contaminating stars will only be aligned along the same columns as a smear target every second quarter.
 We have therefore generated Lomb-Scargle periodograms \citep{lomb,scargle} of each light curve, after clipping for outliers.
@@
 In the case of HD~181878, a red giant, there is clear and significant contamination from a star with several low-frequency pulsations, as is seen in Figure~\ref{contamination}.
-Likewise HD~183383 shows two different stars, depending on the quarter: some parts are likely from an ellipsoidal variable with a period of 6.46 days, other parts are from an RR Lyrae pulsator.
+Likewise the light curve for HD 183383, which variously falls on Modules 8, 12, 14 and 18, shows different behaviour for different quarters: some parts are likely from an ellipsoidal variable with a period of 6.46 days, while other quarters are contaminated by the star RR Lyrae.
 Between seasons, there is an extra hump of power near the red giant oscillations in HD~175740; extra low frequency power in HD~180658; one coherent peak in  HD~182694; high frequency contamination in HD~181597 possibly from an EB; and a very significant difference in amplitude between seasons for BD~+39~3882.
-In other cases visual inspection does not show severe contamination, but in all cases we recommend that users of these light curves carefully check for differences between odd and even quarters.
+In other cases visual inspection does not show severe contamination, but in all cases we recommend that users of these light curves carefully check for differences between quarters, as well as investigating the full frame images for potential contaminants.
 

### 2018-12-07 paper/ms.tex
33 red giants

@@
 We describe the pipeline developed to extract and calibrate these light curves, and show that we attain photometric precision comparable to stars analyzed by the standard pipeline in the nominal \kepler mission.
-In this paper, aside from publishing the light curves of these stars, we focus on 66~red giants for which we detect solar-like oscillations, characterizing 34 of these in detail with spectroscopic chemical abundances and asteroseismic masses as benchmark stars.
+In this paper, aside from publishing the light curves of these stars, we focus on 66~red giants for which we detect solar-like oscillations, characterizing 33 of these in detail with spectroscopic chemical abundances and asteroseismic masses as benchmark stars.
 We also classify the whole sample, finding nearly all to be variable, with classical pulsations and binary effects.
@@
 This sample mostly consists of red giants and hot stars, containing only one~G dwarf.
-We find no transiting planets, but detect one new eclipsing binary, and measure solar-like oscillations in 34~red giants.
+We find no transiting planets, but detect one new eclipsing binary, and measure solar-like oscillations in 33~red giants.
 We do not model main-sequence stars in great detail, but provide some discussion and initial classification of interesting variability.
@@
 We have also obtained high-resolution optical spectroscopy of 63~stars, predominantly giants, with the Tillinghast Reflector \'{E}chelle Spectrograph \citep[TRES;][]{2007RMxAC..28..129S}.
-For the~34 stars with both spectroscopy and asteroseismic parameters we derive fundamental stellar parameters and elemental abundances.
+For the~33 stars with both spectroscopy and asteroseismic parameters we derive fundamental stellar parameters and elemental abundances.
 These asteroseismic constraints can be compared to those from \gaia, offering the opportunity both to test asteroseismic scaling relations and combine both datasets to refine the benchmark star properties further.
@@
 In Table~\ref{all_stars} we have noted these as `long-period variables' (LPVs).
-For the~34 giants for with high-SNR shorter-timescale variability, we have attempted to extract the asteroseismic parameters \numax and $\langle \Dnu \rangle$ \citep{KB95,2013ARA&A..51..353C}.
+For the~33 giants for with high-SNR shorter-timescale variability, we have attempted to extract the asteroseismic parameters \numax and $\langle \Dnu \rangle$ \citep{KB95,2013ARA&A..51..353C}.
 These constrain fundamental stellar parameters through the approximate scaling relations:
@@
 
-We obtained good estimates of these asteroseismic parameters for 34 targets, presented in Table~\ref{astero_table}.
+We obtained good estimates of these asteroseismic parameters for 33 targets, presented in Table~\ref{astero_table}.
 In the remainder of cases, as noted above, very-low-frequency ($\lesssim 2\muHz$) oscillations are affected by filter artefacts from detrending, and we were not able to obtain good estimates for these stars.
@@
 We determined the mass, radius, and age for the 33 red giants from their atmospheric and asteroseismic observables (see Table~\ref{astero_table}) using the BAyesian STellar Algorithm \citep[\textsc{basta}][]{silvaaguirre2015,silvaaguirre2017}.
-\textsc{basta} compares the observed properties with predictions from theoretical models of stellar evolution, in this case the recently updated BaSTI (a Bag of Stellar Tracks and Isochrones) stellar models and isochrones library \citep{Hidalgo:2018dy} with overshooting and no mass-loss.
+\textsc{basta} compares the observed properties with predictions from theoretical models of stellar evolution, in this case the recently updated BaSTI (a Bag of Stellar Tracks and Isochrones) stellar models and isochrones library \citep{Hidalgo:2018dy}.
+No diffusion or rotational mixing was included, while core overshoot with an efficiency of 0.20 times the pressure scale height as described in \citet{Hidalgo:2018dy}.
 
@@
 
+To gauge the level of improvement in our understanding of these stars, in Figure~\ref{gaia_comparison} we plot the radii determined here against those from the \gaia~DR2 catalog determined by the stellar bolometric flux and parallax.
+We find that there is a dramatic improvement in the precision of the stellar radii determined here: some stars which did not previously have radii now have precise radii, and for those inferred from \gaia, the new radii are much more precise.
+
 \begin{figure}
@@
 Using asteroseismic constraints only (red) and asteroseismic and spectroscopic constraints jointly (blue) we infer the masses of each star in the asteroseismic sample of giants.}
+\end{figure}
+
+\begin{figure}
+\noindent\includegraphics[width=8.5cm,keepaspectratio]{gaia_comparison.eps}
+
+\caption{\label{gaia_comparison}
+A comparison of the stellar radii determined here from asteroseismology and spectroscopy to those from the \gaia~DR2 catalogue.
+The precision of the new radii from stellar modelling are a dramatic improvement on those from \gaia.
+}
 \end{figure}
@@
 TRW acknowledges the support of the Australian Research Council (grant DP150100250).
+TRW and VSA acknowledge
+the support of the Villum Foundation (research grant 10118).
 DWL acknowledges partial support from the Kepler Extended Mission under NASA Cooperative Agreement NNX13AB58A with the Smithsonian Astrophysical Observatory.
@@
 
-BJSP acknowledges being on the traditional territory of the Lenape Nations and recognizes that Manhattan continues to be the home to many Algonkian peoples.
+% BJSP acknowledges being on the traditional territory of the Lenape Nations and recognizes that Manhattan continues to be the home to many Algonkian peoples.
 We give blessings and thanks to the Lenape people and Lenape Nations in recognition that we are carrying out this work on their indigenous homelands.
 We would like to acknowledge the Gadigal Clan of the Eora Nation as the traditional owners of the land on which the University of Sydney is built and on which some of this work was carried out, and pay their respects to their knowledge, and their elders past, present and future.
+%% Take this out for MNRAS
 

### 2018-12-07 paper/ms.tex
some fixes

@@
 We can assess the importance of this contamination by considering differences between quarters.
-Because the Kepler spacecraft rotates $90^\circ$ between successive quarters, stars are observed on different CCD modules with the exception of stars on the central Module 13.
+Because the Kepler spacecraft rotates $90^\circ$ between successive quarters, stars are observed on different CCD modules with the exception of stars on the central Module~13.
 Minor variations in the precise alignment of each CCD mean that the contribution from contaminating stars varies from quarter to quarter.
-Differences are clearer for Module 13, where contaminating stars will only be aligned along the same columns as a smear target every second quarter.
+Differences are clearer for Module~13, where contaminating stars will only be aligned along the same columns as a smear target every second quarter.
 We have therefore generated Lomb-Scargle periodograms \citep{lomb,scargle} of each light curve, after clipping for outliers.
@@
 
-In the case of HD~181878, a red giant, there is clear and significant contamination from a star with several low-frequency pulsations, as is seen in Figure~\ref{contamination}.
-Likewise the light curve for HD 183383, which variously falls on Modules 8, 12, 14 and 18, shows different behaviour for different quarters: some parts are likely from an ellipsoidal variable with a period of 6.46 days, while other quarters are contaminated by the star RR Lyrae.
+In the case of HD~181878, a red giant on Module~13, there is clear and significant contamination from a star with several low-frequency pulsations, as is seen in Figure~\ref{contamination}.
+Likewise the light curve for HD 183383, which variously falls on Modules~8, 12, 14 and~18, shows different behaviour for different quarters: some parts are likely from an ellipsoidal variable with a period of 6.46 days, while other quarters are contaminated by the star RR Lyrae.
 Between seasons, there is an extra hump of power near the red giant oscillations in HD~175740; extra low frequency power in HD~180658; one coherent peak in  HD~182694; high frequency contamination in HD~181597 possibly from an EB; and a very significant difference in amplitude between seasons for BD~+39~3882.
@@
 To gauge the level of improvement in our understanding of these stars, in Figure~\ref{gaia_comparison} we plot the radii determined here against those from the \gaia~DR2 catalog determined by the stellar bolometric flux and parallax.
-We find that there is a dramatic improvement in the precision of the stellar radii determined here: some stars which did not previously have radii now have precise radii, and for those inferred from \gaia, the new radii are much more precise.
+While not all of our targets have \gaia radii, we find that where they do both catalogues have comparable precision, but differ by many sigma.
+While
 
@@
 \caption{\label{gaia_comparison}
-A comparison of the stellar radii determined here from asteroseismology and spectroscopy to those from the \gaia~DR2 catalogue.
-The precision of the new radii from stellar modelling are a dramatic improvement on those from \gaia.
-}
+A comparison of the stellar radii determined here from asteroseismology and spectroscopy to those from the \gaia~DR2 catalogue. The catalogues disagree in most cases very significantly.}
 \end{figure}

### 2018-12-08 paper/ms.tex
gaia

@@
 To gauge the level of improvement in our understanding of these stars, in Figure~\ref{gaia_comparison} we plot the radii determined here against those from the \gaia~DR2 catalog determined by the stellar bolometric flux and parallax.
-While not all of our targets have \gaia radii, we find that where they do both catalogues have comparable precision, but differ by many sigma.
-While
+While not all of our targets have \gaia radii, we find that while there is overall agreement to within a few $\sigma$, the results from stellar modelling are consistently slightly larger than those from \gaia.
+One star noticeably very different: BD+39~3577 has a precise \gaia radius of $9.14^{+0.25}_{-0.13}$~\rsun, but $24.78^{+0.88}_{-0.72}$~\rsun from modelling.
+% Likewise BD+42~3150 has a \gaia radius of $15.70^{+0.52}_{-0.76}$~\rsun but $11.27^{+0.39}_{-0.41}$~\rsun from stellar modelling.
+It is unclear why this would be the case; it is possible that an unidentified binary companion has affected either the asteroseismic detection or parallax.
 

### 2018-12-20 paper/ms.tex
huber radii

@@
 For the solar values, we adopted $\nu_{\text{max, }\odot}=3090$~$\mu$Hz, $\Delta\nu_{\odot}=135.1$~$\mu$Hz \citep{huber2011}, and $T_{\text{eff, }\odot}=5777$~K.
+\newpage
 
@@
 To gauge the level of improvement in our understanding of these stars, in Figure~\ref{gaia_comparison} we plot the radii determined here against those from the \gaia~DR2 catalog determined by the stellar bolometric flux and parallax.
+We also calculate \gaia-like stellar bolometric radii using \texttt{isoclassify} \citep{huber2017} using our new spectroscopic \teff measurements rather than those from \gaia~DR2, together with \gaia~DR2 parallaxes spectroscopic \logg, $Z$, and SIMBAD $V$.
 While not all of our targets have \gaia radii, we find that while there is overall agreement to within a few $\sigma$, the results from stellar modelling are consistently slightly larger than those from \gaia.
-One star noticeably very different: BD+39~3577 has a precise \gaia radius of $9.14^{+0.25}_{-0.13}$~\rsun, but $24.78^{+0.88}_{-0.72}$~\rsun from modelling.
-% Likewise BD+42~3150 has a \gaia radius of $15.70^{+0.52}_{-0.76}$~\rsun but $11.27^{+0.39}_{-0.41}$~\rsun from stellar modelling.
+This discrepancy goes away for most stars when we use our own \texttt{isoclassify} radii, suggesting that this is an effect of \teff calibration.
+Two stars are noticeably very different: BD+39~3577 has a precise \gaia radius of $9.14^{+0.25}_{-0.13}$~\rsun, but $24.78^{+0.88}_{-0.72}$~\rsun from modelling.
 It is unclear why this would be the case; it is possible that an unidentified binary companion has affected either the asteroseismic detection or parallax.
+Likewise BD+42~3150 has a \gaia radius of $15.70^{+0.52}_{-0.76}$~\rsun but $11.27^{+0.39}_{-0.41}$~\rsun from stellar modelling, but of our sample it has the lowest \gaia parallax over error at only 18.0, and this anomalously high value is likely noise.
+Agreement for large-radius ($>30 \rsun$) stars is poorer, even though the \gaia parallax-over-error is apparently adequate.
+This disagreement, unlike for medium radius stars, is pronounced mainly for the \texttt{isoclassify} radii rather than \gaia~DR2, suggesting that our $V$ band bolometric corrections for these more yellow (\gaia $Bp-Rp \sim 0.25$) stars are insufficiently accurate.
 
@@
 \begin{figure}
-\noindent\includegraphics[width=8.5cm,keepaspectratio]{gaia_comparison.eps}
+\noindent\includegraphics[width=8.5cm,keepaspectratio]{combined_radii.eps}
 
 \caption{\label{gaia_comparison}
-A comparison of the stellar radii determined here from asteroseismology and spectroscopy to those from the \gaia~DR2 catalogue. The catalogues disagree in most cases very significantly.}
+A comparison of the stellar radii determined here from asteroseismology and spectroscopy to those from the \gaia~DR2 catalogue and from our own calculations based on \gaia parallaxes and TRES spectroscopy.
+There is overall good agreement except for very large radii, except for BD+39~3577 (marked), which we do not understand.}
 \end{figure}

### 2019-03-11 paper/ms.tex
new spectral reduction

@@
 \usepackage{xspace}
+\usepackage{fontawesome}
 
@@
 David W. Latham,$^{8}$
-Conny Aerts,$^{9,10}$\newauthor
+Madeline Lucey,$^{6}$\newauthor
+Conny Aerts,$^{9,10}$
 Suzanne Aigrain,$^{3}$ 
 Victoria Antoci,$^{5}$
-Timothy R. Bedding,$^{11,5}$
-Dominic M. Bowman,$^{9}$\newauthor
+Timothy R. Bedding,$^{11,5}$\newauthor
+Dominic M. Bowman,$^{9}$
 Ashley Chontos,$^{12}$
 Gilbert A. Esquerdo,$^{8}$
-Daniel Huber,$^{12}$
-Paula Jofr\'{e},$^{13}$\newauthor
-Madeline Lucey,$^{6}$
+Daniel Huber,$^{12}$\newauthor
+Paula Jofr\'{e},$^{13}$
 Simon J. Murphy,$^{11,5}$
-Timothy van Reeth,$^{11,5}$\newauthor
-Victor Silva Aguirre,$^{5}$
+Timothy van Reeth,$^{11,5}$
+Victor Silva Aguirre,$^{5}$\newauthor
 Jie Yu$^{11,5}$ 
@@
 All source code, light curves, TRES spectra, and asteroseismic and stellar parameters are publicly available as a \kepler legacy sample.
+\href{https://github.com/benjaminpope/k2halo}{\faGithub}
 \end{abstract}
@@
 \begin{figure*}
-\noindent\includegraphics[width=0.7\textwidth,keepaspectratio]{chem_pope.png}
+\noindent\includegraphics[width=0.7\textwidth,keepaspectratio]{Pope_alpha_oddZ.pdf}
 
@@
 \begin{figure*}
-\noindent\includegraphics[width=0.7\textwidth,keepaspectratio]{chem_ncap_pope.pdf}
+\noindent\includegraphics[width=0.7\textwidth,keepaspectratio]{Pope_ncap.pdf}
 

### 2019-03-12 paper/ms.tex
github link
bad stars text

@@
 All source code, light curves, TRES spectra, and asteroseismic and stellar parameters are publicly available as a \kepler legacy sample.
-\href{https://github.com/benjaminpope/k2halo}{\faGithub}
+\href{https://github.com/benjaminpope/smearcampaign}{\faGithub}
 \end{abstract}
@@
 For deriving abundances, \teff was fixed from the results of an initial SPC fit, while \logg was fixed to the seismic values.
+For four stars with low \logg and metallicity (BD+43~3171, HD~174020, HD~180682, and HD~181022), the stellar spectral templates in SPC gave unsatisfactory fits.
+In these cases, \teff was fixed to the results of a broadband spectral energy distribution (SED) fit to archival photometry as catalogued by \citet{Mcdonald2017}, and \logg calculated from these without iteration.
+
 The other stellar atmospheric parameters including the microturbulent velocity ($v_{\text{mic}}$), broadening (convolution by $v_{\text{mac}}$, $v_{\sin{i}}$ and the instrumental line profile), as well as [Fe/H] and chemical abundances for 20 chemical species were derived using the Brussels Automatic Code for Characterizing High accUracy Spectra \citep[BACCHUS:][]{bacchus}.

### 2019-03-14 paper/ms.tex
final?

@@
 %By comparing asteroseismic stellar ages to stellar rotation periods, \citet{angusgyro} have shown that gyrochronology models cannot fit the data with a single relation, leading~\citet{vansadersgyro}~to suggest a qualitative change in dynamo mechanism as stars age through the main-sequence.
-\newpage
+% \newpage
 
@@
 It is unclear why this would be the case; it is possible that an unidentified binary companion has affected either the asteroseismic detection or parallax.
-Likewise BD+42~3150 has a \gaia radius of $15.70^{+0.52}_{-0.76}$~\rsun but $11.27^{+0.39}_{-0.41}$~\rsun from stellar modelling, but of our sample it has the lowest \gaia parallax over error at only 18.0, and this anomalously high value is likely noise.
-Agreement for large-radius ($>30 \rsun$) stars is poorer, even though the \gaia parallax-over-error is apparently adequate.
-This disagreement, unlike for medium radius stars, is pronounced mainly for the \texttt{isoclassify} radii rather than \gaia~DR2, suggesting that our $V$ band bolometric corrections for these more yellow (\gaia $Bp-Rp \sim 0.25$) stars are insufficiently accurate.
+Likewise BD+42~3150 has a \gaia radius of $15.70^{+0.52}_{-0.76}$~\rsun but $11.27^{+0.39}_{-0.41}$~\rsun from stellar modelling, but of our sample it has the lowest \gaia parallax over error at only 18.0, and this anomalously high value is likely due to noise.
+Agreement for large-radius ($>30 \rsun$) stars is somewhat poorer, even though the \gaia parallax-over-error is apparently adequate.
+This dispersion, unlike for medium radius stars, is more pronounced for the \texttt{isoclassify} radii than for \gaia~DR2, suggesting that our $V$ band bolometric corrections for these more yellow (\gaia $Bp-Rp \sim 0.25$) stars are insufficiently accurate.
 
@@
 A comparison of the stellar radii determined here from asteroseismology and spectroscopy to those from the \gaia~DR2 catalogue and from our own calculations based on \gaia parallaxes and TRES spectroscopy.
-There is overall good agreement except for very large radii, except for BD+39~3577 (marked), which we do not understand.}
+There is overall good agreement except for very large radii, and except for BD+39~3577 (marked), which we do not understand.}
 \end{figure}

### 2019-03-15 paper/ms.tex
Fixes
typos

@@
 
-\title[The Kepler Smear Campaign]{The \textit{Kepler} Smear Campaign I: An Asteroseismic Catalogue of Bright Red Giants}
+\title[The Kepler Smear Campaign]{The \textit{Kepler} Smear Campaign}
 
@@
 %By comparing asteroseismic stellar ages to stellar rotation periods, \citet{angusgyro} have shown that gyrochronology models cannot fit the data with a single relation, leading~\citet{vansadersgyro}~to suggest a qualitative change in dynamo mechanism as stars age through the main-sequence.
-% \newpage
 
@@
 The availability of \kepler data remains significantly incomplete down to fainter magnitudes, and in this work we consider $Kp=9$ to be an arbitrary cutoff for bright stars of interest.
-In the \ktwo mission \citep{k2early}, very saturated stars have been observed with `halo photometry' using unsaturated pixels in a specially-determined region around bright stars, including the Pleiades \citep{halo}, Aldebaran \citep{aldebaran}, and $\rho$~Leonis \citep{rholeo}.
+In the \ktwo mission \citep{k2early}, very saturated stars have been observed with `halo photometry' using unsaturated pixels in a specially-determined region around bright stars, including the Pleiades \citep{halo}, Aldebaran \citep{aldebaran}, $\iota$~Librae \citep{Buysschaert2018}, and $\rho$~Leonis \citep{rholeo}.
 Unfortunately, in the four-year \kepler sample, photometry of such saturated stars was rarely attempted.
@@
 In Table~\ref{all_stars} we have noted these as `long-period variables' (LPVs).
-For the~33 giants for with high-SNR shorter-timescale variability, we have attempted to extract the asteroseismic parameters \numax and $\langle \Dnu \rangle$ \citep{KB95,2013ARA&A..51..353C}.
+For the~33 giants with high-SNR shorter-timescale variability, we have attempted to extract the asteroseismic parameters \numax and $\langle \Dnu \rangle$ \citep{KB95,2013ARA&A..51..353C}.
 These constrain fundamental stellar parameters through the approximate scaling relations:

### 2019-03-15 paper/ms.tex
typos

@@
 
-Among the~66 red giants identified in this sample, for~32 the timescale of their variability is similar to the length of a \kepler quarter and they are thus badly affected by systematics which are hard to correct with the CBV approach.
+Among the~66 red giants identified in this sample, for~22 the timescale of their variability is similar to the length of a \kepler quarter and they are thus badly affected by systematics which are hard to correct with the CBV approach.
 In Table~\ref{all_stars} we have noted these as `long-period variables' (LPVs).

### 2019-03-15 paper/ms.tex
typos

@@
 %Although this resolution and SNR are sufficient for an exploratory study, a more detailed analysis will require APOGEE or a similar instrument to obtain greater spectral coverage.
-From this observing run we have~33 unique targets with seismic \logg and spectra, comparable to the 36 of the \gaia benchmark set \citep{2018RNAAS...2c.152J} and a significant addition to the ensemble of bright red giants with asteroseismic parameter determinations.
+From this observing run we have~33 unique targets with seismic \logg and spectra, a number comparable to the 36 of the \gaia benchmark set \citep{2018RNAAS...2c.152J} and a significant addition to the ensemble of bright red giants with asteroseismic parameter determinations.
 %Due to observing constraints, we were unable to obtain spectra for BD+42~3150, BD+48~2904, HD~176209, HD~182354, HD~189636AB, or HD~189750.
@@
 
-The other stellar atmospheric parameters including the microturbulent velocity ($v_{\text{mic}}$), broadening (convolution by $v_{\text{mac}}$, $v_{\sin{i}}$ and the instrumental line profile), as well as [Fe/H] and chemical abundances for 20 chemical species were derived using the Brussels Automatic Code for Characterizing High accUracy Spectra \citep[BACCHUS:][]{bacchus}.
+The other stellar atmospheric parameters including the microturbulent velocity ($v_{\text{mic}}$), broadening (convolution by $v_{\text{mac}}$, $v_{\sin{i}}$ and the instrumental line profile), as well as [Fe/H] and chemical abundances for 13 chemical species were derived using the Brussels Automatic Code for Characterizing High accUracy Spectra \citep[BACCHUS:][]{bacchus}.
 The results from this calculation are displayed in Table~\ref{stellar_props}.

### 2019-03-15 paper/ms.tex
final?

@@
 To facilitate open science, we have made the products of this research available online.
-All code used to produce smear light curves is available under a GPL~v3 license at \url{github.com/benjaminpope/keplersmear}.
+All code used to produce smear light curves is available under a GPL~v3 license at \href{https://github.com/benjaminpope/keplersmear}{\nolinkurl{github.com/benjaminpope/keplersmear}}.
 All smear light curves, both including the red giant sample studied in detail in Section~\ref{rgs}, and main-sequence stars as discussed in Sections~\ref{mainseq} and~\ref{ebs}, can be downloaded from the Mikulski Archive for Space Telescopes (MAST) as a High-Level Science Product.
@@
 All smear light curves in this paper, as well as the \LaTeX{} source code used to produce this document, can be found
-at \url{github.com/benjaminpope/smearcampaign}.
+at \href{https://github.com/benjaminpope/smearcampaign}{\nolinkurl{github.com/benjaminpope/smearcampaign}}.
 
@@
 The virtue of these bright stars is that they can be studied with interferometry, and more easily with spectroscopy than fainter targets, permitting especially detailed characterization.
-These stars will also be bright enough to be re-observed with high precision by the Transiting Exoplanet Survey Satellite \citep[][TESS;]{tess}.
+These stars will also be bright enough to be re-observed with high precision by the Transiting Exoplanet Survey Satellite \citep[TESS;][]{tess}.
 We have obtained detailed abundances of a subset of the red giants in this sample, with a view to confirming their membership of the Galactic thick and thin disk populations.

### 2019-03-17 paper/ms.tex
aerts changes

@@
 
-The coherent g-mode pulsations in samples of B, A, and F stars observed by \kepler previously showed these stars to be near-rigid rotators \citep{kurtz2014,saio15,triana15,vanreeth15,vanreeth16,vanreeth18,murphy16,schmid16,moravveji16,ouazzani17,papics17,aerts17,szewczuk18,2018arXiv180907779A}.
-These studies cover about 70 stars so far.
+The coherent g-mode pulsations in samples of B, A, and F stars observed by \kepler previously showed these stars to be near-rigid rotators \citep{kurtz2014,saio15,triana15,vanreeth15,vanreeth16,vanreeth18,murphy16,schmid16,moravveji16,ouazzani17,papics17,aerts17,szewczuk18,2018arXiv180907779A,2018A&A...618A..47C,2019MNRAS.482.1757L}.
+These studies cover about 100 stars so far and many more are to come.
+For 37 of the F-type pulsators among those, asteroseismic modelling of the g modes led to their masses, ages, core rotation and core mass with relative precisions of about 10\% \citep{2019MNRAS.tmp..495M}.
+The vast majority of B-type intermediate-mass stars observed byKepler have yet to be subjected to in-depth asteroseismic analyses and modelling of their interior properties.
 However, the vast majority of intermediate-mass stars observed by Kepler have yet to be subjected to in-depth asteroseismic analyses and modelling of their interior properties.

### 2019-03-20 paper/ms.tex
mistake

@@
 The masked and virtual smear registers each receive $\sim 1/1034$ of the incident flux in each column.
-If this is dominated by the light from a single star, the flux combining both smear registers is equivalent to that of a star $\sim 6.8$~times fainter.
+If this is dominated by the light from a single star, the flux combining both smear registers is equivalent to the normal flux of a star $\sim 6.8$~magnitudes fainter.
 
@@
 \textsc{basta} compares the observed properties with predictions from theoretical models of stellar evolution, in this case the recently updated BaSTI (a Bag of Stellar Tracks and Isochrones) stellar models and isochrones library \citep{Hidalgo:2018dy}.
-No diffusion or rotational mixing was included, while core overshoot with an efficiency of 0.20 times the pressure scale height as described in \citet{Hidalgo:2018dy}.
+The isochrones include core overshooting with an efficiency of 0.20 times the pressure scale height as described in \citet{Hidalgo:2018dy}, but do not include diffusion or rotational mixing.
 

### 2019-03-20 paper/ms.tex
bedding updates

@@
 
-\title[The Kepler Smear Campaign]{The \textit{Kepler} Smear Campaign}
+\title[The Kepler Smear Campaign]{The \textit{Kepler} Smear Campaign: Light curves for 102 Very Bright Stars}
 
@@
 \kepler has revolutionized the field of asteroseismology both for solar-like oscillations \citep{2010PASP..122..131G,2010ApJ...713L.169C} and for coherent heat-engine driven oscillations \citep{2018arXiv180907779A}.
-It has yielded the detection of gravity-dominated mixed mode period spacings for red giants \citep{rggmodes,2014A&A...572L...5M}, enabling probes of interior rotation \citep{rggmoderotation,2012A&A...548A..10M,2012ApJ...756...19D} and distinguishing between hydrogen- and helium-burning cores \citep{rggmodehelium,2012A&A...540A.143M}.
+It has yielded the detection of gravity-dominated mixed-mode period spacings for red giants \citep{rggmodes,2014A&A...572L...5M}, enabling probes of interior rotation \citep{rggmoderotation,2012A&A...548A..10M,2012ApJ...756...19D} and distinguishing between hydrogen- and helium-burning cores \citep{rggmodehelium,2012A&A...540A.143M}.
 It has also permitted the determination of ages and fundamental parameters of cool main-sequence stars \citep{silvaages}, including planet-hosting stars \citep{huberplanetages,silvaaguirre2015,2016MNRAS.456.2183D,2018MNRAS.479.4786V}.
@@
 
-A major outcome of the \kepler asteroseismology programme is a legacy sample of extremely well characterized stars that can serve as benchmarks for future work \citep{keplerlegacy1,silvaaguirre2017,silvaaguirre2015,2016MNRAS.456.2183D}.
-Asteroseismological studies with \kepler complement other probes of stellar physics well: for example, the APOKASC sample of~1916 spectroscopically- and asteroseismically-characterized red giant stars \citep{2014ApJS..215...19P}.
+A major outcome of the \kepler asteroseismology programme is a legacy sample of extremely well-characterized stars that can serve as benchmarks for future work \citep{keplerlegacy1,silvaaguirre2017,silvaaguirre2015,2016MNRAS.456.2183D}.
+Asteroseismological studies with \kepler complement other probes of stellar physics, such as the APOKASC sample of~1916 spectroscopically- and asteroseismically-characterized red giant stars \citep{2014ApJS..215...19P}.
 For this APOKASC sample, \citet{hawkinsapogee} have been able to extract precise elemental abundances by fitting spectroscopic data with \logg and \teff fixed to asteroseismically-determined values.
@@
 This includes only four main-sequence stars much cooler than the Sun, due to the paucity of such stars with asteroseismology.
-This has been accompanied by the release of high resolution spectra \citep{gaiabenchmark2} and formed the basis of extensions to lower metallicities \citep{gaiabenchmark5}, stellar twin studies \citep{gaiabenchmarktwins} and comparisons of stellar abundance determination pipelines \citep{gaiabenchmarkabundances}.
+This has been accompanied by the release of high-resolution spectra \citep{gaiabenchmark2} and formed the basis of extensions to lower metallicities \citep{gaiabenchmark5}, stellar twin studies \citep{gaiabenchmarktwins} and comparisons of stellar abundance determination pipelines \citep{gaiabenchmarkabundances}.
 Furthermore, by combining asteroseismology with optical interferometry, it has been possible to determine fundamental parameters of main-sequence and giant stars with unprecedented precision \citep{huber12,thetacygwhite,white15}.
 
-Brighter \kepler stars are therefore ideal benchmark targets, since photometry can be most easily complemented by \gaia parallaxes, interferometric diameters, and high resolution spectroscopy.  
+Brighter \kepler stars are therefore ideal benchmark targets, since photometry can be most easily complemented by \gaia parallaxes, interferometric diameters, and high-resolution spectroscopy.  
 Unfortunately, the \kepler field was deliberately placed to minimize overall the number of extremely bright stars on the detectors, so that only a dozen stars brighter than~6th~magnitude landed on silicon \citep{2010ApJ...713L..79K}.
-This was because stars brighter than $Kp \sim 11$ saturate the CCD detectors, with their flux distributed along a bleed column and rendering those pixels otherwise unusable.
-Furthermore, due to the limited availablility of bandwidth to download data from the spacecraft, only $\sim 5.7\%$ of pixels on the \kepler detectors are actually downloaded in any one Quarter \citep{2010ApJ...713L..87J}.
-The result of these two target selection constraints is that photometry was obtained for most of the mission for only~35 stars brighter than $Kp<7$ in the \kepler field, while~17 targets in this range were observed for less than half the mission and~29 targets brighter than this threshold were entirely ignored.
+This was because stars brighter than $Kp \sim 11$ saturated the CCD detectors, with their flux distributed along a bleed column and rendering those pixels otherwise unusable.
+Furthermore, due to the limited bandwidth to download data from the spacecraft, only $\sim 5.7\%$ of pixels on the \kepler detectors were actually downloaded in each Quarter \citep{2010ApJ...713L..87J}.
+The result of these two target selection constraints is that photometry was obtained for most of the mission for only~35 stars brighter than $Kp<7$ in the \kepler field, while a further~17 targets in this range were observed for less than half the mission and~29 targets brighter than this threshold were entirely ignored.
 The availability of \kepler data remains significantly incomplete down to fainter magnitudes, and in this work we consider $Kp=9$ to be an arbitrary cutoff for bright stars of interest.
 In the \ktwo mission \citep{k2early}, very saturated stars have been observed with `halo photometry' using unsaturated pixels in a specially-determined region around bright stars, including the Pleiades \citep{halo}, Aldebaran \citep{aldebaran}, $\iota$~Librae \citep{Buysschaert2018}, and $\rho$~Leonis \citep{rholeo}.
-Unfortunately, in the four-year \kepler sample, photometry of such saturated stars was rarely attempted.
+Unfortunately, in the four-year \kepler sample, photometry of such saturated stars was rarely attempted, with some exceptions, such as RR~Lyrae \citep{Kolenberg2011} and $\theta$~Cyg and 16~Cyg~AB \citep[e.g.][]{thetacygwhite,Guzik2016}.
 
 \citet{orig_smear} noted a way to obtain photometry of every target on-silicon in \kepler using a data channel normally used for calibration, even if active pixels were not allocated and downloaded.
-\kepler employs an inter-line transfer CCD as its detector, which successively shuffles each row of pixels down to the edges of the chip to be read out.
+\kepler employs an inter-line transfer CCD, which successively shuffles each row of pixels to the edges of the chip to be read out.
 Because the \kepler camera lacks a shutter, the detector is exposed to light during the readout process, with the result that fluxes in each pixel are contaminated by light collected from stars in the same column.
@@
 We find no transiting planets, but detect one new eclipsing binary, and measure solar-like oscillations in 33~red giants.
-We do not model main-sequence stars in great detail, but provide some discussion and initial classification of interesting variability.
+We do not model the hot main-sequence stars in great detail, but provide some discussion and initial classification of interesting variability.
 For the oscillating red giants that constitute the bulk of the sample, we determine the asteroseismic parameters \numax and \Dnu, and therefore stellar masses and \logg measurements.
@@
 
-We have obtained smear light curves for our sample of red giant stars with the \texttt{keplersmear} pipeline as described in Section~\ref{photometry}, performed asteroseismology on all of these to extract \numax and therefore \logg as described in Section~\ref{asteroseismology}, and combined these with TRES spectra to obtain chemical abundances as described in Section~\ref{spectroscopy}.
-
 \subsection{Sample}
@@
 We selected all stars on-silicon in \kepler with $Kp<9$ that were targeted for fewer than $8$ quarters.
-The majority of these were not previously targeted at all, but sixteen stars were to some extent observed conventionally: these are listed in Table~\ref{quarters}.
+The majority of these were not previously targeted at all, but sixteen stars were to some extent observed conventionally; these are listed in Table~\ref{quarters}.
 A number of these lay at the edge of a detector, with the result that in some cadences the centroid of the star did not lie on the chip; light curves from these targets were found to be of extremely low quality and all of these stars were discarded.

### 2019-03-20 paper/ms.tex
tim edits

@@
 We can assess the importance of this contamination by considering differences between quarters.
-Because the Kepler spacecraft rotates $90^\circ$ between successive quarters, stars are observed on different CCD modules with the exception of stars on the central Module~13.
+Because the Kepler spacecraft rotates $90^\circ$ between successive quarters, stars were observed on different CCD modules with the exception of stars on the central Module~13.
 Minor variations in the precise alignment of each CCD mean that the contribution from contaminating stars varies from quarter to quarter.
@@
 
-Several stars in the sample show the `hump-and-spike' morphology in their power spectra \citep[][a broad `hump' of low-amplitude oscillations dominated by one high amplitude coherent oscillation toward the high frequency end of this band]{2013MNRAS.431.2240B,2014MNRAS.441.3543B,2017MNRAS.467.1830B,2018MNRAS.474.2774S}: these are marked `H+S' in Table~\ref{stellar_props}.
+Several stars in the sample show the `hump-and-spike' morphology in their power spectra \citep[a broad `hump' of low-amplitude oscillations dominated by one high amplitude coherent oscillation toward the high frequency end of this band;][]{2013MNRAS.431.2240B,2014MNRAS.441.3543B,2017MNRAS.467.1830B,2018MNRAS.474.2774S}: these are marked `H+S' in Table~\ref{stellar_props}.
 %HD~186155 (HR~7495), 14~Cyg (HD~185872, HR~7483), HD~189178 (HR~7628), HD~183362 (HR~7403), and HD~184787. 

### 2019-03-22 paper/ms.tex
apj format

@@
 % Basic setup. Most papers should leave these options alone.
-\documentclass[a4paper,fleqn,usenatbib]{mnras}
+% \documentclass[a4paper,fleqn,usenatbib]{mnras}
+\documentclass[modern]{aastex62}
 
@@
 \newcommand{\gaia}{\textit{Gaia}\xspace}
+\definecolor{linkcolor}{rgb}{0.1216,0.4667,0.7059}
+
+\usepackage{xcolor, fontawesome}
+\definecolor{twitterblue}{RGB}{64,153,255}
+\newcommand\twitter[1]{\href{https://twitter.com/#1 }{\textcolor{twitterblue}{\faTwitter}\,\tt \textcolor{twitterblue}{@#1}}}
+
+\submitjournal{ApJ}
 
@@
 %%%%%%%%%%%%%%%%%%% TITLE PAGE %%%%%%%%%%%%%%%%%%%
+\begin{document}
 
-\title[The Kepler Smear Campaign]{The \textit{Kepler} Smear Campaign: Light curves for 102 Very Bright Stars}
+\title{The \textit{Kepler} Smear Campaign: Light curves for 102 Very Bright Stars}
+\shorttitle{The Kepler Smear Campaign}
+\shortauthors{B. J. S. Pope et al.}
+
+\correspondingauthor{Benjamin J. S. Pope \twitter{fringetracker}}
+\email{benjamin.pope@nyu.edu}
+
+\author[0000-0003-2595-9114]{Benjamin J. S. Pope}
+\affiliation{Center for Cosmology and Particle Physics, Department of Physics, New York University, 726 Broadway, New York, NY 10003, USA}
+\affiliation{NASA Sagan Fellow}
+\affiliation{Oxford Astrophysics, Denys Wilkinson Building, University of Oxford, OX1 3RH, Oxford, UK}
+
+\author[0000-0002-4290-7351]{Guy R. Davies}
+\affiliation{School of Physics and Astronomy, University of Birmingham, Birmingham B15 2TT, UK}
+\affiliation{Stellar Astrophysics Centre, Department of Physics and Astronomy, Aarhus University, Ny Munkegade 120, DK-8000 Aarhus C, Denmark}
+
+\author[0000-0002-1423-2174]{Keith Hawkins}
+\affiliation{Department of Astronomy, The University of Texas at Austin, 2515 Speedway Boulevard, Austin, TX 78712, USA}
+
+\author[0000-0002-6980-3392]{Timothy R. White}
+\affiliation{Research School of Astronomy and Astrophysics, Mount Stromlo Observatory, The Australian National University, Canberra, ACT 2611, Australia}
+\affiliation{Stellar Astrophysics Centre, Department of Physics and Astronomy, Aarhus University, Ny Munkegade 120, DK-8000 Aarhus C, Denmark}
+
+\author[0000-0002-5496-365X]{Amalie Stokholm}
+\affiliation{Stellar Astrophysics Centre, Department of Physics and Astronomy, Aarhus University, Ny Munkegade 120, DK-8000 Aarhus C, Denmark}
+
+\author[0000-0001-6637-5401]{Allyson Bieryla}
+\affiliation{Harvard-Smithsonian Center for Astrophysics, 60 Garden Street, Cambridge, MA 02138, USA}
+
+\author[0000-0001-9911-7388]{David W. Latham}
+\affiliation{Harvard-Smithsonian Center for Astrophysics, 60 Garden Street, Cambridge, MA 02138, USA}
+
+\author{Madeline Lucey}
+\affiliation{Department of Astronomy, The University of Texas at Austin, 2515 Speedway Boulevard, Austin, TX 78712, USA}
+
+\author[0000-0003-1822-7126]{Conny Aerts}
+\affiliation{Instituut voor Sterrenkunde, KU Leuven, Celestijnenlaan 200D, B-3001 Leuven, Belgium}
+\affiliation{Department of Astrophysics, IMAPP, Radboud University Nijmegen, P.O. Box 9010, NL-6500 GL Nijmegen, The Netherlands}
+
+\author[0000-0003-1453-0574]{Suzanne Aigrain}
+\affiliation{Oxford Astrophysics, Denys Wilkinson Building, University of Oxford, OX1 3RH, Oxford, UK}
+
+\author[0000-0002-0865-3650]{Victoria Antoci}
+\affiliation{Stellar Astrophysics Centre, Department of Physics and Astronomy, Aarhus University, Ny Munkegade 120, DK-8000 Aarhus C, Denmark}
+
+\author[0000-0001-5222-4661]{Timothy R. Bedding}
+\affiliation{Sydney Institute for Astronomy, School of Physics A28, The University of Sydney, NSW 2006, Australia}
+\affiliation{Stellar Astrophysics Centre, Department of Physics and Astronomy, Aarhus University, DK-8000 Aarhus C, Denmark}
+
+\author[0000-0001-7402-3852]{Dominic W. Bowman}
+\affiliation{Instituut voor Sterrenkunde, KU Leuven, Celestijnenlaan 200D, B-3001 Leuven, Belgium}
+
+\author[0000-0003-1125-2564	]{Ashley Chontos}
+\affiliation{Institute for Astronomy, University of Hawai'i, 2680 Woodlawn Drive, Honolulu, HI 96822, USA}
+
+\author[0000-0002-9789-5474]{Gilbert A. Esquerdo}
+\affiliation{Harvard-Smithsonian Center for Astrophysics, 60 Garden Street, Cambridge, MA 02138, USA}
+
+\author[0000-0001-8832-4488 ]{Daniel Huber}
+\affiliation{Institute for Astronomy, University of Hawai'i, 2680 Woodlawn Drive, Honolulu, HI 96822, USA}
+\affiliation{SETI Institute, 189 Bernardo Avenue, Mountain View, CA 94043, USA}
+\affiliation{Stellar Astrophysics Centre, Department of Physics and Astronomy, Aarhus University, DK-8000 Aarhus C, Denmark}
+
+\author[0000-0002-0722-7406]{Paula Jofr\'{e}}
+\affiliation{N\'{u}cleo de Astronom\'{i}a, Facultad de Ingenier\'{i}a y Ciencias, Universidad Diego Portales, Ej\'{e}rcito 441, Santiago De, Chile}
+
+\author[0000-0002-5648-3107]{Simon J. Murphy}
+\affiliation{Sydney Institute for Astronomy, School of Physics A28, The University of Sydney, NSW 2006, Australia}
+\affiliation{Stellar Astrophysics Centre, Department of Physics and Astronomy, Aarhus University, DK-8000 Aarhus C, Denmark}
+
+\author[0000-0003-2771-1745]{Timothy van Reeth}
+\affiliation{Sydney Institute for Astronomy, School of Physics A28, The University of Sydney, NSW 2006, Australia}
+\affiliation{Stellar Astrophysics Centre, Department of Physics and Astronomy, Aarhus University, DK-8000 Aarhus C, Denmark}
+
+\author[0000-0002-6137-903X]{Victor Silva Aguirre}
+\affiliation{Stellar Astrophysics Centre, Department of Physics and Astronomy, Aarhus University, DK-8000 Aarhus C, Denmark}
+
+\author[0000-0002-0007-6211]{Jie Yu}
+\affiliation{Sydney Institute for Astronomy, School of Physics A28, The University of Sydney, NSW 2006, Australia}
+\affiliation{Stellar Astrophysics Centre, Department of Physics and Astronomy, Aarhus University, DK-8000 Aarhus C, Denmark}
 
 % This author list is not final! If you think you should be in a different position please do not hesitate to say so.
-\author[B. J. S. Pope et al.]{Benjamin J. S. Pope,$^{1,2,3}$\thanks{E-mail: benjamin.pope@nyu.edu}
-Guy R. Davies,$^{4,5}$
-Keith Hawkins,$^{6}$
-Timothy R. White,$^{7,5}$\newauthor
-Amalie Stokholm,$^{5}$
-Allyson Bieryla,$^{8}$
-David W. Latham,$^{8}$
-Madeline Lucey,$^{6}$\newauthor
-Conny Aerts,$^{9,10}$
-Suzanne Aigrain,$^{3}$ 
-Victoria Antoci,$^{5}$
-Timothy R. Bedding,$^{11,5}$\newauthor
-Dominic M. Bowman,$^{9}$
-Ashley Chontos,$^{12}$
-Gilbert A. Esquerdo,$^{8}$
-Daniel Huber,$^{12}$\newauthor
-Paula Jofr\'{e},$^{13}$
-Simon J. Murphy,$^{11,5}$
-Timothy van Reeth,$^{11,5}$
-Victor Silva Aguirre,$^{5}$\newauthor
-Jie Yu$^{11,5}$ 
-\\
-% List of institutions
-$^{1}$Center for Cosmology and Particle Physics, Department of Physics, New York University, 726 Broadway, New York, NY 10003, USA\\
-$^{2}$NASA Sagan Fellow\\
-$^{3}$Oxford Astrophysics, Denys Wilkinson Building, University of Oxford, OX1 3RH, Oxford, UK\\
-$^{4}$School of Physics and Astronomy, University of Birmingham, Birmingham B15 2TT, UK\\
-$^{5}$Stellar Astrophysics Centre, Department of Physics and Astronomy, Aarhus University, Ny Munkegade 120, DK-8000 Aarhus C, Denmark\\
-$^{6}$Department of Astronomy, The University of Texas at Austin, 2515 Speedway Boulevard, Austin, TX 78712, USA\\
-$^{7}$Research School of Astronomy and Astrophysics, Mount Stromlo Observatory, The Australian National University, Canberra, ACT 2611, Australia\\
-$^{8}$Harvard-Smithsonian Center for Astrophysics, 60 Garden Street, Cambridge, MA 02138, USA\\
-$^{9}$Institute of Astronomy, KU Leuven, Celestijnenlaan 200D, B-3001 Leuven, Belgium\\
-$^{10}$Department of Astrophysics, IMAPP, Radboud University Nijmegen, P.O. Box 9010, 6500 GL Nijmegen, The Netherlands\\
-$^{11}$Sydney Institute for Astronomy (SIfA), School of Physics, University of Sydney, NSW 2006, Australia\\
-$^{12}$Institute for Astronomy, University of Hawai'i, 2680 Woodlawn Drive, Honolulu, HI 96822, USA\\
-$^{13}$N\'{u}cleo de Astronom\'{i}a, Facultad de Ingenier\'{i}a y Ciencias, Universidad Diego Portales, Ej\'{e}rcito 441, Santiago De, Chile\\
-}
-
-% These dates will be filled out by the publisher
-\date{Accepted XXX. Received YYY; in original form ZZZ}
-
-\pubyear{2018}
-
-% Don't change these lines
-\begin{document}
-\label{firstpage}
-\pagerange{\pageref{firstpage}--\pageref{lastpage}}
-\maketitle
 
@@
 All source code, light curves, TRES spectra, and asteroseismic and stellar parameters are publicly available as a \kepler legacy sample.
-\href{https://github.com/benjaminpope/smearcampaign}{\faGithub}
+\href{https://github.com/benjaminpope/smearcampaign}{\color{linkcolor}\faGithub}
 \end{abstract}
@@
 % Don't make up new ones.
-\begin{keywords}
-asteroseismology -- techniques: photometric -- stars: variable: general
-\end{keywords}
+\keywords{asteroseismology -- techniques: photometric -- stars: variable: general
+}
 
@@
 
-\input{quarters.tex}
+% \input{quarters.tex}
+\input{quarters_apj.tex}
 
@@
 \begin{figure*}
-\noindent\includegraphics[width=15cm,keepaspectratio]{gaia_kepler_hr.png}
+\plotone{gaia_kepler_hr.png}
 
@@
 \begin{figure}
-\noindent\includegraphics[width=8cm,keepaspectratio]{contam_HD_181778.png}
-
+\plotone{contam_HD_181778.pdf}
 \caption{\label{contamination}
@@
 \begin{figure}
-\noindent\includegraphics[width=8cm,keepaspectratio]{contam.eps}
+\plotone{contam.eps}
 
@@
 
-\input{all_stars.tex}
-\input{all_Stars2.tex}
+% \input{all_stars.tex}
+% \input{all_Stars2.tex}
+\input{all_stars_apj.tex}
 
@@
 
-\input{astero_table.tex}
+\input{astero_table_apj.tex}
 
@@
 
-\input{stellar_props.tex}
-
-\input{abundances_1.tex}
-\input{abundances_2.tex}
+\input{stellar_props_apj.tex}
+\input{abundances_1_apj.tex}
+\input{abundances_2_apj.tex}
 
@@
 For the solar values, we adopted $\nu_{\text{max, }\odot}=3090$~$\mu$Hz, $\Delta\nu_{\odot}=135.1$~$\mu$Hz \citep{huber2011}, and $T_{\text{eff, }\odot}=5777$~K.
-\newpage
 
@@
 % \noindent\includegraphics[width=17cm,keepaspectratio]{different_constraints_fullsample_ove02.pdf}
-\noindent\includegraphics[width=8.5cm,keepaspectratio]{different_constraints_ben.pdf}
+\plotone{different_constraints_ben.pdf}
 
@@
 \begin{figure}
-\noindent\includegraphics[width=8.5cm,keepaspectratio]{combined_radii.eps}
+\plotone{combined_radii.eps}
 
@@
 \begin{figure*}
-\noindent\includegraphics[width=0.7\textwidth,keepaspectratio]{Pope_alpha_oddZ.pdf}
+\plotone{Pope_alpha_oddZ.pdf}
 
@@
 \begin{figure*}
-\noindent\includegraphics[width=0.7\textwidth,keepaspectratio]{Pope_ncap.pdf}
+\plotone{Pope_ncap.pdf}
 
@@
 \begin{figure*}
-\noindent\includegraphics[width=19cm,keepaspectratio]{HD_183124.png}
+\plotone{HD_183124.png}
 
@@
 \begin{figure*}
-\noindent\includegraphics[width=19cm,keepaspectratio]{HD186255_time-delay_plot.png}
+\plotone{HD186255_time-delay_plot.png}
 
@@
 
-\bibliographystyle{mnras}
 \bibliography{ms} % if your bibtex file is called example.bib
@@
 % Don't change these lines
-\bsp	% typesetting comment
-\label{lastpage}
 \end{document}

### 2019-03-22 paper/quarters_apj.tex
apj format

\begin{deluxetable}{cc}
\tablecaption{Targets observed conventionally for one or more quarters.}
\tablehead{\colhead{Object} & \colhead{Quarters}}
\startdata
HD~174020 & Q2, 6, 10, 14            \\
HD~175841 & Q11-12, 14-16, SC Q3     \\
HD~176582 & Q12-13                   \\
HD~178090 & Q1, 3, 10                \\
HD~180682 & Q0, 3, 7                 \\
HD~181069 & Q1, 10, 13, 14, 17       \\
HD~181878 & Q14-17                   \\
HD~182694 & Q2                       \\
HD~183124 & Even Quarters            \\
HD~185351 & Q1-3; SC Q16             \\
HD~186155 & Q1                       \\
HD~187217 & Q14-17                   \\
HD~188252 & Q13                      \\
HD~189013 & SC Q3                    \\
V380~Cyg  & Q11; SC Q7, 9, 10, 12-17 \\
V819~Cyg  & Q14, 16, 17    \\
\enddata
\tablecomments{Some smear targets were observed conventionally for one or more quarters. 
These are listed below, with SC denoting quarters that were observed in short cadence mode and all others in long cadence.  \label{quarters}}
\end{deluxetable}

### 2019-03-24 paper/ms.tex
updates

@@
 \usepackage{ulem}
+\usepackage{newunicodechar,graphicx}
+
+\DeclareRobustCommand{\okina}{%
+  \raisebox{\dimexpr\fontcharht\font`A-\height}{%
+    \scalebox{0.8}{`}%
+  }%
+}
+\newunicodechar{ʻ}{\okina}
 
@@
 \author[0000-0003-1125-2564	]{Ashley Chontos}
-\affiliation{Institute for Astronomy, University of Hawai'i, 2680 Woodlawn Drive, Honolulu, HI 96822, USA}
+\affiliation{Institute for Astronomy, University of Hawai\okina i, 2680 Woodlawn Drive, Honolulu, HI 96822, USA}
 
@@
 \author[0000-0001-8832-4488 ]{Daniel Huber}
-\affiliation{Institute for Astronomy, University of Hawai'i, 2680 Woodlawn Drive, Honolulu, HI 96822, USA}
+\affiliation{Institute for Astronomy, University of Hawai\okina i, 2680 Woodlawn Drive, Honolulu, HI 96822, USA}
 \affiliation{SETI Institute, 189 Bernardo Avenue, Mountain View, CA 94043, USA}
@@
 All source code, light curves, TRES spectra, and asteroseismic and stellar parameters are publicly available as a \kepler legacy sample.
-\href{https://github.com/benjaminpope/smearcampaign}{\color{linkcolor}\faGithub}
+\href{https://github.com/benjaminpope/smearcampaign}{\faGithub}
 \end{abstract}
@@
 \caption{\label{contamination}
-Power spectra of odd and even quarters of HD~181778.
-It is clear from inspection that while odd quarters have the power spectrum expected of a giant star, even quarters have very high amplitude coherent oscillations.}
+Power spectra of odd and even quarters of HD~181778. Even quarters have very high amplitude coherent oscillations that are absent in odd quarters.}
 \end{figure}
@@
 For the solar values, we adopted $\nu_{\text{max, }\odot}=3090$~$\mu$Hz, $\Delta\nu_{\odot}=135.1$~$\mu$Hz \citep{huber2011}, and $T_{\text{eff, }\odot}=5777$~K.
+We emphasize that all quoted error bars in Tables~\ref{stellar_props} and~\ref{astero_table} are formal uncertainties, and do not take into account systematic differences in asteroseismic measurement methods, effective temperature scales, or stellar model physics.
+For example, recent tests of red giant models imply that systematic age errors can be expected to be significantly larger than the formal age uncertainties in Table~\ref{stellar_props} \citep{Tayar2017}.
 
@@
 A comparison of the stellar radii determined here from asteroseismology and spectroscopy to those from the \gaia~DR2 catalogue and from our own calculations based on \gaia parallaxes and TRES spectroscopy.
-There is overall good agreement except for very large radii, and except for BD+39~3577 (marked), which we do not understand.}
+There is overall good agreement except for very large radii, and except for BD+39~3577 (marked).}
 \end{figure}
@@
 BJSP also acknowledges support from Balliol College and the Clarendon Fund.
-DH acknowledges support by the National Aeronautics and Space Administration through the K2 Guest Observer Program (NNX17AF76G, 80NSSC18K0362) and the National Science Foundation (AST-1717000).
+DH acknowledges support by the National Aeronautics and Space Administration through the K2 Guest Observer Program (NNX17AF76G, 80NSSC19K0108, 80NSSC18K0362) and the National Science Foundation (AST-1717000).
 TRW acknowledges the support of the Australian Research Council (grant DP150100250).
@@
 
-% BJSP acknowledges being on the traditional territory of the Lenape Nations and recognizes that Manhattan continues to be the home to many Algonkian peoples.
+BJSP acknowledges being on the traditional territory of the Lenape Nations and recognizes that Manhattan continues to be the home to many Algonkian peoples.
 We give blessings and thanks to the Lenape people and Lenape Nations in recognition that we are carrying out this work on their indigenous homelands.

### 2019-05-10 paper/ms.tex
smear campaign resubmitted

@@
 \affiliation{Center for Cosmology and Particle Physics, Department of Physics, New York University, 726 Broadway, New York, NY 10003, USA}
+\affiliation{Center for Data Science, New York University, 60 Fifth Ave, New York, NY 10011, USA}
 \affiliation{NASA Sagan Fellow}
@@
 \author[0000-0001-6637-5401]{Allyson Bieryla}
-\affiliation{Harvard-Smithsonian Center for Astrophysics, 60 Garden Street, Cambridge, MA 02138, USA}
+\affiliation{Center for Astrophysics | Harvard \& Smithsonian, 60 Garden Street, Cambridge, MA 02138, USA}
 
 \author[0000-0001-9911-7388]{David W. Latham}
-\affiliation{Harvard-Smithsonian Center for Astrophysics, 60 Garden Street, Cambridge, MA 02138, USA}
+\affiliation{Center for Astrophysics | Harvard \& Smithsonian, 60 Garden Street, Cambridge, MA 02138, USA}
 
@@
 
-\author[0000-0001-7402-3852]{Dominic W. Bowman}
+\author[0000-0001-7402-3852]{Dominic M. Bowman}
 \affiliation{Instituut voor Sterrenkunde, KU Leuven, Celestijnenlaan 200D, B-3001 Leuven, Belgium}
@@
 % Don't make up new ones.
-\keywords{asteroseismology -- techniques: photometric -- stars: variable: general
-}
+\keywords{asteroseismology -- techniques: photometric -- stars: variable: general -- 
+stars: early-type -- stars: red giants -- stars: rotation}
 
@@
 A number of these lay at the edge of a detector, with the result that in some cadences the centroid of the star did not lie on the chip; light curves from these targets were found to be of extremely low quality and all of these stars were discarded.
-After applying these criteria we obtained a list of 102 targets, which are listed in Table~\ref{all_stars} with their \kepler magnitude $Kp$, together with their spectral type from SIMBAD, \gaia~DR2 apparent~$G$ magnitudes and $Bp-Rp$ colours, \gaia~DR2 calibrated distances from \citet{gaiadists}, variability classification and availability of TRES spectroscopy.
+After applying these criteria we obtained a list of 102 targets, which are listed in Table~\ref{all_stars} with their \kepler magnitude $Kp$, together with their spectral type from SIMBAD, \gaia~DR2 apparent~$G$ magnitudes and $Bp-Rp$ colors, \gaia~DR2 calibrated distances from \citet{gaiadists}, variability classification and availability of TRES spectroscopy.
+It should be noted that $Bp-Rp$ colours are not calibrated for reddening and are therefore not a precise measure of stellar temperature.
 The \kepler spacecraft rotates between quarters, so that it cycles through four orientation `seasons' each rotated from the last by $90^{\circ}$.
@@
 
-Figure~\ref{hrdiagram} shows these stars on a colour-magnitude diagram using \gaia $Bp-Rp$ and absolute~$G$ magnitudes and \gaia~DR2 calibrated distances \citep{gaiadists}, overlaid on the \kepler sample from the Bedell \url{gaia-kepler.fun} crossmatch.
+Figure~\ref{hrdiagram} shows these stars on a colour-magnitude diagram using \gaia $Bp-Rp$ and absolute~$G$ magnitudes and \gaia~DR2 calibrated distances \citep{gaiadists}, overlaid on the \kepler sample from the Bedell \href{https://gaia-kepler.fun}{\nolinkurl{gaia-kepler.fun}} crossmatch.
 The smear targets in this diagram selected to have higher apparent brightnesses than the general \kepler population, appear also to have higher intrinsic luminosities.
@@
 \caption{\label{hrdiagram}
-\gaia colour-magnitude diagram of the Smear Campaign stars (orange and teal) overlaid on the sample of \kepler stars with \gaia parallax $\text{SNR} > 25$ (black), using the Bedell \url{gaia-kepler.fun} crossmatch and \gaia~DR2 calibrated distances from \citet{gaiadists}.
+\gaia colour-magnitude diagram of the Smear Campaign stars (orange and teal) overlaid on the sample of \kepler stars with \gaia parallax $\text{SNR} > 25$ (black), using the Bedell \href{https://gaia-kepler.fun}{\nolinkurl{gaia-kepler.fun}} crossmatch and \gaia~DR2 calibrated distances from \citet{gaiadists}.
 The smear sample includes giants and hot main-sequence stars.
 Those giants for which TRES spectroscopy have been obtained are highlighted in teal.
-An interactive version of this diagram is available as supplementary material from the journal or at \url{benjaminpope.github.io/data/cmd_smear.html}.}
+Three stars discussed in the text are marked with $\star$ symbols.
+An interactive version of this diagram is available as supplementary material from the journal or at  \href{https://benjaminpope.github.io/data/cmd_smear.html}{\nolinkurl{benjaminpope.github.io/data/cmd_smear.html}}.}
 \end{figure*}
@@
 We investigate these further, finding that in some of these cases  there was no obvious problem.
-For example, the classical pulsator HD~175841 showed amplitude changes of several pulsations but the overall distribution seemed very similar, from which we conclude that the variation is probably astrophysical.
+For example, the classical pulsator HD~175841 showed amplitude changes of several pulsations but the overall distribution seemed very similar, from which we conclude that the variation is probably astrophysical \citep[as in][]{2016MNRAS.460.1970B}.
 
 In the case of HD~181878, a red giant on Module~13, there is clear and significant contamination from a star with several low-frequency pulsations, as is seen in Figure~\ref{contamination}.
-Likewise the light curve for HD 183383, which variously falls on Modules~8, 12, 14 and~18, shows different behaviour for different quarters: some parts are likely from an ellipsoidal variable with a period of 6.46 days, while other quarters are contaminated by the star RR Lyrae.
+Likewise the light curve for HD 183383, which variously falls on Modules~8, 12, 14 and~18, shows different behaviour for different quarters: some parts are likely from an ellipsoidal variable with a period of 6.46 days, while other quarters are contaminated by the star RR~Lyrae.
+The effects of this contamination in the time domain are shown in Figure~\ref{contamination_timeseries}: there is very little discernable effect for HD~181878 by eye, whereas the RR~Lyr contamination in HD~183383 is readily apparent.
 Between seasons, there is an extra hump of power near the red giant oscillations in HD~175740; extra low frequency power in HD~180658; one coherent peak in  HD~182694; high frequency contamination in HD~181597 possibly from an EB; and a very significant difference in amplitude between seasons for BD~+39~3882.
@@
 \begin{figure}
+\plotone{contam_timeseries.pdf}
+\caption{\label{contamination_timeseries}
+Time series of Quarters 12-13 of HD~181778 and HD~183383, both of which show contamination.
+For HD~181778, contamination is not apparent to the eye in the time series, but Figure~\ref{contamination} showed that in its power spectrum there is a significant effect from a coherent oscillator.
+Meanwhile in HD~183383, even quarters show easily visible contamination from the star RR~Lyr, some quarters worse than others, while odd quarters show low amplitude coherent variability consistent with an ellipsoidal variable.}
+\end{figure}
+
+\begin{figure}
 \plotone{contam.eps}
@@
 \end{figure}
-
-% \input{all_stars.tex}
-% \input{all_Stars2.tex}
-\input{all_stars_apj.tex}
 
@@
 For this dataset, \dnu is not constrained, but mean $\langle \Dnu \rangle$ is typically well-constrained and its posterior marginal distribution is well-represented by a single Gaussian.
+We fit and report also the dimensionless parameter $\epsilon$ is the offset of the lowest frequency in the comb of p-modes from zero frequency in units of $\Dnu$.
 
@@
 We determined the mass, radius, and age for the 33 red giants from their atmospheric and asteroseismic observables (see Table~\ref{astero_table}) using the BAyesian STellar Algorithm \citep[\textsc{basta}][]{silvaaguirre2015,silvaaguirre2017}.
-\textsc{basta} compares the observed properties with predictions from theoretical models of stellar evolution, in this case the recently updated BaSTI (a Bag of Stellar Tracks and Isochrones) stellar models and isochrones library \citep{Hidalgo:2018dy}.
+\textsc{basta} compares the observed properties (\teff, \feh, \logg, \Dnu, and \numax) with predictions from theoretical models of stellar evolution, in this case the recently updated BaSTI (a Bag of Stellar Tracks and Isochrones) stellar models and isochrones library \citep{Hidalgo:2018dy}.
 The isochrones include core overshooting with an efficiency of 0.20 times the pressure scale height as described in \citet{Hidalgo:2018dy}, but do not include diffusion or rotational mixing.
@@
 To gauge the level of improvement in our understanding of these stars, in Figure~\ref{gaia_comparison} we plot the radii determined here against those from the \gaia~DR2 catalog determined by the stellar bolometric flux and parallax.
-We also calculate \gaia-like stellar bolometric radii using \texttt{isoclassify} \citep{huber2017} using our new spectroscopic \teff measurements rather than those from \gaia~DR2, together with \gaia~DR2 parallaxes spectroscopic \logg, $Z$, and SIMBAD $V$.
-While not all of our targets have \gaia radii, we find that while there is overall agreement to within a few $\sigma$, the results from stellar modelling are consistently slightly larger than those from \gaia.
+We also calculate \gaia-like stellar bolometric radii using the software \texttt{isoclassify} \citep{huber2017}, using as our input \teff values our new spectroscopic \teff, \feh, and \logg measurements rather than those from \gaia~DR2, together with \gaia~DR2 parallaxes, and SIMBAD $V$.
+While not all of our targets have radii in the \gaia catalogs, for those that do we find that there is overall agreement to within a few $\sigma$, but that the results from stellar modelling are consistently slightly larger than those from \gaia.
 This discrepancy goes away for most stars when we use our own \texttt{isoclassify} radii, suggesting that this is an effect of \teff calibration.
@@
 \caption{\label{gaia_comparison}
-A comparison of the stellar radii determined here from asteroseismology and spectroscopy to those from the \gaia~DR2 catalogue and from our own calculations based on \gaia parallaxes and TRES spectroscopy.
+A comparison of the stellar radii determined here from asteroseismology and spectroscopy to those from the \gaia~DR2 catalogue ($y$-axis) and from our own calculations based on \gaia parallaxes and TRES spectroscopy ($x$-axis).
+Blue points are from \gaia measurements explicitly, and orange points \gaia-like calculations using \texttt{isoclassify} \citep{huber2017} and substituting own $T_{eff}$ measurements rather than those from \gaia.
+The green line overlaid shows a 1:1 relation.
 There is overall good agreement except for very large radii, and except for BD+39~3577 (marked).}
@@
 For 37 of the F-type pulsators among those, asteroseismic modelling of the g modes led to their masses, ages, core rotation and core mass with relative precisions of about 10\% \citep{2019MNRAS.tmp..495M}.
-The vast majority of B-type intermediate-mass stars observed byKepler have yet to be subjected to in-depth asteroseismic analyses and modelling of their interior properties.
 However, the vast majority of intermediate-mass stars observed by Kepler have yet to be subjected to in-depth asteroseismic analyses and modelling of their interior properties.
@@
 The few that were monitored did not reveal suitable oscillation frequency patterns to achieve a unique mode identification, which is a requirement to perform asteroseismic modelling.
-The investigation of pulsation modes in high-mass stars using high-quality \kepler smear data combined with high-precision spectroscopy to identify the modes \citep[Chapter 6]{aertsbook} is an exciting prospect for asteroseismology, as the interior physics of these stars are largely unknown, yet they play a pivotal role in stellar and galactic evolution.
+The investigation of pulsation modes in high-mass stars using high-quality \kepler smear data combined with high-precision spectroscopy to identify the modes \citep[Chapter 6]{aertsbook} is an exciting prospect for asteroseismology, as the interior physics of these stars are largely unknown \citep[e.g.][]{2019arXiv190502120B}, yet they play a pivotal role in stellar and galactic evolution.
 The in-depth asteroseismic analysis of the smear data for the~B~stars will be the subject of future work.
@@
 
-Several stars in the sample show the `hump-and-spike' morphology in their power spectra \citep[a broad `hump' of low-amplitude oscillations dominated by one high amplitude coherent oscillation toward the high frequency end of this band;][]{2013MNRAS.431.2240B,2014MNRAS.441.3543B,2017MNRAS.467.1830B,2018MNRAS.474.2774S}: these are marked `H+S' in Table~\ref{stellar_props}.
+Several stars in the sample show the `hump-and-spike' morphology in their power spectra \citep[a broad `hump' of low-amplitude oscillations dominated by one high amplitude coherent oscillation toward the high frequency end of this band;][]{2013MNRAS.431.2240B,2014MNRAS.441.3543B,2017MNRAS.467.1830B}.
+\citet{2018MNRAS.474.2774S} have recently interpreted the hump-and-spike power spectra as evidence for Rossby modes.
 %HD~186155 (HR~7495), 14~Cyg (HD~185872, HR~7483), HD~189178 (HR~7628), HD~183362 (HR~7403), and HD~184787. 
+These stars are marked `H+S' in Table~\ref{stellar_props}.
 Of these, HD~186155 and 14~Cyg are the third-- and sixth--brightest stars on silicon, making these the brightest stars that show this effect.
-The identification for HD~189178 is tentative, as the spectrum also shows evidence of SPB pulsations, and for HD~183362 for $\gamma$\,Dor pulsations, while for HD~184787 there is long term variability consistent with contamination.
+The identification for HD~189178 is tentative, as the power spectrum also shows evidence of SPB pulsations.
+This is likewise the case for HD~183362 which shows $\gamma$\,Dor pulsations, and for HD~184787 there is long-term variability consistent with contamination.
 The other hump-and-spike identifications seem secure.
-\citet{2018MNRAS.474.2774S} have recently interpreted the hump-and-spike power spectra as evidence for Rossby modes.
 The F5 star HD~186155, identified by SIMBAD as having a giant spectral type of F5II-III, is shown by its \gaia distance to in fact lie on the main-sequence.
@@
 It is unclear whether the explanation of the hump-and-spike phenomenon will shed light on the strange behaviour of Boyajian's~Star, but it may be relevant.
+
+\begin{figure}
+\plotone{humpandspike.pdf}
+
+\caption{\label{hs_fig}
+Lomb-Scargle periodograms in normalized amplitude of three `Hump and Spike' stars: HD~189718, HD~184787, and HD~183362, with the `hump' features highlighted with red ellipses.}
+\end{figure}
 
@@
 DWL acknowledges partial support from the Kepler Extended Mission under NASA Cooperative Agreement NNX13AB58A with the Smithsonian Astrophysical Observatory.
-The research leading to these results has received funding from the European Research Council (ERC) under the European Union's Horizon 2020 research and innovation programme (grant agreement No670519: MAMSIE).
+The research leading to these results has received funding from the European Research Council (ERC) under the European Union's Horizon 2020 research and innovation programme (grant agreement N$^\circ$670519: MAMSIE).
 VSA acknowledges support the Independent Research Fund Denmark (Research grant 7027-00096B).
@@
 This work has made use of data from the European Space Agency (ESA) mission
-{\it Gaia} (\url{https://www.cosmos.esa.int/gaia}), processed by the {\it Gaia}
-Data Processing and Analysis Consortium (DPAC,
-\url{https://www.cosmos.esa.int/web/gaia/dpac/consortium}). Funding for the DPAC
+{\it Gaia} (\href{https://www.cosmos.esa.int/gaia}{\nolinkurl{cosmos.esa.int/gaia}}), processed by the {\it Gaia}
+Data Processing and Analysis Consortium (DPAC, \href{https://www.cosmos.esa.int/web/gaia/dpac/consortium}{\nolinkurl{cosmos.esa.int/web/gaia/dpac/consortium}}). Funding for the DPAC
 has been provided by national institutions, in particular the institutions
-participating in the {\it Gaia} Multilateral Agreement. This work has made use of the \url{gaia-kepler.fun} crossmatch database created by Megan Bedell.
+participating in the {\it Gaia} Multilateral Agreement. This work has made use of the \href{https://gaia-kepler.fun}{\nolinkurl{gaia-kepler.fun}} crossmatch database created by Megan Bedell.
 
-This research made use of NASA's Astrophysics Data System; the SIMBAD database, operated at CDS, Strasbourg, France; the IPython package \citep{PER-GRA:2007}; SciPy \citep{jones_scipy_2001}; and Astropy, a community-developed core Python package for Astronomy \citep{astropy}.
+This research made use of NASA's Astrophysics Data System; the SIMBAD database, operated at CDS, Strasbourg, France.
 Some of the data presented in this paper were obtained from the Mikulski Archive for Space Telescopes (MAST).
@@
 We acknowledge the support of the Group of Eight universities and the German Academic Exchange Service through the Go8 Australia-Germany Joint Research Co-operation Scheme.
+
+\software{IPython  \citep{PER-GRA:2007}; SciPy \citep{jones_scipy_2001}; and Astropy, a community-developed core Python package for Astronomy \citep{astropy}.}
 
@@
 \bibliography{ms} % if your bibtex file is called example.bib
+
+\appendix
+
+% \input{all_stars.tex}
+% \input{all_Stars2.tex}
+\input{all_stars_apj.tex}
 

### 2019-05-17 paper/ms.tex
updates

@@
 For this dataset, \dnu is not constrained, but mean $\langle \Dnu \rangle$ is typically well-constrained and its posterior marginal distribution is well-represented by a single Gaussian.
-We fit and report also the dimensionless parameter $\epsilon$ is the offset of the lowest frequency in the comb of p-modes from zero frequency in units of $\Dnu$.
+We also fit the dimensionless parameter $\epsilon$, which is the offset of the lowest frequency in the comb of p-modes from zero in units of $\Dnu$.
 
@@
 To gauge the level of improvement in our understanding of these stars, in Figure~\ref{gaia_comparison} we plot the radii determined here against those from the \gaia~DR2 catalog determined by the stellar bolometric flux and parallax.
-We also calculate \gaia-like stellar bolometric radii using the software \texttt{isoclassify} \citep{huber2017}, using as our input \teff values our new spectroscopic \teff, \feh, and \logg measurements rather than those from \gaia~DR2, together with \gaia~DR2 parallaxes, and SIMBAD $V$.
+We also calculate \gaia-like stellar bolometric radii using the software \texttt{isoclassify} \citep{huber2017}, using our new spectroscopic \teff, \feh, and \logg measurements rather than those from \gaia~DR2, together with \gaia~DR2 parallaxes, and SIMBAD $V$.
 While not all of our targets have radii in the \gaia catalogs, for those that do we find that there is overall agreement to within a few $\sigma$, but that the results from stellar modelling are consistently slightly larger than those from \gaia.
@@
 To facilitate open science, we have made the products of this research available online.
-All code used to produce smear light curves is available under a GPL~v3 license at \href{https://github.com/benjaminpope/keplersmear}{\nolinkurl{github.com/benjaminpope/keplersmear}}.
-All smear light curves, both including the red giant sample studied in detail in Section~\ref{rgs}, and main-sequence stars as discussed in Sections~\ref{mainseq} and~\ref{ebs}, can be downloaded from the Mikulski Archive for Space Telescopes (MAST) as a High-Level Science Product.
-TRES spectra will be made available from the ExoFOP-TESS website, and all asteroseismic parameters and derived stellar parameters for the red giants in Section~\ref{rgs} are provided in an online-only table as Supplementary Material to this paper.
+All code used to produce smear light curves is available under a GPL~v3 license\footnote{ \href{https://github.com/benjaminpope/keplersmear}{\nolinkurl{github.com/benjaminpope/keplersmear}} \citep{keplersmear_zenodo}}.
+All smear light curves, both including the red giant sample studied in detail in Section~\ref{rgs}, and main-sequence stars as discussed in Sections~\ref{mainseq} and~\ref{ebs}, can be downloaded from the Mikulski Archive for Space Telescopes (MAST) as a High Level Science Product\footnote{\dataset[10.17909/t9-4sgf-9c19]{\doi{10.17909/t9-4sgf-9c19}}}.
+TRES spectra are available from the ExoFOP-TESS website\footnote{\dataset[exofop.ipac.caltech.edu/tess/]{https://exofop.ipac.caltech.edu/tess/}}.
 

### 2019-05-17 paper/ms.tex
new figures

@@
 \begin{figure*}
-\plotone{Pope_alpha_oddZ.pdf}
+\plotone{Pope_Fig7_v1.pdf}
 
@@
 The [Mg/Fe], [Si/Fe], [Ti/Fe], [V/Fe] (left panel) and [Al/Fe], [Ca/Fe], [Ni/Fe], [Cr/Fe] (right panel) abundance ratios as a function of iron for our stars (black circles).
-We also show a representative sample of Galactic disk stars from \citet[open red squares]{Bensby2014}, \citet[open orange squares]{Adibekyan2012}, and \citet[light green circles]{Battistini2015}.
+We also show a representative sample of Galactic disk stars from \citet[open red squares]{Bensby2014}, \citet[open blue squares]{Adibekyan2012}, and \citet[teal circles]{Battistini2015}.
 These elemental ratios show that the chemical composition of our sample is consistent with the Galactic disk population.
@@
 Nevertheless, we conclude all elemental abundance ratios studied our sample most closely resemble the Galactic disk.
+
 \begin{figure*}
-\plotone{Pope_ncap.pdf}
-
+\plotone{Pope_Fig8_v1.pdf}
 \caption{\label{fig:ncap}
 The [Mg/Fe], [Si/Fe], [Ti/Fe], [V/Fe] (left panel) and [Al/Fe], [Ca/Fe], [Ni/Fe], [Cr/Fe] (right panel) abundance ratios as a function of iron for our stars (black circles).
-We also show a representative sample of Galactic disk stars from \citet[open red square,][]{Bensby2014}, \citet[green circles][]{Battistini2016}.
+We also show a representative sample of Galactic disk stars from \citet[open red square,][]{Bensby2014}, \citet[blue circles][]{Battistini2016}.
 These elemental ratios give a representive example of the chemical composition of our sample and show they are consistent with the Galactic disk population.

### 2019-05-17 paper/ms.tex
phrasing

@@
 
-In Fig.~\ref{alphael}, we display the [Mg/Fe] abundance ratio as a function of [Fe/H] for our stars (black circles), compared\footnote{There may to be systematics between our [X/Fe] abundance scale and those of our comparison samples.} to representative thick and thin disk stars from \cite[open red squares]{Bensby2014} and \cite[open orange triangles]{Adibekyan2012}.
+In Fig.~\ref{alphael}, we display the [Mg/Fe] abundance ratio as a function of [Fe/H] for our stars (black circles), compared\footnote{There may to be systematics between our [X/Fe] abundance scale and those of our comparison samples.} to representative thick and thin disk stars from \cite[open red squares]{Bensby2014} and \cite[open blue triangles]{Adibekyan2012}.
 
@@
 The [Mg/Fe], [Si/Fe], [Ti/Fe], [V/Fe] (left panel) and [Al/Fe], [Ca/Fe], [Ni/Fe], [Cr/Fe] (right panel) abundance ratios as a function of iron for our stars (black circles).
-We also show a representative sample of Galactic disk stars from \citet[open red square,][]{Bensby2014}, \citet[blue circles][]{Battistini2016}.
+We also show a representative sample of Galactic disk stars from \citet[red,][]{Bensby2014}, \citet[blue][]{Battistini2016}.
 These elemental ratios give a representive example of the chemical composition of our sample and show they are consistent with the Galactic disk population.

### 2019-05-17 notebooks/rg-figure.py
new fig 9 and code

@@ -1,0 +1,47 @@
+# publication quality plot
+
+import matplotlib.pyplot as plt
+import numpy as np
+#import pandas as pd
+import matplotlib as mpl 
+mpl.rcParams['font.size']=22               #10 
+mpl.rcParams["font.family"] = "Times New Roman"
+
+file = "HD_183124_smear_combined.clip.ts.fft"  # best one
+
+data1 =  np.genfromtxt(file, names=True)
+freq = data1['fre']
+power = data1['power']
+
+f, (ax1, ax2) = plt.subplots(1,2, gridspec_kw = {'width_ratios':[3,1]}, figsize=(16,9))
+
+ax1.plot(freq, power, color='black')
+#ax1.title(file)
+ax1.set_xlabel('Frequency ($\mu$Hz)')
+ax1.set_ylabel('Power density (ppm$^2/\mu$Hz)')
+ax1.set_xlim(20,60)
+ax1.set_ylim(0,200000)
+
+peaks =  np.genfromtxt(file+'.peaks', comments='#')
+ax1.scatter(peaks, 60000 + 0*peaks, marker='o')
+
+radial = np.array([30.7, 34.8, 39.3, 43.6, 47.9])
+radial = np.array([26.3, 30.7, 34.8, 39.3, 43.6, 47.9, 52])
+for i in range(0, radial.size):
+    ax1.plot([radial[i], radial[i]],[0, 1e6], color='black', linestyle='dotted')
+
+period = 1e6/peaks
+
+radial = np.array([30.7, 34.8, 39.3, 43.6, 47.9])
+
+
+for DP in [300.1]:
+#    ax2.figure(figsize=(8/1.5,12/1.5))
+    ax2.plot(np.mod(period, DP), peaks, '-o')
+    ax2.set_xlim(0,300)
+    ax2.set_xlabel('Period mod ' + str(DP) +' (s)')
+    ax2.set_ylabel('Frequency ($\mu$Hz)')
+    for i in range(0, radial.size):
+        ax2.plot([0, 350], [radial[i], radial[i]], color='black', linestyle='dotted')
+
+plt.savefig('../paper/HD_183124.pdf',bbox_inches='tight')

### 2019-05-17 notebooks/rg-figure.py
font fixed

@@ -4,7 +4,7 @@ import matplotlib.pyplot as plt
 import numpy as np
 #import pandas as pd
 import matplotlib as mpl 
-mpl.rcParams['font.size']=22               #10 
+mpl.rcParams['font.size']=24               #10 
 mpl.rcParams["font.family"] = "Times New Roman"
 
 file = "HD_183124_smear_combined.clip.ts.fft"  # best one

### 2019-05-20 paper/ms.tex
lucey orcid
update
figures and tables amended
figures
final version?
typo

@@
 
-\author{Madeline Lucey}
+\author[0000-0001-7297-8508]{Madeline Lucey}
 \affiliation{Department of Astronomy, The University of Texas at Austin, 2515 Speedway Boulevard, Austin, TX 78712, USA}
@@
 
-% \begin{figure}
-% \noindent\includegraphics[width=8cm,keepaspectratio]{venn.png}
-% \caption{\label{venn}
-% Venn diagram showing the overall structure of the \kepler Smear Campaign sample, showing the subsets for which TRES spectroscopy and asteroseismology are available and their overlap.}
-% \end{figure}
-
 We can assess the importance of this contamination by considering differences between quarters.
@@
 \begin{figure}
-\plotone{contam.eps}
-
+\plotone{contam.pdf}
 \caption{\label{contamination2}
@@
 \begin{figure}
-% \noindent\includegraphics[width=17cm,keepaspectratio]{different_constraints_fullsample_ove02.pdf}
 \plotone{different_constraints_ben.pdf}
-
 \caption{\label{masses}
@@
 \begin{figure}
-\plotone{combined_radii.eps}
+\plotone{combined_radii.pdf}
 
@@
 
-In Fig.~\ref{alphael}, we display the [Mg/Fe] abundance ratio as a function of [Fe/H] for our stars (black circles), compared\footnote{There may to be systematics between our [X/Fe] abundance scale and those of our comparison samples.} to representative thick and thin disk stars from \cite[open red squares]{Bensby2014} and \cite[open blue triangles]{Adibekyan2012}.
+In Fig.~\ref{alphael}, we display the [Mg/Fe] abundance ratio as a function of [Fe/H] for our stars (black circles), compared\footnote{There may be systematics between our [X/Fe] abundance scale and those of our comparison samples.} to representative thick and thin disk stars from \cite[open red squares]{Bensby2014} and \cite[open blue triangles]{Adibekyan2012}.
 
@@
 \begin{figure*}
-\plotone{HD_183124.png}
-
+\plotone{HD_183124.pdf}
 \caption{\label{HD_183124}
@@
 Finally, HD\,186255 is probably a binary with a period of $\sim$415\,d (Figure~\ref{pm}), but there is a slight aperiodicity in the time delays, likely caused by beating between pulsation modes that are not well-separated in the frequency.
-That, coupled with the fact that this star falls on the failed Module 3 and is therefore missing data every 4th quarter (i.e.
+That, coupled with the fact that this star falls on the failed Module~3 and is therefore missing data every 4th quarter (i.e.
 $\sim$93 of every 372.5\,d), makes the binary classification uncertain.
@@
 \begin{figure*}
-\plotone{HD186255_time-delay_plot.png}
-
+\plotone{HD186255_time_delay.pdf}
 \caption{\label{pm}

### 2019-05-20 paper/ms.tex
zenodo citation

@@
 All smear light curves in this paper, as well as the \LaTeX{} source code used to produce this document, can be found
-at \href{https://github.com/benjaminpope/smearcampaign}{\nolinkurl{github.com/benjaminpope/smearcampaign}}.
+at \href{https://github.com/benjaminpope/smearcampaign}{\nolinkurl{github.com/benjaminpope/smearcampaign}}\footnote{\dataset[10.5281/zenodo.3066218]{\doi{10.5281/zenodo.3066218}} \citep{smearcampaign_zenodo}}.
 

### 2019-05-23 paper/ms.tex
reviewer thank
correction
caldwell comments

@@
 
+\author[0000-0003-1963-9616]{Douglas A. Caldwell}
+\affiliation{SETI Institute, 189 Bernardo Avenue, Mountain View, CA 94043, USA}
+
 \author[0000-0003-1125-2564	]{Ashley Chontos}
@@
 \citet{orig_smear} noted a way to obtain photometry of every target on-silicon in \kepler using a data channel normally used for calibration, even if active pixels were not allocated and downloaded.
-\kepler employs an inter-line transfer CCD, which successively shuffles each row of pixels to the edges of the chip to be read out.
 Because the \kepler camera lacks a shutter, the detector is exposed to light during the readout process, with the result that fluxes in each pixel are contaminated by light collected from stars in the same column.
 This is a particularly serious issue for faint stars in the same detector column as brighter stars, and it is important to calibrate this at each readout stage.
-Six rows of blank `masked' pixels were allocated in each column to measure the smear bias; furthermore, six `virtual' rows were recorded at the end of the readout, with the result that twelve rows of pixels sample the smear bias in each column.
+Twelve rows of blank `masked' pixels were allocated in each column to measure the smear bias; furthermore, twelve `virtual' rows were recorded at the end of the readout, with the result that twelve rows of pixels sample the smear bias in each column.
 \citet{orig_smear} realized that these encode the light curves of bright targets in a 1D projection of the star field.
-The masked and virtual smear registers each receive $\sim 1/1034$ of the incident flux in each column.
-If this is dominated by the light from a single star, the flux combining both smear registers is equivalent to the normal flux of a star $\sim 6.8$~magnitudes fainter.
+Compared to the flux in the science image for a given target, the masked and virtual smear rows each receive an incident flux in proportion to the relative exposure times of the smear versus imaging pixels:  $\sim (0.52\,\text{s}/1070\,\text{rows})/6.2\,\text{s}$.
+If the smear flux is dominated by the light from a single star, the combined flux from the 24 smear rows is equivalent to the normal flux of a star $\sim 6.8$ magnitudes fainter.
 
@@
 
+We would like to thank the anonymous reviewer, whose comments significantly improved this paper.
+
 This work was performed in part under contract with the Jet Propulsion Laboratory (JPL) funded by NASA through the Sagan Fellowship Program executed by the NASA Exoplanet Science Institute.
